### 2016-04-27 Background/history.tex
Initial commit from thesis docs

\section{History of E-Mail Injection}

E-Mail Header Injection seems to have been first documented over a decade ago, in a late 2004 article on phpsecure.info \cite{Tobozo} accredited to user \lstinline|tobozo@phpsecure.info| describing how this vulnerability existed in the reference implementation of the \dq{\texttt{mail}} function in PHP, and how it can be exploited. More recently, a blog post by Damon Kohler \cite{DK} and an accompanying wiki article \cite{Injection} describe the attack vector and outline a few defense measures for the same.

As this vulnerability was initially found in the \emph{mail()} function of PHP, E-Mail Header Injection can be traced to as early as the beginning of the 2000's, present in the \emph{mail()} implementation of PHP 4.0.

The vulnerability was also described briefly (less than a page) by Stuttard and Pinto in their widely acclaimed book, ``\emph{The Web Application Hacker's Handbook: Discovering and Exploiting Security Flaws}'' \cite{stuttard2011web}. 
A concise timeline of the vulnerability is presented in Table~\ref{tab:history}.

An example of the vulnerable code written in PHP is shown in Listing~\ref{code:phpemi}. This code takes in user input from the PHP superglobal \dq{\texttt{\$\_REQUEST[\textquotesingle email\textquotesingle]}}, and stores it in the variable \dq{\texttt{\$from}}, which is later passed to the \dq{\texttt{mail}} function to construct and send the e-mail.
\input{Background/php.tex}

When this code is given the malicious input \dq{\texttt{\lstinline{sai@sai.com\\nBCC:spc@spc.com}}} as the value of the \dq{\texttt{\$\_REQUEST[\textquotesingle email\textquotesingle]}}, it generates the SMTP Headers shown in Listing~\ref{code:smtpheaders}. It can be seen that the `CC' (carbon copy) header that we injected appears as part of the resulting SMTP message. This will make the e-mail get sent to the e-mail address specified as part of the `CC' as well.
\input{Background/smtpheaders}
\input{Background/history_table}

### 2016-04-27 Background/impact.tex
Initial commit from thesis docs

\section{Potential Impact}

The impact of the vulnerability can be pretty far-reaching.
Table~\ref{tab:usage} shows the current server-side language usage statistics on the Web \cite{W3techs}.

\begin{table}[!tb]
	\centering
	\begin{tabular}{|p{4cm}|p{4cm}|}
		\hline
		\multicolumn{1}{|c|}{\textbf{Server Side Language}} & \multicolumn{1}{c|}{\textbf{\% of Usage}}\\
		\hline
		PHP & 81.9\\
		\hline    
		ASP.NET & 15.8\\
		\hline
		Java & 3.1\\
		\hline
		Ruby & 0.6\\
		\hline
		Perl & 0.5\\
		\hline
		JavaScript & 0.2\\
		\hline
		Python & 0.2\\
		\hline

	\end{tabular}
	\caption[\titlecap{Language usage statistics}]{Language usage statistics compiled from w3techs \cite{W3techs}.}
	\label{tab:usage}
\end{table}

PHP, Java, Python, and Ruby (combined) account for over 85\%\,\footnotemark{} of the websites measured. The vulnerability can be exploited to do potentially any of the following:

\footnotetext{A website may use more than one server-side programming language}

\begin{itemize}
	\item Phishing and Spoofing Attacks\\
    Phishing \cite{wiki:Phishing} (a variation of spoofing \cite{wiki:Spoofing_attack}) refers to an attack where the recipient of an e-mail is made to believe that the e-mail is a legitimate one. The e-mail usually redirects them to a malicious website, which then steals their credentials.

    E-Mail Header Injection gives attackers the ability to inject arbitrary headers into an e-mail sent by a website and control the output of the e-mail. This adds credibility to the generated e-mail, as it is sent right from the websites and people are more ready to trust e-mail that is received from the website directly and can thus result in more successful phishing attacks.

	\item Spam Networks\\
	Spam networks can use E-Mail Header Injection vulnerabilities on the ability to send a large amount of e-mail from servers that are trusted. By adding additional \dq{\texttt{cc}} or \dq{\texttt{bcc}} headers to the generated e-mail, attackers can easily achieve this effect.

	Due to the e-mails being from trusted domains, recipient e-mail clients might not flag them as spam. If they do flag them as spam, then that can lead to the website being blacklisted as a spam generator.

	\item Information Extraction of legitimate users\\
	E-Mails can contains sensitive data that is meant to be accessed only by the user. Due to E-Mail Header Injection, an attacker can easily add a \dq{\texttt{bcc}} header, and send the e-mail to himself, thereby extracting important information.
	User privacy can thus be compromised, and loss of private information can by itself lead to other attacks.

	\item Denial of service by attacking the underlying mail server\\
    Denial of service attacks (DoS), can also be aided by E-Mail Header Injection. The ability to send hundreds of thousands of e-mails by just injecting one header field can result in overloading the mail server, and cause crashes and/or instability. 
\end{itemize}

It is evident that E-Mail Header Injection is a critical vulnerability that web applications must address.

### 2016-04-27 Background/lang_aff.tex
Initial commit from thesis docs

\section{Languages Affected}
\label{languages}
This section describes the popular languages which exhibit this type of vulnerability. This section is not intended as a complete reference of vulnerable functions and methods, but rather as a guide that specifies which parts of the language are known to have the vulnerability.

\subsubsection{PHP} 
PHP was one of the first languages found to have this vulnerability in its implementation of the \emph{mail()} function. The early finding of this vulnerability can be attributed in part to the success and popularity of the language for creating web pages. According to w3techs \cite{W3techs}, PHP is used by 81.9\% of all the websites in existence, thereby creating the possibility of this vulnerability to be widespread.

PHP's low barrier to entry and lack of developer education about the existence of this vulnerability have contributed to the vulnerability continuing to exist in the language.
After 13 further iterations of the language since the 4.0 release (the current version is 7.1), the \emph{mail()} function is yet to be fixed after 15 years. However, it is specified in the PHP documentation \cite{PHPDocs} that the \emph{mail()} function does not protect against this vulnerability.
A working code sample of the vulnerability, written in PHP~5.6 (latest well-supported version), is shown in  Listing~\ref{code:phpemi}.

\subsubsection{Python} 
A bug was filed about the vulnerability in Python's implementation of the \emph{email.header} library and its header parsing functions allowing newlines in early 2009, which was followed up with a partial patch in early 2011.

Unfortunately, the bug fix was only for the \emph{email.header} package, and thus is still prevalent in other frequently used packages such as \emph{email.parser}, where both the classic \emph{Parser()} and the newer \emph{FeedParser()} exhibit the vulnerability even in the latest versions - \emph{2.7.11} and \emph{3.5}. The bug fix was also not backported to older versions of Python. 
There is no mention of the vulnerability in the Python documentation for either library.
A working code sample of the vulnerability, written in Python 2.7.11, is shown in Listing~\ref{code:pyemi}.
\input{Background/py.tex}

\subsubsection{Java} 
Java has a bug report about E-Mail Header Injection filed against its JavaMail API. A detailed write-up by Alexandre Herzog \cite{Herzog.2014} is complete with a proof of concept program that exploits the API to inject headers.

\subsubsection{Ruby}
From our preliminary testing, Ruby's built-in Net::SMTP library has this vulnerability. This is not documented on the library's homepage.
A working code sample of the vulnerability, written in Ruby 2.0.0 (the latest stable version at the time of writing), is shown in Listing~\ref{code:rubyemi}.

\input{Background/ruby.tex}

### 2016-04-27 Background/pbm_bg.tex
Initial commit from thesis docs

\section{Problem Background}

E-Mail Header Injection belongs to a broad class of vulnerabilities known simply as injection attacks. However, unlike its more popular siblings, SQL injection \cite{sql1}, \cite{sql0}, \cite{sql2}, Cross-Site Scripting (XSS) \cite{Injection1}, \cite{KleinAmit} or even HTTP Header Injection \cite{sessionride}, relatively little research is available on E-Mail Header Injection.

As with other vulnerabilities in this class, E-Mail Header Injection is caused due to improper sanitization (or lack thereof) of user input. If the script that constructs e-mails from user input fails to check for the presence of e-mail headers in the user input, a malicious user --- using a well-crafted payload --- can control the headers set for this particular e-mail. This can be leveraged to enable malicious attacks, including, but not limited to, spoofing, phishing, etc.

### 2016-04-27 Background/php.tex
Initial commit from thesis docs

\lstset{language=PHP,caption={PHP program with e-mail header injection vulnerability.},label={code:phpemi}}
\begin{lstlisting}
$from = $_REQUEST['email'];
$subject = "Hello Sai Pc";
$message = "We need you to reset your password";
$to = "schand31@asu.edu";

// example attack string to be injected as the value for
// $_REQUEST['email'] => 'sai@sai.com\nCC:spc@spc.com'
$retValue = mail($to, $subject, $message, "From: $from");
// E-Mail gets sent to both schand31@asu.edu AND spc@spc.com
\end{lstlisting}

### 2016-04-27 Background/py.tex
Initial commit from thesis docs

\lstset{language=Python,caption={Python program with e-mail header injection vulnerability.},label={code:pyemi}}
\begin{lstlisting}
from email.parser import Parser
import cgi
form = cgi.FieldStorage()
to = form["email"] # input() exhibits the same behavior
msg = """To: """ + to + """\n
From: <user@example.com>\n
Subject: Test message\n\n
Body would go here\n"""

f = FeedParser() # Parser.parsestr() also 
# contains the same vulnerability
f.feed(msg)
headers = FeedParser.close(f)

# attack string => 'sai@sai.com\nBCC:spc@spc.com'
# for form["email"]

# both to:sai@sai.com AND bcc:spc@spc.com 
# are added to the headers
print 'To: %s' % headers['to']
print 'BCC: %s' % headers['bcc']
\end{lstlisting}

### 2016-04-27 Background/ruby.tex
Initial commit from thesis docs

\lstset{language=Ruby,caption={Ruby program with e-mail header injection vulnerability.},label={code:rubyemi}}
\begin{lstlisting}
require 'sinatra'
require 'net/smtp'

get '/hello' do
email = params[:email]

message = """
From: Sai <schand31@asu.edu>
Subject: SMTP e-mail test
To: #{email}

This is a test e-mail message.
"""
# construct a post request with email set to attack_string
# attack_string => sai@sai.com%0abcc:spc@spc.com%0aSubject:Hello
Net::SMTP.start('localhost', 1025) do |smtp|
smtp.send_message message, 'schand31@asu.edu',
'to@todomain.com'
end
# Headers get added, and Subject field changes to what we set.
end
\end{lstlisting}

### 2016-04-27 Discussion/lessons.tex
Initial commit from thesis docs

\section{Lessons Learned}
    From our results, it is evident that the vulnerability exists in the wild. Despite its relatively low occurrence rate compared to the more popular SQL Injection and XSS (Cross-Site Scripting), when we take the total number of websites on the World Wide Web --- 1,018,863,952 according to Internet Live Stats \cite{InternetLiveStats2016} as of early 2016 --- and calculate \successDelta\ percent (the occurrence rate of E-Mail Header Injection vulnerability as found by our system) of that number, we end up with 11,309,390 websites - a pretty significant number. We agree that an extrapolation of that kind might not be an accurate measure of the prevalence of the vulnerability. However, even with as few as a thousand websites affected by this vulnerability, it can still have a disastrous impact on these websites, and also on overall World Wide Web due to the traffic caused by the sheer number of generated e-mails.

    After analyzing the results, we would like to make a few more observations. We believe that one of the reasons for the small percentage of occurrence (compared to SQL Injection or XSS), can be attributed to what we like to call the `car parking analogy'.
    The car parking analogy is something like this: Imagine that we are parking a car on a road that is prone to attacks by thieves. Now, if all the cars were unlocked, the car that is most likely to get stolen is quite unsurprisingly the most expensive one or the one that is easiest to get away with.

    Now imagine the same thing on the World Wide Web: we have websites that can each have multiple vulnerabilities. Now, it makes sense for an attacker to try and attack websites with more widespread vulnerabilities such as SQL Injection or XSS, rather than attempt to exploit E-Mail Header Injection, seeing as this requires a more concentrated effort, with carefully crafted payloads and a waiting time for the e-mail to be delivered. SQL Injection attacks and XSS attacks are also better documented, with well-known attack vectors, and automated tools to help detect the presence of these vulnerabilities on websites.

    This also gives more incentive for the website developer to add protection against attacks such as SQL injection and XSS. The developer might then (possibly with the help of a sanitization library) sanitize the user input and remove \emph{all} special characters, including the newline characters (\textbackslash{}n, \textbackslash{}r), which adversely affects E-Mail Header Injection attacks.

	We come to this conclusion because of our discovery of the \dq{\texttt{To header injection}}. Clearly, this is possible due to incomplete sanitization performed by the application. We suspect that this incomplete sanitization is actually sanitization that is performed for some other vulnerability, and not specifically for E-Mail Header Injection attacks. We would also like to remark that \dq{\texttt{To header injection}} is not complete E-Mail Header Injection, but only a special subset.

    Thus, indirectly, this kind of protection against other attacks affects the attempts to perform E-Mail Header Injection. However, this does not completely negate the attempts if the checks are only on the client-side. Also, even with server-side validation, often, the only input fields that are validated are ones that are either inserted into the database (SQL Injection) and the ones that are displayed to the user as part of the web site (XSS).

	A second and a far more common reason for our fuzzing attempts to fail is the bot-blocking mechanisms built into the websites. CAPTCHAs (as explained in Section \ref{issues:captcha} and in the following section) pose a very difficult problem for our system to exploit E-Mail Header Injection, even if it is present.

	This does not mean that the vulnerability is not a large threat. In fact, this vulnerability can also have some major consequences, the least of which can be spamming and phishing attacks.
	In today's digital world, identity theft has become all the more common. E-Mail Header Injection provides attackers with the ability to easily extract information about users, not just from a server, but from the user himself, by sending him fake messages that look extremely authentic, since these messages are sent by the mail server of the website itself.

    From our research, we found two different forms of the E-Mail Header Injection Vulnerability: the first one is the traditional one, where we are able to inject any header into the forms, allowing us complete control over the contents of the e-mail. We identify this with the presence of both the \dq{\texttt{bcc}} header and the \dq{\texttt{x-check}} header. This is the most potent form of the vulnerability and is found on quite a few websites. This is also the vulnerability that is documented and discussed on many websites.

    The second attack is an interesting one, as this has not yet been documented, and provides the ability to inject multiple e-mail addresses into only the \dq{\texttt{To}} field. We christened this as \dq{\texttt{To header injection}}. In this form of the vulnerability, we are able to simply add addresses to the \dq{\texttt{To}} field of the form with newlines separating the e-mail addresses. Whether this particular form of the vulnerability is found due to the websites in question, or whether this is an implementation issue with a particular language or framework, is unclear. However, from our preliminary analysis, it is evident that these websites do not share much with respect to the languages and frameworks used. 
    Even in this form of the attack, we are still able to extract information that should be private to a given user, and in some of these cases, able to inject enough data to spoof the first few lines of the e-mail message. From Table~\ref{tab:analysis}, information leakage using \dq{\texttt{To header injection}} was possible on 142 forms, while spoofing using \dq{\texttt{To header injection}} was possible on 11 forms.

    While not being as impactful as the primary vulnerability, this second form of the vulnerability does still provide the ability to send e-mails to multiple recipients, and can easily result in information leakage or spam generation on a large scale.

### 2016-04-27 Discussion/limits.tex
Initial commit from thesis docs

\section[Limitations]{Limitations of the Project}
\label{limitations}
	This section complements Section \ref{sys:issues}, and discusses the limitations of our project. The following list, although not exhaustive, goes into the limitations of our project in detail: 
	\begin{itemize}
		\item CAPTCHAs - As noted in section \ref*{issues:captcha}, CAPTCHAs pose a significant problem to our automated system. As CAPTCHAs are designed to be robust, there is no easy way to break them. There has been considerable research in this area \cite{captchas2}, \cite{captchas} to name a few and although not impossible to break, it remains out of the scope of this project, and thus, we chose to ignore websites which require CAPTCHA verification.
		\item JavaScript Apps - Due to the growing emphasis on responsive web applications, more and more single-page web applications are being built purely with JavaScript. Even conventional applications are now making use of JavaScript to dynamically insert content and update the pages. This means that these dynamically injected components are not a part of the initial source code that is sent to the client by the web server.

		Thus, our system never receives dynamically injected forms from the web server and hence is unable to detect whether these vulnerabilities are present in such forms. The only workaround would be, to use a JavaScript engine to query for the \lstinline|document.getElementsByTagName('html')[0].innerHTML| (from inside web browser automation tools like Selenium, etc.), and then use that as the source code for our URL.

		Since this would add unnecessary bulk and complexity to our application, we chose not to do it, and thus, we consider this to be a limitation.

		\item Blogs powered by WordPress/Drupal\\
        In addition to what was discussed in Section \ref{issues:cms}, we found that certain WordPress `plugins' also prevent the E-Mail Header Injection attack by sanitizing user input on Contact Forms. Some of these plugins are discussed in the following section. Although not all websites built with WordPress are secure from the attack, between the presence of the plugins on some websites, and getting tagged as `spambots' by others, we were able to do vulnerability analysis on very few sites powered by WordPress.

		\item Blacklisting by websites and ISPs\\
        During the actual crawl, our system was blacklisted by a few websites (mostly WordPress ones), and Internet Service Providers (ISPs). We then created a blacklist of our own to ensure that we did not inject these websites. The result was that we could not gather any data about these websites.

		\item E-Mail libraries\\
        E-Mail libraries like the PHP Extension and Application Repository's (PEAR) mail library provide sanitization checks for user input. While this is technically not a limitation of our project, it still makes it such that we are not able to inject these sites successfully.
        A few other libraries for each language are discussed in the following section.

        \item Websites that are not in English\\
        Because we are only searching for the words `e-mail', `mail' or `email' within the form, if the website does not use English names for its forms, our system will not be able to find the presence of an e-mail field. An example is shown in Listing~\ref{code:htmlfrench}. Here, the French word for `e-mail' --- courrier électronique --- is used, and our system is unable to find the presence of the e-mail form.
	\end{itemize}

\lstset{language=HTML,caption={HTML page with e-mail form, written in a different language - French.},label={code:htmlfrench}, literate=%
	{é}{{\'e}}1}
\begin{lstlisting}
<!doctype html>
<html lang="fr">
<head>
<meta charset="utf-8">
<meta name="author" content="Sai Pc">
<title>Mock Email</title></head>
<body>
<form action="{Replace with path to back-end}" method="post">
<input type="text" placeholder="courrier électronique" 
	name="courrier_électronique"><br>
<textarea name="msg" rows="20" cols="120"></textarea>
<input type="submit" value="courrier électronique!">
</form></body>
</html>
\end{lstlisting}

### 2016-04-27 Discussion/mitigation.tex
Initial commit from thesis docs

\section[Mitigation Strategy]{How to prevent this attack}
\label{disc:mitigation}
This section describes the most common measures that can be taken to prevent the occurrence of this vulnerability, or at least reduce the impact.
\begin{itemize}
	\item Use Mail Libraries\\
	This is the preferred way of combating this vulnerability. Using a library that is well tested can remove the burden of input sanitization from the developer. Also, since most of these libraries are open-source, bugs are identified quicker and fixes are readily available.
	A list of known secure libraries for each popular language and framework is shown in Table~\ref{tab:maillib}.

	Using libraries such as PEAR Mail, PHPMailer, Apache Commons E-Mail, Contact Form 7, and Swiftmailer can significantly reduce the occurrence of E-Mail Header Injection vulnerability.
	\begin{table}[!htbp]
		\centering
		\begin{tabular}{|l|l|}
			\hline
			\multicolumn{1}{|c|}{\textbf{Language}} &
			\multicolumn{1}{c|}{\textbf{Mail Libraries}} \\
			\hline
			PHP & {{PEAR Mail\tablefootnote{PEAR Mail Website: https://pear.php.net/package/Mail}, PHPMailer\tablefootnote{PHPMailer Website: https://github.com/PHPMailer/PHPMailer}, Swiftmailer\tablefootnote{Swiftmailer Website: http://swiftmailer.org/}}}\\
			\hline
			Python & SMTPLib with email.header.Header\tablefootnote{instead of using email.parser.Parser to parse the header}\\
			\hline
			Java & Apache Commons E-Mail\tablefootnote{Apache Commons E-Mail: https://commons.apache.org/proper/commons-email/}\\
			\hline
			Ruby & Ruby Mail \textgreater{}= 2.6\tablefootnote{Ruby Mail Website: https://rubygems.org/gems/mail}\\
			\hline
			WordPress & Contact Form 7\tablefootnote{Contact Form 7 Download: https://wordpress.org/plugins/contact-form-7/}\\
			\hline
		\end{tabular}
		\caption[\titlecap{Mail libraries that prevent e-mail header injection}]{Mail libraries that prevent e-mail header injection.}
		\label{tab:maillib}
	\end{table}
	% changes to be made amrked in sublime
	\item Use a Content Management System (CMS) \\
	Content management systems like WordPress and Drupal include certain libraries and plugins to prevent E-Mail Header Injection. Thus, websites built with such CMS' are usually resistant to these attacks. However, it is advised to use the right E-Mail plugins when using such CMS', as not all plugins might be secure.
	An example of a secure plug-in is included as part of Table~\ref{tab:maillib}.

	\item Input Validation\\
	If neither of the two options above is feasible, due to reasons such as the website being an in-house production, or due to lack of support infrastructure, developers can choose to perform proper input sanitization. Sanitization should be done keeping in mind RFC5322 \cite{rfc5322}, and care must be taken to ensure that all edge cases are taken into account.

	Client Side validation alone is not sufficient, and must be supplemented by server-side validation to mitigate the attack. Constant updates to validation methods are required so that new attack vectors do not harm the website in any way.
	Test driven development for such validation methods is also encouraged so that we can be reasonably sure of our defense mechanisms.
\end{itemize}

### 2016-04-27 Experiment/celery.tex
Initial commit from thesis docs

\section{Celery Queues}
\label{exp:Celery}
We used a Celery task queue running on RabbitMQ to overcome the GIL. According to Celery Project Homepage \cite{Celery}:
\begin{quotation}
``Celery is an asynchronous task queue/job queue based on distributed message passing.''
\end{quotation}

Simply put, Celery allows us to process multiple tasks in parallel by making use of what is known as a task queue. Celery instantiates multiple workers that listen to these queues and processes each task individually. This simulates pseudo-parallel processing to a certain degree, by allowing us to run multiple instances of the same program. It does this by using a message broker called RabbitMQ.
According to RabbitMQ's Wikipedia page \cite{wiki:RabbitMQ},
\begin{quotation}
``RabbitMQ is an open source message broker software that implements the Advanced Message Queuing Protocol (AMQP)''
\end{quotation}
RabbitMQ facilitates the storage and transport of messages on queuing systems. It is also cross-platform and open source, providing us with clients and servers for many different languages, thereby being the ideal fit for Celery.
Thus, by using Celery and RabbitMQ together, we were able to achieve a certain degree of parallelism that would not have been possible with traditional Python.

%The next chapter presents our results and showcases our analysis of the said results.

### 2016-04-27 Experiment/languages.tex
Initial commit from thesis docs

\section{Languages Used}

We used Python 2 to build the system. The following factors influenced our choice of language: text processing capabilities, PCRE (Perl Compatible Regular Expressions) compatibility, and the numerous libraries for HTML Parsing, HTTP request generation, mail processing etc.
We made use of the following major libraries (shown in Table~\ref{tab:libs}) for our system.

\begin{table}[!htbp]
	\centering
	\begin{tabular}{|c|c|}
		\hline
		\multicolumn{1}{|c|}{\textbf{Library}} &
		\multicolumn{1}{c|}{\textbf{Functionality}} \\
		\hline
		Requests & HTTP Request Generation\\
		\hline
		Beautiful Soup & HTML Parsing\\
		\hline
		Mailbox & Mail Processing\\
		\hline
		Celery & Task Queues\\
		\hline
	\end{tabular}
	\caption[\titlecap{Python libraries}]{Libraries that we used and their functions.}
	\label{tab:libs}
\end{table}

Despite the many benefits that Python 2 provides, we had certain issues with the language --- discussed in Section \ref{issues:parallel} --- such as Python's GIL (Global Interpreter Lock) which does not allow the running of multiple native threads concurrently.
The following section (Section \ref{exp:Celery}) describes in detail the task queue system (Celery) that we used to overcome this limitation of Python.

### 2016-04-27 Experiment/platform.tex
Initial commit from thesis docs

\section[Platform]{Platforms and Software}

We enumerate the platforms and the software used for our project in Table~\ref{tab:platsw}.
\begin{table}[!htbp]
	\centering
	\begin{tabular}{|c|c|}
		\hline
		Operating system & Ubuntu 14.04\\
		\hline
		Server & Apache - 2.4.17\\
		\hline
		Database & MariaDB - 10.1.9\\
		\hline
		Mail Server & Postfix - 2.11.0\\
		\hline
		Other software used & Mailcatcher, PostMan, HTTPRequester, RabbitMQ\\
		\hline
	\end{tabular}
	\caption[\titlecap{Platforms and software}]{Platforms and software used for our project.}
	\label{tab:platsw}
\end{table}

### 2016-04-27 Results/analysis.tex
Initial commit from thesis docs

\section[Analysis of Data]{Our Analysis of the received e-mail Data}
During our analysis of the received e-mails, we found that the e-mails that we received belonged to one of three broad categories:
\begin{enumerate}
	\item E-Mails with the \dq{\texttt{bcc}} header successfully injected\\
	This form of injection was our initial objective and we found 265 such e-mails in our received e-mails. This indicates that the websites that sent out these e-mails are vulnerable to e-mail header injection, where we could inject and manipulate any header.

	\item E-Mails with the \dq{\texttt{to}} header successfully injected\\
	We discovered an unintended vulnerability which we would like to christen `TO~header injection'. These injections reflect the ability to inject any number of e-mail addresses into the \dq{\texttt{to}} field while being unable to inject any other header into the e-mails. We attribute this behavior to inconsistent sanitization by the application. 
	The vulnerability is further aided by the leniency shown by mail servers, wherein they parsed malformed e-mail addresses and delivered it to the right mail server, and on the receiving end, the mail was delivered to the right mailbox.

	While not allowing us complete control over the e-mails sent, `TO header injection' makes it possible to append any number of e-mail addresses, thereby enabling us to leak information, and/or perform DoS (Denial of Service) attacks.

	\item E-Mails with the \dq{\texttt{x-check}} header successfully injected\\
    The third category of e-mails received were e-mails with the \dq{\texttt{x-check}} header injected. As discussed in Section~\ref{analyze:detect_x_check}, 
    these let us differentiate between unsuccessful attempts and successful attempts by injecting the additional header, allowing us to check whether headers other than the \dq{\texttt{bcc}} header can be injected into the generated e-mail. 
\end{enumerate}
We list each category and the number of e-mails received by the category in Table~\ref{tab:analysis}.

\input{Results/data_analysis}
We explain the combination of these header injections (4-7) as follows:
\begin{itemize}
	\item E-Mail Header Injections with \dq{\texttt{bcc}} and \dq{\texttt{x-check}} headers\\
	These represent the perfect attack scenario where we are able to inject multiple headers into the e-mails. We can see that over 75\% of the received \dq{\texttt{bcc}} header injected e-mails are also susceptible to other header injections.

	\item Both \dq{\texttt{To}} header injections and \dq{\texttt{x-check}} headers \\
	This combination shows us that in addition to being able to inject into the \dq{\texttt{To}} fields, we are able to inject additional headers into the e-mail. It is not clear what causes this behavior; however, these can be exploited to achieve the same result as a regular E-Mail Header Injection.

	\item \dq{\texttt{x-check}} headers found in `nuser' e-mails\\
	In addition to analyzing the `maluser' account, we also analyze emails received by the `nuser' account. We explain the presence of these headers in the following paragraph.

	\item Unique \dq{\texttt{x-check}} headers found in `nuser' e-mails\\
	These represent the e-mails with \lstinline|form_ids| that were \emph{not} already found in the `maluser' account. We attribute these e-mails to (probably) having a backend that was built with Python or another language having a similar behavior with respect to constructing headers.

	\item Total successful injections\\
	This represents the total number of successful injections our system made. This includes the E-Mail Header Injections with \dq{\texttt{bcc}} header\,(1), \dq{\texttt{To}} header injections alone\,(3), and Unique \dq{\texttt{x-check}} headers found in `nuser' e-mails\,(7). This is the total number of vulnerabilities that were found by our system.

\end{itemize}

### 2016-04-27 Results/data_analysis.tex
Initial commit from thesis docs

\begin{table}[!htbp]
	\centering
	\begin{tabular}{|c|l|c|}
		\hline
		\multicolumn{1}{|c|}{\textbf{S.No}} &
		\multicolumn{1}{c|}{\textbf{Type of Injection}} &
		\multicolumn{1}{p{3cm}|}{\centering \textbf{No. of e-mails received}}\\
		\hline
		1 & E-Mail Header Injections with `bcc' header & 265\\
		\hline
		2 & E-Mail Header Injections with `x-check' header & 214\\
		\hline
		3 & `To header' injections alone & 142\\
		\hline
		4 & E-Mail Header Injections with `bcc' and `x-check' headers & 188\\
		\hline
		5 & Both `To header' injections and x-check headers &
		11\\
		\hline
		6 & `x-check' headers found in `nuser' e-mails & 56\\
		\hline
		7 & Unique `x-check' headers found in `nuser' e-mails & 26\\
		\hline
		8 & Total successful injections (1 + 3 + 7) & 433\\

		\hline
	\end{tabular}
	\caption[\titlecap{Analysis of the data}]{Classification of the e-mails that we received into broad categories of the vulnerability.}
	\label{tab:analysis}
\end{table}

### 2016-04-27 Results/fuzz_result.tex
Initial commit from thesis docs

\section{Fuzzed data}
We performed our fuzzing attempts on the gathered data with both the regular payload and malicious payload. Table~\ref{tab:fuzzed_data} shows the quantity of e-mails that we received for each payload. We explain in detail what each piece of data shown in the table represents, in the following sections.
\input{Results/fuzzed_data}
\paragraph{E-Mail received from forms}
The e-mails that we received can be broadly categorized into two categories:
\begin{enumerate}
	\item E-Mails due to regular payload\\
	This represents the total number of websites that sent e-mails to us. This indicates that we were able to successfully submit the forms on these sites.

	\item E-Mails due to malicious payload\\
    Once we receive an e-mail from a website due to the regular payload, we go back and fuzz those forms with more malicious payloads. This field, in essence, represents the total number of unique URLs that contain E-Mail Header Injection vulnerability.
\end{enumerate}

### 2016-04-27 Results/pipeline.tex
Initial commit from thesis docs

\section[The Pipeline]{Understanding the pipeline}
This section serves to represent our pipeline quantitatively and graphically. Table~\ref{tab:pipeline} showcases the data gathered by our pipeline, with the differential changes at each stage of the pipeline.

At each stage of the pipeline, the amount of data trickles down, for instance, out of the \urls\ URLs we crawled, only \forms\ forms (\formsDelta) were found. Out of these, only \emailforms\ forms (\emailformsDelta) contained e-mail fields.

In our fuzzing attempts, the same behavior is repeated. We fuzzed \fuzzed\ forms with the regular payload, which resulted in a total of \recd\ e-mails (\recdDelta). After analysis of the received e-mails, we further fuzzed \fuzzed\ forms, which resulted in \success\ e-mails (\successDelta) which contain the vulnerability.
\input{Results/pipeline_table}

\begin{figure}
	\centering
	\includegraphics[width=16cm, height=9cm]{Results/emailheaderpipeline}
	\caption[\titlecap{E-Mail header injection Pipeline}]{Pipeline - shows the quantity of data gathered at each stage of the pipeline.}
	\label{fig:pipeline}
\end{figure}

Thus, our pipeline can be visualized as a funnel (shown in Figure~\ref{fig:pipeline}), where the quantity decreases until it reaches the end product.

From our research, it is clear that E-Mail Header Injection is quite widespread as a vulnerability, appearing on \successDelta\ of forms that we were able to perform automated attacks on. This value acts as a lower bound for E-Mail Header Injection vulnerability, and can quite easily be much more if the attacks were of a more concentrated nature, crafted for the individual websites and less automated. We discuss this possibility, and other concepts such as limitations in the following chapter.

### 2016-04-27 Results/pre_result.tex
Initial commit from thesis docs

\section{Collected Data}
From our extensive crawl of the web, we were able to gather the data shown in Table~\ref{tab:data}. The following paragraphs describe in detail what each kind of data represents, and what they signify.

\input{data}

\paragraph{URL's crawled}
This represents the total number of unique URLs that we crawled on the World Wide Web. It is to be noted that this quantity refers to unique URL's, and not websites.

\paragraph{Total Forms found}
This represents the total number of forms that were found on the URL's crawled. We found a total of \forms\ forms from 
\uniqueforms\ unique domains.

\paragraph{Forms with E-Mail Fields}
This represents the total number of forms that were found to contain e-mail fields. We found \emailforms\ such forms from \uniqueemailforms\ unique domains.

### 2016-04-27 System/approach.tex
Initial commit from thesis docs

\section[Approach]{Our Approach to measure prevalence of E-Mail Header Injection}
\label{sys:appr}
We took a black-box approach to measure the prevalence of E-Mail Header Injection vulnerability on the World Wide Web. Black-box testing \cite{wiki:Black-box_testing} is a way to examine the functionality of an application without looking at its source code.

As we did not have the source code for each of these websites, black-box testing was the ideal approach for this project. Black-box testing allows our system to detect E-Mail Header Injection vulnerabilities in any server-side language (not simply those we identified in Section~\ref{languages}). A high level logical overview of our system is presented in Figure~\ref{fig:overall}. The components shown in Figure~\ref{fig:overall} can be more broadly categorized into different modules, as discussed in the following section.

\begin{figure}
	\centering
	\includegraphics[width=14cm, height=7cm]{System/overall_design}
	\caption[\titlecap{Overall system architecture - logical overview}]{Overall system architecture - logical overview.}
	\label{fig:overall}
\end{figure}

### 2016-04-27 System/assumptions.tex
Initial commit from thesis docs

\section{Assumptions}
We made certain assumptions while building the system. This section describes the assumptions and explores to what extent these hold true:
\begin{enumerate}
	\item \textbf{Crawler is not blocked by firewalls}\\
	This is a requisite for our system to work. If the Crawler is blocked for any reason, we do not get the data feed for our system, and without this input, it is almost impossible to set our system up.
	\item \textbf{The Crawler feed is an ideal representation of the World Wide Web} \\
	This is a reasonable expectation, albeit an unrealistic one.

	It is unrealistic because Crawlers work on the concept of proximity. They detect for the presence of In-Links and Out-Links from a particular URL, and hence the returned URLs are usually related to each other (at least the ones that are returned adjacent to each other).

	However, this assumption is reasonable due to the `Law of averages' \cite{wiki:Law_of_averages}, the `Law of big numbers' \cite{wiki:Law_of_large_numbers}, and the concept of `Regression to the mean' \cite{wiki:Regression_toward_the_mean}. Simply stated, a crawl of this large magnitude should give us a very distributed sample of the overall Web, eventually converging to the average of all websites in existence.

	\item \textbf{Injection of \dq{\texttt{bcc}} indicates the existence of E-Mail Header Injection Vulnerability} \\
	We assume that the ability to inject a \dq{\texttt{bcc}} header field is proof that the E-Mail Header Injection vulnerability exists in the application. We do not inject any additional payloads that can modify the subject, message body, etc.\ as this analysis is designed to be as benign as possible.
	We believe that this is a reasonable assumption, as altering e-mail headers is a goal of exploiting E-Mail Header Injection vulnerability.
\end{enumerate}

That concludes our discussion about the design of the system. To recap, we discussed our approach, the system architecture and how the components fit into our architecture. We also discussed the issues faced, and the assumptions that we made while building the system. %The next chapter describes, in brief, the experimental setup we used for our system.

### 2016-04-27 System/components.tex
Initial commit from thesis docs

\section{System Components}
\label{Comp}

The Data Gathering module and Payload Injection module are made up of a number of smaller components. This section describes in detail the functionality of each of the components.

\subsection{Crawler}
\label{Comp:Crawler}
We used an open-source Apache Nutch based Crawler. The Crawler provides us with a continuous feed of URLs and the HTML contained in those pages. This feed is sent to our Form Parser over a Celery Queue.

\subsection{Form Parser}
\label{Comp:FP}
The actual pipeline begins at the Form Parser. This module is responsible for parsing the HTML and retrieving data about the forms on the page, including the following:
\begin{itemize}
	\item Form attributes, such as method and action. These dictate where we send the HTTP request and what kind of request it is (GET or POST).
	\item Data about the input fields, such as their attributes, names, and default values. The default values are essential for fields like \colorbox{lightgray}{\lstinline{<input type="hidden">}} as these fields are usually used to check for the submission of forms by bots.
	\item Presence of the \colorbox{lightgray}{\lstinline{<base>}} element in the HTML, as this affects the final URL to which the form is to be submitted.
	\item Headers associated with the page, such as \emph{referrer}. Once again, these were required to avoid the website from ignoring our system as a bot.
\end{itemize} 
The Form Parser stores all this data in our database, so as to allow us to reconstruct the forms later for fuzzing, as required.

\subsection{E-Mail Field Checker}
\label{Comp:EMFC}
The E-Mail Field Checker script is the final stage in the Data Gathering pipeline. It receives the output of the previous stage---form data from the queue---and checks for the presence of e-mail fields in those forms. If any e-mail fields are found, it stores references to these forms in a separate table. This separates the forms that are potentially vulnerable from the forms that are not.

The E-Mail Field Checker searches for the words `e-mail', `mail' or `email' within the form, instead of an explicit e-mail field (e.g.,\ \colorbox{lightgray}{\lstinline{<input type="email">}}). This is by design, taking into account a very common design pattern used by web developers, where they may have a text field with an \dq{\texttt{id}} or \dq{\texttt{name}} set to `email', instead of an actual e-mail field, for purposes of backward compatibility with older browsers.

Compared to searching for explicit e-mail fields, by searching for the presence of the words `e-mail', `mail' or `email' in the form, we are assured very few false negatives. This is because our system is bound to find e-mail fields with their \dq{\texttt{type}}, \dq{\texttt{name}}, or \dq{\texttt{id}} set to one of these words. The system is also substantially faster as we do not have to parse the individual form fields at this point in the pipeline. However, despite the advantages, this might also lead to a false positive rate. We discuss this possibility in detail in Section \ref*{issues:fpr} - Design Issues.

The output of this stage is stored in the database for persistence and acts as the input to the `Payload Injection' pipeline.

\subsection{E-Mail Form Retriever}
\label{Comp:EMFR}
The E-Mail Form Retriever is the first stage in the Payload Injection Pipeline. It has the following important functions:
\begin{itemize}
	\item Retrieve the newly inserted forms in the `\lstinline{email_forms}' table, checking to ensure no duplication occurs before the fuzzing stage.
	\item Reconstruct each form, using the data stored in the `\lstinline{form}' table, complete with input fields and their values.
	\item Construct the URL for the `action' attribute of the form so that we can send the HTTP request to the correct URL. 
\end{itemize}

\subsection{Fuzzer}
\label{Comp:Fuzzer}
The Fuzzer is the heart of the system and is the only component that interacts directly with the external websites. The Fuzzer is split into smaller modules, each of which is responsible for a particular type of fuzzing.  We inject payloads in two different stages, to improve the efficiency, and reduce the total number of HTTP requests we generate. This is because making HTTP requests is an expensive process \cite{McGrath2009}, and can be a cause of bottlenecks in a Crawler-Fuzzer system \cite{ShkapenyukTorstenSuel2001}.
The two different types of payloads we use for fuzzing are:
\paragraph{Non-Malicious Payload}
\label{Comp:Fuzzer:nmp}
The regular or non-malicious payload is a straight forward E-Mail address of the format -- `reguser(xxxx)@example.com', where `xxxx' is replaced by our internal `\lstinline{form_id}', to create a one-to-one mapping of the payloads to the forms, and `example.com' is replaced by the required domain. In our case, this domain was `wackopicko.com'.
This non-malicious payload allows us to check whether we can inject data into a form and whether we can overcome the `anti-bot' measures on the given website, without attempting to fuzz the website.

\paragraph{Malicious Payload}
\label{Comp:Fuzzer:mp}
In the malicious payload scenario, we inject the fields with the \dq{\texttt{bcc}} (blind carbon copy) element. If the vulnerability is present, this will cause the server to send a copy of the e-mail to the e-mail address we added as part of the `bcc' field.

We consider a special case: the addition of a \dq{\texttt{x-check:in}} header field to the payloads. This is due to Python's exhibited behavior when attaching
headers. Instead of overwriting a header if it is already present, it ignores duplicate headers. So, in case the \dq{\texttt{bcc}} field is already present as part of the headers, our injected \dq{\texttt{bcc}} header would be ignored. To overcome this, we need to inject a new header that is not likely to be generated by the web application. Hence, we inject our own \dq{\texttt{x-check:in}} header to ensure we can get results if the injection was successful.

The malicious payloads consist of 4 different payloads. Each of these payloads is crafted for a particular use case. The four payloads are:
\lstset{language=html}
\begin{enumerate}
	\item
	%inside the lstinline, we need to use \\ for \textbackslash
	\colorbox{lightgray}{\lstinline{nuser(xxxx)@wackopicko.com\\nbcc:maluser(xxxx)@wackopicko.com}} - This is the most minimal payload, it injects a `newline' character followed by the `bcc' field.
	\item \colorbox{lightgray}{\lstinline{nuser(xxxx)@wackopicko.com\\r\\nbcc:maluser(xxxx)@wackopicko.com}} - This payload is added for purposes of cross-platform fuzzing: `\textbackslash{}r\textbackslash{}n' is the `Carriage Return - New Line (CRLF)' used on Windows systems. 
	\item \colorbox{lightgray}{\lstinline{nuser(xxxx)@wackopicko.com\\nbcc:maluser(xxxx)@wackopicko.com\\nx-check:in}} - As discussed above, the addition of the \dq{\texttt{x-check:in}} header is to inject Python based websites.
	\item \colorbox{lightgray}{\lstinline{nuser(xxxx)@wackopicko.com\\r\\nbcc:maluser(xxxx)@wackopicko.com\\r\\nx-check:in}} - Same as the previous payload, but containing the additional `\textbackslash{}r' for Windows compatibility.

\end{enumerate}
The `xxxx' in all of the payloads is replaced by our internal `\lstinline{form_id}', so as to create a one-to-one mapping of the payloads to the forms. The coverage provided by each payload is shown in Table~\ref{tab:payloadcov}.\\

\begin{table}[!htbp]
	\centering
	\begin{tabular}{|c|c|c|}
		\hline
		\multicolumn{1}{|c|}{\textbf{Payload}} & \multicolumn{1}{c}{\textbf{Languages covered}} & \multicolumn{1}{|c|}{\textbf{Platforms covered}}\\
		\hline
		1 & PHP, Java, Ruby, etc. & Unix\\
		\hline
		2 & PHP, Java, Ruby, etc. & Windows\\
		\hline
		3 & Python & Unix\\
		\hline
		4 & Python & Windows\\
		\hline
	\end{tabular}
	\caption[\titlecap{Payload coverage}]{Payload coverage, each payload covers a different platform/language.}
	\label{tab:payloadcov}
\end{table}
Along with the payload, the Fuzzer also injects data into the other fields of the form. This data must pass validation constraints on the individual input fields e.g.,\ for a name field, numbers might not be allowed. It is essential that the data we inject into the input fields adhere to the constraints. Our Fuzzer does this by making use of a `Data Dictionary' which has predefined `keys' and `values' for standard input fields such as \texttt{name}, \texttt{date}, \texttt{username}, \texttt{password}, \texttt{text}, and \texttt{submit}. The default values for these are generated on-the-fly for each form, based on generally followed guidelines for such fields. For example, password fields should consist of at least one uppercase letter, one lowercase letter, and a special character.

Once the data (including the payload) for the form is ready, the Fuzzer constructs the appropriate HTTP request (GET or POST) and sends the HTTP request to the URL that was generated by the E-Mail Form Retriever (Section~\ref{Comp:EMFR}).

\subsection{E-Mail Analyzer}
\label{Comp:EMA}
The E-Mail Analyzer checks for the presence of injected data in the received e-mails. This module works on the e-mails received and stored by our Postfix server, and depending on the user who received the e-mail, it performs different functions.
\paragraph{Analyzing regular e-mail}
`Regular e-mail' refers to the e-mails received by the \colorbox{lightgray}{\lstinline{reguser(xxxx)@wackopicko.com}} --- where `xxxx' is our internal `\lstinline{form_id}' --- that were sent due to injecting the `regular or non-malicious' payload (discussed in Section~\ref{Comp:Fuzzer:nmp}). The objective of the analysis on this e-mail is identify if the input fields that we injected with data appear on the resulting e-mail, and if so, which fields appear where.

To find this, we read through each received e-mail, and check whether \emph{any} of the fields we injected with data appear as part of either the headers or the body of the e-mail. If they do, we add them to the list of fields that can potentially result in an E-Mail Header Injection for the given e-mail. we then pass on this information back to the Fuzzer pipeline, along with the `\lstinline{form_id}', so that the Fuzzer can now inject the malicious payloads into the same form.

\paragraph{Analyzing e-mail with payloads}
The `e-mails with payloads' refer to e-mails received by either the \colorbox{lightgray}{\lstinline{nuser(xxxx)@wackopicko.com}} or \colorbox{lightgray}{\lstinline{maluser(xxxx)@wackopicko.com}} accounts. These e-mails were received due to injecting the malicious payloads that were discussed in Section. \ref{Comp:Fuzzer:mp}. Analysis of these e-mails is considerably simpler than that of the regular e-mails. This is due to the fact that this involves lesser processing of the contents of the e-mail compared to the previous section.
\subparagraph{Detecting injected bcc headers}
As discussed in the payloads section (\ref{Comp:Fuzzer:mp}), the payloads were crafted in such a way that the e-mails received by `maluser' account directly indicate the presence of the injected `bcc' field. Thus, we simply parse the E-Mails and store them in the Database.

\label{analyze:detect_x_check}
\subparagraph{Detecting injected x-check headers}
E-Mails not received by the `maluser' account but by the `nuser' account constitute a special category of e-mails.
These e-mails could have been generated due to two reasons:
\begin{enumerate}
	\item The websites performed some sanitization routines and stripped out the \dq{\texttt{bcc}} part of the payload, thereby sending e-mails only to the `nuser' account. These e-mails then act as proof that the vulnerability was not found on the given website.
	\item A more conducive scenario is when the \dq{\texttt{bcc}} header was ignored for some reason, e.g.\ Python's default behavior when it encounters duplicate headers. In this case, we check whether the e-mail contains the custom header \dq{\texttt{x-check}}. If it does, then this is a successful exploit of the vulnerability, and we store it in the database.
\end{enumerate}
\subsection{Database}
We collect and store as much data as possible at each stage of the pipeline. This is due to the two following reasons:
\begin{enumerate}
	\item The data is used to validate our findings.
	\item The data collected can be used for other research projects in this area.
\end{enumerate}
Each table in our database is listed in Table~\ref{tab:dbtf} along with the data it is designed to hold. A schema of the database is shown in Figure~\ref{fig:dbschema}.

\begin{table}[!htbp]
	\centering
	\input{System/tables}        
	\caption[\titlecap{Database - tables}]{The different tables in our database.}
	\label{tab:dbtf}
\end{table}

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=15cm, height=11cm]{System/dbschema}
	\caption[\titlecap{Database schema}]{Database schema.}
	\label{fig:dbschema}
\end{figure}

### 2016-04-27 System/issues.tex
Initial commit from thesis docs

\section[Issues]{Design Issues}
\label{sys:issues}
This section will describe the issues we faced with the design decisions we made, and how we did our best to mitigate them, and their effect on the system.

\begin{itemize}
	\item \label{issues:fpr}False Positive rate for the E-Mail Field Checker\\
	As discussed in Section \ref{Comp:EMFC}, we only search for the words `email', `mail' or `e-mail' (case insensitive) inside the forms to detect the presence of e-mail fields, instead of searching for an \colorbox{lightgray}{\lstinline{<input type = email>}}. This might result in a false positive in certain forms, like the one shown in Listing. \ref{code:false_positive}.

	\lstset{language=HTML,caption={E-Mail field checker - false positives, the system\\incorrectly classifies this as an e-mail form.},label={code:false_positive}}
	\begin{lstlisting}
	<form method="post">
	E-Mail us if you have any questions!!
	<input type="text" name="query"><br>
	<input type="submit" value="Search">
	</form>
	\end{lstlisting}

	The word `E-Mail' on Line 2 will result in our system classifying this form as a potential e-mail form, while it clearly is not. However, as we will see, this is not really a significant issue, as despite being added to the \lstinline{`email_forms'} table, this form will never be injected in the `fuzzer' due to the absence of the appropriate input field in the form. We chose to go with this design, as it allows us to detect almost every form that provides the capability to send or receive e-mail.

	\item Parallelism for the system\\
	\label{issues:parallel}
	Every component in the pipeline benefits hugely from parallel processing of the data. However, Python's GIL (Global Interpreter Lock) does not allow the running of multiple native threads concurrently. To overcome this, we used a Celery task queue (discussed in Section \ref{exp:Celery}), which allowed a level of parallelism that Python does not provide by default. Even though this makes the system faster than a single-threaded approach, it still leaves room for improvement in terms of performance. Despite the speed drop that results from lack of full parallelism, we chose to go with Python, for the raw power it provides, its text processing capabilities, PCRE (Perl Compatible Regular Expressions) compatibility, and the numerous libraries available for parsing HTML, interfacing with databases and generating HTTP requests.

	\item URL Construction\\
	The multiple ways in which a URL is specified (i.e.\ Relative and Absolute URLs) complicates the construction of the URL from the `action' attribute of the form.  As an example, the following URLs are all equivalent (as parsed by a browser, assuming we are in the path `www.website.com'):

	\begin{itemize}
		\item \colorbox{lightgray}{\lstinline{action=mail.php}}
		\item \colorbox{lightgray}{\lstinline{action=./mail.php}}
		\item \colorbox{lightgray}{\lstinline{action=http://website.com/mail.php}}
		\item \colorbox{lightgray}{\lstinline{action=www.website.com/mail.php}}
	\end{itemize}
	Add to this, if the form is a self-referencing form\,\footnotemark, and is present in mail.php, the following are equivalent to the above URLs as well:
	\footnotetext{A self-referencing form is one which submits the form data to itself. It includes logic to both display the form and process it. It is a \emph{very} common feature in PHP-based scripts.}
	\begin{itemize}
		\item \colorbox{lightgray}{\lstinline{action=""}}
		\item \colorbox{lightgray}{\lstinline{action=#}}
		\item `action' is completely omitted
	\end{itemize}
	Also, relative URLs pose another problem. If the URL of the form page ends with `/' and the `action' specifies a path starting with `/' (illustrated in Listing \ref{issues:url}), we would need to strip one of the two slashes. This increases the overall complexity of our URL generator, as we have to account for all these possibilities.

	\lstset{language=HTML,caption={URL construction, the resulting url needs to be www.website.com/mail.php and not www.website.com//mail.php},label={issues:url}}
	\begin{lstlisting}
	Current URL = www.website.com/
	<form action=/mail.php>
	\end{lstlisting}

	As using a browser engine to reconstruct these URLs  and connecting it to the fuzzer pipeline would have added unnecessary bulk to the project, we chose to go with a best-effort approach to this problem, where our system covers all these possibilities with a lightweight URL Generator, however, we cannot know for certain whether this works for other unforeseen ways of specifying a URL.

	\item Black-box Testing\\
	The approach that we have selected --- Black-box testing --- is highly beneficial as explained in Section \ref{sys:appr}. However, it also has a drawback in that we cannot verify whether the reported vulnerability exists in the source code or is a feature of the website (e.g., the website allows users to send bulk e-mail, adding as many \dq{\texttt{cc}} or \dq{\texttt{bcc}} headers). We have to manually e-mail the developers to get this feedback.

	\item Mapping responses to requests\\
	As we are generating multiple payloads for each form, and the received e-mail may not contain the name of the domain from which we received the e-mail, it is difficult to map the response e-mails to the right requests. We instead use the `\lstinline{form_id}' as part of the payload to map responses to requests accurately.

	\item Bot Blockers\\
	\label{issues:captcha}
    Because our system is fully automated, it is also susceptible to being stopped by `bot-blockers' i.e.\ mechanisms built-in to a website to prevent automated crawls or form submissions. Measures like CAPTCHA (Completely Automated Public Turing test to tell Computers and Humans Apart) and hidden form fields are often used to detect bots \cite{captchas3}, \cite{captchas2}.

    We have made sure that we do not affect hidden fields in the form, however, we do not have an anti-CAPTCHA functionality built into our system, and thus our system will not test such websites.

	\item Handling Malformed HTML\\
    The parser that we use for HTML parsing --- Beautiful Soup --- does not try to parse malformed HTML, and throws an exception on encountering malformed content. Thus, we have designed the system to exit gracefully on such occasions. A side-effect of this is that our system is unable to parse websites with bad markup\,\footnotemark.

    \footnotetext{We do not have any data about whether bad markup indicates an overall lower quality of the website, and thus cannot comment on whether such websites are more likely to have vulnerabilities, although the author strongly suspects that that might be the case.}

	\item Crawling WordPress and other CMS-based websites\\
	\label{issues:cms}
	In contrast to bot blockers that try to prevent the automated systems from attacking them, WordPress and other CMS based websites use a blacklisting approach to prevent bot attacks. Unfortunately, because we generate multiple requests to each website, this results in our IPs getting blacklisted. To overcome this, we did two things:
	\begin{enumerate}
		\item Used an IP range of 60 different IP addresses. 
		\item Used a blacklist of our own to prevent our Fuzzer from fuzzing websites that are known to blacklist automated crawlers.
	\end{enumerate}
\end{itemize}

### 2016-04-27 System/proof_of_concept.tex
Initial commit from thesis docs

\section{Proof of Concept Attacks}
The previous section (Section~\ref{Arch:Test}) discussed in detail how we verified that our system functions according to our expectations. This section describes how we validated our expectations. In order to do this, we constructed three sets of web applications in PHP, Python, and Ruby. Each of these applications was a simple web app that accepted user input to construct and send an E-Mail.

The front-end for each of the three applications is shown in Listing~\ref{code:html}. The server-side code for the three languages are shown in Listings~\ref{code:phpemi}, \ref{code:pyemi}, and \ref{code:rubyemi}.

We tested for the headers being injected in real-time by running an instance of MailCatcher, set to listen on all SMTP messages. A sample screenshot of a fuzzed request for the Ruby backend (generated in PostMan) is shown in Figure~\ref{fig:postmanruby}. The e-mail sent due to injecting this payload (as captured by MailCatcher) is shown in Figure~\ref{fig:mailcatcherruby}. It can be seen that the headers have been added to the resulting e-mail, and we have successfully managed to overwrite the \dq{\texttt{Subject}} field with our message, `hello'.

A similar injection example for PHP is shown in Figure~\ref{fig:postmanphp} and the corresponding e-mail caught by MailCatcher is shown in Figure~\ref{fig:mailcatcherphp}. The astute reader might have noticed that in the given examples we have used `\%0a' to separate the headers, while in Section~\ref{Comp:Fuzzer:mp}, we had used `\textbackslash{}n'. This is due to URL encoding \cite{rfc1738}, wherein special characters in th URL are `encoded' or `escaped' with their ASCII equivalent.
The reason why we do not have to do this with the payloads our system injects is due to the fact that the Python Requests library that we use to generate the HTTP requests automatically does this encoding for us.

\lstset{language=HTML,caption={HTML page for showcasing e-mail header injection, a simple front-end for our examples.},label={code:html}}
\begin{lstlisting}
<!doctype html>
<html lang="en">
<head>
<meta charset="utf-8">
<meta name="author" content="Sai Pc">
<title>Mock Email</title>
</head>
<body>
<form action="{Replace with path to back-end}" method="post">
<input type="text" placeholder="Email" name="email" id="e-mail"><br>
<textarea name="msg" rows="20" cols="120"></textarea>
<input type="submit" value="Email Me!">
</form>
</body>
</html>
\end{lstlisting}

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=14cm, height=8cm]{System/EMI_Postman_Ruby}
	\caption[\titlecap{Fuzzing a request for the Ruby backend}]{Fuzzing a request for the Ruby backend, the payload can be seen inside the address bar.}
	\label{fig:postmanruby}
\end{figure}

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=14cm, height=8cm]{System/EMI_Mailcatcher_Ruby}
	\caption[\titlecap{E-Mail header injection proof of concept - Ruby}]{E-Mail header injection proof of concept - Ruby, we can see that multiple headers (bcc, x-check, subject) have been inserted into the resulting e-mail.}
	\label{fig:mailcatcherruby}
\end{figure}

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=14cm, height=8cm]{System/EMI_Postman_PHP}
	\caption[\titlecap{Fuzzing a request for the PHP backend}]{Fuzzing a request for the PHP backend, the payload can be seen inside the address bar on top.}
	\label{fig:postmanphp}
\end{figure}

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=14cm, height=8cm]{System/EMI_Mailcatcher_PHP}
	\caption[\titlecap{E-Mail header injection proof of concept - PHP}]{E-Mail header injection proof of concept - PHP, we can see that multiple headers (bcc, x-check, subject) have been inserted into the resulting e-mail.}
	\label{fig:mailcatcherphp}
\end{figure}

### 2016-04-27 System/sys_arch.tex
Initial commit from thesis docs

\section{System Architecture}
\label{sys:arch}
The black-box testing system can be divided broadly into two modules; Data Gathering and Payload Injection.
\begin{enumerate}
	\item Data Gathering\\
	The Data Gathering module (shown in Figure~\ref{fig:crawler}) is primarily responsible for the following activities:
	\begin{itemize}
		\item Interface with the Crawler (Section \ref{Comp:Crawler}) and receive the URLs.
		\item Parse the HTML for the corresponding URL and store the relevant form data (Section \ref{Comp:FP}).
		\item Check for the presence of forms that allow the user to send/receive e-mail, and store references to these forms (Section \ref{Comp:EMFC}).
	\end{itemize} 
	\item Payload Injection\\
	The Payload Injection module (shown in Figure~\ref{fig:fuzzer}) is primarily responsible for the following activities:
	\begin{itemize}
		\item Retrieve the forms that allow users of a website to send/receive e-mail and reconstruct these forms (Section \ref{Comp:EMFR}).
		\item Inject these forms with benign data (non-malicious payloads) and generate an HTTP request to the corresponding URL (Section \ref{Comp:Fuzzer:nmp}).
		\item Analyze the e-mails, extracting the header fields and checking for the presence of the injected payloads (Section \ref{Comp:EMA}).
		\item Inject the forms that sent us e-mails with malicious payloads, and generate an HTTP request to the corresponding URL to check if E-Mail Header Injection vulnerability exists in that form (Section \ref{Comp:Fuzzer:mp}).
	\end{itemize} 
	The functionality of each component is discussed further in the `Components' section (Section~\ref{Comp}). The Payload Injection pipeline is not a linear, but cyclic process, as we inject different payloads and analyze the received e-mails.
\end{enumerate}

\begin{figure}
	\centering
	\includegraphics[width=14cm, height=7cm]{System/crawler_design}
	\caption[\titlecap{System architecture - crawler}]{System architecture - crawler \& form parser.}
	\label{fig:crawler}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=16cm, height=9cm]{System/fuzzer_design}
	\caption[\titlecap{System architecture - fuzzer {\&} e-mail analyzer}]{System architecture - fuzzer {\&} e-mail analyzer.}
	\label{fig:fuzzer}
\end{figure}

### 2016-04-27 System/tables.tex
Initial commit from thesis docs

\begin{tabular}{|p{1cm}|p{5cm}|p{8cm}|}
	\hline
	\multicolumn{1}{|c|}{\textbf{S.No}} & \multicolumn{1}{c}{\textbf{Table Name}} & 
	\multicolumn{1}{|c|}{\textbf{Purpose}}\\
	\hline
	1 & form & To hold data about all the forms that we receive from the Form Parser.\\
	\hline
	2 & {{email\_forms}} & Holds the output of the E-Mail Field Checker, i.e.\ references to the ID's of the forms that contain E-Mail fields. \\
	\hline
	3 & params & Holds the actual input fields of the forms, including their default values.\\
	\hline
	4 & {{fuzzed\_forms}} & Holds the data of the forms that were injected, including the payload used to inject and the URL to which the HTTP Request was delivered.\\
	\hline
	5 & {{received\_emails}} & Contains data about the E-Mails received for the regular payload, including which injected data fields were present in the E-Mail.\\
	\hline
	6 & {{successful\_attack\_emails}} & Contains data about the E-Mails received for the malicious payload. This contains the end result of the payload injection pipeline.\\
	\hline
	7 & requests & Contains data about the requests generated for each URL.\\
	\hline
	8 & {{blacklisted\_urls}} & Used for skipping certain websites that may blacklist our Crawler-Fuzzer.\\
	\hline
\end{tabular}

### 2016-04-27 System/test_plan.tex
Initial commit from thesis docs

\section{Test Suite}
\label{Arch:Test}
The test plan for our system includes a set of unit tests for each module in the pipeline. Further, we have unit tests for every %every instead of each
individual function in the modules. The functions are tested separately, using mocks and stubs, so as to ensure isolated testing.
This section outlines the test plan in the following manner. We list the modules that are tested, and then describe what each unit test tests for.
\begin{itemize}
	\item Form Parser
	\begin{itemize}
		\item \colorbox{lightgray}{\lstinline{test_url_exception}} - Tests whether the system handles incorrect or malformed URLs properly and terminates cleanly.
		\item \colorbox{lightgray}{\lstinline{test_db_connection}} - Tests whether the Database Connection is set up and queries can be executed.
		\item \colorbox{lightgray}{\lstinline{test_form_parser}} - Tests for the proper parsing of HTML, and if the system exits cleanly in case parsing is not possible.
	\end{itemize}

	\item E-Mail Field Checker
	\begin{itemize}
		\item \colorbox{lightgray}{\lstinline{test_check_for_email}} - Tests whether the system finds E-Mail fields in the form when the words `e-mail' or `email' are present in the form (case insensitive).
		\item \colorbox{lightgray}{\lstinline{test_check_for_no_email}} - Tests whether the system finds no E-Mail fields when the words `e-mail' or `email' are \emph{not} present in the form (case insensitive).
	\end{itemize}

	\item E-Mail Form Retriever
	\begin{itemize}
		\item \colorbox{lightgray}{\lstinline{test_reconstruct_form}} - Tests for the proper reconstruction of the form stored in the Database.
		\item \colorbox{lightgray}{\lstinline{test_construct_url}} - Tests whether the URL for submission was constructed properly, includes checks for relative URLs, absolute URLs, and presence of \lstinline{`base'} tags.
		\item \colorbox{lightgray}{\lstinline{test_email_form_retriever_already_fuzzed}} - Tests for duplicate fuzz requests, and whether the system rejects these requests.
		\item \colorbox{lightgray}{\lstinline{test_email_form_retriever_calls_fuzzer_for_new_fuzz}} - Tests whether the E-Mail Form Retriever calls the Fuzzer module with the proper data when it gets a new fuzz request.
	\end{itemize}

	\item Fuzzer
	\begin{itemize}
		\item \colorbox{lightgray}{\lstinline{test_send_get_request}} - Tests for the proper handling of GET requests.
		\item \colorbox{lightgray}{\lstinline{test_send_post_request}} - Tests for the proper handling of POST requests.
		\item \colorbox{lightgray}{\lstinline{test_correct_fuzzer_data}} - Tests whether the payload generated for the given form data is correct and consistent. Also tests whether the payload was part of the resulting HTTP request.
		\item \colorbox{lightgray}{\lstinline{test_incorrect_fuzzer_data}} - Tests for incorrect form data, and ensures that a payload does not end up in the wrong input field in the resulting HTTP request.
	\end{itemize}
	\item E-Mail Analyzer
	\begin{itemize}
		\item \colorbox{lightgray}{\lstinline{test_load_mail}} - Tests whether the E-Mails are loaded and parsed correctly by the E-Mail Analyzer.
		\item \colorbox{lightgray}{\lstinline{test_parse_headers}} - Tests for the proper parsing of headers present in the E-Mail.
		\item \colorbox{lightgray}{\lstinline{test_analyze_regular_mail}} - Tests whether the E-Mail Analyzer parses the regular E-Mail properly and extracts the injected input fields that are present in the E-Mail.
		\item \colorbox{lightgray}{\lstinline{test_analyze_malicious_mail}} - Tests whether the E-Mail Analyzer parses the E-Mails received due to the malicious payloads properly, is able to extract the `bcc' headers, and is able to link them to the proper fuzzing request and payload.
		\item \colorbox{lightgray}{\lstinline{test_analyze_x_check_header}} - Tests whether the `x-check' header is read by the E-Mail Analyzer.
	\end{itemize}
\end{itemize}
The unit tests were written using Python's built-in `Unittest' module, mocking was done using the built-in `MagicMock' module. The tests allow us to be reasonably certain that our system works as expected.

### 2016-04-27 abstract.tex
Initial commit from thesis docs

\begin{abstract}
	E-Mail header injection vulnerability is a class of vulnerability that can occur in web applications that use user input to construct e-mail messages. E-Mail injection is possible when the mailing script fails to check for the presence of e-mail headers in user input (either form fields or URL parameters). The vulnerability exists in the reference implementation of the built-in \dq{mail} functionality in popular languages like PHP, Java, Python, and Ruby\@. With the proper injection string, this vulnerability can be exploited to inject additional headers and/or modify existing headers in an E-Mail message, allowing an attacker to completely alter the content of the e-mail.
	\paragraph{}
	This thesis develops a scalable mechanism to automatically detect E-Mail Header Injection vulnerability and uses this mechanism to quantify the prevalence of E\-Mail Header Injection vulnerabilities on the Internet. Using a black-box testing approach, the system crawled \urls\ URLs to find URLs which contained form fields. \forms\ such forms were found by the system, of which \emailforms\ forms contained e-mail fields. The system used this data feed to discern the forms that could be fuzzed with malicious payloads. Amongst the \fuzzed\ forms tested, \recd\ forms were found to be injectable with more malicious payloads. The system tested \malfuzzed\ of these, and was able to find \success\ vulnerable URLs across \domains\ domains, which proves that the threat is widespread and deserves future research attention.

\end{abstract}

### 2016-04-27 conclusion.tex
Initial commit from thesis docs

\chapter{Conclusion}
We have showcased a novel approach involving black-box testing to identify the presence of E-Mail Header Injection in a web application. Using this approach, we have demonstrated that our system was able to crawl \urls\ web pages finding \forms\ forms, out of which \emailforms\ forms were fuzzable. We fuzzed \fuzzed\ forms and found \recd\  forms that allowed us to send/receive e-mails. Out of these, we were able to inject malicious payloads into \malfuzzed\ forms, identifying \success\ vulnerable forms (\successDelta\ success rate). This indicates that the vulnerability is widespread, and needs attention from both web application developers and library makers.

We hope that our work sheds light on the prevalence of this vulnerability and that it ensures that the implementation of the `mail' function in popular languages is fixed to differentiate between User-supplied headers, and headers that are legitimately added by the application, and that the RFC's are updated to be more stringent and make it less ambiguous for future implementations.

### 2016-04-27 data_analysis.tex
Initial commit from thesis docs

--- 2016-04-27 Results/data_analysis.tex
@@
 		\hline
-		1 & E-Mail Header Injections with `bcc' header & 265\\
+		1 & E-Mail Header Injections with `bcc' header & 180\\
 		\hline
-		2 & E-Mail Header Injections with `x-check' header & 214\\
+		2 & E-Mail Header Injections with `x-check' header & 153\\
 		\hline
-		3 & `To header' injections alone & 142\\
+		3 & `To header' injections alone & 83\\
 		\hline
-		4 & E-Mail Header Injections with `bcc' and `x-check' headers & 188\\
+		4 & E-Mail Header Injections with `bcc' and `x-check' headers & 136\\
 		\hline
-		5 & Both `To header' injections and x-check headers &
-		11\\
+		5 & Both `To header' injections and x-check headers & 9\\
 		\hline
-		6 & `x-check' headers found in `nuser' e-mails & 56\\
+		6 & `x-check' headers found in `nuser' e-mails & 40\\
 		\hline
-		7 & Unique `x-check' headers found in `nuser' e-mails & 26\\
-		\hline
-		8 & Total successful injections (1 + 3 + 7) & 433\\
-
+		7 & Unique `x-check' headers found in `nuser' e-mails & 16\\
 		\hline

### 2016-04-27 dis.tex
Initial commit from thesis docs

\documentclass[12pt,letterpaper]{report}
\usepackage[square,numbers]{natbib}
\usepackage{geometry}
\usepackage{fancyhdr}
\usepackage{afterpage}
\usepackage{graphicx}
\usepackage{amsmath,amssymb,amsbsy}
\usepackage{dcolumn,array}
\usepackage{tocloft}

% for title case
\usepackage{titlecaps}
\Addlcwords{and, the, or, of, that, our, by}

% avoid widows
\usepackage[all]{nowidow}
\clubpenalty=10000

\usepackage{asudis}
%% These are for including code
%% and for upquotes
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{listings}
\usepackage{listingsutf8}
\usepackage{comment}
\usepackage{color}
\usepackage{dirtytalk} % for quotations
\usepackage[justification=centering]{caption}
\usepackage[pageanchor=true,plainpages=false,pdfpagelabels,bookmarks,bookmarksnumbered,hidelinks]{hyperref}

% for footnotes in tables
\usepackage{tablefootnote}

% for arithmetic
\usepackage{xintexpr}

\usepackage{textcomp}     % access \textquotesingle

\definecolor{mygray}{rgb}{0.6,0.6,0.6}
\definecolor{lightgray}{rgb}{0.92,0.92,0.92}
\definecolor{darkgreen}{rgb}{0,0.7,0}
% default options for listings
\lstset{
	backgroundcolor=\color{lightgray},
	basicstyle=\footnotesize,
	breaklines=true, 
	captionpos=b,
	commentstyle=\color{darkgreen}, 
	frame=single,
	keywordstyle=\color{blue}, 
	numbers=left,
	numbersep=5pt,
	numberstyle=\tiny\color{mygray},
	rulecolor=\color{black},
	showstringspaces=false,
	upquote=true
}

\newcommand{\dq}[1]{``{#1}''}
%% THIS IS THE DATA FOR OUR THESIS, UPDATING HERE WILL UPDATE EVERYWHERE %%
\newcommand{\urls}{17,686,161}

\newcommand{\forms}{5,562,533}
\newcommand{\formsDelta}{31.45\%}

\newcommand{\emailforms}{918,988}
\newcommand{\emailformsDelta}{16.52\%}

\newcommand{\fuzzed}{756,588}
\newcommand{\fuzzedDelta}{82.33\%}

\newcommand{\recd}{44,735}
\newcommand{\recdDelta}{5.91\%}

\newcommand{\malfuzzed}{38,989}
\newcommand{\malfuzzedDelta}{87.16\%}

\newcommand{\success}{433}
\newcommand{\successDelta}{1.11\%}

\newcommand{\domains}{182}

% these refer to unique domains, not unique forms
\newcommand{\uniqueforms}{650,394}
\newcommand{\uniqueemailforms}{151,795}

\begin{document}
%-----------------------front matter
\pagenumbering{roman}
\title{E-Mail Header Injections\\
	An Analysis of the World Wide Web}

\author{Sai Prashanth Chandramouli}
\degreeName{Master of Science}
\paperType{Thesis}
\defensemonth{April}
\defenseyear{2016}
\gradmonth{May}
\gradyear{2016}
\chair{Adam Doup\'{e}}
\memberOne{Gail-Joon Ahn}
\memberTwo{Ziming Zhao}
%%\memberThree{Your third member}
%%\memberFour{Your third member}

\maketitle
\doublespace
\include{abstract}
\dedicationpage{To my mother and father, for giving me the life I dreamt of,\\
To my sister, who constantly made me do better just to keep up with her,\\
To my family in Phoenix, for always being there,\\
To God, for making me so lucky, for letting me be strong when I had nothing, and making me believe when no one else would have.}
\begin{acknowledgements}
	\input{sample_acknowledgements}
\end{acknowledgements}
\tableofcontents
% This puts the word "Page" right justified above everything else.
\addtocontents{toc}{~\hfill Page\par}
% Asking LaTeX for a new page here guarantees that the LOF is on a separate page
% after the TOC ends.
\newpage
% Making the LOT and LOF "parts" rather than chapters gets them indented at
% level -1 according to the chart: top of page 4 of the document at
% ftp://tug.ctan.org/pub/tex-archive/macros/latex/contrib/tocloft/tocloft.pdf
\addcontentsline{toc}{part}{LIST OF TABLES}
\renewcommand{\cftlabel}{Table}
\listoftables
% This gets the headers for the LOT right on the first page.  Subsequent pages
% are handled by the fancyhdr code in the asudis.sty file.
\addtocontents{lot}{Table~\hfill Page \par}
\newpage
\addcontentsline{toc}{part}{LIST OF FIGURES}
\addtocontents{toc}{CHAPTER \par}
\renewcommand{\cftlabel}{Figure}
% This gets the headers for the LOF right on the first page.  Subsequent pages
% are handled by the fancyhdr code in the asudis.sty file.
\addtocontents{lof}{Figure~\hfill Page \par}
\listoffigures
%-----------------------body
\doublespace
\pagenumbering{arabic}
\include{introduction}
\include{problem_background}
\include{sys_design}
\include{exp_setup}
\include{results}
\include{discussion}
\include{rel_work}
\include{conclusion}

%-----------------------back matter
{\singlespace
% Making the references a "part" rather than a chapter gets it indented at
% level -1 according to the chart: top of page 4 of the document at
% ftp://tug.ctan.org/pub/tex-archive/macros/latex/contrib/tocloft/tocloft.pdf
\addcontentsline{toc}{part}{REFERENCES}
\bibliographystyle{asudis}
\bibliography{biblio}}
\nocite{*}
\renewcommand{\chaptername}{APPENDIX}
\addtocontents{toc}{APPENDIX \par}
\appendix
\include{appendix1}
\end{document}

### 2016-04-27 exp_setup.tex
Initial commit from thesis docs

\chapter{Evaluation}
This chapter describes the experimental setup for our project including the servers used, the software and the platforms involved, the languages used, and the task queue system that was used for parallelism. We follow this up with our evaluation of the system, with a test suite, and proof of concept examples.

\input{Experiment/sys_config}
\input{Experiment/platform}
\input{Experiment/languages}
\input{Experiment/celery}
\input{System/test_plan}
\input{System/proof_of_concept}

### 2016-04-27 introduction.tex
Initial commit from thesis docs

\chapter{Introduction}
\paragraph{}
	The World Wide Web has single-handedly brought about a change in the way we use computers. The ubiquitous nature of the Web has made it possible for the general public to access it anywhere and on multiple devices like phones, laptops, personal digital assistants, and even on TVs and cars. This has ushered in an era of responsive web applications which depend on user input. While this rapid pace of development has improved the speed of dissemination of information, it does come at a cost. Attackers have an added incentive to break into user's e-mail accounts more than ever. E-Mail accounts are usually connected to almost all other online accounts of a user, and e-mails continue to serve as the principal mode of official communication on the web for most institutions. Thus, the impact an attacker can have by having control over the e-mail communication sent by websites to users is of an enormous magnitude.

	Since attackers typically masquerade themselves as users of the system, if user input is to be trusted, then developers need to have proper sanitization routines in place. Many different injection attacks such as SQL injection or cross-site scripting (XSS) \cite{OWASPT10} are possible due to improper sanitization of user input.

	Our research focuses on a lesser known injection attack known as E-Mail Header Injection. E-Mail Header Injection can be considered as the e-mail equivalent of HTTP Header Injection vulnerability \cite{wiki:HTTP_headerinjection}. The vulnerability exists in the reference implementation of the built-in \dq{\texttt{mail}} functionality in popular languages like PHP, Java, Python, and Ruby. With the proper injection string, this vulnerability can be exploited to inject additional headers and/or modify existing headers in an e-mail message --- with the potential to alter the contents of the e-mail message --- while still appearing to be from a legitimate source.

	E-Mail Header Injection attacks have the potential to allow an attacker to perform e-mail spoofing, resulting in phishing attacks that can lead to identity theft.
	The objective of our research is to study the prevalence of this vulnerability on the World Wide Web, and identify whether further research is required in this area.

	We performed an expansive crawl of the web, extracting forms with e-mail fields, and injecting them with different payloads to infer the existence of E-Mail Header Injection vulnerability. We then audited received e-mails to see if any of the injected data was present. This allowed us to classify whether a particular URL was vulnerable to the attack. The entire system works in a black-box manner, without looking at the web application's source code, and only analyzes the e-mails we receive based on the injected payloads.

\paragraph{Structure of document} % describes the remaining sections and gives a short desc about them
This thesis document is divided logically into the following sections:
\begin{itemize}
	\item Chapter 2 discusses the background of E-Mail Header Injection, a brief history of the vulnerability, and enumerates the languages and platforms affected by this vulnerability.

	\item Chapter 3 discusses the System design, the architecture, and the components of the system.

	\item Chapter 4 describes the experimental setup and sheds light on how we overcame the issues and assumptions discussed in Chapter 3.

	\item Chapter 5 presents our findings and our analysis of the results.

	\item Chapter 6 continues the discussion of the results; the lessons learned over the course of the project, limitations, and a suitable mitigation strategy to overcome the vulnerability.

	\item Chapter 7 explores related work in the area.

	\item Chapter 8 concludes this thesis, with ideas to expand the research in this area.
\end{itemize}

\paragraph{} % summary paragraph
We hope that our research sheds some light on this relatively less well-known vulnerability, and find out its prevalence on the World Wide Web. In summary, we make the following contributions:
\begin{itemize}

	\item{A black-box approach to detecting the presence of E-Mail Header Injection vulnerability in a web application.}

	\item{A detection and classification tool based on the above approach, which will automatically detect such E-Mail Header Injection vulnerabilities in a web application.}

	\item{A quantification of the presence of such vulnerabilities on the World Wide Web, based on a crawl of the Web, including \urls\ URLs and \forms\ forms.}

\end{itemize}

\paragraph{}

### 2016-04-27 rel_work.tex
Initial commit from thesis docs

\chapter{Related Work}

There are different approaches to finding vulnerabilities in web applications, two of them being Black-Box testing and White-Box testing.
Our work is based on the black-box testing approach to finding vulnerabilities on websites, and there has been plenty of research that has made use of this methodology \cite{Beizer:1995:BTT:202699}, \cite{Huang}, \cite{kals2006secubat}, \cite{payet13:ears-in-the-wild}, \cite{zanero2005automatic}. There has been significant discussion on both the benefits of such an approach \cite{black-box} and its shortcomings \cite{Doupe2012}, \cite{Doupe2010}.

Our work does not intend to act as a vulnerability scanner, but as a means to identify the presence of E-Mail Header Injection vulnerabilities in a given web application. In this sense, since we are injecting payloads into the web application, our work is related to other injection based attacks, such as SQL Injection \cite{sql1}, \cite{sql0}, \cite{sql2}, Cross-Site Scripting --- XSS --- \cite{Injection1}, \cite{KleinAmit}, HTTP Header Injection \cite{sessionride}, and is very closely related to Simple Mail Transfer Protocol (SMTP) Injection \cite{Terada2015}.

The attack described by Terada \cite{Terada2015} is one that attacks the underlying SMTP mail servers by injecting SMTP commands (which are closely related to E-Mail Headers and usually have a one-to-one mapping, e.g. `To' e-mail header has a corresponding `To' SMTP header) to exploit the SMTP server's pipelining mechanism. The paper also describes proof-of-concept attacks against certain mailing libraries like `Ruby Mail' and `JavaMail'. This attack, although trying to achieve a similar result, is distinctly different from ours. The paper by itself makes this observation and discusses why it is different from E-Mail Header Injection.

In comparison, our work tries to exploit application-level flaws in user input sanitization, which allow us to perform this attack. Our work does not intend to exploit the pipelining mechanism, but to exploit the implementation of the mail function in most popular programming languages, which leaves them with no way to distinguish between user supplied headers and headers that are legitimately added by the application.

As specified before, although this vulnerability has been present for over a decade, there has not been much written about it in the literature, and we only find a few articles on the Internet describing the attack.

The first documented article dates to over a decade ago; a late 2004 article on phpsecure.info \cite{Tobozo} accredited to user \lstinline|tobozo@phpsecure.info| describing how this vulnerability existed in the reference implementation of the mail function in PHP, and how it can be exploited. Following this, we found other blog posts \cite{Calin}, \cite{DK}, \cite{Injection2}, \cite{Nicol}, \cite{Pope}, each describing how to exploit the vulnerability by using newlines to camouflage headers inside user input. A wiki entry \cite{Injection} also describes the ways to prevent such an attack. However, none of these articles have performed these attacks against real-life websites.

Another blog post written by user Voxel@Night on Vexatious Tendencies \cite{Tendencies2014}, recounts an actual attack against a WordPress plugin, `Contact Form', with a proof of concept\footnotemark. It also showcases the vulnerable code in the plugin that causes this vulnerability to be present. However, this article targets just one plugin and does not aim to find the prevalence of said plugin usage. Neither does it inform the creators of the plug-in to fix the discovered vulnerability.
\footnotetext{Note that this plugin is used actively on 300,000 websites (according to \cite{BestWebSoft2016}), but is yet to be fixed.}
The vulnerability was described briefly by Stuttard and Pinto in their book, ``\emph{The Web Application Hacker's Handbook: Discovering and Exploiting Security Flaws}'' \cite{stuttard2011web}. The book, however, does not go into detail on either the attack or the ways to mitigate such an attack. Our work, on the other hand discusses the means to mitigate the attack. We also describe, in detail, the payloads that can be used and the need for varying the payloads (Section. \ref{Comp:Fuzzer:mp}).

To the best of our knowledge, no other research has been conducted to determine the prevalence of this vulnerability across the World Wide Web. We have managed to, on a large scale, crawl and inject websites with comparatively benign payloads (such as the BCC header) to identify the existence of this vulnerability without causing any ostensible harm to the website. Our injected payloads do not contain any special characters other than the newline characters and thus cannot cause any unintended consequences. Also, since we are only injecting a payload with the `bcc' header, the underlying mail servers should not be affected by the additional load. Our work serves to not only prove the existence of the vulnerability on the World Wide Web but to quantify it.

%The next and final chapter starts by outlining our contributions and closes with concluding remarks about the project.

### 2016-04-27 sample_acknowledgements.tex
Initial commit from thesis docs

A project of this size is never easy to complete without the help and support of other people. I would like to take this opportunity to thank some of them.

This thesis would not have been possible without the help and guidance of my thesis advisor, and committee chair --- the brilliant Dr.\,Adam Doup\'{e}.
This project was his brainchild, and he held my hand through the entire project. Thank you for everything you did, Adam.

I would like to thank Dr.\,Gail-Joon Ahn, for being part of the committee, for all his help, and his valuable input on the changes to be made to make the project more impactful.

I would also like to thank Dr.\,Ziming Zhao, for being a part of my committee, and for the constant motivation.

I would like to thank the members of the SEFCOM, for their support, and would like to especially thank Mike Mabey, for helping set up the infrastructure for this project, and Marthony Taguinod, for helping me document this project.

### 2016-05-05 dis.tex
fixing the small things first

@@
-\documentclass[12pt,letterpaper]{report}
+% This is "sig-alternate.tex" V2.1 April 2013
+% This file should be compiled with V2.5 of "sig-alternate.cls" May 2012
+%
+% This example file demonstrates the use of the 'sig-alternate.cls'
+% V2.5 LaTeX2e document class file. It is for those submitting
+% articles to ACM Conference Proceedings WHO DO NOT WISH TO
+% STRICTLY ADHERE TO THE SIGS (PUBS-BOARD-ENDORSED) STYLE.
+% The 'sig-alternate.cls' file will produce a similar-looking,
+% albeit, 'tighter' paper resulting in, invariably, fewer pages.
+%
+% ----------------------------------------------------------------------------------------------------------------
+% This .tex file (and associated .cls V2.5) produces:
+%       1) The Permission Statement
+%       2) The Conference (location) Info information
+%       3) The Copyright Line with ACM data
+%       4) NO page numbers
+%
+% as against the acm_proc_article-sp.cls file which
+% DOES NOT produce 1) thru' 3) above.
+%
+% Using 'sig-alternate.cls' you have control, however, from within
+% the source .tex file, over both the CopyrightYear
+% (defaulted to 200X) and the ACM Copyright Data
+% (defaulted to X-XXXXX-XX-X/XX/XX).
+% e.g.
+% \CopyrightYear{2007} will cause 2007 to appear in the copyright line.
+% \crdata{0-12345-67-8/90/12} will cause 0-12345-67-8/90/12 to appear in the copyright line.
+%
+% ---------------------------------------------------------------------------------------------------------------
+% This .tex source is an example which *does* use
+% the .bib file (from which the .bbl file % is produced).
+% REMEMBER HOWEVER: After having produced the .bbl file,
+% and prior to final submission, you *NEED* to 'insert'
+% your .bbl file into your source .tex file so as to provide
+% ONE 'self-contained' source file.
+%
+% ================= IF YOU HAVE QUESTIONS =======================
+% Questions regarding the SIGS styles, SIGS policies and
+% procedures, Conferences etc. should be sent to
+% Adrienne Griscti (griscti@acm.org)
+%
+% Technical questions _only_ to
+% Gerald Murray (murray@hq.acm.org)
+% ===============================================================
+%
+% For tracking purposes - this is V2.0 - May 2012
+
+\documentclass{sig-alternate-05-2015}
 \usepackage[square,numbers]{natbib}
@@
 \begin{document}
-%-----------------------front matter
-\pagenumbering{roman}
-\title{E-Mail Header Injections\\
-	An Analysis of the World Wide Web}
 
-\author{Sai Prashanth Chandramouli}
-\degreeName{Master of Science}
-\paperType{Thesis}
-\defensemonth{April}
-\defenseyear{2016}
-\gradmonth{May}
-\gradyear{2016}
-\chair{Adam Doup\'{e}}
-\memberOne{Gail-Joon Ahn}
-\memberTwo{Ziming Zhao}
-%%\memberThree{Your third member}
-%%\memberFour{Your third member}
+	% Copyright
+	\setcopyright{acmcopyright}
+	%\setcopyright{acmlicensed}
+	%\setcopyright{rightsretained}
+	%\setcopyright{usgov}
+	%\setcopyright{usgovmixed}
+	%\setcopyright{cagov}
+	%\setcopyright{cagovmixed}
+
+	% DOI
+	\doi{10.475/123_4}
+
+	% ISBN
+	\isbn{123-4567-24-567/08/06}
+
+	%Conference
+	\conferenceinfo{PLDI '13}{June 16--19, 2013, Seattle, WA, USA}
+
+	\acmPrice{\$15.00}
+
+	%
+	% --- Author Metadata here ---
+	\conferenceinfo{WOODSTOCK}{'97 El Paso, Texas USA}
+	%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
+	%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
+	% --- End of Author Metadata ---
+
+	\title{Alternate {\ttlit ACM} SIG Proceedings Paper in LaTeX
+		Format\titlenote{(Produces the permission block, and
+			copyright information). For use with
+			SIG-ALTERNATE.CLS. Supported by ACM.}}
+	\subtitle{[Extended Abstract]
+		\titlenote{A full version of this paper is available as
+			\textit{Author's Guide to Preparing ACM SIG Proceedings Using
+				\LaTeX$2_\epsilon$\ and BibTeX} at
+			\texttt{www.acm.org/eaddress.htm}}}
+	%
+	% You need the command \numberofauthors to handle the 'placement
+	% and alignment' of the authors beneath the title.
+	%
+	% For aesthetic reasons, we recommend 'three authors at a time'
+	% i.e. three 'name/affiliation blocks' be placed beneath the title.
+	%
+	% NOTE: You are NOT restricted in how many 'rows' of
+	% "name/affiliations" may appear. We just ask that you restrict
+	% the number of 'columns' to three.
+	%
+	% Because of the available 'opening page real-estate'
+	% we ask you to refrain from putting more than six authors
+	% (two rows with three columns) beneath the article title.
+	% More than six makes the first-page appear very cluttered indeed.
+	%
+	% Use the \alignauthor commands to handle the names
+	% and affiliations for an 'aesthetic maximum' of six authors.
+	% Add names, affiliations, addresses for
+	% the seventh etc. author(s) as the argument for the
+	% \additionalauthors command.
+	% These 'additional authors' will be output/set for you
+	% without further effort on your part as the last section in
+	% the body of your article BEFORE References or any Appendices.
+
+	\numberofauthors{8} %  in this sample file, there are a *total*
+	% of EIGHT authors. SIX appear on the 'first-page' (for formatting
+	% reasons) and the remaining two appear in the \additionalauthors section.
+	%
+	\author{
+		% You can go ahead and credit any number of authors here,
+		% e.g. one 'row of three' or two rows (consisting of one row of three
+		% and a second row of one, two or three).
+		%
+		% The command \alignauthor (no curly braces needed) should
+		% precede each author name, affiliation/snail-mail address and
+		% e-mail address. Additionally, tag each line of
+		% affiliation/address with \affaddr, and tag the
+		% e-mail address with \email.
+		%
+		% 1st. author
+		\alignauthor
+		Ben Trovato\titlenote{Dr.~Trovato insisted his name be first.}\\
+		\affaddr{Institute for Clarity in Documentation}\\
+		\affaddr{1932 Wallamaloo Lane}\\
+		\affaddr{Wallamaloo, New Zealand}\\
+		\email{trovato@corporation.com}
+		% 2nd. author
+		\alignauthor
+		G.K.M. Tobin\titlenote{The secretary disavows
+			any knowledge of this author's actions.}\\
+		\affaddr{Institute for Clarity in Documentation}\\
+		\affaddr{P.O. Box 1212}\\
+		\affaddr{Dublin, Ohio 43017-6221}\\
+		\email{webmaster@marysville-ohio.com}
+		% 3rd. author
+		\alignauthor Lars Th{\o}rv{\"a}ld\titlenote{This author is the
+			one who did all the really hard work.}\\
+		\affaddr{The Th{\o}rv{\"a}ld Group}\\
+		\affaddr{1 Th{\o}rv{\"a}ld Circle}\\
+		\affaddr{Hekla, Iceland}\\
+		\email{larst@affiliation.org}
+		\and  % use '\and' if you need 'another row' of author names
+		% 4th. author
+		\alignauthor Lawrence P. Leipuner\\
+		\affaddr{Brookhaven Laboratories}\\
+		\affaddr{Brookhaven National Lab}\\
+		\affaddr{P.O. Box 5000}\\
+		\email{lleipuner@researchlabs.org}
+		% 5th. author
+		\alignauthor Sean Fogarty\\
+		\affaddr{NASA Ames Research Center}\\
+		\affaddr{Moffett Field}\\
+		\affaddr{California 94035}\\
+		\email{fogartys@amesres.org}
+		% 6th. author
+		\alignauthor Charles Palmer\\
+		\affaddr{Palmer Research Laboratories}\\
+		\affaddr{8600 Datapoint Drive}\\
+		\affaddr{San Antonio, Texas 78229}\\
+		\email{cpalmer@prl.com}
+	}
+	% There's nothing stopping you putting the seventh, eighth, etc.
+	% author on the opening page (as the 'third row') but we ask,
+	% for aesthetic reasons that you place these 'additional authors'
+	% in the \additional authors block, viz.
+	\additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
+		email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
+		(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
+	\date{30 July 1999}
+	% Just remember to make sure that the TOTAL number of authors
+	% is the number that will appear on the first page PLUS the
+	% number that will appear in the \additionalauthors section.
 
 	\maketitle
-\doublespace
-\include{abstract}
-\dedicationpage{To my mother and father, for giving me the life I dreamt of,\\
-To my sister, who constantly made me do better just to keep up with her,\\
-To my family in Phoenix, for always being there,\\
-To God, for making me so lucky, for letting me be strong when I had nothing, and making me believe when no one else would have.}
-\begin{acknowledgements}
-	\input{sample_acknowledgements}
-\end{acknowledgements}
-\tableofcontents
-% This puts the word "Page" right justified above everything else.
-\addtocontents{toc}{~\hfill Page\par}
-% Asking LaTeX for a new page here guarantees that the LOF is on a separate page
-% after the TOC ends.
-\newpage
-% Making the LOT and LOF "parts" rather than chapters gets them indented at
-% level -1 according to the chart: top of page 4 of the document at
-% ftp://tug.ctan.org/pub/tex-archive/macros/latex/contrib/tocloft/tocloft.pdf
-\addcontentsline{toc}{part}{LIST OF TABLES}
-\renewcommand{\cftlabel}{Table}
-\listoftables
-% This gets the headers for the LOT right on the first page.  Subsequent pages
-% are handled by the fancyhdr code in the asudis.sty file.
-\addtocontents{lot}{Table~\hfill Page \par}
-\newpage
-\addcontentsline{toc}{part}{LIST OF FIGURES}
-\addtocontents{toc}{CHAPTER \par}
-\renewcommand{\cftlabel}{Figure}
-% This gets the headers for the LOF right on the first page.  Subsequent pages
-% are handled by the fancyhdr code in the asudis.sty file.
-\addtocontents{lof}{Figure~\hfill Page \par}
-\listoffigures
-%-----------------------body
-\doublespace
-\pagenumbering{arabic}
-\include{introduction}
-\include{problem_background}
-\include{sys_design}
-\include{exp_setup}
-\include{results}
-\include{discussion}
-\include{rel_work}
-\include{conclusion}
+	\begin{abstract}
+		This paper provides a sample of a \LaTeX\ document which conforms,
+		somewhat loosely, to the formatting guidelines for
+		ACM SIG Proceedings. It is an {\em alternate} style which produces
+		a {\em tighter-looking} paper and was designed in response to
+		concerns expressed, by authors, over page-budgets.
+		It complements the document \textit{Author's (Alternate) Guide to
+			Preparing ACM SIG Proceedings Using \LaTeX$2_\epsilon$\ and Bib\TeX}.
+		This source file has been written with the intention of being
+		compiled under \LaTeX$2_\epsilon$\ and BibTeX.
 
-%-----------------------back matter
-{\singlespace
-% Making the references a "part" rather than a chapter gets it indented at
-% level -1 according to the chart: top of page 4 of the document at
-% ftp://tug.ctan.org/pub/tex-archive/macros/latex/contrib/tocloft/tocloft.pdf
-\addcontentsline{toc}{part}{REFERENCES}
-\bibliographystyle{asudis}
-\bibliography{biblio}}
-\nocite{*}
-\renewcommand{\chaptername}{APPENDIX}
-\addtocontents{toc}{APPENDIX \par}
+		The developers have tried to include every imaginable sort
+		of ``bells and whistles", such as a subtitle, footnotes on
+		title, subtitle and authors, as well as in the text, and
+		every optional component (e.g. Acknowledgments, Additional
+		Authors, Appendices), not to mention examples of
+		equations, theorems, tables and figures.
+
+		To make best use of this sample document, run it through \LaTeX\
+		and BibTeX, and compare this source code with the printed
+		output produced by the dvi file. A compiled PDF version
+		is available on the web page to help you with the
+		`look and feel'.
+	\end{abstract}
+
+	%
+	% The code below should be generated by the tool at
+	% http://dl.acm.org/ccs.cfm
+	% Please copy and paste the code instead of the example below. 
+	%
+	\begin{CCSXML}
+		<ccs2012>
+		<concept>
+		<concept_id>10010520.10010553.10010562</concept_id>
+		<concept_desc>Computer systems organization~Embedded systems</concept_desc>
+		<concept_significance>500</concept_significance>
+		</concept>
+		<concept>
+		<concept_id>10010520.10010575.10010755</concept_id>
+		<concept_desc>Computer systems organization~Redundancy</concept_desc>
+		<concept_significance>300</concept_significance>
+		</concept>
+		<concept>
+		<concept_id>10010520.10010553.10010554</concept_id>
+		<concept_desc>Computer systems organization~Robotics</concept_desc>
+		<concept_significance>100</concept_significance>
+		</concept>
+		<concept>
+		<concept_id>10003033.10003083.10003095</concept_id>
+		<concept_desc>Networks~Network reliability</concept_desc>
+		<concept_significance>100</concept_significance>
+		</concept>
+		</ccs2012>  
+	\end{CCSXML}
+
+	\ccsdesc[500]{Computer systems organization~Embedded systems}
+	\ccsdesc[300]{Computer systems organization~Redundancy}
+	\ccsdesc{Computer systems organization~Robotics}
+	\ccsdesc[100]{Networks~Network reliability}
+
+	%
+	% End generated code
+	%
+
+	%
+	%  Use this command to print the description
+	%
+	\printccsdesc
+
+	% We no longer use \terms command
+	%\terms{Theory}
+
+	\keywords{ACM proceedings; \LaTeX; text tagging}
+
+	\section{Introduction}
+	The \textit{proceedings} are the records of a conference.
+	ACM seeks to give these conference by-products a uniform,
+	high-quality appearance.  To do this, ACM has some rigid
+	requirements for the format of the proceedings documents: there
+	is a specified format (balanced  double columns), a specified
+	set of fonts (Arial or Helvetica and Times Roman) in
+	certain specified sizes (for instance, 9 point for body copy),
+	a specified live area (18 $\times$ 23.5 cm [7" $\times$ 9.25"]) centered on
+	the page, specified size of margins (1.9 cm [0.75"]) top, (2.54 cm [1"]) bottom
+	and (1.9 cm [.75"]) left and right; specified column width
+	(8.45 cm [3.33"]) and gutter size (.83 cm [.33"]).
+
+	The good news is, with only a handful of manual
+	settings\footnote{Two of these, the {\texttt{\char'134 numberofauthors}}
+		and {\texttt{\char'134 alignauthor}} commands, you have
+		already used; another, {\texttt{\char'134 balancecolumns}}, will
+		be used in your very last run of \LaTeX\ to ensure
+		balanced column heights on the last page.}, the \LaTeX\ document
+	class file handles all of this for you.
+
+	The remainder of this document is concerned with showing, in
+	the context of an ``actual'' document, the \LaTeX\ commands
+	specifically available for denoting the structure of a
+	proceedings paper, rather than with giving rigorous descriptions
+	or explanations of such commands.
+
+	\section{The {\secit Body} of The Paper}
+	Typically, the body of a paper is organized
+	into a hierarchical structure, with numbered or unnumbered
+	headings for sections, subsections, sub-subsections, and even
+	smaller sections.  The command \texttt{{\char'134}section} that
+	precedes this paragraph is part of such a
+	hierarchy.\footnote{This is the second footnote.  It
+		starts a series of three footnotes that add nothing
+		informational, but just give an idea of how footnotes work
+		and look. It is a wordy one, just so you see
+		how a longish one plays out.} \LaTeX\ handles the numbering
+	and placement of these headings for you, when you use
+	the appropriate heading commands around the titles
+	of the headings.  If you want a sub-subsection or
+	smaller part to be unnumbered in your output, simply append an
+	asterisk to the command name.  Examples of both
+	numbered and unnumbered headings will appear throughout the
+	balance of this sample document.
+
+	Because the entire article is contained in
+	the \textbf{document} environment, you can indicate the
+	start of a new paragraph with a blank line in your
+	input file; that is why this sentence forms a separate paragraph.
+
+	\subsection{Type Changes and {\subsecit Special} Characters}
+	We have already seen several typeface changes in this sample.  You
+	can indicate italicized words or phrases in your text with
+	the command \texttt{{\char'134}textit}; emboldening with the
+	command \texttt{{\char'134}textbf}
+	and typewriter-style (for instance, for computer code) with
+	\texttt{{\char'134}texttt}.  But remember, you do not
+	have to indicate typestyle changes when such changes are
+	part of the \textit{structural} elements of your
+	article; for instance, the heading of this subsection will
+	be in a sans serif\footnote{A third footnote, here.
+		Let's make this a rather short one to
+		see how it looks.} typeface, but that is handled by the
+	document class file. Take care with the use
+	of\footnote{A fourth, and last, footnote.}
+	the curly braces in typeface changes; they mark
+	the beginning and end of
+	the text that is to be in the different typeface.
+
+	You can use whatever symbols, accented characters, or
+	non-English characters you need anywhere in your document;
+	you can find a complete list of what is
+	available in the \textit{\LaTeX\
+		User's Guide}\cite{Lamport:LaTeX}.
+
+	\subsection{Math Equations}
+	You may want to display math equations in three distinct styles:
+	inline, numbered or non-numbered display.  Each of
+	the three are discussed in the next sections.
+
+	\subsubsection{Inline (In-text) Equations}
+	A formula that appears in the running text is called an
+	inline or in-text formula.  It is produced by the
+	\textbf{math} environment, which can be
+	invoked with the usual \texttt{{\char'134}begin. . .{\char'134}end}
+	construction or with the short form \texttt{\$. . .\$}. You
+	can use any of the symbols and structures,
+	from $\alpha$ to $\omega$, available in
+	\LaTeX\cite{Lamport:LaTeX}; this section will simply show a
+	few examples of in-text equations in context. Notice how
+	this equation: \begin{math}\lim_{n\rightarrow \infty}x=0\end{math},
+	set here in in-line math style, looks slightly different when
+	set in display style.  (See next section).
+
+	\subsubsection{Display Equations}
+	A numbered display equation -- one set off by vertical space
+	from the text and centered horizontally -- is produced
+	by the \textbf{equation} environment. An unnumbered display
+	equation is produced by the \textbf{displaymath} environment.
+
+	Again, in either environment, you can use any of the symbols
+	and structures available in \LaTeX; this section will just
+	give a couple of examples of display equations in context.
+	First, consider the equation, shown as an inline equation above:
+	\begin{equation}\lim_{n\rightarrow \infty}x=0\end{equation}
+	Notice how it is formatted somewhat differently in
+	the \textbf{displaymath}
+	environment.  Now, we'll enter an unnumbered equation:
+	\begin{displaymath}\sum_{i=0}^{\infty} x + 1\end{displaymath}
+	and follow it with another numbered equation:
+	\begin{equation}\sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f\end{equation}
+	just to demonstrate \LaTeX's able handling of numbering.
+
+	\subsection{Citations}
+	Citations to articles \cite{bowman:reasoning,
+		clark:pct, braams:babel, herlihy:methodology},
+	conference proceedings \cite{clark:pct} or
+	books \cite{salas:calculus, Lamport:LaTeX} listed
+	in the Bibliography section of your
+	article will occur throughout the text of your article.
+	You should use BibTeX to automatically produce this bibliography;
+	you simply need to insert one of several citation commands with
+	a key of the item cited in the proper location in
+	the \texttt{.tex} file \cite{Lamport:LaTeX}.
+	The key is a short reference you invent to uniquely
+	identify each work; in this sample document, the key is
+	the first author's surname and a
+	word from the title.  This identifying key is included
+	with each item in the \texttt{.bib} file for your article.
+
+	The details of the construction of the \texttt{.bib} file
+	are beyond the scope of this sample document, but more
+	information can be found in the \textit{Author's Guide},
+	and exhaustive details in the \textit{\LaTeX\ User's
+		Guide}\cite{Lamport:LaTeX}.
+
+	This article shows only the plainest form
+	of the citation command, using \texttt{{\char'134}cite}.
+	This is what is stipulated in the SIGS style specifications.
+	No other citation format is endorsed or supported.
+
+	\subsection{Tables}
+	Because tables cannot be split across pages, the best
+	placement for them is typically the top of the page
+	nearest their initial cite.  To
+	ensure this proper ``floating'' placement of tables, use the
+	environment \textbf{table} to enclose the table's contents and
+	the table caption.  The contents of the table itself must go
+	in the \textbf{tabular} environment, to
+	be aligned properly in rows and columns, with the desired
+	horizontal and vertical rules.  Again, detailed instructions
+	on \textbf{tabular} material
+	is found in the \textit{\LaTeX\ User's Guide}.
+
+	Immediately following this sentence is the point at which
+	Table 1 is included in the input file; compare the
+	placement of the table here with the table in the printed
+	dvi output of this document.
+
+	\begin{table}
+		\centering
+		\caption{Frequency of Special Characters}
+		\begin{tabular}{|c|c|l|} \hline
+			Non-English or Math&Frequency&Comments\\ \hline
+			\O & 1 in 1,000& For Swedish names\\ \hline
+			$\pi$ & 1 in 5& Common in math\\ \hline
+			\$ & 4 in 5 & Used in business\\ \hline
+			$\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
+			\hline\end{tabular}
+	\end{table}
+
+	To set a wider table, which takes up the whole width of
+	the page's live area, use the environment
+	\textbf{table*} to enclose the table's contents and
+	the table caption.  As with a single-column table, this wide
+	table will ``float" to a location deemed more desirable.
+	Immediately following this sentence is the point at which
+	Table 2 is included in the input file; again, it is
+	instructive to compare the placement of the
+	table here with the table in the printed dvi
+	output of this document.
+
+	\begin{table*}
+		\centering
+		\caption{Some Typical Commands}
+		\begin{tabular}{|c|c|l|} \hline
+			Command&A Number&Comments\\ \hline
+			\texttt{{\char'134}alignauthor} & 100& Author alignment\\ \hline
+			\texttt{{\char'134}numberofauthors}& 200& Author enumeration\\ \hline
+			\texttt{{\char'134}table}& 300 & For tables\\ \hline
+			\texttt{{\char'134}table*}& 400& For wider tables\\ \hline\end{tabular}
+	\end{table*}
+	% end the environment with {table*}, NOTE not {table}!
+
+	\subsection{Figures}
+	Like tables, figures cannot be split across pages; the
+	best placement for them
+	is typically the top or the bottom of the page nearest
+	their initial cite.  To ensure this proper ``floating'' placement
+	of figures, use the environment
+	\textbf{figure} to enclose the figure and its caption.
+
+	This sample document contains examples of \textbf{.eps} files to be
+	displayable with \LaTeX.  If you work with pdf\LaTeX, use files in the
+	\textbf{.pdf} format.  Note that most modern \TeX\ system will convert
+	\textbf{.eps} to \textbf{.pdf} for you on the fly.  More details on
+	each of these is found in the \textit{Author's Guide}.
+
+	\begin{figure}
+		\centering
+		%\includegraphics{fly.eps}
+		\caption{A sample black and white graphic.}
+	\end{figure}
+
+	\begin{figure}
+		\centering
+		%\includegraphics[height=1in, width=1in]{fly.eps}
+		\caption{A sample black and white graphic
+			that has been resized with the \texttt{includegraphics} command.}
+	\end{figure}
+
+	As was the case with tables, you may want a figure
+	that spans two columns.  To do this, and still to
+	ensure proper ``floating'' placement of tables, use the environment
+	\textbf{figure*} to enclose the figure and its caption.
+	and don't forget to end the environment with
+	{figure*}, not {figure}!
+
+	\begin{figure*}
+		\centering
+		%\includegraphics{flies.eps}
+		\caption{A sample black and white graphic
+			that needs to span two columns of text.}
+	\end{figure*}
+
+	\subsection{Theorem-like Constructs}
+	Other common constructs that may occur in your article are
+	the forms for logical constructs like theorems, axioms,
+	corollaries and proofs.  There are
+	two forms, one produced by the
+	command \texttt{{\char'134}newtheorem} and the
+	other by the command \texttt{{\char'134}newdef}; perhaps
+	the clearest and easiest way to distinguish them is
+	to compare the two in the output of this sample document:
+
+	This uses the \textbf{theorem} environment, created by
+	the\linebreak\texttt{{\char'134}newtheorem} command:
+	\newtheorem{theorem}{Theorem}
+	\begin{theorem}
+		Let $f$ be continuous on $[a,b]$.  If $G$ is
+		an antiderivative for $f$ on $[a,b]$, then
+		\begin{displaymath}\int^b_af(t)dt = G(b) - G(a).\end{displaymath}
+	\end{theorem}
+
+	The other uses the \textbf{definition} environment, created
+	by the \texttt{{\char'134}newdef} command:
+	\newdef{definition}{Definition}
+	\begin{definition}
+		If $z$ is irrational, then by $e^z$ we mean the
+		unique number which has
+		logarithm $z$: \begin{displaymath}{\log e^z = z}\end{displaymath}
+	\end{definition}
+
+	Two lists of constructs that use one of these
+	forms is given in the
+	\textit{Author's  Guidelines}.
+
+	There is one other similar construct environment, which is
+	already set up
+	for you; i.e. you must \textit{not} use
+	a \texttt{{\char'134}newdef} command to
+	create it: the \textbf{proof} environment.  Here
+	is a example of its use:
+	\begin{proof}
+		Suppose on the contrary there exists a real number $L$ such that
+		\begin{displaymath}
+		\lim_{x\rightarrow\infty} \frac{f(x)}{g(x)} = L.
+		\end{displaymath}
+		Then
+		\begin{displaymath}
+		l=\lim_{x\rightarrow c} f(x)
+		= \lim_{x\rightarrow c}
+		\left[ g{x} \cdot \frac{f(x)}{g(x)} \right ]
+		= \lim_{x\rightarrow c} g(x) \cdot \lim_{x\rightarrow c}
+		\frac{f(x)}{g(x)} = 0\cdot L = 0,
+		\end{displaymath}
+		which contradicts our assumption that $l\neq 0$.
+	\end{proof}
+
+	Complete rules about using these environments and using the
+	two different creation commands are in the
+	\textit{Author's Guide}; please consult it for more
+	detailed instructions.  If you need to use another construct,
+	not listed therein, which you want to have the same
+	formatting as the Theorem
+	or the Definition\cite{salas:calculus} shown above,
+	use the \texttt{{\char'134}newtheorem} or the
+	\texttt{{\char'134}newdef} command,
+	respectively, to create it.
+
+	\subsection*{A {\secit Caveat} for the \TeX\ Expert}
+	Because you have just been given permission to
+	use the \texttt{{\char'134}newdef} command to create a
+	new form, you might think you can
+	use \TeX's \texttt{{\char'134}def} to create a
+	new command: \textit{Please refrain from doing this!}
+	Remember that your \LaTeX\ source code is primarily intended
+	to create camera-ready copy, but may be converted
+	to other forms -- e.g. HTML. If you inadvertently omit
+	some or all of the \texttt{{\char'134}def}s recompilation will
+	be, to say the least, problematic.
+
+	\section{Conclusions}
+	This paragraph will end the body of this sample document.
+	Remember that you might still have Acknowledgments or
+	Appendices; brief samples of these
+	follow.  There is still the Bibliography to deal with; and
+	we will make a disclaimer about that here: with the exception
+	of the reference to the \LaTeX\ book, the citations in
+	this paper are to articles which have nothing to
+	do with the present subject and are used as
+	examples only.
+	%\end{document}  % This is where a 'short' article might terminate
+
+	%ACKNOWLEDGMENTS are optional
+	\section{Acknowledgments}
+	This section is optional; it is a location for you
+	to acknowledge grants, funding, editing assistance and
+	what have you.  In the present case, for example, the
+	authors would like to thank Gerald Murray of ACM for
+	his help in codifying this \textit{Author's Guide}
+	and the \textbf{.cls} and \textbf{.tex} files that it describes.
+
+	%
+	% The following two commands are all you need in the
+	% initial runs of your .tex file to
+	% produce the bibliography for the citations in your paper.
+	\bibliographystyle{abbrv}
+	\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this case
+	% You must have a proper ".bib" file
+	%  and remember to run:
+	% latex bibtex latex latex
+	% to resolve all references
+	%
+	% ACM needs 'a single self-contained file'!
+	%
+	%APPENDICES are optional
+	%\balancecolumns
 	\appendix
-\include{appendix1}
+	%Appendix A
+	\section{Headings in Appendices}
+	The rules about hierarchical headings discussed above for
+	the body of the article are different in the appendices.
+	In the \textbf{appendix} environment, the command
+	\textbf{section} is used to
+	indicate the start of each Appendix, with alphabetic order
+	designation (i.e. the first is A, the second B, etc.) and
+	a title (if you include one).  So, if you need
+	hierarchical structure
+	\textit{within} an Appendix, start with \textbf{subsection} as the
+	highest level. Here is an outline of the body of this
+	document in Appendix-appropriate form:
+	\subsection{Introduction}
+	\subsection{The Body of the Paper}
+	\subsubsection{Type Changes and  Special Characters}
+	\subsubsection{Math Equations}
+	\paragraph{Inline (In-text) Equations}
+	\paragraph{Display Equations}
+	\subsubsection{Citations}
+	\subsubsection{Tables}
+	\subsubsection{Figures}
+	\subsubsection{Theorem-like Constructs}
+	\subsubsection*{A Caveat for the \TeX\ Expert}
+	\subsection{Conclusions}
+	\subsection{Acknowledgments}
+	\subsection{Additional Authors}
+	This section is inserted by \LaTeX; you do not insert it.
+	You just add the names and information in the
+	\texttt{{\char'134}additionalauthors} command at the start
+	of the document.
+	\subsection{References}
+	Generated by bibtex from your ~.bib file.  Run latex,
+	then bibtex, then latex twice (to resolve references)
+	to create the ~.bbl file.  Insert that ~.bbl file into
+	the .tex source file and comment out
+	the command \texttt{{\char'134}thebibliography}.
+	% This next section command marks the start of
+	% Appendix B, and does not continue the present hierarchy
+	\section{More Help for the Hardy}
+	The sig-alternate.cls file itself is chock-full of succinct
+	and helpful comments.  If you consider yourself a moderately
+	experienced to expert user of \LaTeX, you may find reading
+	it useful but please remember not to change it.
+	%\balancecolumns % GM June 2007
+	% That's all folks!
 \end{document}

### 2016-05-05 dis.tex
still not able to get it to work

@@
 \documentclass{sig-alternate-05-2015}
-\usepackage[square,numbers]{natbib}
-\usepackage{geometry}
-\usepackage{fancyhdr}
-\usepackage{afterpage}
-\usepackage{graphicx}
-\usepackage{amsmath,amssymb,amsbsy}
-\usepackage{dcolumn,array}
-\usepackage{tocloft}
-
-% for title case
-\usepackage{titlecaps}
-\Addlcwords{and, the, or, of, that, our, by}
-
-% avoid widows
-\usepackage[all]{nowidow}
-\clubpenalty=10000
-
-\usepackage{asudis}
-%% These are for including code
-%% and for upquotes
-\usepackage[T1]{fontenc}
-\usepackage{textcomp}
-\usepackage{listings}
-\usepackage{listingsutf8}
-\usepackage{comment}
-\usepackage{color}
-\usepackage{dirtytalk} % for quotations
-\usepackage[justification=centering]{caption}
-\usepackage[pageanchor=true,plainpages=false,pdfpagelabels,bookmarks,bookmarksnumbered,hidelinks]{hyperref}
-
-% for footnotes in tables
-\usepackage{tablefootnote}
-
-% for arithmetic
-\usepackage{xintexpr}
-
-\usepackage{textcomp}     % access \textquotesingle
-
-\definecolor{mygray}{rgb}{0.6,0.6,0.6}
-\definecolor{lightgray}{rgb}{0.92,0.92,0.92}
-\definecolor{darkgreen}{rgb}{0,0.7,0}
-% default options for listings
-\lstset{
-	backgroundcolor=\color{lightgray},
-	basicstyle=\footnotesize,
-	breaklines=true, 
-	captionpos=b,
-	commentstyle=\color{darkgreen}, 
-	frame=single,
-	keywordstyle=\color{blue}, 
-	numbers=left,
-	numbersep=5pt,
-	numberstyle=\tiny\color{mygray},
-	rulecolor=\color{black},
-	showstringspaces=false,
-	upquote=true
-}
-
 \newcommand{\dq}[1]{``{#1}''}

### 2016-05-05 abstract.tex
abstract done

@@
 With the proper injection string, this vulnerability can be exploited to inject additional headers and/or modify existing headers in an E-Mail message, allowing an attacker to completely alter the content of the e-mail.
-	\paragraph{}
+
 	This thesis develops a scalable mechanism to automatically detect E-Mail Header Injection vulnerability and uses this mechanism to quantify the prevalence of E\-Mail Header Injection vulnerabilities on the Internet.
@@
 The system tested \malfuzzed\ of these, and was able to find \success\ vulnerable URLs across \domains\ domains, which proves that the threat is widespread and deserves future research attention.
-
 \end{abstract}

### 2016-05-05 paper.tex
slowly adding packages without breaking stuff
abstract done

--- 2016-05-05 dis.tex
@@
 \documentclass{sig-alternate-05-2015}
+
 \usepackage[square,numbers]{natbib}
-\usepackage{geometry}
-\usepackage{fancyhdr}
-\usepackage{afterpage}
-\usepackage{graphicx}
-\usepackage{amsmath,amssymb,amsbsy}
-\usepackage{dcolumn,array}
-\usepackage{tocloft}
-
-% for title case
-\usepackage{titlecaps}
-\Addlcwords{and, the, or, of, that, our, by}
-
-% avoid widows
-\usepackage[all]{nowidow}
-\clubpenalty=10000
-
-\usepackage{asudis}
-%% These are for including code
-%% and for upquotes
-\usepackage[T1]{fontenc}
-\usepackage{textcomp}
-\usepackage{listings}
-\usepackage{listingsutf8}
-\usepackage{comment}
-\usepackage{color}
-\usepackage{dirtytalk} % for quotations
 \usepackage[justification=centering]{caption}
 \usepackage[pageanchor=true,plainpages=false,pdfpagelabels,bookmarks,bookmarksnumbered,hidelinks]{hyperref}
+\usepackage{color}
+\definecolor{mygray}{rgb}{0.6,0.6,0.6}
+\definecolor{lightgray}{rgb}{0.92,0.92,0.92}
+\definecolor{darkgreen}{rgb}{0,0.7,0}
 
@@
 
-% for arithmetic
-\usepackage{xintexpr}
-
+% default options for listings
+\usepackage{listings}
+\usepackage{listingsutf8}
 \usepackage{textcomp}     % access \textquotesingle
-
-\definecolor{mygray}{rgb}{0.6,0.6,0.6}
-\definecolor{lightgray}{rgb}{0.92,0.92,0.92}
-\definecolor{darkgreen}{rgb}{0,0.7,0}
-% default options for listings
 \lstset{
@@
 
-	\title{Alternate {\ttlit ACM} SIG Proceedings Paper in LaTeX
-		Format\titlenote{(Produces the permission block, and
-			copyright information). For use with
-			SIG-ALTERNATE.CLS. Supported by ACM.}}
-	\subtitle{[Extended Abstract]
-		\titlenote{A full version of this paper is available as
-			\textit{Author's Guide to Preparing ACM SIG Proceedings Using
-				\LaTeX$2_\epsilon$\ and BibTeX} at
-			\texttt{www.acm.org/eaddress.htm}}}
+	\title{E-jection fraction - Tracking how your website pumps out E-Mails}
 	%
@@
 	\maketitle
-	\begin{abstract}
-		This paper provides a sample of a \LaTeX\ document which conforms,
-		somewhat loosely, to the formatting guidelines for
-		ACM SIG Proceedings. It is an {\em alternate} style which produces
-		a {\em tighter-looking} paper and was designed in response to
-		concerns expressed, by authors, over page-budgets.
-		It complements the document \textit{Author's (Alternate) Guide to
-			Preparing ACM SIG Proceedings Using \LaTeX$2_\epsilon$\ and Bib\TeX}.
-		This source file has been written with the intention of being
-		compiled under \LaTeX$2_\epsilon$\ and BibTeX.
-
-		The developers have tried to include every imaginable sort
-		of ``bells and whistles", such as a subtitle, footnotes on
-		title, subtitle and authors, as well as in the text, and
-		every optional component (e.g. Acknowledgments, Additional
-		Authors, Appendices), not to mention examples of
-		equations, theorems, tables and figures.
-
-		To make best use of this sample document, run it through \LaTeX\
-		and BibTeX, and compare this source code with the printed
-		output produced by the dvi file. A compiled PDF version
-		is available on the web page to help you with the
-		`look and feel'.
-	\end{abstract}
+	\input{abstract}
 
@@
 		\centering
-		%\includegraphics{fly.eps}
+		%\includegraphics{System/fuzzer_design}
 		\caption{A sample black and white graphic.}

### 2016-05-05 introduction.tex
added intro, pb bg, needs formatting

@@
-\chapter{Introduction}
-\paragraph{}
 	The World Wide Web has single-handedly brought about a change in the way we use computers.
@@
 
-\paragraph{Structure of document} % describes the remaining sections and gives a short desc about them
+\subsection*{Structure of document} % describes the remaining sections and gives a short desc about them
 This thesis document is divided logically into the following sections:
@@
 
-\paragraph{} % summary paragraph
 We hope that our research sheds some light on this relatively less well-known vulnerability, and find out its prevalence on the World Wide Web. In summary, we make the following contributions:
@@
 \end{itemize}
-
-\paragraph{}

### 2016-05-05 paper.tex
added intro, pb bg, needs formatting

@@
 
+% for title caps
+\usepackage{titlecaps}
+\Addlcwords{and, the, or, of, that, our, by, a, prevent, for}
+
 % default options for listings
@@
 %% THIS IS THE DATA FOR OUR THESIS, UPDATING HERE WILL UPDATE EVERYWHERE %%
-\newcommand{\urls}{17,686,161}
+\newcommand{\urls}{21,675,680}
 
-\newcommand{\forms}{5,562,533}
-\newcommand{\formsDelta}{31.45\%}
+\newcommand{\forms}{6,794,917}
+\newcommand{\formsDelta}{31.35\%}
 
-\newcommand{\emailforms}{918,988}
-\newcommand{\emailformsDelta}{16.52\%}
+\newcommand{\emailforms}{1,132,157}
+\newcommand{\emailformsDelta}{16.66\%}
 
-\newcommand{\fuzzed}{756,588}
-\newcommand{\fuzzedDelta}{82.33\%}
+\newcommand{\fuzzed}{934,016}
+\newcommand{\fuzzedDelta}{82.50\%}
 
-\newcommand{\recd}{44,735}
-\newcommand{\recdDelta}{5.91\%}
+\newcommand{\recd}{52,724}
+\newcommand{\recdDelta}{5.64\%}
 
-\newcommand{\malfuzzed}{38,989}
-\newcommand{\malfuzzedDelta}{87.16\%}
+\newcommand{\malfuzzed}{46,156}
+\newcommand{\malfuzzedDelta}{87.54\%}
 
-\newcommand{\success}{433}
-\newcommand{\successDelta}{1.11\%}
+\newcommand{\success}{496}
+\newcommand{\successDelta}{1.07\%}
 
-\newcommand{\domains}{182}
-
+\newcommand{\domains}{222}
+\newcommand{\ips}{292}
 % these refer to unique domains, not unique forms
-\newcommand{\uniqueforms}{650,394}
-\newcommand{\uniqueemailforms}{151,795}
+\newcommand{\uniqueforms}{1,019,921}
+\newcommand{\uniqueemailforms}{197,570}
 
@@
 	\section{Introduction}
-	The \textit{proceedings} are the records of a conference.
-	ACM seeks to give these conference by-products a uniform,
-	high-quality appearance.  To do this, ACM has some rigid
-	requirements for the format of the proceedings documents: there
-	is a specified format (balanced  double columns), a specified
-	set of fonts (Arial or Helvetica and Times Roman) in
-	certain specified sizes (for instance, 9 point for body copy),
-	a specified live area (18 $\times$ 23.5 cm [7" $\times$ 9.25"]) centered on
-	the page, specified size of margins (1.9 cm [0.75"]) top, (2.54 cm [1"]) bottom
-	and (1.9 cm [.75"]) left and right; specified column width
-	(8.45 cm [3.33"]) and gutter size (.83 cm [.33"]).
+	\input{introduction}
 
-	The good news is, with only a handful of manual
-	settings\footnote{Two of these, the {\texttt{\char'134 numberofauthors}}
-		and {\texttt{\char'134 alignauthor}} commands, you have
-		already used; another, {\texttt{\char'134 balancecolumns}}, will
-		be used in your very last run of \LaTeX\ to ensure
-		balanced column heights on the last page.}, the \LaTeX\ document
-	class file handles all of this for you.
-
-	The remainder of this document is concerned with showing, in
-	the context of an ``actual'' document, the \LaTeX\ commands
-	specifically available for denoting the structure of a
-	proceedings paper, rather than with giving rigorous descriptions
-	or explanations of such commands.
+	\input{problem_background}
 

### 2016-05-06 paper.tex
slight formatting changes done
added biblio
fixing more shtuff
lil adds

@@
 
-	\section{Introduction}
 	\input{introduction}
@@
 		User's Guide}\cite{Lamport:LaTeX}.
-
-	\subsection{Math Equations}
-	You may want to display math equations in three distinct styles:
-	inline, numbered or non-numbered display.  Each of
-	the three are discussed in the next sections.
-
-	\subsubsection{Inline (In-text) Equations}
-	A formula that appears in the running text is called an
-	inline or in-text formula.  It is produced by the
-	\textbf{math} environment, which can be
-	invoked with the usual \texttt{{\char'134}begin. . .{\char'134}end}
-	construction or with the short form \texttt{\$. . .\$}. You
-	can use any of the symbols and structures,
-	from $\alpha$ to $\omega$, available in
-	\LaTeX\cite{Lamport:LaTeX}; this section will simply show a
-	few examples of in-text equations in context. Notice how
-	this equation: \begin{math}\lim_{n\rightarrow \infty}x=0\end{math},
-	set here in in-line math style, looks slightly different when
-	set in display style.  (See next section).
-
-	\subsubsection{Display Equations}
-	A numbered display equation -- one set off by vertical space
-	from the text and centered horizontally -- is produced
-	by the \textbf{equation} environment. An unnumbered display
-	equation is produced by the \textbf{displaymath} environment.
-
-	Again, in either environment, you can use any of the symbols
-	and structures available in \LaTeX; this section will just
-	give a couple of examples of display equations in context.
-	First, consider the equation, shown as an inline equation above:
-	\begin{equation}\lim_{n\rightarrow \infty}x=0\end{equation}
-	Notice how it is formatted somewhat differently in
-	the \textbf{displaymath}
-	environment.  Now, we'll enter an unnumbered equation:
-	\begin{displaymath}\sum_{i=0}^{\infty} x + 1\end{displaymath}
-	and follow it with another numbered equation:
-	\begin{equation}\sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f\end{equation}
-	just to demonstrate \LaTeX's able handling of numbering.
-
-	\subsection{Citations}
-	Citations to articles \cite{bowman:reasoning,
-		clark:pct, braams:babel, herlihy:methodology},
-	conference proceedings \cite{clark:pct} or
-	books \cite{salas:calculus, Lamport:LaTeX} listed
-	in the Bibliography section of your
-	article will occur throughout the text of your article.
-	You should use BibTeX to automatically produce this bibliography;
-	you simply need to insert one of several citation commands with
-	a key of the item cited in the proper location in
-	the \texttt{.tex} file \cite{Lamport:LaTeX}.
-	The key is a short reference you invent to uniquely
-	identify each work; in this sample document, the key is
-	the first author's surname and a
-	word from the title.  This identifying key is included
-	with each item in the \texttt{.bib} file for your article.
-
-	The details of the construction of the \texttt{.bib} file
-	are beyond the scope of this sample document, but more
-	information can be found in the \textit{Author's Guide},
-	and exhaustive details in the \textit{\LaTeX\ User's
-		Guide}\cite{Lamport:LaTeX}.
-
-	This article shows only the plainest form
-	of the citation command, using \texttt{{\char'134}cite}.
-	This is what is stipulated in the SIGS style specifications.
-	No other citation format is endorsed or supported.
 
@@
 	\bibliographystyle{abbrv}
-	\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this case
+	\bibliography{biblio}  
 	% You must have a proper ".bib" file

### 2016-05-11 System/components.tex
chap3 added

@@
-\section{System Components}
+\subsection{System Components}
 \label{Comp}
@@
 
-\subsection{Crawler}
+\subsubsection{Crawler}
 \label{Comp:Crawler}
@@
 
-\subsection{Form Parser}
+\subsubsection{Form Parser}
 \label{Comp:FP}
@@
 
-\subsection{E-Mail Field Checker}
+\subsubsection{E-Mail Field Checker}
 \label{Comp:EMFC}
@@
 
-\subsection{E-Mail Form Retriever}
+\subsubsection{E-Mail Form Retriever}
 \label{Comp:EMFR}
@@
 
-\subsection{Fuzzer}
+\subsubsection{Fuzzer}
 \label{Comp:Fuzzer}
@@
 
-\subsection{E-Mail Analyzer}
+\subsubsection{E-Mail Analyzer}
 \label{Comp:EMA}
@@
 This is due to the fact that this involves lesser processing of the contents of the e-mail compared to the previous section.
-\subparagraph{Detecting injected bcc headers}
+\paragraph{Detecting injected bcc headers}
 As discussed in the payloads section (\ref{Comp:Fuzzer:mp}), the payloads were crafted in such a way that the e-mails received by `maluser' account directly indicate the presence of the injected `bcc' field.
@@
 \label{analyze:detect_x_check}
-\subparagraph{Detecting injected x-check headers}
+\paragraph{Detecting injected x-check headers}
 E-Mails not received by the `maluser' account but by the `nuser' account constitute a special category of e-mails.
@@
 \end{enumerate}
-\subsection{Database}
+\subsubsection{Database}
 We collect and store as much data as possible at each stage of the pipeline. This is due to the two following reasons:

### 2016-05-11 System/proof_of_concept.tex
chap4 added

@@
-\section{Proof of Concept Attacks}
+\subsection{Proof of Concept Attacks}
 The previous section (Section~\ref{Arch:Test}) discussed in detail how we verified that our system functions according to our expectations.

### 2016-05-11 exp_setup.tex
chap4 added

@@
-\chapter{Evaluation}
+\section{Evaluation}
 This chapter describes the experimental setup for our project including the servers used, the software and the platforms involved, the languages used, and the task queue system that was used for parallelism.

### 2016-05-11 Results/analysis.tex
chap5 added

@@
-\section[Analysis of Data]{Our Analysis of the received e-mail Data}
+\subsection[Analysis of Data]{Our Analysis of the received e-mail Data}
 During our analysis of the received e-mails, we found that the e-mails that we received belonged to one of three broad categories:

### 2016-05-11 conclusion.tex
chap8 added

@@
-\chapter{Conclusion}
+\section{Conclusions}
 We have showcased a novel approach involving black-box testing to identify the presence of E-Mail Header Injection in a web application.

### 2016-05-11 paper.tex
changesto be made
adding chap3
chap4 added
chap5 added
chap6 added
chap7 added
chap8 added

@@
 
-	\section{The {\secit Body} of The Paper}
-	Typically, the body of a paper is organized
-	into a hierarchical structure, with numbered or unnumbered
-	headings for sections, subsections, sub-subsections, and even
-	smaller sections.  The command \texttt{{\char'134}section} that
-	precedes this paragraph is part of such a
-	hierarchy.\footnote{This is the second footnote.  It
-		starts a series of three footnotes that add nothing
-		informational, but just give an idea of how footnotes work
-		and look. It is a wordy one, just so you see
-		how a longish one plays out.} \LaTeX\ handles the numbering
-	and placement of these headings for you, when you use
-	the appropriate heading commands around the titles
-	of the headings.  If you want a sub-subsection or
-	smaller part to be unnumbered in your output, simply append an
-	asterisk to the command name.  Examples of both
-	numbered and unnumbered headings will appear throughout the
-	balance of this sample document.
+	\input{sys_design}
 
-	Because the entire article is contained in
-	the \textbf{document} environment, you can indicate the
-	start of a new paragraph with a blank line in your
-	input file; that is why this sentence forms a separate paragraph.
+	\input{exp_setup}
 
-	\subsection{Type Changes and {\subsecit Special} Characters}
-	We have already seen several typeface changes in this sample.  You
-	can indicate italicized words or phrases in your text with
-	the command \texttt{{\char'134}textit}; emboldening with the
-	command \texttt{{\char'134}textbf}
-	and typewriter-style (for instance, for computer code) with
-	\texttt{{\char'134}texttt}.  But remember, you do not
-	have to indicate typestyle changes when such changes are
-	part of the \textit{structural} elements of your
-	article; for instance, the heading of this subsection will
-	be in a sans serif\footnote{A third footnote, here.
-		Let's make this a rather short one to
-		see how it looks.} typeface, but that is handled by the
-	document class file. Take care with the use
-	of\footnote{A fourth, and last, footnote.}
-	the curly braces in typeface changes; they mark
-	the beginning and end of
-	the text that is to be in the different typeface.
+	\input{results}
 
-	You can use whatever symbols, accented characters, or
-	non-English characters you need anywhere in your document;
-	you can find a complete list of what is
-	available in the \textit{\LaTeX\
-		User's Guide}\cite{Lamport:LaTeX}.
+	\input{discussion}
+
+	\input{rel_work}
+
+	\input{conclusion}
 

### 2016-05-11 paper.tex
finished adding all chapters, editing left

@@
 
-	\subsection{Tables}
-	Because tables cannot be split across pages, the best
-	placement for them is typically the top of the page
-	nearest their initial cite.  To
-	ensure this proper ``floating'' placement of tables, use the
-	environment \textbf{table} to enclose the table's contents and
-	the table caption.  The contents of the table itself must go
-	in the \textbf{tabular} environment, to
-	be aligned properly in rows and columns, with the desired
-	horizontal and vertical rules.  Again, detailed instructions
-	on \textbf{tabular} material
-	is found in the \textit{\LaTeX\ User's Guide}.
-
-	Immediately following this sentence is the point at which
-	Table 1 is included in the input file; compare the
-	placement of the table here with the table in the printed
-	dvi output of this document.
-
-	\begin{table}
-		\centering
-		\caption{Frequency of Special Characters}
-		\begin{tabular}{|c|c|l|} \hline
-			Non-English or Math&Frequency&Comments\\ \hline
-			\O & 1 in 1,000& For Swedish names\\ \hline
-			$\pi$ & 1 in 5& Common in math\\ \hline
-			\$ & 4 in 5 & Used in business\\ \hline
-			$\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
-			\hline\end{tabular}
-	\end{table}
-
-	To set a wider table, which takes up the whole width of
-	the page's live area, use the environment
-	\textbf{table*} to enclose the table's contents and
-	the table caption.  As with a single-column table, this wide
-	table will ``float" to a location deemed more desirable.
-	Immediately following this sentence is the point at which
-	Table 2 is included in the input file; again, it is
-	instructive to compare the placement of the
-	table here with the table in the printed dvi
-	output of this document.
-
-	\begin{table*}
-		\centering
-		\caption{Some Typical Commands}
-		\begin{tabular}{|c|c|l|} \hline
-			Command&A Number&Comments\\ \hline
-			\texttt{{\char'134}alignauthor} & 100& Author alignment\\ \hline
-			\texttt{{\char'134}numberofauthors}& 200& Author enumeration\\ \hline
-			\texttt{{\char'134}table}& 300 & For tables\\ \hline
-			\texttt{{\char'134}table*}& 400& For wider tables\\ \hline\end{tabular}
-	\end{table*}
-	% end the environment with {table*}, NOTE not {table}!
-
-	\subsection{Figures}
-	Like tables, figures cannot be split across pages; the
-	best placement for them
-	is typically the top or the bottom of the page nearest
-	their initial cite.  To ensure this proper ``floating'' placement
-	of figures, use the environment
-	\textbf{figure} to enclose the figure and its caption.
-
-	This sample document contains examples of \textbf{.eps} files to be
-	displayable with \LaTeX.  If you work with pdf\LaTeX, use files in the
-	\textbf{.pdf} format.  Note that most modern \TeX\ system will convert
-	\textbf{.eps} to \textbf{.pdf} for you on the fly.  More details on
-	each of these is found in the \textit{Author's Guide}.
-
-	\begin{figure}
-		\centering
-		%\includegraphics{System/fuzzer_design}
-		\caption{A sample black and white graphic.}
-	\end{figure}
-
-	\begin{figure}
-		\centering
-		%\includegraphics[height=1in, width=1in]{fly.eps}
-		\caption{A sample black and white graphic
-			that has been resized with the \texttt{includegraphics} command.}
-	\end{figure}
-
-	As was the case with tables, you may want a figure
-	that spans two columns.  To do this, and still to
-	ensure proper ``floating'' placement of tables, use the environment
-	\textbf{figure*} to enclose the figure and its caption.
-	and don't forget to end the environment with
-	{figure*}, not {figure}!
-
-	\begin{figure*}
-		\centering
-		%\includegraphics{flies.eps}
-		\caption{A sample black and white graphic
-			that needs to span two columns of text.}
-	\end{figure*}
-
-	\subsection{Theorem-like Constructs}
-	Other common constructs that may occur in your article are
-	the forms for logical constructs like theorems, axioms,
-	corollaries and proofs.  There are
-	two forms, one produced by the
-	command \texttt{{\char'134}newtheorem} and the
-	other by the command \texttt{{\char'134}newdef}; perhaps
-	the clearest and easiest way to distinguish them is
-	to compare the two in the output of this sample document:
-
-	This uses the \textbf{theorem} environment, created by
-	the\linebreak\texttt{{\char'134}newtheorem} command:
-	\newtheorem{theorem}{Theorem}
-	\begin{theorem}
-		Let $f$ be continuous on $[a,b]$.  If $G$ is
-		an antiderivative for $f$ on $[a,b]$, then
-		\begin{displaymath}\int^b_af(t)dt = G(b) - G(a).\end{displaymath}
-	\end{theorem}
-
-	The other uses the \textbf{definition} environment, created
-	by the \texttt{{\char'134}newdef} command:
-	\newdef{definition}{Definition}
-	\begin{definition}
-		If $z$ is irrational, then by $e^z$ we mean the
-		unique number which has
-		logarithm $z$: \begin{displaymath}{\log e^z = z}\end{displaymath}
-	\end{definition}
-
-	Two lists of constructs that use one of these
-	forms is given in the
-	\textit{Author's  Guidelines}.
-
-	There is one other similar construct environment, which is
-	already set up
-	for you; i.e. you must \textit{not} use
-	a \texttt{{\char'134}newdef} command to
-	create it: the \textbf{proof} environment.  Here
-	is a example of its use:
-	\begin{proof}
-		Suppose on the contrary there exists a real number $L$ such that
-		\begin{displaymath}
-		\lim_{x\rightarrow\infty} \frac{f(x)}{g(x)} = L.
-		\end{displaymath}
-		Then
-		\begin{displaymath}
-		l=\lim_{x\rightarrow c} f(x)
-		= \lim_{x\rightarrow c}
-		\left[ g{x} \cdot \frac{f(x)}{g(x)} \right ]
-		= \lim_{x\rightarrow c} g(x) \cdot \lim_{x\rightarrow c}
-		\frac{f(x)}{g(x)} = 0\cdot L = 0,
-		\end{displaymath}
-		which contradicts our assumption that $l\neq 0$.
-	\end{proof}
-
-	Complete rules about using these environments and using the
-	two different creation commands are in the
-	\textit{Author's Guide}; please consult it for more
-	detailed instructions.  If you need to use another construct,
-	not listed therein, which you want to have the same
-	formatting as the Theorem
-	or the Definition\cite{salas:calculus} shown above,
-	use the \texttt{{\char'134}newtheorem} or the
-	\texttt{{\char'134}newdef} command,
-	respectively, to create it.
-
-	\subsection*{A {\secit Caveat} for the \TeX\ Expert}
-	Because you have just been given permission to
-	use the \texttt{{\char'134}newdef} command to create a
-	new form, you might think you can
-	use \TeX's \texttt{{\char'134}def} to create a
-	new command: \textit{Please refrain from doing this!}
-	Remember that your \LaTeX\ source code is primarily intended
-	to create camera-ready copy, but may be converted
-	to other forms -- e.g. HTML. If you inadvertently omit
-	some or all of the \texttt{{\char'134}def}s recompilation will
-	be, to say the least, problematic.
-
-	\section{Conclusions}
-	This paragraph will end the body of this sample document.
-	Remember that you might still have Acknowledgments or
-	Appendices; brief samples of these
-	follow.  There is still the Bibliography to deal with; and
-	we will make a disclaimer about that here: with the exception
-	of the reference to the \LaTeX\ book, the citations in
-	this paper are to articles which have nothing to
-	do with the present subject and are used as
-	examples only.
-	%\end{document}  % This is where a 'short' article might terminate
-
-	%ACKNOWLEDGMENTS are optional
-	\section{Acknowledgments}
-	This section is optional; it is a location for you
-	to acknowledge grants, funding, editing assistance and
-	what have you.  In the present case, for example, the
-	authors would like to thank Gerald Murray of ACM for
-	his help in codifying this \textit{Author's Guide}
-	and the \textbf{.cls} and \textbf{.tex} files that it describes.
-
 	%
@@
 	%\balancecolumns
-	\appendix
-	%Appendix A
-	\section{Headings in Appendices}
-	The rules about hierarchical headings discussed above for
-	the body of the article are different in the appendices.
-	In the \textbf{appendix} environment, the command
-	\textbf{section} is used to
-	indicate the start of each Appendix, with alphabetic order
-	designation (i.e. the first is A, the second B, etc.) and
-	a title (if you include one).  So, if you need
-	hierarchical structure
-	\textit{within} an Appendix, start with \textbf{subsection} as the
-	highest level. Here is an outline of the body of this
-	document in Appendix-appropriate form:
-	\subsection{Introduction}
-	\subsection{The Body of the Paper}
-	\subsubsection{Type Changes and  Special Characters}
-	\subsubsection{Math Equations}
-	\paragraph{Inline (In-text) Equations}
-	\paragraph{Display Equations}
-	\subsubsection{Citations}
-	\subsubsection{Tables}
-	\subsubsection{Figures}
-	\subsubsection{Theorem-like Constructs}
-	\subsubsection*{A Caveat for the \TeX\ Expert}
-	\subsection{Conclusions}
-	\subsection{Acknowledgments}
-	\subsection{Additional Authors}
-	This section is inserted by \LaTeX; you do not insert it.
-	You just add the names and information in the
-	\texttt{{\char'134}additionalauthors} command at the start
-	of the document.
-	\subsection{References}
-	Generated by bibtex from your ~.bib file.  Run latex,
-	then bibtex, then latex twice (to resolve references)
-	to create the ~.bbl file.  Insert that ~.bbl file into
-	the .tex source file and comment out
-	the command \texttt{{\char'134}thebibliography}.
-	% This next section command marks the start of
-	% Appendix B, and does not continue the present hierarchy
-	\section{More Help for the Hardy}
-	The sig-alternate.cls file itself is chock-full of succinct
-	and helpful comments.  If you consider yourself a moderately
-	experienced to expert user of \LaTeX, you may find reading
-	it useful but please remember not to change it.
-	%\balancecolumns % GM June 2007
-	% That's all folks!
+
 \end{document}

### 2016-05-11 introduction.tex
slight formatting changes done
prelim edit chap1

@@
+\section{Introduction}
 	The World Wide Web has single-handedly brought about a change in the way we use computers.
@@
 
-\subsection*{Structure of document} % describes the remaining sections and gives a short desc about them
-This thesis document is divided logically into the following sections:
-\begin{itemize}
-	\item Chapter 2 discusses the background of E-Mail Header Injection, a brief history of the vulnerability, and enumerates the languages and platforms affected by this vulnerability.
-
-	\item Chapter 3 discusses the System design, the architecture, and the components of the system.
-
-	\item Chapter 4 describes the experimental setup and sheds light on how we overcame the issues and assumptions discussed in Chapter 3.
-
-	\item Chapter 5 presents our findings and our analysis of the results.
-
-	\item Chapter 6 continues the discussion of the results; the lessons learned over the course of the project, limitations, and a suitable mitigation strategy to overcome the vulnerability.
-
-	\item Chapter 7 explores related work in the area.
-
-	\item Chapter 8 concludes this thesis, with ideas to expand the research in this area.
-\end{itemize}
-
 We hope that our research sheds some light on this relatively less well-known vulnerability, and find out its prevalence on the World Wide Web. In summary, we make the following contributions:

### 2016-05-13 Background/history.tex
slight formatting changes done
fixed most emph/quote/texttt issues

@@
-\section{History of E-Mail Injection}
+\subsection{History of E-Mail Injection}
 
-E-Mail Header Injection seems to have been first documented over a decade ago, in a late 2004 article on phpsecure.info \cite{Tobozo} accredited to user \lstinline|tobozo@phpsecure.info| describing how this vulnerability existed in the reference implementation of the \dq{\texttt{mail}} function in PHP, and how it can be exploited.
+E-Mail Header Injection seems to have been first documented over a decade ago, in a late 2004 article on phpsecure.info \cite{Tobozo} accredited to user \lstinline|tobozo@phpsecure.info| describing how this vulnerability existed in the reference implementation of the \texttt{mail()} function in PHP, and how it can be exploited.
 More recently, a blog post by Damon Kohler \cite{DK} and an accompanying wiki article \cite{Injection} describe the attack vector and outline a few defense measures for the same.
 
-As this vulnerability was initially found in the \emph{mail()} function of PHP, E-Mail Header Injection can be traced to as early as the beginning of the 2000's, present in the \emph{mail()} implementation of PHP 4.0.
-
-The vulnerability was also described briefly (less than a page) by Stuttard and Pinto in their widely acclaimed book, ``\emph{The Web Application Hacker's Handbook: Discovering and Exploiting Security Flaws}'' \cite{stuttard2011web}.
-A concise timeline of the vulnerability is presented in Table~\ref{tab:history}.
+As this vulnerability was initially found in the \texttt{mail()} function of PHP, E-Mail Header Injection can be traced to as early as the beginning of the 2000's, present in the \texttt{mail()} implementation of PHP 4.0.
 
 An example of the vulnerable code written in PHP is shown in Listing~\ref{code:phpemi}.
-This code takes in user input from the PHP superglobal \dq{\texttt{\$\_REQUEST[\textquotesingle email\textquotesingle]}}, and stores it in the variable \dq{\texttt{\$from}}, which is later passed to the \dq{\texttt{mail}} function to construct and send the e-mail.
+This code takes in user input from the PHP superglobal \texttt{\$\_REQUEST[\textquotesingle email\textquotesingle]}, and stores it in the variable \texttt{\$from}, which is later passed to the \texttt{mail()} function to construct and send the e-mail.
 \input{Background/php.tex}
 
-When this code is given the malicious input \dq{\texttt{\lstinline{sai@sai.com\\nBCC:spc@spc.com}}} as the value of the \dq{\texttt{\$\_REQUEST[\textquotesingle email\textquotesingle]}}, it generates the SMTP Headers shown in Listing~\ref{code:smtpheaders}.
-It can be seen that the `CC' (carbon copy) header that we injected appears as part of the resulting SMTP message.
-This will make the e-mail get sent to the e-mail address specified as part of the `CC' as well.
+When this code is given the malicious input \texttt{\lstinline{sai@sai.com\\nBCC:spc@spc.com}} as the value of the \texttt{\$\_REQUEST[\textquotesingle email\textquotesingle]}, it generates the SMTP Headers shown in Listing~\ref{code:smtpheaders}.
+It can be seen that the \texttt{CC} (carbon copy) header that we injected appears as part of the resulting SMTP message.
+This will make the e-mail get sent to the e-mail address specified as part of the \texttt{CC} as well.
 \input{Background/smtpheaders}
-\input{Background/history_table}
+%\input{Background/history_table}

### 2016-05-13 Background/impact.tex
slight formatting changes done
fixed most emph/quote/texttt issues

@@
-\section{Potential Impact}
+\subsection{Potential Impact}
 
@@
 	Spam networks can use E-Mail Header Injection vulnerabilities on the ability to send a large amount of e-mail from servers that are trusted.
-By adding additional \dq{\texttt{cc}} or \dq{\texttt{bcc}} headers to the generated e-mail, attackers can easily achieve this effect.
+By adding additional \texttt{cc} or \texttt{bcc} headers to the generated e-mail, attackers can easily achieve this effect.
 
@@
 	E-Mails can contains sensitive data that is meant to be accessed only by the user.
-Due to E-Mail Header Injection, an attacker can easily add a \dq{\texttt{bcc}} header, and send the e-mail to himself, thereby extracting important information.
+Due to E-Mail Header Injection, an attacker can easily add a \texttt{bcc} header, and send the e-mail to himself, thereby extracting important information.
 	User privacy can thus be compromised, and loss of private information can by itself lead to other attacks.

### 2016-05-13 Discussion/lessons.tex
chap6 added
fixed most emph/quote/texttt issues

@@
-\section{Lessons Learned}
+\subsection{Lessons Learned}
     From our results, it is evident that the vulnerability exists in the wild.
@@
 
-	We come to this conclusion because of our discovery of the \dq{\texttt{To header injection}}.
+	We come to this conclusion because of our discovery of the \texttt{To header injection}.
 Clearly, this is possible due to incomplete sanitization performed by the application.
 We suspect that this incomplete sanitization is actually sanitization that is performed for some other vulnerability, and not specifically for E-Mail Header Injection attacks.
-We would also like to remark that \dq{\texttt{To header injection}} is not complete E-Mail Header Injection, but only a special subset.
+We would also like to remark that \texttt{To header injection} is not complete E-Mail Header Injection, but only a special subset.
 
@@
     From our research, we found two different forms of the E-Mail Header Injection Vulnerability: the first one is the traditional one, where we are able to inject any header into the forms, allowing us complete control over the contents of the e-mail.
-We identify this with the presence of both the \dq{\texttt{bcc}} header and the \dq{\texttt{x-check}} header.
+We identify this with the presence of both the \texttt{bcc} header and the \texttt{x-check} header.
 This is the most potent form of the vulnerability and is found on quite a few websites.
@@
 
-    The second attack is an interesting one, as this has not yet been documented, and provides the ability to inject multiple e-mail addresses into only the \dq{\texttt{To}} field.
-We christened this as \dq{\texttt{To header injection}}.
-In this form of the vulnerability, we are able to simply add addresses to the \dq{\texttt{To}} field of the form with newlines separating the e-mail addresses.
+    The second attack is an interesting one, as this has not yet been documented, and provides the ability to inject multiple e-mail addresses into only the \texttt{To} field.
+We christened this as \texttt{To header injection}.
+In this form of the vulnerability, we are able to simply add addresses to the \texttt{To} field of the form with newlines separating the e-mail addresses.
 Whether this particular form of the vulnerability is found due to the websites in question, or whether this is an implementation issue with a particular language or framework, is unclear.
@@
     Even in this form of the attack, we are still able to extract information that should be private to a given user, and in some of these cases, able to inject enough data to spoof the first few lines of the e-mail message.
-From Table~\ref{tab:analysis}, information leakage using \dq{\texttt{To header injection}} was possible on 142 forms, while spoofing using \dq{\texttt{To header injection}} was possible on 11 forms.
+From Table~\ref{tab:analysis}, information leakage using \texttt{To header injection} was possible on 142 forms, while spoofing using \texttt{To header injection} was possible on 11 forms.
 

### 2016-05-13 Discussion/limits.tex
chap6 added
fixed most emph/quote/texttt issues

@@
-\section[Limitations]{Limitations of the Project}
+\subsection[Limitations]{Limitations of the Project}
 \label{limitations}
@@
 		\item Blogs powered by WordPress/Drupal\\
-        In addition to what was discussed in Section \ref{issues:cms}, we found that certain WordPress `plugins' also prevent the E-Mail Header Injection attack by sanitizing user input on Contact Forms.
+        In addition to what was discussed in Section \ref{issues:cms}, we found that certain WordPress plugins also prevent the E-Mail Header Injection attack by sanitizing user input on Contact Forms.
 Some of these plugins are discussed in the following section.
@@
         \item Websites that are not in English\\
-        Because we are only searching for the words `e-mail', `mail' or `email' within the form, if the website does not use English names for its forms, our system will not be able to find the presence of an e-mail field.
+        Because we are only searching for the words \texttt{e-mail}, \texttt{mail} or \texttt{email} within the form, if the website does not use English names for its forms, our system will not be able to find the presence of an e-mail field.
 An example is shown in Listing~\ref{code:htmlfrench}.
-Here, the French word for `e-mail' --- courrier électronique --- is used, and our system is unable to find the presence of the e-mail form.
+Here, the French word for \texttt{e-mail} --- courrier électronique --- is used, and our system is unable to find the presence of the e-mail form.
 	\end{itemize}

### 2016-05-13 Results/analysis.tex
fixed most emph/quote/texttt issues

@@
 \begin{enumerate}
-	\item E-Mails with the \dq{\texttt{bcc}} header successfully injected\\
+	\item E-Mails with the \texttt{bcc} header successfully injected\\
 	This form of injection was our initial objective and we found 265 such e-mails in our received e-mails.
@@
 
-	\item E-Mails with the \dq{\texttt{to}} header successfully injected\\
-	We discovered an unintended vulnerability which we would like to christen `TO~header injection'.
-These injections reflect the ability to inject any number of e-mail addresses into the \dq{\texttt{to}} field while being unable to inject any other header into the e-mails.
+	\item E-Mails with the \texttt{to} header successfully injected\\
+	We discovered an unintended vulnerability which we would like to christen \texttt{TO~header injection}.
+These injections reflect the ability to inject any number of e-mail addresses into the \texttt{to} field while being unable to inject any other header into the e-mails.
 We attribute this behavior to inconsistent sanitization by the application.
@@
 
-	While not allowing us complete control over the e-mails sent, `TO header injection' makes it possible to append any number of e-mail addresses, thereby enabling us to leak information, and/or perform DoS (Denial of Service) attacks.
+	While not allowing us complete control over the e-mails sent, \texttt{TO header injection} makes it possible to append any number of e-mail addresses, thereby enabling us to leak information, and/or perform DoS (Denial of Service) attacks.
 
-	\item E-Mails with the \dq{\texttt{x-check}} header successfully injected\\
-    The third category of e-mails received were e-mails with the \dq{\texttt{x-check}} header injected. As discussed in Section~\ref{analyze:detect_x_check}, 
-    these let us differentiate between unsuccessful attempts and successful attempts by injecting the additional header, allowing us to check whether headers other than the \dq{\texttt{bcc}} header can be injected into the generated e-mail.
+	\item E-Mails with the \texttt{x-check} header successfully injected\\
+    The third category of e-mails received were e-mails with the \texttt{x-check} header injected. As discussed in Section~\ref{analyze:detect_x_check}, 
+    these let us differentiate between unsuccessful attempts and successful attempts by injecting the additional header, allowing us to check whether headers other than the \texttt{bcc} header can be injected into the generated e-mail.
 \end{enumerate}
@@
 \begin{itemize}
-	\item E-Mail Header Injections with \dq{\texttt{bcc}} and \dq{\texttt{x-check}} headers\\
+	\item E-Mail Header Injections with \texttt{bcc} and \texttt{x-check} headers\\
 	These represent the perfect attack scenario where we are able to inject multiple headers into the e-mails.
-We can see that over 75\% of the received \dq{\texttt{bcc}} header injected e-mails are also susceptible to other header injections.
+We can see that over 75\% of the received \texttt{bcc} header injected e-mails are also susceptible to other header injections.
 
-	\item Both \dq{\texttt{To}} header injections and \dq{\texttt{x-check}} headers \\
-	This combination shows us that in addition to being able to inject into the \dq{\texttt{To}} fields, we are able to inject additional headers into the e-mail.
+	\item Both \texttt{To} header injections and \texttt{x-check} headers \\
+	This combination shows us that in addition to being able to inject into the \texttt{To} fields, we are able to inject additional headers into the e-mail.
 It is not clear what causes this behavior; however, these can be exploited to achieve the same result as a regular E-Mail Header Injection.
 
-	\item \dq{\texttt{x-check}} headers found in `nuser' e-mails\\
-	In addition to analyzing the `maluser' account, we also analyze emails received by the `nuser' account. We explain the presence of these headers in the following paragraph.
+	\item \texttt{x-check} headers found in \texttt{nuser} e-mails\\
+	In addition to analyzing the \texttt{maluser} account, we also analyze emails received by the \texttt{nuser} account. We explain the presence of these headers in the following paragraph.
 
-	\item Unique \dq{\texttt{x-check}} headers found in `nuser' e-mails\\
-	These represent the e-mails with \lstinline|form_ids| that were \emph{not} already found in the `maluser' account.
+	\item Unique \texttt{x-check} headers found in \texttt{nuser} e-mails\\
+	These represent the e-mails with \lstinline|form_ids| that were \emph{not} already found in the \texttt{maluser} account.
 We attribute these e-mails to (probably) having a backend that was built with Python or another language having a similar behavior with respect to constructing headers.
@@
 	This represents the total number of successful injections our system made.
-This includes the E-Mail Header Injections with \dq{\texttt{bcc}} header\,(1), \dq{\texttt{To}} header injections alone\,(3), and Unique \dq{\texttt{x-check}} headers found in `nuser' e-mails\,(7).
+This includes the E-Mail Header Injections with \texttt{bcc} header\,(1), \texttt{To} header injections alone\,(3), and Unique \texttt{x-check} headers found in \texttt{nuser} e-mails\,(7).
 This is the total number of vulnerabilities that were found by our system.

### 2016-05-13 Results/data_analysis.tex
fixed most emph/quote/texttt issues

@@
 		\hline
-		1 & E-Mail Header Injections with `bcc' header & 265\\
+		1 & E-Mail Header Injections with \texttt{bcc} header & 265\\
 		\hline
-		2 & E-Mail Header Injections with `x-check' header & 214\\
+		2 & E-Mail Header Injections with \texttt{x-check} header & 214\\
 		\hline
-		3 & `To header' injections alone & 142\\
+		3 & \texttt{To header} injections alone & 142\\
 		\hline
-		4 & E-Mail Header Injections with `bcc' and `x-check' headers & 188\\
+		4 & E-Mail Header Injections with \texttt{bcc} and \texttt{x-check} headers & 188\\
 		\hline
-		5 & Both `To header' injections and x-check headers &
+		5 & Both \texttt{To header} injections and x-check headers &
 		11\\
 		\hline
-		6 & `x-check' headers found in `nuser' e-mails & 56\\
+		6 & \texttt{x-check} headers found in \texttt{nuser} e-mails & 56\\
 		\hline
-		7 & Unique `x-check' headers found in `nuser' e-mails & 26\\
+		7 & Unique \texttt{x-check} headers found in \texttt{nuser} e-mails & 26\\
 		\hline

### 2016-05-13 System/assumptions.tex
chap3 added
fixed most emph/quote/texttt issues

@@
-\section{Assumptions}
+\subsection{Assumptions}
 We made certain assumptions while building the system. This section describes the assumptions and explores to what extent these hold true:
@@
 
-	\item \textbf{Injection of \dq{\texttt{bcc}} indicates the existence of E-Mail Header Injection Vulnerability} \\
-	We assume that the ability to inject a \dq{\texttt{bcc}} header field is proof that the E-Mail Header Injection vulnerability exists in the application.
+	\item \textbf{Injection of \texttt{bcc} indicates the existence of E-Mail Header Injection Vulnerability} \\
+	We assume that the ability to inject a \texttt{bcc} header field is proof that the E-Mail Header Injection vulnerability exists in the application.
 We do not inject any additional payloads that can modify the subject, message body, etc.\ as this analysis is designed to be as benign as possible.

### 2016-05-13 System/components.tex
fixed most emph/quote/texttt issues

@@
 
-The E-Mail Field Checker searches for the words `e-mail', `mail' or `email' within the form, instead of an explicit e-mail field (e.g.,\ \colorbox{lightgray}{\lstinline{<input type="email">}}).
-This is by design, taking into account a very common design pattern used by web developers, where they may have a text field with an \dq{\texttt{id}} or \dq{\texttt{name}} set to `email', instead of an actual e-mail field, for purposes of backward compatibility with older browsers.
+The E-Mail Field Checker searches for the words \texttt{e-mail}, \texttt{mail} or \texttt{email} within the form, instead of an explicit e-mail field (e.g.,\ \colorbox{lightgray}{\lstinline{<input type="email">}}).
+This is by design, taking into account a very common design pattern used by web developers, where they may have a text field with an \texttt{id} or \texttt{name} set to \texttt{email}, instead of an actual e-mail field, for purposes of backward compatibility with older browsers.
 
-Compared to searching for explicit e-mail fields, by searching for the presence of the words `e-mail', `mail' or `email' in the form, we are assured very few false negatives.
-This is because our system is bound to find e-mail fields with their \dq{\texttt{type}}, \dq{\texttt{name}}, or \dq{\texttt{id}} set to one of these words.
+Compared to searching for explicit e-mail fields, by searching for the presence of the words \texttt{e-mail}, \texttt{mail} or \texttt{email} in the form, we are assured very few false negatives.
+This is because our system is bound to find e-mail fields with their \texttt{type}, \texttt{name}, or \texttt{id} set to one of these words.
 The system is also substantially faster as we do not have to parse the individual form fields at this point in the pipeline.
@@
 \begin{itemize}
-	\item Retrieve the newly inserted forms in the `\lstinline{email_forms}' table, checking to ensure no duplication occurs before the fuzzing stage.
-	\item Reconstruct each form, using the data stored in the `\lstinline{form}' table, complete with input fields and their values.
-	\item Construct the URL for the `action' attribute of the form so that we can send the HTTP request to the correct URL. 
+	\item Retrieve the newly inserted forms in the \texttt{email\_forms} table, checking to ensure no duplication occurs before the fuzzing stage.
+	\item Reconstruct each form, using the data stored in the \texttt{form} table, complete with input fields and their values.
+	\item Construct the URL for the \texttt{action} attribute of the form so that we can send the HTTP request to the correct URL. 
 \end{itemize}
@@
 \label{Comp:Fuzzer:nmp}
-The regular or non-malicious payload is a straight forward E-Mail address of the format -- `reguser(xxxx)@example.com', where `xxxx' is replaced by our internal `\lstinline{form_id}', to create a one-to-one mapping of the payloads to the forms, and `example.com' is replaced by the required domain.
-In our case, this domain was `wackopicko.com'.
+The regular or non-malicious payload is a straight forward E-Mail address of the format -- \texttt{reguser(xxxx)@example.com}, where \texttt{xxxx} is replaced by our internal \texttt{form\_id}, to create a one-to-one mapping of the payloads to the forms, and \texttt{example.com} is replaced by the required domain.
+In our case, this domain was \texttt{wackopicko.com}.
 This non-malicious payload allows us to check whether we can inject data into a form and whether we can overcome the `anti-bot' measures on the given website, without attempting to fuzz the website.
@@
 \label{Comp:Fuzzer:mp}
-In the malicious payload scenario, we inject the fields with the \dq{\texttt{bcc}} (blind carbon copy) element.
-If the vulnerability is present, this will cause the server to send a copy of the e-mail to the e-mail address we added as part of the `bcc' field.
+In the malicious payload scenario, we inject the fields with the \texttt{bcc} (blind carbon copy) element.
+If the vulnerability is present, this will cause the server to send a copy of the e-mail to the e-mail address we added as part of the \texttt{bcc} field.
 
-We consider a special case: the addition of a \dq{\texttt{x-check:in}} header field to the payloads. This is due to Python's exhibited behavior when attaching
+We consider a special case: the addition of a \texttt{x-check:in} header field to the payloads. This is due to Python's exhibited behavior when attaching
 headers.
 Instead of overwriting a header if it is already present, it ignores duplicate headers.
-So, in case the \dq{\texttt{bcc}} field is already present as part of the headers, our injected \dq{\texttt{bcc}} header would be ignored.
+So, in case the \texttt{bcc} field is already present as part of the headers, our injected \texttt{bcc} header would be ignored.
 To overcome this, we need to inject a new header that is not likely to be generated by the web application.
-Hence, we inject our own \dq{\texttt{x-check:in}} header to ensure we can get results if the injection was successful.
+Hence, we inject our own \texttt{x-check:in} header to ensure we can get results if the injection was successful.
 
@@
 	%inside the lstinline, we need to use \\ for \textbackslash
-	\colorbox{lightgray}{\lstinline{nuser(xxxx)@wackopicko.com\\nbcc:maluser(xxxx)@wackopicko.com}} - This is the most minimal payload, it injects a `newline' character followed by the `bcc' field.
-	\item \colorbox{lightgray}{\lstinline{nuser(xxxx)@wackopicko.com\\r\\nbcc:maluser(xxxx)@wackopicko.com}} - This payload is added for purposes of cross-platform fuzzing: `\textbackslash{}r\textbackslash{}n' is the `Carriage Return - New Line (CRLF)' used on Windows systems.
-	\item \colorbox{lightgray}{\lstinline{nuser(xxxx)@wackopicko.com\\nbcc:maluser(xxxx)@wackopicko.com\\nx-check:in}} - As discussed above, the addition of the \dq{\texttt{x-check:in}} header is to inject Python based websites.
-	\item \colorbox{lightgray}{\lstinline{nuser(xxxx)@wackopicko.com\\r\\nbcc:maluser(xxxx)@wackopicko.com\\r\\nx-check:in}} - Same as the previous payload, but containing the additional `\textbackslash{}r' for Windows compatibility.
+	\colorbox{lightgray}{\lstinline{nuser(xxxx)@wackopicko.com\\nbcc:maluser(xxxx)@wackopicko.com}} - This is the most minimal payload, it injects a `newline' character followed by the \texttt{bcc} field.
+	\item \colorbox{lightgray}{\lstinline{nuser(xxxx)@wackopicko.com\\r\\nbcc:maluser(xxxx)@wackopicko.com}} - This payload is added for purposes of cross-platform fuzzing: \texttt{\textbackslash{}r\textbackslash{}n} is the `Carriage Return - New Line (CRLF)' used on Windows systems.
+	\item \colorbox{lightgray}{\lstinline{nuser(xxxx)@wackopicko.com\\nbcc:maluser(xxxx)@wackopicko.com\\nx-check:in}} - As discussed above, the addition of the \texttt{x-check:in} header is to inject Python based websites.
+	\item \colorbox{lightgray}{\lstinline{nuser(xxxx)@wackopicko.com\\r\\nbcc:maluser(xxxx)@wackopicko.com\\r\\nx-check:in}} - Same as the previous payload, but containing the additional \texttt{\textbackslash{}r} for Windows compatibility.
 
 \end{enumerate}
-The `xxxx' in all of the payloads is replaced by our internal `\lstinline{form_id}', so as to create a one-to-one mapping of the payloads to the forms.
+The \texttt{xxxx} in all of the payloads is replaced by our internal \texttt{form\_id}, so as to create a one-to-one mapping of the payloads to the forms.
 The coverage provided by each payload is shown in Table~\ref{tab:payloadcov}.\\
@@
 \paragraph{Analyzing regular e-mail}
-`Regular e-mail' refers to the e-mails received by the \colorbox{lightgray}{\lstinline{reguser(xxxx)@wackopicko.com}} --- where `xxxx' is our internal `\lstinline{form_id}' --- that were sent due to injecting the `regular or non-malicious' payload (discussed in Section~\ref{Comp:Fuzzer:nmp}).
+`Regular e-mail' refers to the e-mails received by the \colorbox{lightgray}{\lstinline{reguser(xxxx)@wackopicko.com}} --- where \texttt{xxxx} is our internal \texttt{form\_id} --- that were sent due to injecting the `regular or non-malicious' payload (discussed in Section~\ref{Comp:Fuzzer:nmp}).
 The objective of the analysis on this e-mail is identify if the input fields that we injected with data appear on the resulting e-mail, and if so, which fields appear where.
@@
 If they do, we add them to the list of fields that can potentially result in an E-Mail Header Injection for the given e-mail.
-we then pass on this information back to the Fuzzer pipeline, along with the `\lstinline{form_id}', so that the Fuzzer can now inject the malicious payloads into the same form.
+we then pass on this information back to the Fuzzer pipeline, along with the \texttt{form\_id}, so that the Fuzzer can now inject the malicious payloads into the same form.
 
@@
 \paragraph{Detecting injected bcc headers}
-As discussed in the payloads section (\ref{Comp:Fuzzer:mp}), the payloads were crafted in such a way that the e-mails received by `maluser' account directly indicate the presence of the injected `bcc' field.
+As discussed in the payloads section (\ref{Comp:Fuzzer:mp}), the payloads were crafted in such a way that the e-mails received by \texttt{maluser} account directly indicate the presence of the injected \texttt{bcc} field.
 Thus, we simply parse the E-Mails and store them in the Database.
@@
 \paragraph{Detecting injected x-check headers}
-E-Mails not received by the `maluser' account but by the `nuser' account constitute a special category of e-mails.
+E-Mails not received by the \texttt{maluser} account but by the \texttt{nuser} account constitute a special category of e-mails.
 These e-mails could have been generated due to two reasons:
 \begin{enumerate}
-	\item The websites performed some sanitization routines and stripped out the \dq{\texttt{bcc}} part of the payload, thereby sending e-mails only to the `nuser' account.
+	\item The websites performed some sanitization routines and stripped out the \texttt{bcc} part of the payload, thereby sending e-mails only to the \texttt{nuser} account.
 These e-mails then act as proof that the vulnerability was not found on the given website.
-	\item A more conducive scenario is when the \dq{\texttt{bcc}} header was ignored for some reason, e.g.\ Python's default behavior when it encounters duplicate headers.
-In this case, we check whether the e-mail contains the custom header \dq{\texttt{x-check}}.
+	\item A more conducive scenario is when the \texttt{bcc} header was ignored for some reason, e.g.\ Python's default behavior when it encounters duplicate headers.
+In this case, we check whether the e-mail contains the custom header \texttt{x-check}.
 If it does, then this is a successful exploit of the vulnerability, and we store it in the database.

### 2016-05-13 System/issues.tex
chap3 added
fixed most emph/quote/texttt issues

@@
-\section[Issues]{Design Issues}
+\subsection[Issues]{Design Issues}
 \label{sys:issues}
@@
 	\item \label{issues:fpr}False Positive rate for the E-Mail Field Checker\\
-	As discussed in Section \ref{Comp:EMFC}, we only search for the words `email', `mail' or `e-mail' (case insensitive) inside the forms to detect the presence of e-mail fields, instead of searching for an \colorbox{lightgray}{\lstinline{<input type = email>}}.
+	As discussed in Section \ref{Comp:EMFC}, we only search for the words \texttt{email}, \texttt{mail} or \texttt{e-mail} (case insensitive) inside the forms to detect the presence of e-mail fields, instead of searching for an \colorbox{lightgray}{\lstinline{<input type = email>}}.
 This might result in a false positive in certain forms, like the one shown in Listing.
@@
 
-	The word `E-Mail' on Line 2 will result in our system classifying this form as a potential e-mail form, while it clearly is not.
-However, as we will see, this is not really a significant issue, as despite being added to the \lstinline{`email_forms'} table, this form will never be injected in the `fuzzer' due to the absence of the appropriate input field in the form.
+	The word \texttt{E-Mail} on Line 2 will result in our system classifying this form as a potential e-mail form, while it clearly is not.
+However, as we will see, this is not really a significant issue, as despite being added to the \texttt{email\_forms} table, this form will never be injected in the `fuzzer' due to the absence of the appropriate input field in the form.
 We chose to go with this design, as it allows us to detect almost every form that provides the capability to send or receive e-mail.
@@
 	\item URL Construction\\
-	The multiple ways in which a URL is specified (i.e.\ Relative and Absolute URLs) complicates the construction of the URL from the `action' attribute of the form.
-As an example, the following URLs are all equivalent (as parsed by a browser, assuming we are in the path `www.website.com'):
+	The multiple ways in which a URL is specified (i.e.\ Relative and Absolute URLs) complicates the construction of the URL from the \texttt{action} attribute of the form.
+As an example, the following URLs are all equivalent (as parsed by a browser, assuming we are in the path \texttt{www.website.com}):
 
@@
 		\item \colorbox{lightgray}{\lstinline{action=#}}
-		\item `action' is completely omitted
+		\item \texttt{action} is completely omitted
 	\end{itemize}
 	Also, relative URLs pose another problem.
-If the URL of the form page ends with `/' and the `action' specifies a path starting with `/' (illustrated in Listing \ref{issues:url}), we would need to strip one of the two slashes.
+If the URL of the form page ends with `/' and the \texttt{action} specifies a path starting with `/' (illustrated in Listing \ref{issues:url}), we would need to strip one of the two slashes.
 This increases the overall complexity of our URL generator, as we have to account for all these possibilities.
@@
 	The approach that we have selected --- Black-box testing --- is highly beneficial as explained in Section \ref{sys:appr}.
-However, it also has a drawback in that we cannot verify whether the reported vulnerability exists in the source code or is a feature of the website (e.g., the website allows users to send bulk e-mail, adding as many \dq{\texttt{cc}} or \dq{\texttt{bcc}} headers).
+However, it also has a drawback in that we cannot verify whether the reported vulnerability exists in the source code or is a feature of the website (e.g., the website allows users to send bulk e-mail, adding as many \texttt{cc} or \texttt{bcc} headers).
 We have to manually e-mail the developers to get this feedback.
@@
 	As we are generating multiple payloads for each form, and the received e-mail may not contain the name of the domain from which we received the e-mail, it is difficult to map the response e-mails to the right requests.
-We instead use the `\lstinline{form_id}' as part of the payload to map responses to requests accurately.
+We instead use the \texttt{form\_id} as part of the payload to map responses to requests accurately.
 

### 2016-05-13 System/proof_of_concept.tex
fixed most emph/quote/texttt issues

@@
 The e-mail sent due to injecting this payload (as captured by MailCatcher) is shown in Figure~\ref{fig:mailcatcherruby}.
-It can be seen that the headers have been added to the resulting e-mail, and we have successfully managed to overwrite the \dq{\texttt{Subject}} field with our message, `hello'.
+It can be seen that the headers have been added to the resulting e-mail, and we have successfully managed to overwrite the \texttt{Subject} field with our message, `hello'.
 
 A similar injection example for PHP is shown in Figure~\ref{fig:postmanphp} and the corresponding e-mail caught by MailCatcher is shown in Figure~\ref{fig:mailcatcherphp}.
-The astute reader might have noticed that in the given examples we have used `\%0a' to separate the headers, while in Section~\ref{Comp:Fuzzer:mp}, we had used `\textbackslash{}n'.
+The astute reader might have noticed that in the given examples we have used \texttt{\%0a} to separate the headers, while in Section~\ref{Comp:Fuzzer:mp}, we had used \texttt{\textbackslash{}n}.
 This is due to URL encoding \cite{rfc1738}, wherein special characters in th URL are `encoded' or `escaped' with their ASCII equivalent.

### 2016-05-13 conclusion.tex
fixed most emph/quote/texttt issues

@@
 
-We hope that our work sheds light on the prevalence of this vulnerability and that it ensures that the implementation of the `mail' function in popular languages is fixed to differentiate between User-supplied headers, and headers that are legitimately added by the application, and that the RFC's are updated to be more stringent and make it less ambiguous for future implementations.
+We hope that our work sheds light on the prevalence of this vulnerability and that it ensures that the implementation of the \texttt{mail} function in popular languages is fixed to differentiate between User-supplied headers, and headers that are legitimately added by the application, and that the RFC's are updated to be more stringent and make it less ambiguous for future implementations.

### 2016-05-13 data_analysis.tex
fixed most emph/quote/texttt issues

@@
 		\hline
-		1 & E-Mail Header Injections with `bcc' header & 180\\
+		1 & E-Mail Header Injections with \texttt{bcc} header & 180\\
 		\hline
-		2 & E-Mail Header Injections with `x-check' header & 153\\
+		2 & E-Mail Header Injections with \texttt{x-check} header & 153\\
 		\hline
-		3 & `To header' injections alone & 83\\
+		3 & \texttt{To header} injections alone & 83\\
 		\hline
-		4 & E-Mail Header Injections with `bcc' and `x-check' headers & 136\\
+		4 & E-Mail Header Injections with \texttt{bcc} and \texttt{x-check} headers & 136\\
 		\hline
-		5 & Both `To header' injections and x-check headers & 9\\
+		5 & Both \texttt{To header} injections and x-check headers & 9\\
 		\hline
-		6 & `x-check' headers found in `nuser' e-mails & 40\\
+		6 & \texttt{x-check} headers found in \texttt{nuser} e-mails & 40\\
 		\hline
-		7 & Unique `x-check' headers found in `nuser' e-mails & 16\\
+		7 & Unique \texttt{x-check} headers found in \texttt{nuser} e-mails & 16\\
 		\hline

### 2016-05-13 introduction.tex
fixed most emph/quote/texttt issues

@@
 E-Mail Header Injection can be considered as the e-mail equivalent of HTTP Header Injection vulnerability \cite{wiki:HTTP_headerinjection}.
-The vulnerability exists in the reference implementation of the built-in \dq{\texttt{mail}} functionality in popular languages like PHP, Java, Python, and Ruby.
+The vulnerability exists in the reference implementation of the built-in \texttt{mail} functionality in popular languages like PHP, Java, Python, and Ruby.
 With the proper injection string, this vulnerability can be exploited to inject additional headers and/or modify existing headers in an e-mail message --- with the potential to alter the contents of the e-mail message --- while still appearing to be from a legitimate source.

### 2016-05-13 rel_work.tex
chap7 added
fixed most emph/quote/texttt issues

@@
-\chapter{Related Work}
+\section{Related Work}
 
@@
 The attack described by Terada \cite{Terada2015} is one that attacks the underlying SMTP mail servers by injecting SMTP commands (which are closely related to E-Mail Headers and usually have a one-to-one mapping, e.g.
-`To' e-mail header has a corresponding `To' SMTP header) to exploit the SMTP server's pipelining mechanism.
-The paper also describes proof-of-concept attacks against certain mailing libraries like `Ruby Mail' and `JavaMail'.
+\texttt{To} e-mail header has a corresponding \texttt{To} SMTP header) to exploit the SMTP server's pipelining mechanism.
+The paper also describes proof-of-concept attacks against certain mailing libraries like \texttt{Ruby Mail} and \texttt{JavaMail}.
 This attack, although trying to achieve a similar result, is distinctly different from ours.
@@
 
-Another blog post written by user Voxel@Night on Vexatious Tendencies \cite{Tendencies2014}, recounts an actual attack against a WordPress plugin, `Contact Form', with a proof of concept\footnotemark.
+Another blog post written by user Voxel@Night on Vexatious Tendencies \cite{Tendencies2014}, recounts an actual attack against a WordPress plugin, \texttt{Contact Form}, with a proof of concept\footnotemark.
 It also showcases the vulnerable code in the plugin that causes this vulnerability to be present.
@@
 Our injected payloads do not contain any special characters other than the newline characters and thus cannot cause any unintended consequences.
-Also, since we are only injecting a payload with the `bcc' header, the underlying mail servers should not be affected by the additional load.
+Also, since we are only injecting a payload with the \texttt{bcc} header, the underlying mail servers should not be affected by the additional load.
 Our work serves to not only prove the existence of the vulnerability on the World Wide Web but to quantify it.
-
-%The next and final chapter starts by outlining our contributions and closes with concluding remarks about the project.

### 2016-05-13 Background/lang_aff.tex
slight formatting changes done
condensing pocs

@@
-\section{Languages Affected}
+\subsection{Languages Affected}
 \label{languages}
@@
 
-\subsubsection{PHP} 
-PHP was one of the first languages found to have this vulnerability in its implementation of the \emph{mail()} function.
+\begin{itemize}
+\item{\textbf{PHP}} - PHP was one of the first languages found to have this vulnerability in its implementation of the \emph{mail()} function.
 The early finding of this vulnerability can be attributed in part to the success and popularity of the language for creating web pages.
@@
 
-PHP's low barrier to entry and lack of developer education about the existence of this vulnerability have contributed to the vulnerability continuing to exist in the language.
 After 13 further iterations of the language since the 4.0 release (the current version is 7.1), the \emph{mail()} function is yet to be fixed after 15 years.
@@
 
-\subsubsection{Python} 
+\item{\textbf{Python}} -
 A bug was filed about the vulnerability in Python's implementation of the \emph{email.header} library and its header parsing functions allowing newlines in early 2009, which was followed up with a partial patch in early 2011.
@@
 
-\subsubsection{Java} 
+\item{\textbf{Java}} -
 Java has a bug report about E-Mail Header Injection filed against its JavaMail API.
@@
 
-\subsubsection{Ruby}
+\item{\textbf{Ruby}} -
 From our preliminary testing, Ruby's built-in Net::SMTP library has this vulnerability. This is not documented on the library's homepage.
-A working code sample of the vulnerability, written in Ruby 2.0.0 (the latest stable version at the time of writing), is shown in Listing~\ref{code:rubyemi}.
+%A working code sample of the vulnerability, written in Ruby 2.0.0 (the latest stable version at the time of writing), is shown in Listing~\ref{code:rubyemi}.
 
-\input{Background/ruby.tex}
+%\input{Background/ruby.tex}
+
+\end{itemize}

### 2016-05-13 Background/lang_aff.tex
fixing emph

@@
 \begin{itemize}
-\item{\textbf{PHP}} - PHP was one of the first languages found to have this vulnerability in its implementation of the \emph{mail()} function.
+\item{\textbf{PHP}} - PHP was one of the first languages found to have this vulnerability in its implementation of the \texttt{mail()} function.
 The early finding of this vulnerability can be attributed in part to the success and popularity of the language for creating web pages.
@@
 
-After 13 further iterations of the language since the 4.0 release (the current version is 7.1), the \emph{mail()} function is yet to be fixed after 15 years.
-However, it is specified in the PHP documentation \cite{PHPDocs} that the \emph{mail()} function does not protect against this vulnerability.
+After 13 further iterations of the language since the 4.0 release (the current version is 7.1), the \texttt{mail()} function is yet to be fixed after 15 years.
+However, it is specified in the PHP documentation \cite{PHPDocs} that the \texttt{mail()} function does not protect against this vulnerability.
 A working code sample of the vulnerability, written in PHP~5.6 (latest well-supported version), is shown in  Listing~\ref{code:phpemi}.
@@
 \item{\textbf{Python}} -
-A bug was filed about the vulnerability in Python's implementation of the \emph{email.header} library and its header parsing functions allowing newlines in early 2009, which was followed up with a partial patch in early 2011.
+A bug was filed about the vulnerability in Python's implementation of the \texttt{email.header} library and its header parsing functions allowing newlines in early 2009, which was followed up with a partial patch in early 2011.
 
-Unfortunately, the bug fix was only for the \emph{email.header} package, and thus is still prevalent in other frequently used packages such as \emph{email.parser}, where both the classic \emph{Parser()} and the newer \emph{FeedParser()} exhibit the vulnerability even in the latest versions - \emph{2.7.11} and \emph{3.5}.
+Unfortunately, the bug fix was only for the \texttt{email.header} package, and thus is still prevalent in other frequently used packages such as \texttt{email.parser}, where both the classic \texttt{Parser()} and the newer \texttt{FeedParser()} exhibit the vulnerability even in the latest versions - \texttt{2.7.11} and \texttt{3.5}.
 The bug fix was also not backported to older versions of Python.

### 2016-05-13 Background/lang_aff.tex
prelim edit chap2

@@
 \begin{itemize}
-\item{\textbf{PHP}} - PHP was one of the first languages found to have this vulnerability in its implementation of the \texttt{mail()} function.
+\item{\textbf{PHP}} - PHP was one of the first languages found to have this vulnerability in its implementation of the \texttt{mail()} function at the time of release of PHP~4.0.
 The early finding of this vulnerability can be attributed in part to the success and popularity of the language for creating web pages.

### 2016-05-14 System/approach.tex
adding chap3
chap3 prelim edit

@@
-\section[Approach]{Our Approach to measure prevalence of E-Mail Header Injection}
+\subsection{Approach}
 \label{sys:appr}
@@
 Black-box testing allows our system to detect E-Mail Header Injection vulnerabilities in any server-side language (not simply those we identified in Section~\ref{languages}).
-A high level logical overview of our system is presented in Figure~\ref{fig:overall}.
+The overall architecture of our system is presented in Figure~\ref{fig:overall}.
 The components shown in Figure~\ref{fig:overall} can be more broadly categorized into different modules, as discussed in the following section.
 
-\begin{figure}
+\begin{figure*}
 	\centering
-	\includegraphics[width=14cm, height=7cm]{System/overall_design}
-	\caption[\titlecap{Overall system architecture - logical overview}]{Overall system architecture - logical overview.}
+	\includegraphics[width=14cm, height=7cm]{overall}
+	\caption{Overall system architecture.}
 	\label{fig:overall}
-\end{figure}
+\end{figure*}

### 2016-05-14 System/components.tex
fixed emph
chap3 prelim edit

@@
 	\item Presence of the \colorbox{lightgray}{\lstinline{<base>}} element in the HTML, as this affects the final URL to which the form is to be submitted.
-	\item Headers associated with the page, such as \emph{referrer}. Once again, these were required to avoid the website from ignoring our system as a bot.
+	\item Headers associated with the page, such as \texttt{referrer}. Once again, these were required to avoid the website from ignoring our system as a bot.
 \end{itemize} 
@@
 The regular or non-malicious payload is a straight forward E-Mail address of the format -- \texttt{reguser(xxxx)@example.com}, where \texttt{xxxx} is replaced by our internal \texttt{form\_id}, to create a one-to-one mapping of the payloads to the forms, and \texttt{example.com} is replaced by the required domain.
-In our case, this domain was \texttt{wackopicko.com}.
 This non-malicious payload allows us to check whether we can inject data into a form and whether we can overcome the `anti-bot' measures on the given website, without attempting to fuzz the website.
@@
 	%inside the lstinline, we need to use \\ for \textbackslash
-	\colorbox{lightgray}{\lstinline{nuser(xxxx)@wackopicko.com\\nbcc:maluser(xxxx)@wackopicko.com}} - This is the most minimal payload, it injects a `newline' character followed by the \texttt{bcc} field.
-	\item \colorbox{lightgray}{\lstinline{nuser(xxxx)@wackopicko.com\\r\\nbcc:maluser(xxxx)@wackopicko.com}} - This payload is added for purposes of cross-platform fuzzing: \texttt{\textbackslash{}r\textbackslash{}n} is the `Carriage Return - New Line (CRLF)' used on Windows systems.
-	\item \colorbox{lightgray}{\lstinline{nuser(xxxx)@wackopicko.com\\nbcc:maluser(xxxx)@wackopicko.com\\nx-check:in}} - As discussed above, the addition of the \texttt{x-check:in} header is to inject Python based websites.
-	\item \colorbox{lightgray}{\lstinline{nuser(xxxx)@wackopicko.com\\r\\nbcc:maluser(xxxx)@wackopicko.com\\r\\nx-check:in}} - Same as the previous payload, but containing the additional \texttt{\textbackslash{}r} for Windows compatibility.
+	\colorbox{lightgray}{\lstinline{nuser(xxxx)@example.com\\nbcc:maluser(xxxx)@example.com}} - This is the most minimal payload, it injects a `newline' character followed by the \texttt{bcc} field.
+	\item \colorbox{lightgray}{\lstinline{nuser(xxxx)@example.com\\r\\nbcc:maluser(xxxx)@example.com}} - This payload is added for purposes of cross-platform fuzzing: \texttt{\textbackslash{}r\textbackslash{}n} is the `Carriage Return - New Line (CRLF)' used on Windows systems.
+	\item \colorbox{lightgray}{\lstinline{nuser(xxxx)@example.com\\nbcc:maluser(xxxx)@example.com\\nx-check:in}} - As discussed above, the addition of the \texttt{x-check:in} header is to inject Python based websites.
+	\item \colorbox{lightgray}{\lstinline{nuser(xxxx)@example.com\\r\\nbcc:maluser(xxxx)@example.com\\r\\nx-check:in}} - Same as the previous payload, but containing the additional \texttt{\textbackslash{}r} for Windows compatibility.
 
@@
 
-\subsubsection{E-Mail Analyzer}
+\subsubsection{Injection Verification}
 \label{Comp:EMA}
-The E-Mail Analyzer checks for the presence of injected data in the received e-mails.
+The Injection Verification module checks for the presence of injected data in the received e-mails.
 This module works on the e-mails received and stored by our Postfix server, and depending on the user who received the e-mail, it performs different functions.
 \paragraph{Analyzing regular e-mail}
-`Regular e-mail' refers to the e-mails received by the \colorbox{lightgray}{\lstinline{reguser(xxxx)@wackopicko.com}} --- where \texttt{xxxx} is our internal \texttt{form\_id} --- that were sent due to injecting the `regular or non-malicious' payload (discussed in Section~\ref{Comp:Fuzzer:nmp}).
+`Regular e-mail' refers to the e-mails received by the \colorbox{lightgray}{\lstinline{reguser(xxxx)@example.com}} --- where \texttt{xxxx} is our internal \texttt{form\_id} --- that were sent due to injecting the `regular or non-malicious' payload (discussed in Section~\ref{Comp:Fuzzer:nmp}).
 The objective of the analysis on this e-mail is identify if the input fields that we injected with data appear on the resulting e-mail, and if so, which fields appear where.
@@
 \paragraph{Analyzing e-mail with payloads}
-The `e-mails with payloads' refer to e-mails received by either the \colorbox{lightgray}{\lstinline{nuser(xxxx)@wackopicko.com}} or \colorbox{lightgray}{\lstinline{maluser(xxxx)@wackopicko.com}} accounts.
+The `e-mails with payloads' refer to e-mails received by either the \colorbox{lightgray}{\lstinline{nuser(xxxx)@example.com}} or \colorbox{lightgray}{\lstinline{maluser(xxxx)@example.com}} accounts.
 These e-mails were received due to injecting the malicious payloads that were discussed in Section.
@@
 \end{enumerate}
-\subsubsection{Database}
-We collect and store as much data as possible at each stage of the pipeline. This is due to the two following reasons:
-\begin{enumerate}
-	\item The data is used to validate our findings.
-	\item The data collected can be used for other research projects in this area.
-\end{enumerate}
-Each table in our database is listed in Table~\ref{tab:dbtf} along with the data it is designed to hold. A schema of the database is shown in Figure~\ref{fig:dbschema}.
-
-\begin{table}[!htbp]
-	\centering
-	\input{System/tables}        
-	\caption[\titlecap{Database - tables}]{The different tables in our database.}
-	\label{tab:dbtf}
-\end{table}
-
-\begin{figure}[!htbp]
-	\centering
-	\includegraphics[width=15cm, height=11cm]{System/dbschema}
-	\caption[\titlecap{Database schema}]{Database schema.}
-	\label{fig:dbschema}
-\end{figure}

### 2016-05-14 System/sys_arch.tex
chap3 added
chap3 prelim edit

@@
-\section{System Architecture}
+\subsection{System Architecture}
 \label{sys:arch}
@@
 \end{enumerate}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=14cm, height=7cm]{System/crawler_design}
-	\caption[\titlecap{System architecture - crawler}]{System architecture - crawler \& form parser.}
-	\label{fig:crawler}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=16cm, height=9cm]{System/fuzzer_design}
-	\caption[\titlecap{System architecture - fuzzer {\&} e-mail analyzer}]{System architecture - fuzzer {\&} e-mail analyzer.}
-	\label{fig:fuzzer}
-\end{figure}

### 2016-05-14 Background/history.tex
fixed citation spaces

@@
 
-E-Mail Header Injection seems to have been first documented over a decade ago, in a late 2004 article on phpsecure.info \cite{Tobozo} accredited to user \lstinline|tobozo@phpsecure.info| describing how this vulnerability existed in the reference implementation of the \texttt{mail()} function in PHP, and how it can be exploited.
-More recently, a blog post by Damon Kohler \cite{DK} and an accompanying wiki article \cite{Injection} describe the attack vector and outline a few defense measures for the same.
+E-Mail Header Injection seems to have been first documented over a decade ago, in a late 2004 article on phpsecure.info~\cite{Tobozo} accredited to user \lstinline|tobozo@phpsecure.info| describing how this vulnerability existed in the reference implementation of the \texttt{mail()} function in PHP, and how it can be exploited.
+More recently, a blog post by Damon Kohler~\cite{DK} and an accompanying wiki article~\cite{Injection} describe the attack vector and outline a few defense measures for the same.
 

### 2016-05-14 Background/impact.tex
condensing pocs
fixed citation spaces

@@
 The impact of the vulnerability can be pretty far-reaching.
-Table~\ref{tab:usage} shows the current server-side language usage statistics on the Web \cite{W3techs}.
+Table~\ref{tab:usage} shows the current server-side language usage statistics on the Web~\cite{W3techs}.
 
@@
 		\hline
-		ASP.NET & 15.8\\
-		\hline
 		Java & 3.1\\
@@
 		Ruby & 0.6\\
-		\hline
-		Perl & 0.5\\
-		\hline
-		JavaScript & 0.2\\
 		\hline
@@
 	\end{tabular}
-	\caption[\titlecap{Language usage statistics}]{Language usage statistics compiled from w3techs \cite{W3techs}.}
+	\caption[\titlecap{Language usage statistics}]{Language usage statistics compiled from w3techs~\cite{W3techs}.}
 	\label{tab:usage}
@@
 	\item Phishing and Spoofing Attacks\\
-    Phishing \cite{wiki:Phishing} (a variation of spoofing \cite{wiki:Spoofing_attack}) refers to an attack where the recipient of an e-mail is made to believe that the e-mail is a legitimate one.
+    Phishing~\cite{wiki:Phishing} (a variation of spoofing~\cite{wiki:Spoofing_attack}) refers to an attack where the recipient of an e-mail is made to believe that the e-mail is a legitimate one.
 The e-mail usually redirects them to a malicious website, which then steals their credentials.

### 2016-05-14 Background/lang_aff.tex
fixed citation spaces

@@
 The early finding of this vulnerability can be attributed in part to the success and popularity of the language for creating web pages.
-According to w3techs \cite{W3techs}, PHP is used by 81.9\% of all the websites in existence, thereby creating the possibility of this vulnerability to be widespread.
+According to w3techs~\cite{W3techs}, PHP is used by 81.9\% of all the websites in existence, thereby creating the possibility of this vulnerability to be widespread.
 
 After 13 further iterations of the language since the 4.0 release (the current version is 7.1), the \texttt{mail()} function is yet to be fixed after 15 years.
-However, it is specified in the PHP documentation \cite{PHPDocs} that the \texttt{mail()} function does not protect against this vulnerability.
+However, it is specified in the PHP documentation~\cite{PHPDocs} that the \texttt{mail()} function does not protect against this vulnerability.
 A working code sample of the vulnerability, written in PHP~5.6 (latest well-supported version), is shown in  Listing~\ref{code:phpemi}.
@@
 Java has a bug report about E-Mail Header Injection filed against its JavaMail API.
-A detailed write-up by Alexandre Herzog \cite{Herzog.2014} is complete with a proof of concept program that exploits the API to inject headers.
+A detailed write-up by Alexandre Herzog~\cite{Herzog.2014} is complete with a proof of concept program that exploits the API to inject headers.
 

### 2016-05-14 Background/pbm_bg.tex
slight formatting changes done
fixed most emph/quote/texttt issues
fixed citation spaces

@@
-\section{Problem Background}
-
 E-Mail Header Injection belongs to a broad class of vulnerabilities known simply as injection attacks.
-However, unlike its more popular siblings, SQL injection \cite{sql1}, \cite{sql0}, \cite{sql2}, Cross-Site Scripting (XSS) \cite{Injection1}, \cite{KleinAmit} or even HTTP Header Injection \cite{sessionride}, relatively little research is available on E-Mail Header Injection.
+However, unlike its more popular siblings, SQL injection~\cite{sql1}, \cite{sql0}, \cite{sql2}, Cross-Site Scripting (XSS) \cite{Injection1}, \cite{KleinAmit} or even HTTP Header Injection~\cite{sessionride}, relatively little research is available on E-Mail Header Injection.
 

### 2016-05-14 Discussion/lessons.tex
fixed citation spaces

@@
     From our results, it is evident that the vulnerability exists in the wild.
-Despite its relatively low occurrence rate compared to the more popular SQL Injection and XSS (Cross-Site Scripting), when we take the total number of websites on the World Wide Web --- 1,018,863,952 according to Internet Live Stats \cite{InternetLiveStats2016} as of early 2016 --- and calculate \successDelta\ percent (the occurrence rate of E-Mail Header Injection vulnerability as found by our system) of that number, we end up with 11,309,390 websites - a pretty significant number.
+Despite its relatively low occurrence rate compared to the more popular SQL Injection and XSS (Cross-Site Scripting), when we take the total number of websites on the World Wide Web --- 1,018,863,952 according to Internet Live Stats~\cite{InternetLiveStats2016} as of early 2016 --- and calculate \successDelta\ percent (the occurrence rate of E-Mail Header Injection vulnerability as found by our system) of that number, we end up with 11,309,390 websites - a pretty significant number.
 We agree that an extrapolation of that kind might not be an accurate measure of the prevalence of the vulnerability.

### 2016-05-14 Discussion/limits.tex
fixed citation spaces

@@
 As CAPTCHAs are designed to be robust, there is no easy way to break them.
-There has been considerable research in this area \cite{captchas2}, \cite{captchas} to name a few and although not impossible to break, it remains out of the scope of this project, and thus, we chose to ignore websites which require CAPTCHA verification.
+There has been considerable research in this area~\cite{captchas2}, \cite{captchas} to name a few and although not impossible to break, it remains out of the scope of this project, and thus, we chose to ignore websites which require CAPTCHA verification.
 		\item JavaScript Apps - Due to the growing emphasis on responsive web applications, more and more single-page web applications are being built purely with JavaScript.

### 2016-05-14 Discussion/mitigation.tex
chap6 added
chap7 added
fixed citation spaces

@@
-\section[Mitigation Strategy]{How to prevent this attack}
+\subsection[Mitigation Strategy]{How to prevent this attack}
 \label{disc:mitigation}
@@
 	\end{table}
-	% changes to be made amrked in sublime
 	\item Use a Content Management System (CMS) \\
@@
 	If neither of the two options above is feasible, due to reasons such as the website being an in-house production, or due to lack of support infrastructure, developers can choose to perform proper input sanitization.
-Sanitization should be done keeping in mind RFC5322 \cite{rfc5322}, and care must be taken to ensure that all edge cases are taken into account.
+Sanitization should be done keeping in mind RFC5322~\cite{rfc5322}, and care must be taken to ensure that all edge cases are taken into account.
 

### 2016-05-14 System/components.tex
fixed citation spaces

@@
 We inject payloads in two different stages, to improve the efficiency, and reduce the total number of HTTP requests we generate.
-This is because making HTTP requests is an expensive process \cite{McGrath2009}, and can be a cause of bottlenecks in a Crawler-Fuzzer system \cite{ShkapenyukTorstenSuel2001}.
+This is because making HTTP requests is an expensive process~\cite{McGrath2009}, and can be a cause of bottlenecks in a Crawler-Fuzzer system~\cite{ShkapenyukTorstenSuel2001}.
 The two different types of payloads we use for fuzzing are:
@@
 This is due to the fact that this involves lesser processing of the contents of the e-mail compared to the previous section.
-\paragraph{Detecting injected bcc headers}
+\paragraph{Detecting injected \texttt{bcc} headers}
 As discussed in the payloads section (\ref{Comp:Fuzzer:mp}), the payloads were crafted in such a way that the e-mails received by \texttt{maluser} account directly indicate the presence of the injected \texttt{bcc} field.
@@
 \label{analyze:detect_x_check}
-\paragraph{Detecting injected x-check headers}
+\paragraph{Detecting injected \texttt{x-check} headers}
 E-Mails not received by the \texttt{maluser} account but by the \texttt{nuser} account constitute a special category of e-mails.

### 2016-05-14 System/issues.tex
fixed citation spaces

@@
     Because our system is fully automated, it is also susceptible to being stopped by `bot-blockers' i.e.\ mechanisms built-in to a website to prevent automated crawls or form submissions.
-Measures like CAPTCHA (Completely Automated Public Turing test to tell Computers and Humans Apart) and hidden form fields are often used to detect bots \cite{captchas3}, \cite{captchas2}.
+Measures like CAPTCHA (Completely Automated Public Turing test to tell Computers and Humans Apart) and hidden form fields are often used to detect bots~\cite{captchas3}, \cite{captchas2}.
 

### 2016-05-14 System/proof_of_concept.tex
fixed citation spaces

@@
-\subsection{Proof of Concept Attacks}
-The previous section (Section~\ref{Arch:Test}) discussed in detail how we verified that our system functions according to our expectations.
+\subsection*{Proof of Concept Attacks}
 This section describes how we validated our expectations.
@@
 The front-end for each of the three applications is shown in Listing~\ref{code:html}.
-The server-side code for the three languages are shown in Listings~\ref{code:phpemi}, \ref{code:pyemi}, and \ref{code:rubyemi}.
+The server-side code for the PHP and Python are shown in Listings~\ref{code:phpemi} and \ref{code:pyemi} respectively.
 
@@
 
-A similar injection example for PHP is shown in Figure~\ref{fig:postmanphp} and the corresponding e-mail caught by MailCatcher is shown in Figure~\ref{fig:mailcatcherphp}.
-The astute reader might have noticed that in the given examples we have used \texttt{\%0a} to separate the headers, while in Section~\ref{Comp:Fuzzer:mp}, we had used \texttt{\textbackslash{}n}.
-This is due to URL encoding \cite{rfc1738}, wherein special characters in th URL are `encoded' or `escaped' with their ASCII equivalent.
+The astute reader might have noticed that in the given example we have used \texttt{\%0a} to separate the headers, while in Section~\ref{Comp:Fuzzer:mp}, we had used \texttt{\textbackslash{}n}.
+This is due to URL encoding~\cite{rfc1738}, wherein special characters in th URL are `encoded' or `escaped' with their ASCII equivalent.
 The reason why we do not have to do this with the payloads our system injects is due to the fact that the Python Requests library that we use to generate the HTTP requests automatically does this encoding for us.
@@
 \end{figure}
-
-\begin{figure}[!htbp]
-	\centering
-	\includegraphics[width=14cm, height=8cm]{System/EMI_Postman_PHP}
-	\caption[\titlecap{Fuzzing a request for the PHP backend}]{Fuzzing a request for the PHP backend, the payload can be seen inside the address bar on top.}
-	\label{fig:postmanphp}
-\end{figure}
-
-\begin{figure}[!htbp]
-	\centering
-	\includegraphics[width=14cm, height=8cm]{System/EMI_Mailcatcher_PHP}
-	\caption[\titlecap{E-Mail header injection proof of concept - PHP}]{E-Mail header injection proof of concept - PHP, we can see that multiple headers (bcc, x-check, subject) have been inserted into the resulting e-mail.}
-	\label{fig:mailcatcherphp}
-\end{figure}

### 2016-05-14 exp_setup.tex
fixed citation spaces

@@
-\section{Evaluation}
-This chapter describes the experimental setup for our project including the servers used, the software and the platforms involved, the languages used, and the task queue system that was used for parallelism.
-We follow this up with our evaluation of the system, with a test suite, and proof of concept examples.
+\section{Implementation}
 
 \input{Experiment/sys_config}
-\input{Experiment/platform}
-\input{Experiment/languages}
-\input{Experiment/celery}
-\input{System/test_plan}
+%\input{Experiment/platform}
+%\input{Experiment/languages}
+%\input{Experiment/celery}
+%\input{System/test_plan}
 \input{System/proof_of_concept}

### 2016-05-14 rel_work.tex
fixed citation spaces

@@
 There are different approaches to finding vulnerabilities in web applications, two of them being Black-Box testing and White-Box testing.
-Our work is based on the black-box testing approach to finding vulnerabilities on websites, and there has been plenty of research that has made use of this methodology \cite{Beizer:1995:BTT:202699}, \cite{Huang}, \cite{kals2006secubat}, \cite{payet13:ears-in-the-wild}, \cite{zanero2005automatic}.
-There has been significant discussion on both the benefits of such an approach \cite{black-box} and its shortcomings \cite{Doupe2012}, \cite{Doupe2010}.
+Our work is based on the black-box testing approach to finding vulnerabilities on websites, and there has been plenty of research that has made use of this methodology~\cite{Beizer:1995:BTT:202699}, \cite{Huang}, \cite{kals2006secubat}, \cite{payet13:ears-in-the-wild}, \cite{zanero2005automatic}.
+There has been significant discussion on both the benefits of such an approach~\cite{black-box} and its shortcomings~\cite{Doupe2012}, \cite{Doupe2010}.
 
 Our work does not intend to act as a vulnerability scanner, but as a means to identify the presence of E-Mail Header Injection vulnerabilities in a given web application.
-In this sense, since we are injecting payloads into the web application, our work is related to other injection based attacks, such as SQL Injection \cite{sql1}, \cite{sql0}, \cite{sql2}, Cross-Site Scripting --- XSS --- \cite{Injection1}, \cite{KleinAmit}, HTTP Header Injection \cite{sessionride}, and is very closely related to Simple Mail Transfer Protocol (SMTP) Injection \cite{Terada2015}.
+In this sense, since we are injecting payloads into the web application, our work is related to other injection based attacks, such as SQL Injection~\cite{sql1}, \cite{sql0}, \cite{sql2}, Cross-Site Scripting --- XSS --- \cite{Injection1}, \cite{KleinAmit}, HTTP Header Injection~\cite{sessionride}, and is very closely related to Simple Mail Transfer Protocol (SMTP) Injection~\cite{Terada2015}.
 
-The attack described by Terada \cite{Terada2015} is one that attacks the underlying SMTP mail servers by injecting SMTP commands (which are closely related to E-Mail Headers and usually have a one-to-one mapping, e.g.
+The attack described by Terada~\cite{Terada2015} is one that attacks the underlying SMTP mail servers by injecting SMTP commands (which are closely related to E-Mail Headers and usually have a one-to-one mapping, e.g.
 \texttt{To} e-mail header has a corresponding \texttt{To} SMTP header) to exploit the SMTP server's pipelining mechanism.
@@
 
-The first documented article dates to over a decade ago; a late 2004 article on phpsecure.info \cite{Tobozo} accredited to user \lstinline|tobozo@phpsecure.info| describing how this vulnerability existed in the reference implementation of the mail function in PHP, and how it can be exploited.
-Following this, we found other blog posts \cite{Calin}, \cite{DK}, \cite{Injection2}, \cite{Nicol}, \cite{Pope}, each describing how to exploit the vulnerability by using newlines to camouflage headers inside user input.
-A wiki entry \cite{Injection} also describes the ways to prevent such an attack.
+The first documented article dates to over a decade ago; a late 2004 article on phpsecure.info~\cite{Tobozo} accredited to user \lstinline|tobozo@phpsecure.info| describing how this vulnerability existed in the reference implementation of the mail function in PHP, and how it can be exploited.
+Following this, we found other blog posts~\cite{Calin}, \cite{DK}, \cite{Injection2}, \cite{Nicol}, \cite{Pope}, each describing how to exploit the vulnerability by using newlines to camouflage headers inside user input.
+A wiki entry~\cite{Injection} also describes the ways to prevent such an attack.
 However, none of these articles have performed these attacks against real-life websites.
 
-Another blog post written by user Voxel@Night on Vexatious Tendencies \cite{Tendencies2014}, recounts an actual attack against a WordPress plugin, \texttt{Contact Form}, with a proof of concept\footnotemark.
+Another blog post written by user Voxel@Night on Vexatious Tendencies~\cite{Tendencies2014}, recounts an actual attack against a WordPress plugin, \texttt{Contact Form}, with a proof of concept\footnotemark.
 It also showcases the vulnerable code in the plugin that causes this vulnerability to be present.
@@
 Neither does it inform the creators of the plug-in to fix the discovered vulnerability.
-\footnotetext{Note that this plugin is used actively on 300,000 websites (according to \cite{BestWebSoft2016}), but is yet to be fixed.}
+\footnotetext{Note that this plugin is used actively on 300,000 websites (according to~\cite{BestWebSoft2016}), but is yet to be fixed.}
 The vulnerability was described briefly by Stuttard and Pinto in their book, ``\emph{The Web Application Hacker's Handbook: Discovering and Exploiting Security Flaws}'' \cite{stuttard2011web}.

### 2016-05-14 System/components.tex
fixed stupid texttt linebreak problem

@@
 	\item
-	%inside the lstinline, we need to use \\ for \textbackslash
-	\colorbox{lightgray}{\lstinline{nuser(xxxx)@example.com\\nbcc:maluser(xxxx)@example.com}} - This is the most minimal payload, it injects a `newline' character followed by the \texttt{bcc} field.
-	\item \colorbox{lightgray}{\lstinline{nuser(xxxx)@example.com\\r\\nbcc:maluser(xxxx)@example.com}} - This payload is added for purposes of cross-platform fuzzing: \texttt{\textbackslash{}r\textbackslash{}n} is the `Carriage Return - New Line (CRLF)' used on Windows systems.
-	\item \colorbox{lightgray}{\lstinline{nuser(xxxx)@example.com\\nbcc:maluser(xxxx)@example.com\\nx-check:in}} - As discussed above, the addition of the \texttt{x-check:in} header is to inject Python based websites.
-	\item \colorbox{lightgray}{\lstinline{nuser(xxxx)@example.com\\r\\nbcc:maluser(xxxx)@example.com\\r\\nx-check:in}} - Same as the previous payload, but containing the additional \texttt{\textbackslash{}r} for Windows compatibility.
+	\texttt{nuser(xxxx)@example.com\textbackslash{}n\\bcc:maluser(xxxx)@example.com}
+
+	This is the most minimal payload, it injects a `newline' character followed by the \texttt{bcc} field.
+
+	\item \texttt{nuser(xxxx)@example.com\textbackslash{}r\textbackslash{}n\\bcc:maluser(xxxx)@example.com}
+
+	This payload is added for purposes of cross-platform fuzzing: \texttt{\textbackslash{}r\textbackslash{}n} is the `Carriage Return - New Line (CRLF)' used on Windows systems.
+
+	\item \texttt{nuser(xxxx)@example.com\textbackslash{}n\\bcc:maluser(xxxx)@example.com\textbackslash{}nx-check:in}
+
+	As discussed above, the addition of the \texttt{x-check:in} header is to inject Python based websites.
+
+	\item \texttt{nuser(xxxx)@example.com\textbackslash{}r\textbackslash{}n\\bcc:maluser(xxxx)@example.com\textbackslash{}r\textbackslash{}nx-check:in}
+
+	Same as the previous payload, but containing the additional \texttt{\textbackslash{}r} for Windows compatibility.
 
@@
 \paragraph{Analyzing regular e-mail}
+\sloppy
 `Regular e-mail' refers to the e-mails received by the \colorbox{lightgray}{\lstinline{reguser(xxxx)@example.com}} --- where \texttt{xxxx} is our internal \texttt{form\_id} --- that were sent due to injecting the `regular or non-malicious' payload (discussed in Section~\ref{Comp:Fuzzer:nmp}).

### 2016-05-14 paper.tex
prelim edit chap1
fixed stupid texttt linebreak problem

@@
 	backgroundcolor=\color{lightgray},
-	basicstyle=\footnotesize,
+	basicstyle=\small,
 	breaklines=true, 
@@
 	%
-	% ACM needs 'a single self-contained file'!
-	%
-	%APPENDICES are optional
 	%\balancecolumns
-
 \end{document}

### 2016-05-14 Discussion/mitigation.tex
HUGE changes

@@
 			\hline
-			PHP & {{PEAR Mail\tablefootnote{PEAR Mail Website: https://pear.php.net/package/Mail}, PHPMailer\tablefootnote{PHPMailer Website: https://github.com/PHPMailer/PHPMailer}, Swiftmailer\tablefootnote{Swiftmailer Website: http://swiftmailer.org/}}}\\
+			PHP & {{PEAR Mail\tablefootnote{PEAR Mail Website: https://pear.php.net/package/Mail}, PHPMailer\tablefootnote{PHPMailer Website:\\ https://github.com/PHPMailer/PHPMailer}, Swiftmailer\tablefootnote{Swiftmailer Website: http://swiftmailer.org/}}}\\
 			\hline

### 2016-05-14 Results/analysis.tex
HUGE changes

@@
-\subsection[Analysis of Data]{Our Analysis of the received e-mail Data}
+\subsection{Analysis of the received e-mail data}
 During our analysis of the received e-mails, we found that the e-mails that we received belonged to one of three broad categories:

### 2016-05-14 Results/data_analysis.tex
HUGE changes

--- 2016-04-27 Results/data_analysis.tex
@@
-\begin{table}[!htbp]
+\begin{table*}[!htbp]
 	\centering
-	\begin{tabular}{|c|l|c|}
+	\begin{tabular}{|l|c|}
 		\hline
-		\multicolumn{1}{|c|}{\textbf{S.No}} &
-		\multicolumn{1}{c|}{\textbf{Type of Injection}} &
+		\multicolumn{1}{|c|}{\textbf{Type of Injection}} &
 		\multicolumn{1}{p{3cm}|}{\centering \textbf{No. of e-mails received}}\\
 		\hline
-		1 & E-Mail Header Injections with `bcc' header & 265\\
+		E-Mail Header Injections with \texttt{bcc} header & 304\\
 		\hline
-		2 & E-Mail Header Injections with `x-check' header & 214\\
+		E-Mail Header Injections with \texttt{x-check} header & 252\\
 		\hline
-		3 & `To header' injections alone & 142\\
+		\texttt{To header} injections alone & 157\\
 		\hline
-		4 & E-Mail Header Injections with `bcc' and `x-check' headers & 188\\
+		E-Mail Header Injections with \texttt{bcc} and \texttt{x-check} headers & 216\\
 		\hline
-		5 & Both `To header' injections and x-check headers &
-		11\\
+		Both \texttt{To header} injections and x-check headers &
+		12\\
 		\hline
-		6 & `x-check' headers found in `nuser' e-mails & 56\\
+		\texttt{x-check} headers found in \texttt{nuser} e-mails & 67\\
 		\hline
-		7 & Unique `x-check' headers found in `nuser' e-mails & 26\\
+		Unique \texttt{x-check} headers found in \texttt{nuser} e-mails & 35\\
 		\hline
-		8 & Total successful injections (1 + 3 + 7) & 433\\
+		Total successful injections (1 + 3 + 7) & 496\\
 
@@
 	\label{tab:analysis}
-\end{table}
+\end{table*}

### 2016-05-14 Results/disclosure.tex
HUGE changes

\subsection{Responsible Disclosure of Discovered Vulnerabilities}
After we had discovered E-Mail Header Injection vulnerability on a particular website, we e-mailed the developers of these vulnerable websites disclosing the pages that contained the vulnerability, along with a brief description of the vulnerability.
We chose to e-mail the following mailboxes, following the rules specified in RFC~2142~\cite{rfc2142}:
\begin{itemize}
	\item security@domain.com - Used for Security bulletins or queries.
	\item admin@domain.com - Used to contact the administrator of a website.
	\item webmaster@domain.com - Synonym for administrator, same functionality as admin.
\end{itemize}

Out of the \domains\ vulnerable domains found, only 108 websites had the mailboxes specified above set-up to receive e-mails. For the remaining domains, we used the \dq{\texttt{whois}}~\cite{whois} data to get the contact details of the owner, and then e-mailed them with the same disclosure data.

We received 13 developer responses, confirming 9 discovered vulnerabilities. Two of the developers fixed the vulnerability on their website.

From our research, it is clear that E-Mail Header Injection is quite widespread as a vulnerability, appearing on \successDelta\ of forms that we were able to perform automated attacks on. This value acts as a \dq{lower bound} for E-Mail Header Injection vulnerability, and can quite easily be much more if the attacks were of a more concentrated nature, crafted for the individual websites and less automated. We discuss this possibility, and other concepts such as limitations and methods for mitigation of the vulnerability in the following section.

### 2016-05-14 Results/pipeline.tex
chap5 added
HUGE changes

@@
-\section[The Pipeline]{Understanding the pipeline}
+\subsection[The Pipeline]{Understanding the pipeline}
 This section serves to represent our pipeline quantitatively and graphically.
@@
 
-\begin{figure}
-	\centering
-	\includegraphics[width=16cm, height=9cm]{Results/emailheaderpipeline}
-	\caption[\titlecap{E-Mail header injection Pipeline}]{Pipeline - shows the quantity of data gathered at each stage of the pipeline.}
-	\label{fig:pipeline}
-\end{figure}
-
-Thus, our pipeline can be visualized as a funnel (shown in Figure~\ref{fig:pipeline}), where the quantity decreases until it reaches the end product.
-
 From our research, it is clear that E-Mail Header Injection is quite widespread as a vulnerability, appearing on \successDelta\ of forms that we were able to perform automated attacks on.
 This value acts as a lower bound for E-Mail Header Injection vulnerability, and can quite easily be much more if the attacks were of a more concentrated nature, crafted for the individual websites and less automated.
-We discuss this possibility, and other concepts such as limitations in the following chapter.

### 2016-05-15 Results/disclosure.tex
chap5 prelim edits done added table for dev responses

@@
 Out of the \domains\ vulnerable domains found, only 108 websites had the mailboxes specified above set-up to receive e-mails.
-For the remaining domains, we used the \dq{\texttt{whois}}~\cite{whois} data to get the contact details of the owner, and then e-mailed them with the same disclosure data.
+For the remaining domains, we used the \texttt{whois}~\cite{whois} data to get the contact details of the owner, and then e-mailed them with the same disclosure data.
+The number of emails we sent out and the number of developer responses we received is shown in Table~\ref{tab:devresp}.
+
+\begin{table}
+\centering
+\begin{tabular}{|c|c|c|}
+	\hline
+	\multicolumn{1}{|p{2cm}}{\centering \textbf{E-Mailed websites}} &
+	\multicolumn{1}{|p{2cm}|}{\centering \textbf{Developer Responses}} &
+	\multicolumn{1}{p{2cm}|}{\centering \textbf{Confirmed discoveries}}\\
+	\hline
+	293 & 13 & 9 \\
+	\hline
+\end{tabular}
+	\caption[\titlecap{Data gathered by our pipeline}]{Responsible disclosure of the discovered vulnerabilities to developers and the number of received responses.}
+	\label{tab:devresp}
+\end{table}
 

### 2016-05-16 Discussion/lessons.tex
chap6,7,8 prelim edits

@@
 
-    While not being as impactful as the primary vulnerability, this second form of the vulnerability does still provide the ability to send e-mails to multiple recipients, and can easily result in information leakage or spam generation on a large scale.
+    While not being as impactful as the primary vulnerability, this form of the vulnerability does still provide the ability to send e-mails to multiple recipients, and can easily result in information leakage or spam generation on a large scale.

### 2016-05-16 Discussion/limits.tex
chap6,7,8 prelim edits

@@
 \label{limitations}
-	This section complements Section \ref{sys:issues}, and discusses the limitations of our project. The following list, although not exhaustive, goes into the limitations of our project in detail: 
+	This section discusses the limitations of our project. The following list, although not exhaustive, goes into some of them in detail: 
 	\begin{itemize}
-		\item CAPTCHAs - As noted in section \ref*{issues:captcha}, CAPTCHAs pose a significant problem to our automated system.
-As CAPTCHAs are designed to be robust, there is no easy way to break them.
-There has been considerable research in this area~\cite{captchas2}, \cite{captchas} to name a few and although not impossible to break, it remains out of the scope of this project, and thus, we chose to ignore websites which require CAPTCHA verification.
+		\item Bot Blockers and CAPTCHAs\\
+		Because our system is fully automated, it is also susceptible to being stopped by `bot-blockers' i.e.\ mechanisms built-in to a website to prevent automated crawls or form submissions.
+Measures like CAPTCHA (Completely Automated Public Turing test to tell Computers and Humans Apart) and hidden form fields are often used to detect bots~\cite{captchas3}, \cite{captchas2}.
+
+		We have made sure that we do not affect hidden fields in the form, however, despite considerable research in breaking CAPTCHAs~\cite{captchas2}, \cite{captchas} and although not impossible to break, breaking CAPTCHAs remains out of the scope of this project, and thus, we chose to ignore websites which require CAPTCHA verification.
+
 		\item JavaScript Apps - Due to the growing emphasis on responsive web applications, more and more single-page web applications are being built purely with JavaScript.
 Even conventional applications are now making use of JavaScript to dynamically insert content and update the pages.
-This means that these dynamically injected components are not a part of the initial source code that is sent to the client by the web server.
+This means that these dynamically injected components are not a part of the initial source code that is sent to the client by the server.
 
-		Thus, our system never receives dynamically injected forms from the web server and hence is unable to detect whether these vulnerabilities are present in such forms.
-The only workaround would be, to use a JavaScript engine to query for the \lstinline|document.getElementsByTagName('html')[0].innerHTML| (from inside web browser automation tools like Selenium, etc.), and then use that as the source code for our URL.
+		Thus, our system never receives dynamically injected forms from the server and hence is unable to detect whether these vulnerabilities are present in such forms.
+The only workaround would be, to use a JavaScript engine to query for the \texttt{document.getElementsByTagName('html')[0].innerHTML} (from inside web browser automation tools like Selenium, etc.), and then use that as the source code for our URL.
 
@@
 
-		\item Blogs powered by WordPress/Drupal\\
-        In addition to what was discussed in Section \ref{issues:cms}, we found that certain WordPress plugins also prevent the E-Mail Header Injection attack by sanitizing user input on Contact Forms.
-Some of these plugins are discussed in the following section.
-Although not all websites built with WordPress are secure from the attack, between the presence of the plugins on some websites, and getting tagged as `spambots' by others, we were able to do vulnerability analysis on very few sites powered by WordPress.
-
 		\item Blacklisting by websites and ISPs\\
 		During the actual crawl, our system was blacklisted by a few websites (mostly WordPress ones), and Internet Service Providers (ISPs).
-We then created a blacklist of our own to ensure that we did not inject these websites.
-The result was that we could not gather any data about these websites.
+		To overcome this, we did two things:
+		\begin{enumerate}
+			\item Used an IP range of 60 different IP addresses. 
+			\item Used a blacklist of our own to prevent our Fuzzer from fuzzing websites that are known to blacklist automated crawlers.  The result was that we could not gather any data about these websites.
+		\end{enumerate}
+
+		\item Blogs powered by WordPress/Drupal\\
+		We found that certain WordPress plugins prevent the E-Mail Header Injection attack by sanitizing user input on contact forms.
+Some of these plugins are discussed in the following section.
+Although not all websites built with WordPress are secure from the attack, between the presence of the plugins on some websites, and getting tagged as `spambots' by others, we were able to do vulnerability analysis on few sites powered by WordPress.
 
@@
 Here, the French word for \texttt{e-mail} --- courrier électronique --- is used, and our system is unable to find the presence of the e-mail form.
+
+        \item Handling Malformed HTML\\
+        The parser that we use for HTML parsing --- Beautiful Soup --- does not try to parse malformed HTML, and throws an exception on encountering malformed content.
+Thus, we have designed the system to exit gracefully on such occasions.
+A side-effect of this is that our system is unable to parse websites with bad markup\,\footnotemark.
+
+        \footnotetext{We do not have any data about whether bad markup indicates an overall lower quality of the website, and thus cannot comment on whether such websites are more likely to have vulnerabilities, although the author strongly suspects that that might be the case.}
+
+        \item Black-box Testing\\
+        The approach that we have selected --- Black-box testing --- is highly beneficial as explained in Section \ref{sys:appr}.
+However, it also has a drawback in that we cannot verify whether the reported vulnerability exists in the source code or is a feature of the website (e.g., the website allows users to send bulk e-mail, adding as many \texttt{cc} or \texttt{bcc} headers).
+We have to manually e-mail the developers to get this feedback.
+
+       	\item \label{issues:fpr}False Positive rate for the E-Mail Field Checker\\
+       	As discussed in Section \ref{Comp:EMFC}, we only search for the words \texttt{email}, \texttt{mail} or \texttt{e-mail} (case insensitive) inside the forms to detect the presence of e-mail fields, instead of searching for an \colorbox{lightgray}{\lstinline{<input type = email>}}.
+This might result in a false positive in certain forms, like the one shown in Listing.
+\ref{code:false_positive}.
+
+       	\lstset{language=HTML,caption={E-Mail field checker - false positives, the system\\incorrectly classifies this as an e-mail form.},label={code:false_positive}}
+       	\begin{lstlisting}
+       	<form method="post">
+       	E-Mail us if you have any questions!!
+       	<input type="text" name="query"><br>
+       	<input type="submit" value="Search">
+       	</form>
+       	\end{lstlisting}
+
+       	The word \texttt{E-Mail} on Line 2 will result in our system classifying this form as a potential e-mail form, while it clearly is not.
+However, as we will see, this is not really a significant issue, as despite being added to the \texttt{email\_forms} table, this form will never be injected in the `fuzzer' due to the absence of the appropriate input field in the form.
+We chose to go with this design, as it allows us to detect almost every form that provides the capability to send or receive e-mail.
 	\end{itemize}

### 2016-05-16 System/issues.tex
chap6,7,8 prelim edits

@@
 \begin{itemize}
-	\item \label{issues:fpr}False Positive rate for the E-Mail Field Checker\\
-	As discussed in Section \ref{Comp:EMFC}, we only search for the words \texttt{email}, \texttt{mail} or \texttt{e-mail} (case insensitive) inside the forms to detect the presence of e-mail fields, instead of searching for an \colorbox{lightgray}{\lstinline{<input type = email>}}.
-This might result in a false positive in certain forms, like the one shown in Listing.
-\ref{code:false_positive}.
-
-	\lstset{language=HTML,caption={E-Mail field checker - false positives, the system\\incorrectly classifies this as an e-mail form.},label={code:false_positive}}
-	\begin{lstlisting}
-	<form method="post">
-	E-Mail us if you have any questions!!
-	<input type="text" name="query"><br>
-	<input type="submit" value="Search">
-	</form>
-	\end{lstlisting}
-
-	The word \texttt{E-Mail} on Line 2 will result in our system classifying this form as a potential e-mail form, while it clearly is not.
-However, as we will see, this is not really a significant issue, as despite being added to the \texttt{email\_forms} table, this form will never be injected in the `fuzzer' due to the absence of the appropriate input field in the form.
-We chose to go with this design, as it allows us to detect almost every form that provides the capability to send or receive e-mail.
 
@@
 
-	\item Black-box Testing\\
-	The approach that we have selected --- Black-box testing --- is highly beneficial as explained in Section \ref{sys:appr}.
-However, it also has a drawback in that we cannot verify whether the reported vulnerability exists in the source code or is a feature of the website (e.g., the website allows users to send bulk e-mail, adding as many \texttt{cc} or \texttt{bcc} headers).
-We have to manually e-mail the developers to get this feedback.
-
 	\item Mapping responses to requests\\
@@
 
-	\item Bot Blockers\\
-	\label{issues:captcha}
-    Because our system is fully automated, it is also susceptible to being stopped by `bot-blockers' i.e.\ mechanisms built-in to a website to prevent automated crawls or form submissions.
-Measures like CAPTCHA (Completely Automated Public Turing test to tell Computers and Humans Apart) and hidden form fields are often used to detect bots~\cite{captchas3}, \cite{captchas2}.
+%	\item Crawling WordPress and other CMS-based websites\\
+%	\label{issues:cms}
 
-    We have made sure that we do not affect hidden fields in the form, however, we do not have an anti-CAPTCHA functionality built into our system, and thus our system will not test such websites.
-
-	\item Handling Malformed HTML\\
-    The parser that we use for HTML parsing --- Beautiful Soup --- does not try to parse malformed HTML, and throws an exception on encountering malformed content.
-Thus, we have designed the system to exit gracefully on such occasions.
-A side-effect of this is that our system is unable to parse websites with bad markup\,\footnotemark.
-
-    \footnotetext{We do not have any data about whether bad markup indicates an overall lower quality of the website, and thus cannot comment on whether such websites are more likely to have vulnerabilities, although the author strongly suspects that that might be the case.}
-
-	\item Crawling WordPress and other CMS-based websites\\
-	\label{issues:cms}
-	In contrast to bot blockers that try to prevent the automated systems from attacking them, WordPress and other CMS based websites use a blacklisting approach to prevent bot attacks.
-Unfortunately, because we generate multiple requests to each website, this results in our IPs getting blacklisted.
-To overcome this, we did two things:
-	\begin{enumerate}
-		\item Used an IP range of 60 different IP addresses. 
-		\item Used a blacklist of our own to prevent our Fuzzer from fuzzing websites that are known to blacklist automated crawlers.
-	\end{enumerate}
 \end{itemize}

### 2016-05-17 paper.tex
HUGE changes
added my name
added adams name
Removing cruft from the files. Adding makefile and .gitignore

@@
 	% DOI
-	\doi{10.475/123_4}
+	%\doi{10.475/123_4}
 
 	% ISBN
-	\isbn{123-4567-24-567/08/06}
+	%\isbn{123-4567-24-567/08/06}
 
 	%Conference
-	\conferenceinfo{PLDI '13}{June 16--19, 2013, Seattle, WA, USA}
+	%\conferenceinfo{PLDI '13}{June 16--19, 2013, Seattle, WA, USA}
 
-	\acmPrice{\$15.00}
+	%\acmPrice{\$15.00}
 
@@
 	% --- Author Metadata here ---
-	\conferenceinfo{WOODSTOCK}{'97 El Paso, Texas USA}
+	%\conferenceinfo{WOODSTOCK}{'97 El Paso, Texas USA}
 	%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
@@
 
-	\title{E-jection fraction - Tracking how your website pumps out E-Mails}
+	%\title{E-jection fraction - Tracking how your website pumps out
+	%E-Mails}
+    \title{The Prevalence of E-Mail Header Injections on the World
+      Wide Web}
 	%
@@
 
-	\numberofauthors{8} %  in this sample file, there are a *total*
+	\numberofauthors{1} %  in this sample file, there are a *total*
 	% of EIGHT authors. SIX appear on the 'first-page' (for formatting
@@
 	%
+
+    % Note: For CCS submission we need to have it anonymous
+
 	\author{
@@
 		% 1st. author
-		\alignauthor
-		Ben Trovato\titlenote{Dr.~Trovato insisted his name be first.}\\
-		\affaddr{Institute for Clarity in Documentation}\\
-		\affaddr{1932 Wallamaloo Lane}\\
-		\affaddr{Wallamaloo, New Zealand}\\
-		\email{trovato@corporation.com}
-		% 2nd. author
-		\alignauthor
-		G.K.M. Tobin\titlenote{The secretary disavows
-			any knowledge of this author's actions.}\\
-		\affaddr{Institute for Clarity in Documentation}\\
-		\affaddr{P.O. Box 1212}\\
-		\affaddr{Dublin, Ohio 43017-6221}\\
-		\email{webmaster@marysville-ohio.com}
-		% 3rd. author
-		\alignauthor Lars Th{\o}rv{\"a}ld\titlenote{This author is the
-			one who did all the really hard work.}\\
-		\affaddr{The Th{\o}rv{\"a}ld Group}\\
-		\affaddr{1 Th{\o}rv{\"a}ld Circle}\\
-		\affaddr{Hekla, Iceland}\\
-		\email{larst@affiliation.org}
-		\and  % use '\and' if you need 'another row' of author names
-		% 4th. author
-		\alignauthor Lawrence P. Leipuner\\
-		\affaddr{Brookhaven Laboratories}\\
-		\affaddr{Brookhaven National Lab}\\
-		\affaddr{P.O. Box 5000}\\
-		\email{lleipuner@researchlabs.org}
-		% 5th. author
-		\alignauthor Sean Fogarty\\
-		\affaddr{NASA Ames Research Center}\\
-		\affaddr{Moffett Field}\\
-		\affaddr{California 94035}\\
-		\email{fogartys@amesres.org}
-		% 6th. author
-		\alignauthor Charles Palmer\\
-		\affaddr{Palmer Research Laboratories}\\
-		\affaddr{8600 Datapoint Drive}\\
-		\affaddr{San Antonio, Texas 78229}\\
-		\email{cpalmer@prl.com}
+		%% \alignauthor
+		%% Sai Prashanth Chandramouli\\
+		%% \affaddr{Arizona State University}\\
+		%% \email{saipc@asu.edu}
+		%% % 2nd. author
+		%% \alignauthor
+		%% Adam Doup\'{e}\titlenote{The secretary disavows
+		%% 	any knowledge of this author's actions.}\\
+		%% \affaddr{Arizona State University}\\
+		%% \email{doupe@asu.edu}
+		%% % 3rd. author
+		%% \alignauthor Lars Th{\o}rv{\"a}ld\titlenote{This author is the
+		%% 	one who did all the really hard work.}\\
+		%% \affaddr{The Th{\o}rv{\"a}ld Group}\\
+		%% \affaddr{1 Th{\o}rv{\"a}ld Circle}\\
+		%% \affaddr{Hekla, Iceland}\\
+		%% \email{larst@affiliation.org}
+		%% \and  % use '\and' if you need 'another row' of author names
+		%% % 4th. author
+		%% \alignauthor Lawrence P. Leipuner\\
+		%% \affaddr{Brookhaven Laboratories}\\
+		%% \affaddr{Brookhaven National Lab}\\
+		%% \affaddr{P.O. Box 5000}\\
+		%% \email{lleipuner@researchlabs.org}
+		%% % 5th. author
+		%% \alignauthor Sean Fogarty\\
+		%% \affaddr{NASA Ames Research Center}\\
+		%% \affaddr{Moffett Field}\\
+		%% \affaddr{California 94035}\\
+		%% \email{fogartys@amesres.org}
+		%% % 6th. author
+		%% \alignauthor Charles Palmer\\
+		%% \affaddr{Palmer Research Laboratories}\\
+		%% \affaddr{8600 Datapoint Drive}\\
+		%% \affaddr{San Antonio, Texas 78229}\\
+		%% \email{cpalmer@prl.com}
 	}
@@
 	% in the \additional authors block, viz.
-	\additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
-		email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
-		(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
-	\date{30 July 1999}
+	%% \additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
+	%% 	email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
+	%% 	(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
+	%% \date{30 July 1999}
 	% Just remember to make sure that the TOTAL number of authors
@@
 	%
-	\begin{CCSXML}
-		<ccs2012>
-		<concept>
-		<concept_id>10010520.10010553.10010562</concept_id>
-		<concept_desc>Computer systems organization~Embedded systems</concept_desc>
-		<concept_significance>500</concept_significance>
-		</concept>
-		<concept>
-		<concept_id>10010520.10010575.10010755</concept_id>
-		<concept_desc>Computer systems organization~Redundancy</concept_desc>
-		<concept_significance>300</concept_significance>
-		</concept>
-		<concept>
-		<concept_id>10010520.10010553.10010554</concept_id>
-		<concept_desc>Computer systems organization~Robotics</concept_desc>
-		<concept_significance>100</concept_significance>
-		</concept>
-		<concept>
-		<concept_id>10003033.10003083.10003095</concept_id>
-		<concept_desc>Networks~Network reliability</concept_desc>
-		<concept_significance>100</concept_significance>
-		</concept>
-		</ccs2012>  
-	\end{CCSXML}
+	%% \begin{CCSXML}
+	%% 	<ccs2012>
+	%% 	<concept>
+	%% 	<concept_id>10010520.10010553.10010562</concept_id>
+	%% 	<concept_desc>Computer systems organization~Embedded systems</concept_desc>
+	%% 	<concept_significance>500</concept_significance>
+	%% 	</concept>
+	%% 	<concept>
+	%% 	<concept_id>10010520.10010575.10010755</concept_id>
+	%% 	<concept_desc>Computer systems organization~Redundancy</concept_desc>
+	%% 	<concept_significance>300</concept_significance>
+	%% 	</concept>
+	%% 	<concept>
+	%% 	<concept_id>10010520.10010553.10010554</concept_id>
+	%% 	<concept_desc>Computer systems organization~Robotics</concept_desc>
+	%% 	<concept_significance>100</concept_significance>
+	%% 	</concept>
+	%% 	<concept>
+	%% 	<concept_id>10003033.10003083.10003095</concept_id>
+	%% 	<concept_desc>Networks~Network reliability</concept_desc>
+	%% 	<concept_significance>100</concept_significance>
+	%% 	</concept>
+	%% 	</ccs2012>  
+	%% \end{CCSXML}
 
-	\ccsdesc[500]{Computer systems organization~Embedded systems}
-	\ccsdesc[300]{Computer systems organization~Redundancy}
-	\ccsdesc{Computer systems organization~Robotics}
-	\ccsdesc[100]{Networks~Network reliability}
+	%% \ccsdesc[500]{Computer systems organization~Embedded systems}
+	%% \ccsdesc[300]{Computer systems organization~Redundancy}
+	%% \ccsdesc{Computer systems organization~Robotics}
+	%% \ccsdesc[100]{Networks~Network reliability}
 
@@
 	%
-	\printccsdesc
+	% \printccsdesc
 
@@
 
-	\keywords{ACM proceedings; \LaTeX; text tagging}
+	% \keywords{ACM proceedings; \LaTeX; text tagging}
 

### 2016-05-18 Background/impact.tex
fixed bibtex entries for phishing, spoofing

@@
 	\item Phishing and Spoofing Attacks\\
-    Phishing~\cite{wiki:Phishing} (a variation of spoofing~\cite{wiki:Spoofing_attack}) refers to an attack where the recipient of an e-mail is made to believe that the e-mail is a legitimate one.
+    Phishing~\cite{phishing} (a variation of spoofing~\cite{spoofing_attack}) refers to an attack where the recipient of an e-mail is made to believe that the e-mail is a legitimate one.
 The e-mail usually redirects them to a malicious website, which then steals their credentials.

### 2016-05-18 Discussion/lessons.tex
Removing references to sections that do not exist.

@@
 	A second and a far more common reason for our fuzzing attempts to fail is the bot-blocking mechanisms built into the websites.
-CAPTCHAs (as explained in Section \ref{issues:captcha} and in the following section) pose a very difficult problem for our system to exploit E-Mail Header Injection, even if it is present.
+CAPTCHAs pose a very difficult problem for our system to exploit E-Mail Header Injection, even if it is present.
 

### 2016-05-18 System/sys_arch.tex
Removing references to sections that do not exist.

@@
 	\item Data Gathering\\
-	The Data Gathering module (shown in Figure~\ref{fig:crawler}) is primarily responsible for the following activities:
+	The Data Gathering module is primarily responsible for the following activities:
 	\begin{itemize}
@@
 	\item Payload Injection\\
-	The Payload Injection module (shown in Figure~\ref{fig:fuzzer}) is primarily responsible for the following activities:
+	The Payload Injection module is primarily responsible for the following activities:
 	\begin{itemize}

### 2016-05-19 Background/pbm_bg.tex
Fixed issues reported by chrisper (bugs in writing)

@@
 E-Mail Header Injection belongs to a broad class of vulnerabilities known simply as injection attacks.
-However, unlike its more popular siblings, SQL injection~\cite{sql1}, \cite{sql0}, \cite{sql2}, Cross-Site Scripting (XSS) \cite{Injection1}, \cite{KleinAmit} or even HTTP Header Injection~\cite{sessionride}, relatively little research is available on E-Mail Header Injection.
+However, unlike its more popular siblings, SQL injection~\cite{sql1}, \cite{sql0}, \cite{sql2}, Cross-Site Scripting (XSS)~\cite{Injection1}, \cite{KleinAmit} or even HTTP Header Injection~\cite{sessionride}, relatively little research is available on E-Mail Header Injection.
 

### 2016-05-19 Discussion/limits.tex
Fixed issues reported by chrisper (bugs in writing)

@@
 		\item Bot Blockers and CAPTCHAs\\
-		Because our system is fully automated, it is also susceptible to being stopped by `bot-blockers' i.e.\ mechanisms built-in to a website to prevent automated crawls or form submissions.
+		Because our system is fully automated, it is also susceptible to being stopped by `bot-blockers' i.e.,\ mechanisms built-in to a website to prevent automated crawls or form submissions.
 Measures like CAPTCHA (Completely Automated Public Turing test to tell Computers and Humans Apart) and hidden form fields are often used to detect bots~\cite{captchas3}, \cite{captchas2}.
@@
         \item Black-box Testing\\
-        The approach that we have selected --- Black-box testing --- is highly beneficial as explained in Section \ref{sys:appr}.
+        The approach that we have selected --- Black-box testing --- is highly beneficial as explained in Section~\ref{sys:appr}.
 However, it also has a drawback in that we cannot verify whether the reported vulnerability exists in the source code or is a feature of the website (e.g., the website allows users to send bulk e-mail, adding as many \texttt{cc} or \texttt{bcc} headers).
@@
        	\item \label{issues:fpr}False Positive rate for the E-Mail Field Checker\\
-       	As discussed in Section \ref{Comp:EMFC}, we only search for the words \texttt{email}, \texttt{mail} or \texttt{e-mail} (case insensitive) inside the forms to detect the presence of e-mail fields, instead of searching for an \colorbox{lightgray}{\lstinline{<input type = email>}}.
-This might result in a false positive in certain forms, like the one shown in Listing.
-\ref{code:false_positive}.
+       	As discussed in Section~\ref{Comp:EMFC}, we only search for the words \texttt{email}, \texttt{mail} or \texttt{e-mail} (case insensitive) inside the forms to detect the presence of e-mail fields, instead of searching for an \colorbox{lightgray}{\lstinline{<input type = email>}}.
+This might result in a false positive in certain forms, like the one shown in Listing~\ref{code:false_positive}.
 

### 2016-05-19 System/assumptions.tex
HUGE changes
chap6,7,8 prelim edits
Fixed issues reported by chrisper (bugs in writing)

@@
 \subsection{Assumptions}
-We made certain assumptions while building the system. This section describes the assumptions and explores to what extent these hold true:
+In addition to the limitations that were already discussed, we made certain assumptions while building the system. This section describes the assumptions and explores to what extent these hold true:
 \begin{enumerate}
@@
 	This is a requisite for our system to work. If the Crawler is blocked for any reason, we do not get the data feed for our system, and without this input, it is almost impossible to set our system up.
+
 	\item \textbf{The Crawler feed is an ideal representation of the World Wide Web} \\
@@
 
-	However, this assumption is reasonable due to the `Law of averages' \cite{wiki:Law_of_averages}, the `Law of big numbers' \cite{wiki:Law_of_large_numbers}, and the concept of `Regression to the mean' \cite{wiki:Regression_toward_the_mean}.
+	However, this assumption is reasonable due to the `Law of averages'~\cite{wiki:Law_of_averages}, the `Law of big numbers'~\cite{wiki:Law_of_large_numbers}, and the concept of `Regression to the mean'~\cite{wiki:Regression_toward_the_mean}.
 Simply stated, a crawl of this large magnitude should give us a very distributed sample of the overall Web, eventually converging to the average of all websites in existence.
@@
 We also discussed the issues faced, and the assumptions that we made while building the system.
-%The next chapter describes, in brief, the experimental setup we used for our system.
+%The next section describes, in brief, the experimental setup we used for our system.

### 2016-05-19 System/components.tex
Fixed issues reported by chrisper (bugs in writing)

@@
 However, despite the advantages, this might also lead to a false positive rate.
-We discuss this possibility in detail in Section \ref*{issues:fpr} - Design Issues.
+We discuss this possibility in detail in Section~\ref*{issues:fpr} - Design Issues.
 
@@
 The `e-mails with payloads' refer to e-mails received by either the \colorbox{lightgray}{\lstinline{nuser(xxxx)@example.com}} or \colorbox{lightgray}{\lstinline{maluser(xxxx)@example.com}} accounts.
-These e-mails were received due to injecting the malicious payloads that were discussed in Section.
-\ref{Comp:Fuzzer:mp}.
+These e-mails were received due to injecting the malicious payloads that were discussed in Section~\ref{Comp:Fuzzer:mp}.
 Analysis of these e-mails is considerably simpler than that of the regular e-mails.
@@
 \paragraph{Detecting injected \texttt{bcc} headers}
-As discussed in the payloads section (\ref{Comp:Fuzzer:mp}), the payloads were crafted in such a way that the e-mails received by \texttt{maluser} account directly indicate the presence of the injected \texttt{bcc} field.
+As discussed in the payloads section~(\ref{Comp:Fuzzer:mp}), the payloads were crafted in such a way that the e-mails received by \texttt{maluser} account directly indicate the presence of the injected \texttt{bcc} field.
 Thus, we simply parse the E-Mails and store them in the Database.
@@
 These e-mails then act as proof that the vulnerability was not found on the given website.
-	\item A more conducive scenario is when the \texttt{bcc} header was ignored for some reason, e.g.\ Python's default behavior when it encounters duplicate headers.
+	\item A more conducive scenario is when the \texttt{bcc} header was ignored for some reason, e.g.,\ Python's default behavior when it encounters duplicate headers.
 In this case, we check whether the e-mail contains the custom header \texttt{x-check}.

### 2016-05-19 System/issues.tex
Fixed issues reported by chrisper (bugs in writing)

@@
 However, Python's GIL (Global Interpreter Lock) does not allow the running of multiple native threads concurrently.
-To overcome this, we used a Celery task queue (discussed in Section \ref{exp:Celery}), which allowed a level of parallelism that Python does not provide by default.
+To overcome this, we used a Celery task queue (discussed in Section~\ref{exp:Celery}), which allowed a level of parallelism that Python does not provide by default.
 Even though this makes the system faster than a single-threaded approach, it still leaves room for improvement in terms of performance.
@@
 	Also, relative URLs pose another problem.
-If the URL of the form page ends with `/' and the \texttt{action} specifies a path starting with `/' (illustrated in Listing \ref{issues:url}), we would need to strip one of the two slashes.
+If the URL of the form page ends with `/' and the \texttt{action} specifies a path starting with `/' (illustrated in Listing~\ref{issues:url}), we would need to strip one of the two slashes.
 This increases the overall complexity of our URL generator, as we have to account for all these possibilities.

### 2016-05-19 System/sys_arch.tex
Fixed issues reported by chrisper (bugs in writing)

@@
 	\begin{itemize}
-		\item Interface with the Crawler (Section \ref{Comp:Crawler}) and receive the URLs.
-		\item Parse the HTML for the corresponding URL and store the relevant form data (Section \ref{Comp:FP}).
-		\item Check for the presence of forms that allow the user to send/receive e-mail, and store references to these forms (Section \ref{Comp:EMFC}).
+		\item Interface with the Crawler (Section~\ref{Comp:Crawler}) and receive the URLs.
+		\item Parse the HTML for the corresponding URL and store the relevant form data (Section~\ref{Comp:FP}).
+		\item Check for the presence of forms that allow the user to send/receive e-mail, and store references to these forms (Section~\ref{Comp:EMFC}).
 	\end{itemize} 
@@
 	\begin{itemize}
-		\item Retrieve the forms that allow users of a website to send/receive e-mail and reconstruct these forms (Section \ref{Comp:EMFR}).
-		\item Inject these forms with benign data (non-malicious payloads) and generate an HTTP request to the corresponding URL (Section \ref{Comp:Fuzzer:nmp}).
-		\item Analyze the e-mails, extracting the header fields and checking for the presence of the injected payloads (Section \ref{Comp:EMA}).
-		\item Inject the forms that sent us e-mails with malicious payloads, and generate an HTTP request to the corresponding URL to check if E-Mail Header Injection vulnerability exists in that form (Section \ref{Comp:Fuzzer:mp}).
+		\item Retrieve the forms that allow users of a website to send/receive e-mail and reconstruct these forms (Section~\ref{Comp:EMFR}).
+		\item Inject these forms with benign data (non-malicious payloads) and generate an HTTP request to the corresponding URL (Section~\ref{Comp:Fuzzer:nmp}).
+		\item Analyze the e-mails, extracting the header fields and checking for the presence of the injected payloads (Section~\ref{Comp:EMA}).
+		\item Inject the forms that sent us e-mails with malicious payloads, and generate an HTTP request to the corresponding URL to check if E-Mail Header Injection vulnerability exists in that form (Section~\ref{Comp:Fuzzer:mp}).
 	\end{itemize} 

### 2016-05-19 introduction.tex
fixed citation spaces
Fixed issues reported by chrisper (bugs in writing)

@@
 	Since attackers typically masquerade themselves as users of the system, if user input is to be trusted, then developers need to have proper sanitization routines in place.
-Many different injection attacks such as SQL injection or cross-site scripting (XSS) \cite{OWASPT10} are possible due to improper sanitization of user input.
+Many different injection attacks such as SQL injection or cross-site scripting (XSS)~\cite{OWASPT10} are possible due to improper sanitization of user input.
 
 	Our research focuses on a lesser known injection attack known as E-Mail Header Injection.
-E-Mail Header Injection can be considered as the e-mail equivalent of HTTP Header Injection vulnerability \cite{wiki:HTTP_headerinjection}.
+E-Mail Header Injection can be considered as the e-mail equivalent of HTTP Header Injection vulnerability~\cite{wiki:HTTP_headerinjection}.
 The vulnerability exists in the reference implementation of the built-in \texttt{mail} functionality in popular languages like PHP, Java, Python, and Ruby.

### 2016-05-19 rel_work.tex
Fixed issues reported by chrisper (bugs in writing)

@@
 
-The attack described by Terada~\cite{Terada2015} is one that attacks the underlying SMTP mail servers by injecting SMTP commands (which are closely related to E-Mail Headers and usually have a one-to-one mapping, e.g.
-\texttt{To} e-mail header has a corresponding \texttt{To} SMTP header) to exploit the SMTP server's pipelining mechanism.
+The attack described by Terada~\cite{Terada2015} is one that attacks the underlying SMTP mail servers by injecting SMTP commands (which are closely related to E-Mail Headers and usually have a one-to-one mapping, e.g., \texttt{To} e-mail header has a corresponding \texttt{To} SMTP header) to exploit the SMTP server's pipelining mechanism.
 The paper also describes proof-of-concept attacks against certain mailing libraries like \texttt{Ruby Mail} and \texttt{JavaMail}.
@@
 However, this article targets just one plugin and does not aim to find the prevalence of said plugin usage.
-Neither does it inform the creators of the plug-in to fix the discovered vulnerability.
+Neither does it inform the creators of the plugin to fix the discovered vulnerability.
 \footnotetext{Note that this plugin is used actively on 300,000 websites (according to~\cite{BestWebSoft2016}), but is yet to be fixed.}
-The vulnerability was described briefly by Stuttard and Pinto in their book, ``\emph{The Web Application Hacker's Handbook: Discovering and Exploiting Security Flaws}'' \cite{stuttard2011web}.
+The vulnerability was described briefly by Stuttard and Pinto in their book, ``\emph{The Web Application Hacker's Handbook: Discovering and Exploiting Security Flaws}''~\cite{stuttard2011web}.
 The book, however, does not go into detail on either the attack or the ways to mitigate such an attack.
 Our work, on the other hand discusses the means to mitigate the attack.
-We also describe, in detail, the payloads that can be used and the need for varying the payloads (Section.
-\ref{Comp:Fuzzer:mp}).
+We also describe, in detail, the payloads that can be used and the need for varying the payloads (Section~\ref{Comp:Fuzzer:mp}).
 

### 2016-05-19 Background/php.tex
rewrote code samples to anonymize the paper, removed references to myself and to asu

@@
 $from = $_REQUEST['email'];
-$subject = "Hello Sai Pc";
-$message = "We need you to reset your password";
-$to = "schand31@asu.edu";
+$subject = 'Hello XYZ';
+$message = 'We need you to reset your password';
+$to = 'xyz@xyz.edu';
 
-// example attack string to be injected as the value for
-// $_REQUEST['email'] => 'sai@sai.com\nCC:spc@spc.com'
+// example attack string to be 
+// injected as the value for
+// $_REQUEST['email'] => 
+// 's@s.com\nCC:spc@spc.com'
 $retValue = mail($to, $subject, $message, "From: $from");
-// E-Mail gets sent to both schand31@asu.edu AND spc@spc.com
+// E-Mail gets sent to both 
+// xyz@xyz.edu AND spc@spc.com
 \end{lstlisting}

### 2016-05-19 Background/py.tex
fixing code samples
rewrote code samples to anonymize the paper, removed references to myself and to asu

@@
 form = cgi.FieldStorage()
-to = form["email"] # input() exhibits the same behavior
+to = form["email"] # input() exhibits 
+# the same behavior
 msg = """To: """ + to + """\n
@@
 
-f = FeedParser() # Parser.parsestr() also 
-# contains the same vulnerability
+f = FeedParser() # Parser.parsestr() 
+# also contains the same vulnerability
 f.feed(msg)
@@
 
-# attack string => 'sai@sai.com\nBCC:spc@spc.com'
+# attack string => 
+# 's@s.com\nBCC:spc@spc.com'
 # for form["email"]
 
-# both to:sai@sai.com AND bcc:spc@spc.com 
+# to:s@s.com AND bcc:spc@spc.com 
 # are added to the headers

### 2016-05-19 Discussion/limits.tex
rewrote code samples to anonymize the paper, removed references to myself and to asu

@@
 
-       	\lstset{language=HTML,caption={E-Mail field checker - false positives, the system\\incorrectly classifies this as an e-mail form.},label={code:false_positive}}
+       	\lstset{language=HTML,caption={E-Mail field checker - false positives, the system incorrectly classifies this as an e-mail form.},label={code:false_positive}}
        	\begin{lstlisting}
@@
 <meta charset="utf-8">
-<meta name="author" content="Sai Pc">
+<meta name="author" content="XYZ">
 <title>Mock Email</title></head>
 <body>
-<form action="{Replace with path to back-end}" method="post">
+<form action="{path-to-back-end}" method="post">
 <input type="text" placeholder="courrier électronique"

### 2016-05-19 System/proof_of_concept.tex
chap4 prelim edit
rewrote code samples to anonymize the paper, removed references to myself and to asu

@@
 <meta charset="utf-8">
-<meta name="author" content="Sai Pc">
+<meta name="author" content="XYZ">
 <title>Mock Email</title>
@@
 <body>
-<form action="{Replace with path to back-end}" method="post">
+<form action="{path-to-back-end}" method="post">
 <input type="text" placeholder="Email" name="email" id="e-mail"><br>
@@
 	\centering
-	\includegraphics[width=14cm, height=8cm]{System/EMI_Postman_Ruby}
+	\includegraphics[width=\linewidth]{System/EMI_Postman_Ruby}
 	\caption[\titlecap{Fuzzing a request for the Ruby backend}]{Fuzzing a request for the Ruby backend, the payload can be seen inside the address bar.}
@@
 	\centering
-	\includegraphics[width=14cm, height=8cm]{System/EMI_Mailcatcher_Ruby}
+	\includegraphics[width=\linewidth]{System/EMI_Mailcatcher_Ruby}
 	\caption[\titlecap{E-Mail header injection proof of concept - Ruby}]{E-Mail header injection proof of concept - Ruby, we can see that multiple headers (bcc, x-check, subject) have been inserted into the resulting e-mail.}

### 2016-05-19 paper.tex
rewrote code samples to anonymize the paper, removed references to myself and to asu

@@
 \documentclass{sig-alternate-05-2015}
-
+\usepackage[T1]{fontenc}
 \usepackage[square,numbers]{natbib}
@@
 	backgroundcolor=\color{lightgray},
-	basicstyle=\small,
+	basicstyle=\ttfamily,
 	breaklines=true, 

### 2016-05-19 Discussion/lessons.tex
final data update

@@
     From our results, it is evident that the vulnerability exists in the wild.
-Despite its relatively low occurrence rate compared to the more popular SQL Injection and XSS (Cross-Site Scripting), when we take the total number of websites on the World Wide Web --- 1,018,863,952 according to Internet Live Stats~\cite{InternetLiveStats2016} as of early 2016 --- and calculate \successDelta\ percent (the occurrence rate of E-Mail Header Injection vulnerability as found by our system) of that number, we end up with 11,309,390 websites - a pretty significant number.
+Despite its relatively low occurrence rate compared to the more popular SQL Injection and XSS (Cross-Site Scripting), when we take the total number of websites on the World Wide Web --- 1,018,863,952 according to Internet Live Stats~\cite{InternetLiveStats2016} as of early 2016 --- and calculate \successDelta\ percent (the occurrence rate of E-Mail Header Injection vulnerability as found by our system) of that number, we end up with 14,875,413 websites - a pretty significant number.
 We agree that an extrapolation of that kind might not be an accurate measure of the prevalence of the vulnerability.
@@
     Even in this form of the attack, we are still able to extract information that should be private to a given user, and in some of these cases, able to inject enough data to spoof the first few lines of the e-mail message.
-From Table~\ref{tab:analysis}, information leakage using \texttt{To header injection} was possible on 142 forms, while spoofing using \texttt{To header injection} was possible on 11 forms.
+From Table~\ref{tab:analysis}, information leakage using \texttt{To header injection} was possible on 163 forms, while spoofing using \texttt{To header injection} was possible on 13 forms.
 

### 2016-05-19 Results/analysis.tex
final data update

@@
 	\item E-Mails with the \texttt{to} header successfully injected\\
-	We discovered an unintended vulnerability which we would like to christen \texttt{TO~header injection}.
+	We discovered an unintended vulnerability which we would like to christen \texttt{To~header injection}.
 These injections reflect the ability to inject any number of e-mail addresses into the \texttt{to} field while being unable to inject any other header into the e-mails.
@@
 
-	While not allowing us complete control over the e-mails sent, \texttt{TO header injection} makes it possible to append any number of e-mail addresses, thereby enabling us to leak information, and/or perform DoS (Denial of Service) attacks.
+	While not allowing us complete control over the e-mails sent, \texttt{To header injection} makes it possible to append any number of e-mail addresses, thereby enabling us to leak information, and/or perform DoS (Denial of Service) attacks.
 
@@
 	These represent the perfect attack scenario where we are able to inject multiple headers into the e-mails.
-We can see that over 75\% of the received \texttt{bcc} header injected e-mails are also susceptible to other header injections.
+We can see that over 70\% of the received \texttt{bcc} header injected e-mails are also susceptible to other header injections.
 

### 2016-05-19 Results/data_analysis.tex
final data update

@@
 		\hline
-		E-Mail Header Injections with \texttt{bcc} header & 304\\
+		E-Mail Header Injections with \texttt{bcc} header & 329\\
 		\hline
-		E-Mail Header Injections with \texttt{x-check} header & 252\\
+		E-Mail Header Injections with \texttt{x-check} header & 396\\
 		\hline
-		\texttt{To header} injections alone & 157\\
+		\texttt{To header} injections alone & 163\\
 		\hline
@@
 		Both \texttt{To header} injections and x-check headers &
-		12\\
+		13\\
 		\hline
-		\texttt{x-check} headers found in \texttt{nuser} e-mails & 67\\
+		\texttt{x-check} headers found in \texttt{nuser} e-mails & 219\\
 		\hline
-		Unique \texttt{x-check} headers found in \texttt{nuser} e-mails & 35\\
+		Unique \texttt{x-check} headers found in \texttt{nuser} e-mails & 181\\
 		\hline
-		Total successful injections (1 + 3 + 7) & 496\\
+		Total successful injections (1 + 3 + 7) & \success\ \\
 

### 2016-05-20 abstract.tex
Edits to abstract

@@
 	E-Mail header injection vulnerability is a class of vulnerability that can occur in web applications that use user input to construct e-mail messages.
-E-Mail injection is possible when the mailing script fails to check for the presence of e-mail headers in user input (either form fields or URL parameters).
-The vulnerability exists in the reference implementation of the built-in \dq{mail} functionality in popular languages like PHP, Java, Python, and Ruby\@.
-With the proper injection string, this vulnerability can be exploited to inject additional headers and/or modify existing headers in an E-Mail message, allowing an attacker to completely alter the content of the e-mail.
+E-Mail header injection is possible when the mailing script fails to check for the presence of e-mail headers in user input (either form fields or URL parameters).
+The vulnerability exists in the reference implementation of the built-in mail functionality in popular languages such as PHP, Java, Python, and Ruby.
+With the proper injection string, this vulnerability can be exploited to inject additional headers, modify existing headers, and  alter the content of the e-mail.
 
-	This thesis develops a scalable mechanism to automatically detect E-Mail Header Injection vulnerability and uses this mechanism to quantify the prevalence of E\-Mail Header Injection vulnerabilities on the Internet.
-Using a black-box testing approach, the system crawled \urls\ URLs to find URLs which contained form fields.
-\forms\ such forms were found by the system, of which \emailforms\ forms contained e-mail fields.
-The system used this data feed to discern the forms that could be fuzzed with malicious payloads.
-Amongst the \fuzzed\ forms tested, \recd\ forms were found to be injectable with more malicious payloads.
-The system tested \malfuzzed\ of these, and was able to find \success\ vulnerable URLs across \domains\ domains, which proves that the threat is widespread and deserves future research attention.
+	This paper presents a scalable mechanism to automatically detect E-Mail Header Injection vulnerabilities and uses this mechanism to quantify the prevalence of E\-Mail Header Injection vulnerabilities on the web.
+Using a black-box testing approach, the system crawled \urls URLs identify web pages which contained form fields.
+\forms such forms were found by the system, of which \emailforms forms contained e-mail fields.
+We then test \fuzzed forms to see if they would send us an e-mail, and \recd forms set us an email.
+Of these \malfuzzed forms were tested with E\-mail Header Injection payloads and, of these, we found \success vulnerable URLs across \domains domains.
+Then, to demonstrate that E\-mail Header Injection vulnerabilities are actively being exploited to create a spamming platform, we found \ipsblacklist IPs that were vulnerable on spaming blacklists.
+This work shows that E\-mail Header Injection vulnerabilities are widespread widespread and deserve future research attention.
 \end{abstract}

### 2016-05-20 abstract.tex
Edits to the introduction

@@
 \begin{abstract}
-	E-Mail header injection vulnerability is a class of vulnerability that can occur in web applications that use user input to construct e-mail messages.
-E-Mail header injection is possible when the mailing script fails to check for the presence of e-mail headers in user input (either form fields or URL parameters).
+	\ehi vulnerability is a class of vulnerability that can occur in web applications that use user input to construct \email messages.
+\ehi is possible when the mailing script fails to check for the presence of \email headers in user input (either form fields or URL parameters).
 The vulnerability exists in the reference implementation of the built-in mail functionality in popular languages such as PHP, Java, Python, and Ruby.
-With the proper injection string, this vulnerability can be exploited to inject additional headers, modify existing headers, and  alter the content of the e-mail.
+With the proper injection string, this vulnerability can be exploited to inject additional headers, modify existing headers, and  alter the content of the \email.
 
-	This paper presents a scalable mechanism to automatically detect E-Mail Header Injection vulnerabilities and uses this mechanism to quantify the prevalence of E\-Mail Header Injection vulnerabilities on the web.
+	This paper presents a scalable mechanism to automatically detect \ehi vulnerabilities and uses this mechanism to quantify the prevalence of \ehi vulnerabilities on the web.
 Using a black-box testing approach, the system crawled \urls URLs identify web pages which contained form fields.
-\forms such forms were found by the system, of which \emailforms forms contained e-mail fields.
-We then test \fuzzed forms to see if they would send us an e-mail, and \recd forms set us an email.
-Of these \malfuzzed forms were tested with E\-mail Header Injection payloads and, of these, we found \success vulnerable URLs across \domains domains.
-Then, to demonstrate that E\-mail Header Injection vulnerabilities are actively being exploited to create a spamming platform, we found \ipsblacklist IPs that were vulnerable on spaming blacklists.
-This work shows that E\-mail Header Injection vulnerabilities are widespread widespread and deserve future research attention.
+\forms such forms were found by the system, of which \emailforms forms contained \email fields.
+We then test \fuzzed forms to see if they would send us an \email, and \recd forms set us an \email.
+Of these \malfuzzed forms were tested with \ehi payloads and, of these, we found \success vulnerable URLs across \domains domains.
+Then, to demonstrate that \ehi vulnerabilities are actively being exploited to create a spamming platform, we found \ipsblacklist IPs that were vulnerable on spaming blacklists.
+This work shows that \ehi vulnerabilities are widespread widespread and deserve future research attention.
 \end{abstract}

### 2016-05-20 introduction.tex
Edits to the introduction

@@
 The World Wide Web has single-handedly brought about a change in the way we use computers.
-The ubiquitous nature of the Web has made it possible for the general public to access it anywhere and on multiple devices like phones, laptops, personal digital assistants, and even on TVs and cars.
-This has ushered in an era of responsive web applications which depend on user input.
+The ubiquitous nature of the web has made it possible for anyone to access information and services anywhere and on multiple devices such as phones, laptops, personal digital assistants, TVs, and cars.
+This access has ushered in an era of web applications which depend on user input.
 While this rapid pace of development has improved the speed of dissemination of information, it does come at a cost.
-Attackers have an added incentive to break into user's e-mail accounts more than ever.
+As users move more and more of their personal and financial information to web applications, attackers are responding by using web application vulnerabilities to access this lucrative data.
+
+%% Adam: I don't see how this adds to our story
+%% Attackers have an added incentive to break into user's e-mail accounts more than ever.
 E-Mail accounts are usually connected to almost all other online accounts of a user, and e-mails continue to serve as the principal mode of official communication on the web for most institutions.
-Thus, the impact an attacker can have by having control over the e-mail communication sent by websites to users is of an enormous magnitude.
+Thus, the impact an attacker can have by having control over the \email communication sent by websites to users is of an enormous magnitude.
 
-	Since attackers typically masquerade themselves as users of the system, if user input is to be trusted, then developers need to have proper sanitization routines in place.
-Many different injection attacks such as SQL injection or cross-site scripting (XSS)~\cite{OWASPT10} are possible due to improper sanitization of user input.
+% TODO: Sai, can you add a reference to command injection vulnerabilities here?
+Many common and well-known web application vulnerabilities, such as SQL Injection and Cross-Site Scripting~\cite{OWASPT10}, are command injection vulnerabilities, where malicious user input is used to alter the structure of a command (a SQL query in the case of SQL Injection and JavaScript code in the case of Cross-Site Scripting).
+Developers of web applications must have proper sanitization routines in place to use user input as part of these commands.
 
-	Our research focuses on a lesser known injection attack known as E-Mail Header Injection.
-E-Mail Header Injection can be considered as the e-mail equivalent of HTTP Header Injection vulnerability~\cite{wiki:HTTP_headerinjection}.
-The vulnerability exists in the reference implementation of the built-in \texttt{mail} functionality in popular languages like PHP, Java, Python, and Ruby.
-With the proper injection string, this vulnerability can be exploited to inject additional headers and/or modify existing headers in an e-mail message --- with the potential to alter the contents of the e-mail message --- while still appearing to be from a legitimate source.
+\ehi vulnerabilities are a lesser-known command injection vulnerability.
+\ehi can be considered as the \email equivalent of HTTP Header Injection~\cite{wiki:HTTP_headerinjection}.
+This vulnerability exists in the implementation of the built-in \texttt{mail} functionality in popular languages such as PHP, Java, Python, and Ruby.
+With the proper injection string, \ehi vulnerabilities can be exploited by an attacker to inject additional headers, modify existing headers, or alter the contents of the \email---while still appearing to be from a legitimate source.
+\ehi exploits allow an attacker to perform \email spoofing, resulting in phishing attacks \emph{that are sent from the actual \email server}.
 
-	E-Mail Header Injection attacks have the potential to allow an attacker to perform e-mail spoofing, resulting in phishing attacks that can lead to identity theft.
-	The objective of our research is to study the prevalence of this vulnerability on the World Wide Web, and identify whether further research is required in this area.
+%% The objective of our research is to study the prevalence of this vulnerability on the World Wide Web, and identify whether further research is required in this area.
 
-	We performed an expansive crawl of the web, extracting forms with e-mail fields, and injecting them with different payloads to infer the existence of E-Mail Header Injection vulnerability.
-We then audited received e-mails to see if any of the injected data was present.
+While some command injection vulnerabilities have received extensive attention from the research community, \ehi vulnerabilities have received little focus.
+Therefore, we study the prevalence of \ehi vulnerabilities on the web.
+We performed a crawl of the web, extracted forms with \email fields, and injected them with different payloads to infer the existence of an \ehi vulnerability.
+We then audited received \emails to see if any of the injected data was present.
 This allowed us to classify whether a particular URL was vulnerable to the attack.
-The entire system works in a black-box manner, without looking at the web application's source code, and only analyzes the e-mails we receive based on the injected payloads.
+Our automated system works in a black-box manner, without looking at the web application's source code, and only analyzes the \emails we receive based on the injected payloads.
+\\
 
-We hope that our research sheds some light on this relatively less well-known vulnerability, and find out its prevalence on the World Wide Web. In summary, we make the following contributions:
+\noindent{}In summary, we make the following contributions:
+
 \begin{itemize}
 
-	\item{A black-box approach to detecting the presence of E-Mail Header Injection vulnerability in a web application.}
+\item We develop a black-box approach to detect \ehi vulnerabilities in a web application.
 
-	\item{A detection and classification tool based on the above approach, which will automatically detect such E-Mail Header Injection vulnerabilities in a web application.}
+\item We develop a system to crawl the web and automatically detect \ehi vulnerabilities.
 
-	\item{A quantification of the presence of such vulnerabilities on the World Wide Web, based on a crawl of the Web, including \urls\ URLs and \forms\ forms.}
+\item We use our system to crawl \urls URLs, and we find \success URLs vulnerable to \ehi across \domains domains.
 

### 2016-05-20 Background/history.tex
Edits to background section.

@@
-\subsection{History of E-Mail Injection}
+\subsection{History of \ehi}
 
-E-Mail Header Injection seems to have been first documented over a decade ago, in a late 2004 article on phpsecure.info~\cite{Tobozo} accredited to user \lstinline|tobozo@phpsecure.info| describing how this vulnerability existed in the reference implementation of the \texttt{mail()} function in PHP, and how it can be exploited.
-More recently, a blog post by Damon Kohler~\cite{DK} and an accompanying wiki article~\cite{Injection} describe the attack vector and outline a few defense measures for the same.
+We found the first \ehi description in a late 2004 article on phpsecure.info~\cite{Tobozo} accredited to user \lstinline|tobozo@phpsecure.info| describing how an \ehi vulnerability existed in the implementation of the \texttt{mail()} function in PHP and how it can be exploited.
+More recently, a blog post by Damon Kohler~\cite{DK} and an accompanying wiki article~\cite{Injection} describe the attack vector and outline few defense measures for \ehi vulnerabilities.
 
-As this vulnerability was initially found in the \texttt{mail()} function of PHP, E-Mail Header Injection can be traced to as early as the beginning of the 2000's, present in the \texttt{mail()} implementation of PHP 4.0.
+%% As this vulnerability was initially found in the \texttt{mail()} function of PHP, \ehi can be traced to as early as the beginning of the 2000's, present in the \texttt{mail()} implementation of PHP 4.0.
 
@@
 This code takes in user input from the PHP superglobal \texttt{\$\_REQUEST[\textquotesingle email\textquotesingle]}, and stores it in the variable \texttt{\$from}, which is later passed to the \texttt{mail()} function to construct and send the e-mail.
+
 \input{Background/php.tex}
 
-When this code is given the malicious input \texttt{\lstinline{sai@sai.com\\nBCC:spc@spc.com}} as the value of the \texttt{\$\_REQUEST[\textquotesingle email\textquotesingle]}, it generates the SMTP Headers shown in Listing~\ref{code:smtpheaders}.
+% TODO: Change all domains to example.com
+% TODO: Sai, this is the first time we mention SMTP, need more background and a reference to the RFC.
+
+\textbf{Adam: This example is not correct, the STMP headers in listing 2 should have the "From" headers from the injection.}
+
+When this code is given the malicious input \texttt{\lstinline{sai@sai.com\\nCC:spc@spc.com}} as the value of the \texttt{\$\_REQUEST[\textquotesingle email\textquotesingle]}, it generates the SMTP Headers shown in Listing~\ref{code:smtpheaders}.
 It can be seen that the \texttt{CC} (carbon copy) header that we injected appears as part of the resulting SMTP message.

### 2016-05-20 Background/impact.tex
Edits to background section.

@@
-\subsection{Potential Impact}
+\subsection{Impact of \ehi}
 
-The impact of the vulnerability can be pretty far-reaching.
-Table~\ref{tab:usage} shows the current server-side language usage statistics on the Web~\cite{W3techs}.
+The impact of an \ehi vulnerability can be far-reaching. According to
+w3tech, PHP, Java, Python, and Ruby (combined) account for over
+85\%\,\footnotemark{} of the server-side programming languages in
+websites measured, and the default implementation of the \email functionality of these languages is vulnerable to \ehi.
 
-\begin{table}[!tb]
-	\centering
-	\begin{tabular}{|p{4cm}|p{4cm}|}
-		\hline
-		\multicolumn{1}{|c|}{\textbf{Server Side Language}} & \multicolumn{1}{c|}{\textbf{\% of Usage}}\\
-		\hline
-		PHP & 81.9\\
-		\hline
-		Java & 3.1\\
-		\hline
-		Ruby & 0.6\\
-		\hline
-		Python & 0.2\\
-		\hline
+\footnotetext{A website may use more than one server-side programming language.}
 
-	\end{tabular}
-	\caption[\titlecap{Language usage statistics}]{Language usage statistics compiled from w3techs~\cite{W3techs}.}
-	\label{tab:usage}
-\end{table}
+%% \begin{table}[!tb]
+%% 	\centering
+%% 	\begin{tabular}{|p{4cm}|p{4cm}|}
+%% 		\hline
+%% 		\multicolumn{1}{|c|}{\textbf{Server Side Language}} & \multicolumn{1}{c|}{\textbf{\% of Usage}}\\
+%% 		\hline
+%% 		PHP & 81.9\\
+%% 		\hline
+%% 		Java & 3.1\\
+%% 		\hline
+%% 		Ruby & 0.6\\
+%% 		\hline
+%% 		Python & 0.2\\
+%% 		\hline
 
-PHP, Java, Python, and Ruby (combined) account for over 85\%\,\footnotemark{} of the websites measured. The vulnerability can be exploited to do potentially any of the following:
+%% 	\end{tabular}
+%% 	\caption[\titlecap{Language usage statistics}]{Language usage statistics compiled from w3techs~\cite{W3techs}.}
+%% 	\label{tab:usage}
+%% \end{table}
 
-\footnotetext{A website may use more than one server-side programming language}
+An \ehi vulnerability can be exploited to do potentially any of the
+following:
 
-\begin{itemize}
-	\item Phishing and Spoofing Attacks\\
-    Phishing~\cite{phishing} (a variation of spoofing~\cite{spoofing_attack}) refers to an attack where the recipient of an e-mail is made to believe that the e-mail is a legitimate one.
-The e-mail usually redirects them to a malicious website, which then steals their credentials.
+\noindent \textbf{Phishing and Spoofing Attacks} 
+    Phishing~\cite{phishing} (a variation of spoofing~\cite{spoofing_attack}) refers to an attack where the recipient of an \email is made to believe that the \email is  legitimate when it was really created by a malicious party.
+The \email usually redirects the victim to a malicious website, which then steals their credentials or infects their computer with malware (via a drive-by-download).
 
-    E-Mail Header Injection gives attackers the ability to inject arbitrary headers into an e-mail sent by a website and control the output of the e-mail.
-This adds credibility to the generated e-mail, as it is sent right from the websites and people are more ready to trust e-mail that is received from the website directly and can thus result in more successful phishing attacks.
+    \ehi gives attackers the ability to inject arbitrary headers into an \email sent by a website \emph{and control the output of the \email}.
+This adds credibility to the generated \email, as it is sent from the website's mail server and users (and anti-spam defenses) are more likely to trust an e-mail that is received from the proper mail server.
+Therefore, attackers could leverage \ehi vulnerabilities to perform enhanced phishing attacks.
 
-	\item Spam Networks\\
-	Spam networks can use E-Mail Header Injection vulnerabilities on the ability to send a large amount of e-mail from servers that are trusted.
-By adding additional \texttt{cc} or \texttt{bcc} headers to the generated e-mail, attackers can easily achieve this effect.
+\noindent\textbf{Spam Networks}
+	Spam networks can use \ehi vulnerabilities to send a large amount of \email from servers that are trusted.
+By adding additional \texttt{cc} or \texttt{bcc} headers to the generated e-mail, attackers can easily choose the recipient of the spam email.
 
-	Due to the e-mails being from trusted domains, recipient e-mail clients might not flag them as spam.
-If they do flag them as spam, then that can lead to the website being blacklisted as a spam generator.
+	Due to the \email being from trusted domains, recipient \email clients and anti-spam systems might not flag them as spam.
+If they do flag them as spam, then that can lead to the website being blacklisted as a spam generator (which would cause a Denial of Service on the vulnerable web application).
 
-	\item Information Extraction of legitimate users\\
-	E-Mails can contains sensitive data that is meant to be accessed only by the user.
-Due to E-Mail Header Injection, an attacker can easily add a \texttt{bcc} header, and send the e-mail to himself, thereby extracting important information.
+\noindent\textbf{Information Extraction}
+	\emails can contain sensitive data that is meant to be accessed only by the user.
+Due to an \ehi vulnerability, an attacker can add a \texttt{bcc} header, and the \email server will send a copy of the private \email to the attacker, thereby extracting important information.
 	User privacy can thus be compromised, and loss of private information can by itself lead to other attacks.
 
-	\item Denial of service by attacking the underlying mail server\\
-    Denial of service attacks (DoS), can also be aided by E-Mail Header Injection.
-The ability to send hundreds of thousands of e-mails by just injecting one header field can result in overloading the mail server, and cause crashes and/or instability.
-\end{itemize}
+    \noindent\textbf{Denial of Service}
+    Denial of service attacks (DoS), can also be caused by exploiting an \ehi vulnerability.
+The ability to send many \emails by injecting one header field can result in overloading the mail server and cause crashes or instability.
 
-It is evident that E-Mail Header Injection is a critical vulnerability that web applications must address.
+%It is evident that E-Mail Header Injection is a critical vulnerability that web applications must address.

### 2016-05-20 Background/lang_aff.tex
Edits to background section.

--- 2016-05-13 Background/lang_aff.tex
@@
 \label{languages}
-This section describes the popular languages which exhibit this type of vulnerability.
-This section is not intended as a complete reference of vulnerable functions and methods, but rather as a guide that specifies which parts of the language are known to have the vulnerability.
+This section describes the popular programming languages that contain \ehi vulnerabilities in their standard email libraries.
+This section is not intended as a complete reference of vulnerable functions and methods, but rather as a guide that specifies which parts of the language are vulnerable.
 
-\begin{itemize}
-\item{\textbf{PHP}} - PHP was one of the first languages found to have this vulnerability in its implementation of the \texttt{mail()} function.
+\noindent{\textbf{PHP}} was one of the first languages found to be vulnerable to \ehi in its implementation of the \texttt{mail()} function at the time of release of PHP~4.0.
 The early finding of this vulnerability can be attributed in part to the success and popularity of the language for creating web pages.
-According to w3techs \cite{W3techs}, PHP is used by 81.9\% of all the websites in existence, thereby creating the possibility of this vulnerability to be widespread.
+According to w3techs~\cite{W3techs}, PHP is used by 81.9\% of all the websites.
 
-After 13 further iterations of the language since the 4.0 release (the current version is 7.1), the \texttt{mail()} function is yet to be fixed after 15 years.
-However, it is specified in the PHP documentation \cite{PHPDocs} that the \texttt{mail()} function does not protect against this vulnerability.
+After 13 further iterations of PHP since the 4.0 release (the current version is 7.1), the \texttt{mail()} function is yet to be fixed after 15 years.
+However, it is specified in the PHP documentation~\cite{PHPDocs} that the \texttt{mail()} function does not protect against \ehi.
 A working code sample of the vulnerability, written in PHP~5.6 (latest well-supported version), is shown in  Listing~\ref{code:phpemi}.
 
-\item{\textbf{Python}} -
-A bug was filed about the vulnerability in Python's implementation of the \texttt{email.header} library and its header parsing functions allowing newlines in early 2009, which was followed up with a partial patch in early 2011.
+\noindent{\textbf{Python}}
+A bug was filed about an \ehi vulnerability in Python's implementation of the \texttt{email.header} library and the header parsing functions allowing newlines in early 2009, which was followed by a partial patch in early 2011.
 
-Unfortunately, the bug fix was only for the \texttt{email.header} package, and thus is still prevalent in other frequently used packages such as \texttt{email.parser}, where both the classic \texttt{Parser()} and the newer \texttt{FeedParser()} exhibit the vulnerability even in the latest versions - \texttt{2.7.11} and \texttt{3.5}.
+Unfortunately, the bug fix was only for the \texttt{email.header} package, and thus exists in other frequently used packages such as \texttt{email.parser}, where both the classic \texttt{Parser()} and the newer \texttt{FeedParser()} contain \ehi vulnerabilities even in the latest versions: \texttt{2.7.11} and \texttt{3.5}.
 The bug fix was also not backported to older versions of Python.
@@
 A working code sample of the vulnerability, written in Python 2.7.11, is shown in Listing~\ref{code:pyemi}.
+
 \input{Background/py.tex}
 
-\item{\textbf{Java}} -
-Java has a bug report about E-Mail Header Injection filed against its JavaMail API.
-A detailed write-up by Alexandre Herzog \cite{Herzog.2014} is complete with a proof of concept program that exploits the API to inject headers.
+\noindent{\textbf{Java}} has a bug report about \ehi filed against its \texttt{JavaMail} API.
+A detailed write-up by Alexandre Herzog~\cite{Herzog.2014} contains a proof-of-concept program that exploits the API to inject headers.
 
-\item{\textbf{Ruby}} -
-From our preliminary testing, Ruby's built-in Net::SMTP library has this vulnerability. This is not documented on the library's homepage.
+\noindent{\textbf{Ruby}} 
+From our preliminary testing Ruby's built-in \texttt{Net::SMTP} library also has an \ehi library. This is not documented on the library's homepage.
 %A working code sample of the vulnerability, written in Ruby 2.0.0 (the latest stable version at the time of writing), is shown in Listing~\ref{code:rubyemi}.
@@
 %\input{Background/ruby.tex}
-
-\end{itemize}

### 2016-05-20 Background/pbm_bg.tex
Edits to background section.

@@
-E-Mail Header Injection belongs to a broad class of vulnerabilities known simply as injection attacks.
-However, unlike its more popular siblings, SQL injection~\cite{sql1}, \cite{sql0}, \cite{sql2}, Cross-Site Scripting (XSS)~\cite{Injection1}, \cite{KleinAmit} or even HTTP Header Injection~\cite{sessionride}, relatively little research is available on E-Mail Header Injection.
+\ehi belongs to a broad class of vulnerabilities known as command injection vulnerabilities.
+However, unlike its more popular siblings, SQL injection~\cite{sql1, sql0, sql2}, Cross-Site Scripting~\cite{Injection1, KleinAmit}, or HTTP Header Injection~\cite{sessionride}, relatively little research is available on \ehi vulnerabilities.
 
-As with other vulnerabilities in this class, E-Mail Header Injection is caused due to improper sanitization (or lack thereof) of user input.
-If the script that constructs e-mails from user input fails to check for the presence of e-mail headers in the user input, a malicious user --- using a well-crafted payload --- can control the headers set for this particular e-mail.
-This can be leveraged to enable malicious attacks, including, but not limited to, spoofing, phishing, etc.
+As with other vulnerabilities in this class, \ehi is caused due to improper or nonexistent sanitization of user input.
+If the program that constructs \emails from user input fails to check for the presence of \email headers in the user input, a malicious user---using a well-crafted payload---can control the headers set for this particular e-mail.
+\ehi vulnerabilities can be leveraged to enable malicious attacks, including, but not limited to, spoofing or phishing.

### 2016-05-20 Background/php.tex
Edits to background section.

@@
-\lstset{language=PHP,caption={PHP program with e-mail header injection vulnerability.},label={code:phpemi}}
-\begin{lstlisting}
+\begin{lstlisting}[language=PHP,caption={PHP program with e-mail
+      header injection vulnerability.},label={code:phpemi}, float]
 $from = $_REQUEST['email'];

### 2016-05-20 Background/py.tex
Edits to background section.

@@
-\lstset{language=Python,caption={Python program with e-mail header injection vulnerability.},label={code:pyemi}}
-\begin{lstlisting}
+\begin{lstlisting}[language=Python,caption={Python program with e-mail
+      header injection vulnerability.},label={code:pyemi}, float]
 from email.parser import Parser

### 2016-05-20 Background/ruby.tex
Edits to background section.

@@
-\lstset{language=Ruby,caption={Ruby program with e-mail header injection vulnerability.},label={code:rubyemi}}
-\begin{lstlisting}
+\begin{lstlisting}[language=Ruby,caption={Ruby program with e-mail
+      header injection vulnerability.},label={code:rubyemi}, float]
 require 'sinatra'

### 2016-05-20 Discussion/limits.tex
Edits to background section.

@@
 
-       	\lstset{language=HTML,caption={E-Mail field checker - false positives, the system incorrectly classifies this as an e-mail form.},label={code:false_positive}}
-       	\begin{lstlisting}
+       	\begin{lstlisting}[language=HTML,caption={E-Mail field checker
+              - false positives, the system incorrectly classifies
+              this as an e-mail form.},label={code:false_positive}, float]
 <form method="post">
@@
 
-\lstset{language=HTML,caption={HTML page with e-mail form, written in a different language - French.},label={code:htmlfrench}, literate=%
-	{é}{{\'e}}1}
-\begin{lstlisting}
+\begin{lstlisting}[language=HTML,caption={HTML page with e-mail form, written in a different language - French.},label={code:htmlfrench}, literate=%
+	{é}{{\'e}}1, float]
 <!doctype html>

### 2016-05-20 System/proof_of_concept.tex
Edits to background section.

@@
 
-\lstset{language=HTML,caption={HTML page for showcasing e-mail header injection, a simple front-end for our examples.},label={code:html}}
-\begin{lstlisting}
+\begin{lstlisting}[language=HTML,caption={HTML page for showcasing
+      e-mail header injection, a simple front-end for our
+      examples.},label={code:html}, float]
 <!doctype html>

### 2016-05-21 Background/history.tex
fixed the todos in intro, abstract and background added paragraph and ref to smtp, added ref to command injection changed domains to example.com

@@
 
-% TODO: Change all domains to example.com
+% TODO: Change all domains to example.com - DONE.
 % TODO: Sai, this is the first time we mention SMTP, need more background and a reference to the RFC.
 
-\textbf{Adam: This example is not correct, the STMP headers in listing 2 should have the "From" headers from the injection.}
-
-When this code is given the malicious input \texttt{\lstinline{sai@sai.com\\nCC:spc@spc.com}} as the value of the \texttt{\$\_REQUEST[\textquotesingle email\textquotesingle]}, it generates the SMTP Headers shown in Listing~\ref{code:smtpheaders}.
+\begin{sloppypar}
+When this code is given the malicious input \texttt{\lstinline{abc@example.com\\nCC:spc@example.com}} as the value of the \texttt{\$\_REQUEST[\textquotesingle email\textquotesingle]}, it generates the equivalent SMTP Headers shown in Listing~\ref{code:smtpheaders}.
 It can be seen that the \texttt{CC} (carbon copy) header that we injected appears as part of the resulting SMTP message.
@@
 %\input{Background/history_table}
+\end{sloppypar}

### 2016-05-21 Background/py.tex
fixed the todos in intro, abstract and background added paragraph and ref to smtp, added ref to command injection changed domains to example.com

@@
 # attack string => 
-# 's@s.com\nBCC:spc@spc.com'
+# 'abc@example.com\nBCC:spc@example.com'
 # for form["email"]
 
-# to:s@s.com AND bcc:spc@spc.com 
+# to:abc@example.com AND bcc:spc@example.com 
 # are added to the headers

### 2016-05-21 introduction.tex
fixed the todos in intro, abstract and background added paragraph and ref to smtp, added ref to command injection changed domains to example.com

@@
 
-% TODO: Sai, can you add a reference to command injection vulnerabilities here?
-Many common and well-known web application vulnerabilities, such as SQL Injection and Cross-Site Scripting~\cite{OWASPT10}, are command injection vulnerabilities, where malicious user input is used to alter the structure of a command (a SQL query in the case of SQL Injection and JavaScript code in the case of Cross-Site Scripting).
+% TODO: Sai, can you add a reference to command injection vulnerabilities here? DONE.
+Many common and well-known web application vulnerabilities, such as SQL Injection and Cross-Site Scripting~\cite{OWASPT10}, are command injection vulnerabilities~\cite{commandinjection}, where malicious user input is used to alter the structure of a command (a SQL query in the case of SQL Injection and JavaScript code in the case of Cross-Site Scripting).
 Developers of web applications must have proper sanitization routines in place to use user input as part of these commands.
@@
 This vulnerability exists in the implementation of the built-in \texttt{mail} functionality in popular languages such as PHP, Java, Python, and Ruby.
+The format of \email messages is defined by the Simple Mail Transfer Protocol (SMTP)~\cite{rfc5322}.
+Each \email message is represented by a series of headers separated by newlines, followed by the body content (separated from the headers by two newlines).
+Some of these headers are mandatory (From, To, Date), but the headers could also include other information like the Subject, CC, BCC, etc.
+
+\textbf{Sai: I believe that the discussion of SMTP Headers belongs here, before we say that E-Mail Header Injection can manipulate the headers.
+Do I need to include the message format as a listing?
+I think its superfluous, but let me know.}
+
 With the proper injection string, \ehi vulnerabilities can be exploited by an attacker to inject additional headers, modify existing headers, or alter the contents of the \email---while still appearing to be from a legitimate source.

### 2016-05-23 System/approach.tex
fixed citation spaces
fixed laws wiki entries
Halfway through System Section

@@
 \label{sys:appr}
-We took a black-box approach to measure the prevalence of E-Mail Header Injection vulnerability on the World Wide Web.
-Black-box testing \cite{wiki:Black-box_testing} is a way to examine the functionality of an application without looking at its source code.
+We took a black-box approach to measure the prevalence of \ehi vulnerability on the web.
+Black-box testing~\cite{Beizer:1995:BTT:202699} is a way to examine the functionality of an application without analyzing its source code.
 
-As we did not have the source code for each of these websites, black-box testing was the ideal approach for this project.
-Black-box testing allows our system to detect E-Mail Header Injection vulnerabilities in any server-side language (not simply those we identified in Section~\ref{languages}).
-The overall architecture of our system is presented in Figure~\ref{fig:overall}.
-The components shown in Figure~\ref{fig:overall} can be more broadly categorized into different modules, as discussed in the following section.
+Black-box testing allows our system to detect \ehi vulnerabilities in \emph{any} server-side language (not simply those we identified in Section~\ref{languages}).
+
+The overall architecture of our system is presented in Figure~\ref{fig:overall}. The components shown in Figure~\ref{fig:overall} are discussed in the following section.
 
@@
 	\centering
-	\includegraphics[width=14cm, height=7cm]{overall}
+	\includegraphics[width=.8\textwidth]{overall}
 	\caption{Overall system architecture.}

### 2016-05-23 System/components.tex
Edits to background section.
Halfway through System Section

@@
 
-The Data Gathering module and Payload Injection module are made up of a number of smaller components. This section describes in detail the functionality of each of the components.
+The Data Gathering module and Payload Injection modules are composed of smaller components. This section describes the functionality of each of the components.
 
@@
 \label{Comp:Crawler}
-We used an open-source Apache Nutch based Crawler.
-The Crawler provides us with a continuous feed of URLs and the HTML contained in those pages.
-This feed is sent to our Form Parser over a Celery Queue.
+We used an open-source Apache Nutch based Crawler~\cite{nutch}.
+The Crawler continuously crawls the web.
+The Crawler provides the system with a continuous feed of URLs and the HTML contained in those pages.
 
@@
 \label{Comp:FP}
-The actual pipeline begins at the Form Parser. This module is responsible for parsing the HTML and retrieving data about the forms on the page, including the following:
+The actual analysis pipeline begins at the Form Parser. This module is responsible for parsing the HTML and retrieving data about the HTML forms on the page, including the following:
 \begin{itemize}
-	\item Form attributes, such as method and action. These dictate where we send the HTTP request and what kind of request it is (GET or POST).
-	\item Data about the input fields, such as their attributes, names, and default values.
+	\item Form attributes, such as \texttt{method} and \texttt{action}. These dictate the resulting URL for the HTTP request and the method of the HTTP request.
+	\item Data about the form input fields, such as their attributes, names, and default values.
 The default values are essential for fields like \colorbox{lightgray}{\lstinline{<input type="hidden">}} as these fields are usually used to check for the submission of forms by bots.
-	\item Presence of the \colorbox{lightgray}{\lstinline{<base>}} element in the HTML, as this affects the final URL to which the form is to be submitted.
-	\item Headers associated with the page, such as \texttt{referrer}. Once again, these were required to avoid the website from ignoring our system as a bot.
+	\item Presence of the \colorbox{lightgray}{\lstinline{<base>}} element in the HTML, as this affects the final URL to which the form is to be submitted (if the \texttt{action} attribute is a relative URL).
+      % Adam: this is not correct, the referrer header won't be used when we make the request. We will set the referrer header when we make the request to URL that the form is on
+	%% \item Headers associated with the page, such as \texttt{referrer}. Once again, these were required to avoid the website from ignoring our system as a bot.
 \end{itemize} 
-The Form Parser stores all this data in our database, so as to allow us to reconstruct the forms later for fuzzing, as required.
+The Form Parser stores all this data in our database, so as to allow the system to reconstruct all data necessary for fuzzing the web application.
 
-\subsubsection{E-Mail Field Checker}
+\subsubsection{\Email Field Checker}
 \label{Comp:EMFC}
-The E-Mail Field Checker script is the final stage in the Data Gathering pipeline.
-It receives the output of the previous stage---form data from the queue---and checks for the presence of e-mail fields in those forms.
-If any e-mail fields are found, it stores references to these forms in a separate table.
-This separates the forms that are potentially vulnerable from the forms that are not.
+The \Email Field Checker is the final stage in the Data Gathering module.
+It receives the output of the previous stage---HTML form data---and checks for the presence of \email fields in those forms.
+If any \email fields are found, it stores references to these forms.
+The intuition here is that we do not want to try to fuzz all HTML forms on the web to look for \ehi vulnerabilities, rather just those HTML forms that are likely to invoke server-side email functionality.
 
-The E-Mail Field Checker searches for the words \texttt{e-mail}, \texttt{mail} or \texttt{email} within the form, instead of an explicit e-mail field (e.g.,\ \colorbox{lightgray}{\lstinline{<input type="email">}}).
-This is by design, taking into account a very common design pattern used by web developers, where they may have a text field with an \texttt{id} or \texttt{name} set to \texttt{email}, instead of an actual e-mail field, for purposes of backward compatibility with older browsers.
+The \Email Field Checker searches for the words \texttt{e-mail}, \texttt{mail} or \texttt{email} within the form, instead of an explicit HTML5 \email field (e.g.,\ \colorbox{lightgray}{\lstinline{<input type="email">}}).
+This is by design, taking into account a common design pattern used by web developers, where they may have a text field with an \texttt{id} or \texttt{name} attribute set to \texttt{email}, instead of an actual \email type attribute, for purposes of backward compatibility with older browsers.
 
-Compared to searching for explicit e-mail fields, by searching for the presence of the words \texttt{e-mail}, \texttt{mail} or \texttt{email} in the form, we are assured very few false negatives.
-This is because our system is bound to find e-mail fields with their \texttt{type}, \texttt{name}, or \texttt{id} set to one of these words.
+%% Compared to searching for explicit \email fields, by searching for the presence of the words \texttt{\email}, \texttt{mail} or \texttt{email} in the form, we are assured very few false negatives.
+This is because our system is bound to find \email fields with their \texttt{type}, \texttt{name}, or \texttt{id} set to one of these words.
 The system is also substantially faster as we do not have to parse the individual form fields at this point in the pipeline.
@@
 
-The output of this stage is stored in the database for persistence and acts as the input to the `Payload Injection' pipeline.
+The output of this stage is stored in the database for persistence and acts as the input to the Payload Injection module.
 
-\subsubsection{E-Mail Form Retriever}
+% Adam: This is where I am editing
+\subsubsection{\Email Form Retriever}
 \label{Comp:EMFR}
-The E-Mail Form Retriever is the first stage in the Payload Injection Pipeline. It has the following important functions:
+The \Email Form Retriever is the first stage in the Payload Injection module. It has the following important functions:
 \begin{itemize}
@@
 \label{Comp:Fuzzer:nmp}
-The regular or non-malicious payload is a straight forward E-Mail address of the format -- \texttt{reguser(xxxx)@example.com}, where \texttt{xxxx} is replaced by our internal \texttt{form\_id}, to create a one-to-one mapping of the payloads to the forms, and \texttt{example.com} is replaced by the required domain.
+The regular or non-malicious payload is a straight forward \Email address of the format -- \texttt{reguser(xxxx)@example.com}, where \texttt{xxxx} is replaced by our internal \texttt{form\_id}, to create a one-to-one mapping of the payloads to the forms, and \texttt{example.com} is replaced by the required domain.
 This non-malicious payload allows us to check whether we can inject data into a form and whether we can overcome the `anti-bot' measures on the given website, without attempting to fuzz the website.
@@
 In the malicious payload scenario, we inject the fields with the \texttt{bcc} (blind carbon copy) element.
-If the vulnerability is present, this will cause the server to send a copy of the e-mail to the e-mail address we added as part of the \texttt{bcc} field.
+If the vulnerability is present, this will cause the server to send a copy of the \email to the \email address we added as part of the \texttt{bcc} field.
 
@@
 The malicious payloads consist of 4 different payloads. Each of these payloads is crafted for a particular use case. The four payloads are:
-\lstset{language=html}
+
 \begin{enumerate}
@@
 
-Once the data (including the payload) for the form is ready, the Fuzzer constructs the appropriate HTTP request (GET or POST) and sends the HTTP request to the URL that was generated by the E-Mail Form Retriever (Section~\ref{Comp:EMFR}).
+Once the data (including the payload) for the form is ready, the Fuzzer constructs the appropriate HTTP request (GET or POST) and sends the HTTP request to the URL that was generated by the \Email Form Retriever (Section~\ref{Comp:EMFR}).
 
@@
 \label{Comp:EMA}
-The Injection Verification module checks for the presence of injected data in the received e-mails.
-This module works on the e-mails received and stored by our Postfix server, and depending on the user who received the e-mail, it performs different functions.
-\paragraph{Analyzing regular e-mail}
+The Injection Verification module checks for the presence of injected data in the received \emails.
+This module works on the \emails received and stored by our Postfix server, and depending on the user who received the \email, it performs different functions.
+\paragraph{Analyzing regular \email}
 \sloppy
-`Regular e-mail' refers to the e-mails received by the \colorbox{lightgray}{\lstinline{reguser(xxxx)@example.com}} --- where \texttt{xxxx} is our internal \texttt{form\_id} --- that were sent due to injecting the `regular or non-malicious' payload (discussed in Section~\ref{Comp:Fuzzer:nmp}).
-The objective of the analysis on this e-mail is identify if the input fields that we injected with data appear on the resulting e-mail, and if so, which fields appear where.
+`Regular \email' refers to the \emails received by the \colorbox{lightgray}{\lstinline{reguser(xxxx)@example.com}} --- where \texttt{xxxx} is our internal \texttt{form\_id} --- that were sent due to injecting the `regular or non-malicious' payload (discussed in Section~\ref{Comp:Fuzzer:nmp}).
+The objective of the analysis on this \email is identify if the input fields that we injected with data appear on the resulting \email, and if so, which fields appear where.
 
-To find this, we read through each received e-mail, and check whether \emph{any} of the fields we injected with data appear as part of either the headers or the body of the e-mail.
-If they do, we add them to the list of fields that can potentially result in an E-Mail Header Injection for the given e-mail.
+To find this, we read through each received \email, and check whether \emph{any} of the fields we injected with data appear as part of either the headers or the body of the \email.
+If they do, we add them to the list of fields that can potentially result in an \ehi for the given \email.
 we then pass on this information back to the Fuzzer pipeline, along with the \texttt{form\_id}, so that the Fuzzer can now inject the malicious payloads into the same form.
 
-\paragraph{Analyzing e-mail with payloads}
-The `e-mails with payloads' refer to e-mails received by either the \colorbox{lightgray}{\lstinline{nuser(xxxx)@example.com}} or \colorbox{lightgray}{\lstinline{maluser(xxxx)@example.com}} accounts.
-These e-mails were received due to injecting the malicious payloads that were discussed in Section~\ref{Comp:Fuzzer:mp}.
-Analysis of these e-mails is considerably simpler than that of the regular e-mails.
-This is due to the fact that this involves lesser processing of the contents of the e-mail compared to the previous section.
+\paragraph{Analyzing \email with payloads}
+The `\emails with payloads' refer to \emails received by either the \colorbox{lightgray}{\lstinline{nuser(xxxx)@example.com}} or \colorbox{lightgray}{\lstinline{maluser(xxxx)@example.com}} accounts.
+These \emails were received due to injecting the malicious payloads that were discussed in Section~\ref{Comp:Fuzzer:mp}.
+Analysis of these \emails is considerably simpler than that of the regular \emails.
+This is due to the fact that this involves lesser processing of the contents of the \email compared to the previous section.
 \paragraph{Detecting injected \texttt{bcc} headers}
-As discussed in the payloads section~(\ref{Comp:Fuzzer:mp}), the payloads were crafted in such a way that the e-mails received by \texttt{maluser} account directly indicate the presence of the injected \texttt{bcc} field.
-Thus, we simply parse the E-Mails and store them in the Database.
+As discussed in the payloads section~(\ref{Comp:Fuzzer:mp}), the payloads were crafted in such a way that the \emails received by \texttt{maluser} account directly indicate the presence of the injected \texttt{bcc} field.
+Thus, we simply parse the \emails and store them in the Database.
 
@@
 \paragraph{Detecting injected \texttt{x-check} headers}
-E-Mails not received by the \texttt{maluser} account but by the \texttt{nuser} account constitute a special category of e-mails.
-These e-mails could have been generated due to two reasons:
+\Emails not received by the \texttt{maluser} account but by the \texttt{nuser} account constitute a special category of \emails.
+These \emails could have been generated due to two reasons:
 \begin{enumerate}
-	\item The websites performed some sanitization routines and stripped out the \texttt{bcc} part of the payload, thereby sending e-mails only to the \texttt{nuser} account.
-These e-mails then act as proof that the vulnerability was not found on the given website.
+	\item The websites performed some sanitization routines and stripped out the \texttt{bcc} part of the payload, thereby sending \emails only to the \texttt{nuser} account.
+These \emails then act as proof that the vulnerability was not found on the given website.
 	\item A more conducive scenario is when the \texttt{bcc} header was ignored for some reason, e.g.,\ Python's default behavior when it encounters duplicate headers.
-In this case, we check whether the e-mail contains the custom header \texttt{x-check}.
+In this case, we check whether the \email contains the custom header \texttt{x-check}.
 If it does, then this is a successful exploit of the vulnerability, and we store it in the database.

### 2016-05-23 System/sys_arch.tex
Halfway through System Section

@@
 \label{sys:arch}
-The black-box testing system can be divided broadly into two modules; Data Gathering and Payload Injection.
-\begin{enumerate}
-	\item Data Gathering\\
-	The Data Gathering module is primarily responsible for the following activities:
+Our system can be broadly divided into two modules: Data Gathering and Payload Injection.
+
+The Data Gathering module is responsible for the following activities:
 	\begin{itemize}
@@
 		\item Parse the HTML for the corresponding URL and store the relevant form data (Section~\ref{Comp:FP}).
-		\item Check for the presence of forms that allow the user to send/receive e-mail, and store references to these forms (Section~\ref{Comp:EMFC}).
+		\item Check for the presence of HTML forms that could allow a user to send/receive \email and store references to these forms (Section~\ref{Comp:EMFC}).
 	\end{itemize}
-	\item Payload Injection\\
-	The Payload Injection module is primarily responsible for the following activities:
+
+	The Payload Injection module is responsible for the following activities:
 	\begin{itemize}
-		\item Retrieve the forms that allow users of a website to send/receive e-mail and reconstruct these forms (Section~\ref{Comp:EMFR}).
+		\item Retrieve the HTML forms that could allow a user to send/receive \email and reconstruct these forms (Section~\ref{Comp:EMFR}).
 		\item Inject these forms with benign data (non-malicious payloads) and generate an HTTP request to the corresponding URL (Section~\ref{Comp:Fuzzer:nmp}).
-		\item Analyze the e-mails, extracting the header fields and checking for the presence of the injected payloads (Section~\ref{Comp:EMA}).
-		\item Inject the forms that sent us e-mails with malicious payloads, and generate an HTTP request to the corresponding URL to check if E-Mail Header Injection vulnerability exists in that form (Section~\ref{Comp:Fuzzer:mp}).
+		\item Analyze the received \emails, extracting the \email header fields and checking for the presence of the injected payloads (Section~\ref{Comp:EMA}).
+		\item Inject the HTTP requests that sent us \emails with malicious payloads, and generate an HTTP request to the corresponding URL to check if an \ehi vulnerability exists in that web application (Section~\ref{Comp:Fuzzer:mp}).
 	\end{itemize} 
-	The functionality of each component is discussed further in the `Components' section (Section~\ref{Comp}).
-The Payload Injection pipeline is not a linear, but cyclic process, as we inject different payloads and analyze the received e-mails.
-\end{enumerate}
+	%% The functionality of each component is discussed further in the `Components' section (Section~\ref{Comp}).
+The Payload Injection pipeline is not a linear, but cyclic process, as we inject different payloads and analyze the received \emails.

### 2016-05-23 Background/php.tex

@@
 $message = 'We need you to reset your password';
-$to = 'xyz@xyz.edu';
+$to = 'xyz@example.com';
 
@@
 // $_REQUEST['email'] => 
-// 's@s.com\nCC:spc@spc.com'
+// 'abc@example.com\nCC:spc@example.com'
 $retValue = mail($to, $subject, $message, "From: $from");
 // E-Mail gets sent to both 
-// xyz@xyz.edu AND spc@spc.com
+// xyz@example.com AND spc@example.com
 \end{lstlisting}

### 2016-05-23 Background/ruby.tex

@@
 message = """
-From: Sai <schand31@asu.edu>
+From: Sch <sch@example.com>
 Subject: SMTP e-mail test
@@
 # construct a post request with email set to attack_string
-# attack_string => sai@sai.com%0abcc:spc@spc.com%0aSubject:Hello
+# attack_string => sai@example.com%0abcc:spc@example.com%0aSubject:Hello
 Net::SMTP.start('localhost', 1025) do |smtp|
-smtp.send_message message, 'schand31@asu.edu',
+smtp.send_message message, 'sch@example.com',
 'to@todomain.com'

### 2016-05-23 abstract.tex

@@
 Of these \malfuzzed forms were tested with \ehi payloads and, of these, we found \success vulnerable URLs across \domains domains.
-Then, to demonstrate that \ehi vulnerabilities are actively being exploited to create a spamming platform, we found \ipsblacklist IPs that were vulnerable on spaming blacklists.
+Then, to demonstrate that \ehi vulnerabilities are actively being exploited to create a spamming platform, we found \ipsblacklist IPs that were vulnerable on spamming blacklists.
 This work shows that \ehi vulnerabilities are widespread widespread and deserve future research attention.

### 2016-05-23 System/components.tex
Finished edits to system section.

@@
 
-% Adam: This is where I am editing
 \subsubsection{\Email Form Retriever}
 \label{Comp:EMFR}
-The \Email Form Retriever is the first stage in the Payload Injection module. It has the following important functions:
+The \Email Form Retriever is the first stage in the Payload Injection module. It has the following functions:
 \begin{itemize}
-	\item Retrieve the newly inserted forms in the \texttt{email\_forms} table, checking to ensure no duplication occurs before the fuzzing stage.
-	\item Reconstruct each form, using the data stored in the \texttt{form} table, complete with input fields and their values.
-	\item Construct the URL for the \texttt{action} attribute of the form so that we can send the HTTP request to the correct URL. 
+	\item Retrieve new forms and ensure no duplication occurs before the fuzzing stage.
+	\item Reconstruct each form, using the stored form data, specifically the input fields and their values.
+	\item Construct the target URL for the \texttt{action} attribute of the form to create an HTTP request to the correct URL for fuzzing. 
 \end{itemize}
@@
 \label{Comp:Fuzzer}
-The Fuzzer is the heart of the system and is the only component that interacts directly with the external websites.
+% Adam: we should call these something else but modules. We already have the top two modules, which are composed of components, now we need to split these into something (not components again).
+The Fuzzer is the only component that interacts directly with the external web applications.
 The Fuzzer is split into smaller modules, each of which is responsible for a particular type of fuzzing.
-We inject payloads in two different stages, to improve the efficiency, and reduce the total number of HTTP requests we generate.
-This is because making HTTP requests is an expensive process~\cite{McGrath2009}, and can be a cause of bottlenecks in a Crawler-Fuzzer system~\cite{ShkapenyukTorstenSuel2001}.
-The two different types of payloads we use for fuzzing are:
+The system injects payloads in two stages: the goal is to reduce the total number of HTTP requests the system generates to detect an \ehi vulnerability.
+Making HTTP requests is an expensive process~\cite{McGrath2009}, and can cause bottlenecks in a Crawler-Fuzzer system~\cite{ShkapenyukTorstenSuel2001}.
+The two different types of payloads used for fuzzing are:
 \paragraph{Non-Malicious Payload}
 \label{Comp:Fuzzer:nmp}
-The regular or non-malicious payload is a straight forward \Email address of the format -- \texttt{reguser(xxxx)@example.com}, where \texttt{xxxx} is replaced by our internal \texttt{form\_id}, to create a one-to-one mapping of the payloads to the forms, and \texttt{example.com} is replaced by the required domain.
-This non-malicious payload allows us to check whether we can inject data into a form and whether we can overcome the `anti-bot' measures on the given website, without attempting to fuzz the website.
+The regular or non-malicious payload is simply an \email address.
+The goal is to see if the web application will send an \email message based on our input.
+The specific format of the \email is \texttt{reguser(xxxx)@example.com}, where \texttt{xxxx} is replaced by an internal id that uniquely maps the payload to the form, and \texttt{example.com} is replaced by our domain.
 
@@
 \label{Comp:Fuzzer:mp}
-In the malicious payload scenario, we inject the fields with the \texttt{bcc} (blind carbon copy) element.
-If the vulnerability is present, this will cause the server to send a copy of the \email to the \email address we added as part of the \texttt{bcc} field.
+After receiving an \email from a specific form, we then use the malicious payload to try to exploit an \ehi vulnerability.
+We inject the form parameters with the \texttt{bcc} (blind carbon copy) header.
+If the vulnerability is present, this will cause the server to send a copy of the \email to the \email address we added as the \texttt{bcc} field.
 
-We consider a special case: the addition of a \texttt{x-check:in} header field to the payloads. This is due to Python's exhibited behavior when attaching
+We consider a special case: the addition of an \texttt{x-check:in} header field to the payloads. This is due to Python's exhibited behavior when attaching
 headers.
-Instead of overwriting a header if it is already present, it ignores duplicate headers.
-So, in case the \texttt{bcc} field is already present as part of the headers, our injected \texttt{bcc} header would be ignored.
-To overcome this, we need to inject a new header that is not likely to be generated by the web application.
-Hence, we inject our own \texttt{x-check:in} header to ensure we can get results if the injection was successful.
+Instead of overwriting a header if it is already present, Python will ignore duplicate headers.
+So, if the \texttt{bcc} field is already present as part of the headers, our injected \texttt{bcc} header would be ignored.
+To overcome this, we inject a new header that is not likely to be generated by the web application.
 
-The malicious payloads consist of 4 different payloads. Each of these payloads is crafted for a particular use case. The four payloads are:
+We created four different malicious payloads. Each of these payloads is crafted for a particular use case. The four payloads are:
 
@@
 
-	This is the most minimal payload, it injects a `newline' character followed by the \texttt{bcc} field.
+	This payload is the most minimal payload: it injects a newline character followed by the \texttt{bcc} field.
 
@@
 
-	This payload is added for purposes of cross-platform fuzzing: \texttt{\textbackslash{}r\textbackslash{}n} is the `Carriage Return - New Line (CRLF)' used on Windows systems.
+	This payload is added for purposes of cross-platform fuzzing: \texttt{\textbackslash{}r\textbackslash{}n} is the ``Carriage Return - New Line (CRLF)'' used on Windows systems.
+%Adam: have a citation for this?
 
@@
 
-	As discussed above, the addition of the \texttt{x-check:in} header is to inject Python based websites.
+	As discussed previously, the addition of the \texttt{x-check:in} header is to inject Python-based web applications.
 
@@
 \end{enumerate}
-The \texttt{xxxx} in all of the payloads is replaced by our internal \texttt{form\_id}, so as to create a one-to-one mapping of the payloads to the forms.
+The \texttt{(xxxx)} in each payload is replaced by an internal unique id to create a one-to-one mapping of the payloads to the forms.
+% Adam: If we need to cut things for space, we can cut this next line and the payload coverage table.
 The coverage provided by each payload is shown in Table~\ref{tab:payloadcov}.\\
 
-\begin{table}[!htbp]
+\begin{table}[tbp]
 	\centering
@@
 \end{table}
+
 Along with the payload, the Fuzzer also injects data into the other fields of the form.
-This data must pass validation constraints on the individual input fields e.g.,\ for a name field, numbers might not be allowed.
-It is essential that the data we inject into the input fields adhere to the constraints.
-Our Fuzzer does this by making use of a `Data Dictionary' which has predefined `keys' and `values' for standard input fields such as \texttt{name}, \texttt{date}, \texttt{username}, \texttt{password}, \texttt{text}, and \texttt{submit}.
+This data must pass validation constraints on the individual input fields (e.g.,\ for a name field, numbers might not be allowed).
+To maximize the amount of vulnerabilities the system discovers, the data injected into the input fields should adhere to the constraints.
+The Fuzzer uses a ``Data Dictionary'' which has predefined ``keys'' and ``values'' for standard input fields such as \texttt{name}, \texttt{date}, \texttt{username}, \texttt{password}, \texttt{text}, and \texttt{submit}.
+% Adam: What does it mean here for these to be generated on-the-fly? Using templates?
 The default values for these are generated on-the-fly for each form, based on generally followed guidelines for such fields.
 For example, password fields should consist of at least one uppercase letter, one lowercase letter, and a special character.
+% Adam: can you add a sentence here about crawling and fuzzing fields on the web is an open problem (and cite ``Crawling the hidden web''
 
-Once the data (including the payload) for the form is ready, the Fuzzer constructs the appropriate HTTP request (GET or POST) and sends the HTTP request to the URL that was generated by the \Email Form Retriever (Section~\ref{Comp:EMFR}).
+When the fuzzed data is ready, the Fuzzer constructs the appropriate HTTP request (GET or POST) and sends the HTTP request to the URL that was generated by the \Email Form Retriever (Section~\ref{Comp:EMFR}).
 
@@
 The Injection Verification module checks for the presence of injected data in the received \emails.
-This module works on the \emails received and stored by our Postfix server, and depending on the user who received the \email, it performs different functions.
+This module works on the \emails received and stored by our Postfix server, and, depending on the user account that received the \email, it performs different functions.
 \paragraph{Analyzing regular \email}
 \sloppy
-`Regular \email' refers to the \emails received by the \colorbox{lightgray}{\lstinline{reguser(xxxx)@example.com}} --- where \texttt{xxxx} is our internal \texttt{form\_id} --- that were sent due to injecting the `regular or non-malicious' payload (discussed in Section~\ref{Comp:Fuzzer:nmp}).
+`Regular \email' refers to the \emails received by account \colorbox{lightgray}{\lstinline{reguser(xxxx)@example.com}} that were sent due to injecting the regular, non-malicious, payload (discussed in Section~\ref{Comp:Fuzzer:nmp}).
 The objective of the analysis on this \email is identify if the input fields that we injected with data appear on the resulting \email, and if so, which fields appear where.
 
-To find this, we read through each received \email, and check whether \emph{any} of the fields we injected with data appear as part of either the headers or the body of the \email.
-If they do, we add them to the list of fields that can potentially result in an \ehi for the given \email.
-we then pass on this information back to the Fuzzer pipeline, along with the \texttt{form\_id}, so that the Fuzzer can now inject the malicious payloads into the same form.
+To find this, we parse each received \email, and check whether \emph{any} of the fields we injected with data appear as part of either the headers or the body of the \email.
+If they do, we add them to the list of fields that can potentially result in an \ehi vulnerability for the given \email.
+We then pass on this information back to the Fuzzer pipeline, along with the vulnerable form.
 
 \paragraph{Analyzing \email with payloads}
-The `\emails with payloads' refer to \emails received by either the \colorbox{lightgray}{\lstinline{nuser(xxxx)@example.com}} or \colorbox{lightgray}{\lstinline{maluser(xxxx)@example.com}} accounts.
-These \emails were received due to injecting the malicious payloads that were discussed in Section~\ref{Comp:Fuzzer:mp}.
-Analysis of these \emails is considerably simpler than that of the regular \emails.
-This is due to the fact that this involves lesser processing of the contents of the \email compared to the previous section.
+The ``\emails with payloads'' refers to \emails received by either the \colorbox{lightgray}{\lstinline{nuser(xxxx)@example.com}} or \colorbox{lightgray}{\lstinline{maluser(xxxx)@example.com}} accounts.
+These \emails could only be received as a result of injecting the malicious payloads that were discussed in Section~\ref{Comp:Fuzzer:mp}.
+
 \paragraph{Detecting injected \texttt{bcc} headers}
-As discussed in the payloads section~(\ref{Comp:Fuzzer:mp}), the payloads were crafted in such a way that the \emails received by \texttt{maluser} account directly indicate the presence of the injected \texttt{bcc} field.
-Thus, we simply parse the \emails and store them in the Database.
+As discussed in the payloads section~(\ref{Comp:Fuzzer:mp}), the payloads were crafted such that the \emails received by the \texttt{maluser} account directly indicate the presence of the injected \texttt{bcc} field.
 
@@
 \begin{enumerate}
-	\item The websites performed some sanitization routines and stripped out the \texttt{bcc} part of the payload, thereby sending \emails only to the \texttt{nuser} account.
-These \emails then act as proof that the vulnerability was not found on the given website.
-	\item A more conducive scenario is when the \texttt{bcc} header was ignored for some reason, e.g.,\ Python's default behavior when it encounters duplicate headers.
-In this case, we check whether the \email contains the custom header \texttt{x-check}.
-If it does, then this is a successful exploit of the vulnerability, and we store it in the database.
+	\item The web application performed some sanitization routines and stripped out the \texttt{bcc} part of the payload, thereby sending \emails only to the \texttt{nuser} account.
+These \emails then act as proof that the vulnerability was not found on the given URL.
+	\item The \texttt{bcc} header can be ignored for other reasons (e.g.,\ Python's default behavior when it encounters duplicate headers).
+In this case, we check if the \email contains the custom header \texttt{x-check}.
+If it does, then this is a successful exploit of the vulnerability.
 \end{enumerate}

### 2016-05-23 System/proof_of_concept.tex
Edits to the Implementation section

@@
-\subsection*{Proof of Concept Attacks}
-This section describes how we validated our expectations.
-In order to do this, we constructed three sets of web applications in PHP, Python, and Ruby.
-Each of these applications was a simple web app that accepted user input to construct and send an E-Mail.
+\subsection{Validation}
+To validate our system, we constructed three sets of web applications in PHP, Python, and Ruby.
+Each of these applications was a simple web application that accepted user input to construct and send an \Email.
 
 The front-end for each of the three applications is shown in Listing~\ref{code:html}.
-The server-side code for the PHP and Python are shown in Listings~\ref{code:phpemi} and \ref{code:pyemi} respectively.
+The server-side code for the PHP and Python is shown in Listings~\ref{code:phpemi} and \ref{code:pyemi} respectively.
 
-We tested for the headers being injected in real-time by running an instance of MailCatcher, set to listen on all SMTP messages.
+% Adam: I think it might be nice to have the Ruby code here too.
+
+Before performing out wide scan of the web, we verified that our system was able to detect the \ehi vulnerabilities present in all the sample web applications.
+
+%% We tested for the headers being injected in real-time by running an instance of MailCatcher, set to listen on all SMTP messages.
 A sample screenshot of a fuzzed request for the Ruby backend (generated in PostMan) is shown in Figure~\ref{fig:postmanruby}.
-The e-mail sent due to injecting this payload (as captured by MailCatcher) is shown in Figure~\ref{fig:mailcatcherruby}.
-It can be seen that the headers have been added to the resulting e-mail, and we have successfully managed to overwrite the \texttt{Subject} field with our message, `hello'.
+The \email sent due to injecting this payload (as captured by MailCatcher) is shown in Figure~\ref{fig:mailcatcherruby}.
+It can be seen that the headers have been added to the resulting \email, and we have successfully managed to overwrite the \texttt{Subject} field with our message, `hello'.
 
-The astute reader might have noticed that in the given example we have used \texttt{\%0a} to separate the headers, while in Section~\ref{Comp:Fuzzer:mp}, we had used \texttt{\textbackslash{}n}.
+%% The astute reader might have noticed that in the given example we have used \texttt{\%0a} to separate the headers, while in Section~\ref{Comp:Fuzzer:mp}, we had used \texttt{\textbackslash{}n}.
 This is due to URL encoding~\cite{rfc1738}, wherein special characters in th URL are `encoded' or `escaped' with their ASCII equivalent.
-The reason why we do not have to do this with the payloads our system injects is due to the fact that the Python Requests library that we use to generate the HTTP requests automatically does this encoding for us.
+%% The reason why we do not have to do this with the payloads our system injects is due to the fact that the Python Requests library that we use to generate the HTTP requests automatically does this encoding for us.
 
 \begin{lstlisting}[language=HTML,caption={HTML page for showcasing
-      e-mail header injection, a simple front-end for our
+      \ehi, a simple front-end for our
       examples.},label={code:html}, float]
@@
 <form action="{path-to-back-end}" method="post">
-<input type="text" placeholder="Email" name="email" id="e-mail"><br>
+<input type="text" placeholder="Email" name="email" id="\email"><br>
 <textarea name="msg" rows="20" cols="120"></textarea>
@@
 
-\begin{figure}[!htbp]
-	\centering
-	\includegraphics[width=\linewidth]{System/EMI_Postman_Ruby}
-	\caption[\titlecap{Fuzzing a request for the Ruby backend}]{Fuzzing a request for the Ruby backend, the payload can be seen inside the address bar.}
-	\label{fig:postmanruby}
-\end{figure}
+%% \begin{figure}[!htbp]
+%% 	\centering
+%% 	\includegraphics[width=\linewidth]{System/EMI_Postman_Ruby}
+%% 	\caption[\titlecap{Fuzzing a request for the Ruby backend}]{Fuzzing a request for the Ruby backend, the payload can be seen inside the address bar.}
+%% 	\label{fig:postmanruby}
+%% \end{figure}
 
-\begin{figure}[!htbp]
-	\centering
-	\includegraphics[width=\linewidth]{System/EMI_Mailcatcher_Ruby}
-	\caption[\titlecap{E-Mail header injection proof of concept - Ruby}]{E-Mail header injection proof of concept - Ruby, we can see that multiple headers (bcc, x-check, subject) have been inserted into the resulting e-mail.}
-	\label{fig:mailcatcherruby}
-\end{figure}
+%% \begin{figure}[!htbp]
+%% 	\centering
+%% 	\includegraphics[width=\linewidth]{System/EMI_Mailcatcher_Ruby}
+%% 	\caption[\titlecap{\Email Header Injection proof of concept - Ruby}]{\Email header injection proof of concept - Ruby, we can see that multiple headers (bcc, x-check, subject) have been inserted into the resulting \email.}
+%% 	\label{fig:mailcatcherruby}
+%% \end{figure}

### 2016-05-23 Results/analysis.tex
Edited through the results section

@@
-\subsection{Analysis of the received e-mail data}
-During our analysis of the received e-mails, we found that the e-mails that we received belonged to one of three broad categories:
+\subsection{Analysis of the Received \Email Data}
+During our analysis of the received \emails, we found that the \emails that we received belonged to one of three categories:
 \begin{enumerate}
-	\item E-Mails with the \texttt{bcc} header successfully injected\\
-	This form of injection was our initial objective and we found 265 such e-mails in our received e-mails.
-This indicates that the websites that sent out these e-mails are vulnerable to e-mail header injection, where we could inject and manipulate any header.
+	\item \Emails with the \texttt{bcc} header successfully injected\\
+	  This form of injection was our initial objective, and we found
+% Adam: Sai, why isn't this number a command?
+      265 such \emails in our received \emails. This validates that the web applications that sent these \emails are vulnerable to \ehi.
 
-	\item E-Mails with the \texttt{to} header successfully injected\\
-	We discovered an unintended vulnerability which we would like to christen \texttt{To~header injection}.
-These injections reflect the ability to inject any number of e-mail addresses into the \texttt{to} field while being unable to inject any other header into the e-mails.
+	\item \Emails with the \texttt{to} header successfully injected\\
+	We discovered an unintended vulnerability class during our analysis, which we call \texttt{To~header injection}.
+These injections reflect the ability to inject any number of \email addresses into the \texttt{to} field of the SMTP message while being unable to inject any other header into the \emails.
 We attribute this behavior to inconsistent sanitization by the application.
-	The vulnerability is further aided by the leniency shown by mail servers, wherein they parsed malformed e-mail addresses and delivered it to the right mail server, and on the receiving end, the mail was delivered to the right mailbox.
+    % Adam: I can't understand what this sentence is trying to say
+	The vulnerability is further aided by the leniency shown by mail servers, wherein they parsed malformed \email addresses and delivered it to the right mail server, and on the receiving end, the mail was delivered to the right mailbox.
 
-	While not allowing us complete control over the e-mails sent, \texttt{To header injection} makes it possible to append any number of e-mail addresses, thereby enabling us to leak information, and/or perform DoS (Denial of Service) attacks.
+	While not allowing us complete control over content of the \emails sent, \texttt{To header injection} makes it possible to append any number of \email addresses, thereby enabling us to leak information or perform DoS (Denial of Service) attacks against the web application.
 
-	\item E-Mails with the \texttt{x-check} header successfully injected\\
-    The third category of e-mails received were e-mails with the \texttt{x-check} header injected. As discussed in Section~\ref{analyze:detect_x_check}, 
-    these let us differentiate between unsuccessful attempts and successful attempts by injecting the additional header, allowing us to check whether headers other than the \texttt{bcc} header can be injected into the generated e-mail.
+	\item \Emails with the \texttt{x-check} header successfully injected\\
+    The third category of \emails received were \emails with the \texttt{x-check} header injected. As discussed in Section~\ref{analyze:detect_x_check}, 
+    we can differentiate between unsuccessful attempts and successful attempts by injecting the additional header and checking whether headers other than the \texttt{bcc} header can be injected into the generated \email.
 \end{enumerate}
-We list each category and the number of e-mails received by the category in Table~\ref{tab:analysis}.
+
+% Adam: Sai, we need to put the actual numbers in the text. We cannot count on the readers to look at the table (of course, we should use the commands
+We list each category and the number of \emails received by the category in Table~\ref{tab:analysis}.
 
 \input{Results/data_analysis}
+
 We explain the combination of these header injections (4-7) as follows:
 \begin{itemize}
-	\item E-Mail Header Injections with \texttt{bcc} and \texttt{x-check} headers\\
-	These represent the perfect attack scenario where we are able to inject multiple headers into the e-mails.
-We can see that over 70\% of the received \texttt{bcc} header injected e-mails are also susceptible to other header injections.
+	\item \Email Header Injections with \texttt{bcc} and \texttt{x-check} headers\\
+	  These represent the scenario where an attacker can inject multiple headers into the \emails.
+We can see that over 70\% of the received \texttt{bcc} header injected \emails are also susceptible to other header injections.
+      % Adam: What is the exact percentage? We should use that rather than an approximate number
 
 	\item Both \texttt{To} header injections and \texttt{x-check} headers \\
-	This combination shows us that in addition to being able to inject into the \texttt{To} fields, we are able to inject additional headers into the e-mail.
-It is not clear what causes this behavior; however, these can be exploited to achieve the same result as a regular E-Mail Header Injection.
+	This combination shows us that in addition to being able to inject into the \texttt{To} fields, we injected additional headers into the \email.
+It is not clear what causes this behavior; however, these can be exploited to achieve the same result as a regular \ehi.
 
-	\item \texttt{x-check} headers found in \texttt{nuser} e-mails\\
-	In addition to analyzing the \texttt{maluser} account, we also analyze emails received by the \texttt{nuser} account. We explain the presence of these headers in the following paragraph.
+	\item \texttt{x-check} headers found in \texttt{nuser} \emails\\
+	  In addition to analyzing the \texttt{maluser} account, we also analyze emails received by the \texttt{nuser} account.
+      % Adam: Why aren't we explaining this here? It reads strange.
+      We explain the presence of these headers in the following paragraph.
 
-	\item Unique \texttt{x-check} headers found in \texttt{nuser} e-mails\\
-	These represent the e-mails with \lstinline|form_ids| that were \emph{not} already found in the \texttt{maluser} account.
-We attribute these e-mails to (probably) having a backend that was built with Python or another language having a similar behavior with respect to constructing headers.
+	\item Unique \texttt{x-check} headers found in \texttt{nuser} \emails\\
+	  These represent the \emails with unique form ids that were \emph{not} already found in the \texttt{maluser} account.
+We attribute these \emails to (probably) having a web application that was built with Python or another language having a similar behavior with respect to constructing headers.
+      % Adam: What is the actual behavior? This is confusing.
 
 	\item Total successful injections\\
-	This represents the total number of successful injections our system made.
-This includes the E-Mail Header Injections with \texttt{bcc} header\,(1), \texttt{To} header injections alone\,(3), and Unique \texttt{x-check} headers found in \texttt{nuser} e-mails\,(7).
+	  This represents the total number of successful injections.
+This includes the \ehi with \texttt{bcc} header\,(1), \texttt{To} header injections alone\,(3), and Unique \texttt{x-check} headers found in \texttt{nuser} \emails\,(7).
 This is the total number of vulnerabilities that were found by our system.
 
+      % Adam: we need the actual #s here too. These are the core results of our analysis, they need to be in the text.
+
 \end{itemize}

### 2016-05-23 Results/disclosure.tex
texts
final data update
Edited through the results section

--- 2016-05-14 Results/disclosure.tex
@@
 \subsection{Responsible Disclosure of Discovered Vulnerabilities}
-After we had discovered E-Mail Header Injection vulnerability on a particular website, we e-mailed the developers of these vulnerable websites disclosing the pages that contained the vulnerability, along with a brief description of the vulnerability.
-We chose to e-mail the following mailboxes, following the rules specified in RFC~2142~\cite{rfc2142}:
+After we discovered an \ehi vulnerability on a particular website, we attempted to notify the developers of the vulnerable web application, along with a brief description of the vulnerability.
+We chose to \email the following mailboxes, following the rules specified in RFC~2142~\cite{rfc2142}:
+% Adam: don't we use \texttt for all the email addresses in the paper? We should use the same thing here
 \begin{itemize}
@@
 
-Out of the \domains\ vulnerable domains found, only 108 websites had the mailboxes specified above set-up to receive e-mails.
-For the remaining domains, we used the \dq{\texttt{whois}}~\cite{whois} data to get the contact details of the owner, and then e-mailed them with the same disclosure data.
+% Adam: sai, is this number up-to-date? 
+Out of the \domains\ vulnerable domains found, only 108 websites had the mailboxes able to receive \emails.
+For the remaining domains, we used the \texttt{whois}~\cite{whois} data to find the contact details of the owner, then we \emailed.
+The number of emails we sent and the number of developer responses we received is shown in Table~\ref{tab:devresp}.
 
+\begin{table}[tbp]
+\centering
+\begin{tabular}{|c|c|c|}
+	\hline
+	\multicolumn{1}{|p{2cm}}{\centering \textbf{Notified websites}} &
+	\multicolumn{1}{|p{2cm}|}{\centering \textbf{Developer Responses}} &
+	\multicolumn{1}{p{2cm}|}{\centering \textbf{Confirmed discoveries}}\\
+	\hline
+	\domains\ & 13 & 9 \\
+	\hline
+\end{tabular}
+	\caption[\titlecap{}]{Responsible disclosure of the discovered vulnerabilities to developers and the number of received responses.}
+	\label{tab:devresp}
+\end{table}
+
+% Adam: did we get updated notifications?
 We received 13 developer responses, confirming 9 discovered vulnerabilities. Two of the developers fixed the vulnerability on their website.
-
-From our research, it is clear that E-Mail Header Injection is quite widespread as a vulnerability, appearing on \successDelta\ of forms that we were able to perform automated attacks on.
-This value acts as a \dq{lower bound} for E-Mail Header Injection vulnerability, and can quite easily be much more if the attacks were of a more concentrated nature, crafted for the individual websites and less automated.
-We discuss this possibility, and other concepts such as limitations and methods for mitigation of the vulnerability in the following section.
+% is this done?
+From our research, it is clear that \ehi is quite widespread as a vulnerability, appearing on \successDelta\ of forms that we were able to perform automated attacks on.
+This value acts as a \emph{lower bound} for prevalence of \ehi vulnerability, and can quite easily be larger if the attacks were broader, crafted for the individual web application, and  less automated.

### 2016-05-23 Results/fuzz_result.tex
chap5 added
Edited through the results section

@@
-\section{Fuzzed data}
-We performed our fuzzing attempts on the gathered data with both the regular payload and malicious payload.
-Table~\ref{tab:fuzzed_data} shows the quantity of e-mails that we received for each payload.
-We explain in detail what each piece of data shown in the table represents, in the following sections.
+\subsection{Fuzzed Data}
+Table~\ref{tab:fuzzed_data} shows the quantity of \emails that we received for the benign and malicious payloads. 
 \input{Results/fuzzed_data}
-\paragraph{E-Mail received from forms}
-The e-mails that we received can be broadly categorized into two categories:
+\paragraph{\Email received from forms}
+The \emails that we received can be categorized into two categories:
 \begin{enumerate}
-	\item E-Mails due to regular payload\\
-	This represents the total number of websites that sent e-mails to us. This indicates that we were able to successfully submit the forms on these sites.
+	\item \Emails due to regular payload\\
+	This represents the total number of web applications that sent \emails to us.
+This indicates that we were able to successfully submit the forms on these sites to trigger the web application to send an \email.
 
-	\item E-Mails due to malicious payload\\
-    Once we receive an e-mail from a website due to the regular payload, we go back and fuzz those forms with more malicious payloads.
-This field, in essence, represents the total number of unique URLs that contain E-Mail Header Injection vulnerability.
+	\item \Emails due to malicious payload\\
+    Once we receive an \email from a web application due to the regular payload, we fuzz those forms with the malicious payloads.
+This field represents the total number of unique URLs that are  contain an \ehi vulnerability.
 \end{enumerate}

### 2016-05-23 Results/pipeline.tex
Edited through the results section

@@
-\subsection[The Pipeline]{Understanding the pipeline}
+\subsection[The Pipeline]{Understanding the Pipeline}
 This section serves to represent our pipeline quantitatively and graphically.
@@
 
-At each stage of the pipeline, the amount of data trickles down, for instance, out of the \urls\ URLs we crawled, only \forms\ forms (\formsDelta) were found.
+At each stage of the pipeline, the amount of data decreases, for instance, out of the \urls\ URLs we crawled, only \forms\ forms (\formsDelta) were found.
 Out of these, only \emailforms\ forms (\emailformsDelta) contained e-mail fields.
@@
 
-From our research, it is clear that E-Mail Header Injection is quite widespread as a vulnerability, appearing on \successDelta\ of forms that we were able to perform automated attacks on.
+% Adam: this is an important part of our contribution, but I don't think that it belongs here. 
+%% From our research, it is clear that E-Mail Header Injection is quite widespread as a vulnerability, appearing on \successDelta\ of forms that we were able to perform automated attacks on.
 This value acts as a lower bound for E-Mail Header Injection vulnerability, and can quite easily be much more if the attacks were of a more concentrated nature, crafted for the individual websites and less automated.

### 2016-05-23 Results/pre_result.tex
chap5 added
Edited through the results section

@@
-\section{Collected Data}
-From our extensive crawl of the web, we were able to gather the data shown in Table~\ref{tab:data}.
-The following paragraphs describe in detail what each kind of data represents, and what they signify.
+\subsection{Collected Data}
+
+% TODO: Need to put in a number here, and discuss the high level
+% crawl. 
+We ran the system for XYZ days/hours/whatever
+
+From our extensive crawl of the web, we were able to gather the data
+shown in Table~\ref{tab:data}. Our system crawled \urls unique URLs,
+found a total of \forms\ forms from \uniqueforms\ unique domains, and
+found \emailforms\ forms that contained an \email field from \uniqueemailforms\ unique domains.
 
 \input{data}
-
-\paragraph{URL's crawled}
-This represents the total number of unique URLs that we crawled on the World Wide Web. It is to be noted that this quantity refers to unique URL's, and not websites.
-
-\paragraph{Total Forms found}
-This represents the total number of forms that were found on the URL's crawled. We found a total of \forms\ forms from 
-\uniqueforms\ unique domains.
-
-\paragraph{Forms with E-Mail Fields}
-This represents the total number of forms that were found to contain e-mail fields. We found \emailforms\ such forms from \uniqueemailforms\ unique domains.

### 2016-05-23 Discussion/lessons.tex
edits to discussion section

@@
 \subsection{Lessons Learned}
-    From our results, it is evident that the vulnerability exists in the wild.
-Despite its relatively low occurrence rate compared to the more popular SQL Injection and XSS (Cross-Site Scripting), when we take the total number of websites on the World Wide Web --- 1,018,863,952 according to Internet Live Stats~\cite{InternetLiveStats2016} as of early 2016 --- and calculate \successDelta\ percent (the occurrence rate of E-Mail Header Injection vulnerability as found by our system) of that number, we end up with 14,875,413 websites - a pretty significant number.
-We agree that an extrapolation of that kind might not be an accurate measure of the prevalence of the vulnerability.
+From our results, it is evident that \ehi vulnerabilities exist in the wild.
+% Adam: Sai, I don't understand this math.
+The 1.46% number is calculated based on the number of forms we were able to fuzz with a malicious payload.
+This isn't the same as the number of websites.
+But, using 673/21675680 is not good either because that is # of URLs and it seems like the number you have here is websites.
+What we need is what % of *websites* (probably estimated as domains) did we find to be vulnerable out of *all* websites/domains that we found.
+When we use this number, we need to be clear what it is that we are using.
+Despite its relatively low occurrence rate compared to the more popular SQL Injection and XSS (Cross-Site Scripting), when we consider total number of websites on the World Wide Web--- 1,018,863,952 according to Internet Live Stats~\cite{InternetLiveStats2016} as of early 2016---and calculate \successDelta\ percent (the occurrence rate of \ehi vulnerability as found by our system) of that number, this yields 14,875,413 websites.
+Of course, extrapolation in this way is not an accurate measure of the prevalence of \ehi vulnerabilities.
 However, even with as few as a thousand websites affected by this vulnerability, it can still have a disastrous impact on these websites, and also on overall World Wide Web due to the traffic caused by the sheer number of generated e-mails.
 
-    After analyzing the results, we would like to make a few more observations.
-We believe that one of the reasons for the small percentage of occurrence (compared to SQL Injection or XSS), can be attributed to what we like to call the `car parking analogy'.
-    The car parking analogy is something like this: Imagine that we are parking a car on a road that is prone to attacks by thieves.
+%% We believe that one of the reasons for the small percentage of occurrence (compared to SQL Injection or Cross-Site Scripting), can be attributed to what we like to call the `car parking analogy'.
+%%     The car parking analogy is something like this: Imagine that we are parking a car on a road that is prone to attacks by thieves.
 Now, if all the cars were unlocked, the car that is most likely to get stolen is quite unsurprisingly the most expensive one or the one that is easiest to get away with.
 
-    Now imagine the same thing on the World Wide Web: we have websites that can each have multiple vulnerabilities.
+%%     Now imagine the same thing on the World Wide Web: we have websites that can each have multiple vulnerabilities.
 Now, it makes sense for an attacker to try and attack websites with more widespread vulnerabilities such as SQL Injection or XSS, rather than attempt to exploit E-Mail Header Injection, seeing as this requires a more concentrated effort, with carefully crafted payloads and a waiting time for the e-mail to be delivered.
@@
 
-    This also gives more incentive for the website developer to add protection against attacks such as SQL injection and XSS.
+%%     This also gives more incentive for the website developer to add protection against attacks such as SQL injection and XSS.
 The developer might then (possibly with the help of a sanitization library) sanitize the user input and remove \emph{all} special characters, including the newline characters (\textbackslash{}n, \textbackslash{}r), which adversely affects E-Mail Header Injection attacks.
 
-	We come to this conclusion because of our discovery of the \texttt{To header injection}.
+%% 	We come to this conclusion because of our discovery of the \texttt{To header injection}.
 Clearly, this is possible due to incomplete sanitization performed by the application.
@@
 
-    Thus, indirectly, this kind of protection against other attacks affects the attempts to perform E-Mail Header Injection.
+%%     Thus, indirectly, this kind of protection against other attacks affects the attempts to perform E-Mail Header Injection.
 However, this does not completely negate the attempts if the checks are only on the client-side.
@@
 
-	A second and a far more common reason for our fuzzing attempts to fail is the bot-blocking mechanisms built into the websites.
-CAPTCHAs pose a very difficult problem for our system to exploit E-Mail Header Injection, even if it is present.
+% Adam: Please add a citation to a CAPTCHA paper
+	A common reason for our fuzzing attempts to fail is the bot-blocking mechanisms built into the web applications.
+CAPTCHAs pose a very difficult problem for our system to exploit \ehi, even if it is present.
 
-	This does not mean that the vulnerability is not a large threat. In fact, this vulnerability can also have some major consequences, the least of which can be spamming and phishing attacks.
-	In today's digital world, identity theft has become all the more common.
+	%% This does not mean that the vulnerability is not a large threat. In fact, this vulnerability can also have some major consequences, the least of which can be spamming and phishing attacks.
+	%% In today's digital world, identity theft has become all the more common.
 E-Mail Header Injection provides attackers with the ability to easily extract information about users, not just from a server, but from the user himself, by sending him fake messages that look extremely authentic, since these messages are sent by the mail server of the website itself.
 
-    From our research, we found two different forms of the E-Mail Header Injection Vulnerability: the first one is the traditional one, where we are able to inject any header into the forms, allowing us complete control over the contents of the e-mail.
-We identify this with the presence of both the \texttt{bcc} header and the \texttt{x-check} header.
-This is the most potent form of the vulnerability and is found on quite a few websites.
-This is also the vulnerability that is documented and discussed on many websites.
+    We found two different forms of \ehi: the first one is the traditional one, injecting any header into the \email that allows the attacker complete control over the contents of the \email. 
+The second attack has not yet been documented and provides the ability to inject multiple \email addresses into the \texttt{To} field.
+We call this a \texttt{To header injection}.
+In this  vulnerability, an attacker can add addresses to the \texttt{To} field of the email with newlines separating the \email addresses.
+We could not determine if this vulnerability is due to unique flaws in each web application or if this vulnerability is due to an implementation issue with a particular language or framework.
+However, from our preliminary analysis, it is evident that the vulnerable web applications do not share much in common.
 
-    The second attack is an interesting one, as this has not yet been documented, and provides the ability to inject multiple e-mail addresses into only the \texttt{To} field.
-We christened this as \texttt{To header injection}.
-In this form of the vulnerability, we are able to simply add addresses to the \texttt{To} field of the form with newlines separating the e-mail addresses.
-Whether this particular form of the vulnerability is found due to the websites in question, or whether this is an implementation issue with a particular language or framework, is unclear.
-However, from our preliminary analysis, it is evident that these websites do not share much with respect to the languages and frameworks used.
-    Even in this form of the attack, we are still able to extract information that should be private to a given user, and in some of these cases, able to inject enough data to spoof the first few lines of the e-mail message.
+\texttt{To header injection} allows an attacker to extract information that should be private,
+% Adam: It's not clear what this means that we have enough data to spoof the few lines of the message. I thought to header injection just controls the TO field, not the message contents. 
+and in some of these cases, able to inject enough data to spoof the first few lines of the \email message.
 From Table~\ref{tab:analysis}, information leakage using \texttt{To header injection} was possible on 163 forms, while spoofing using \texttt{To header injection} was possible on 13 forms.
 
-    While not being as impactful as the primary vulnerability, this form of the vulnerability does still provide the ability to send e-mails to multiple recipients, and can easily result in information leakage or spam generation on a large scale.
+    %% While not being as impactful as the primary vulnerability, this form of the vulnerability does still provide the ability to send \emails to multiple recipients, and can easily result in information leakage or spam generation on a large scale.

### 2016-05-23 Discussion/limits.tex
edits to discussion section

@@
-\subsection[Limitations]{Limitations of the Project}
+\subsection[Limitations]{Limitations}
 \label{limitations}
-	This section discusses the limitations of our project. The following list, although not exhaustive, goes into some of them in detail:
-	\begin{itemize}
-		\item Bot Blockers and CAPTCHAs\\
-		Because our system is fully automated, it is also susceptible to being stopped by `bot-blockers' i.e.,\ mechanisms built-in to a website to prevent automated crawls or form submissions.
-Measures like CAPTCHA (Completely Automated Public Turing test to tell Computers and Humans Apart) and hidden form fields are often used to detect bots~\cite{captchas3}, \cite{captchas2}.
 
-		We have made sure that we do not affect hidden fields in the form, however, despite considerable research in breaking CAPTCHAs~\cite{captchas2}, \cite{captchas} and although not impossible to break, breaking CAPTCHAs remains out of the scope of this project, and thus, we chose to ignore websites which require CAPTCHA verification.
+		Because our system is fully automated, it is also susceptible to being stopped by mechanisms in web applications that prevent automated crawls or form submissions.
+Measures such as CAPTCHA (Completely Automated Public Turing test to tell Computers and Humans Apart) and hidden form fields are often used to detect bots~\cite{captchas3, captchas2}.
 
-		\item JavaScript Apps - Due to the growing emphasis on responsive web applications, more and more single-page web applications are being built purely with JavaScript.
-Even conventional applications are now making use of JavaScript to dynamically insert content and update the pages.
-This means that these dynamically injected components are not a part of the initial source code that is sent to the client by the server.
+		We made sure that we do not fuzz hidden fields in the form, however, despite considerable active research in breaking CAPTCHAs~\cite{captchas2, captchas}, breaking CAPTCHAs remains out of the scope of this project.
 
-		Thus, our system never receives dynamically injected forms from the server and hence is unable to detect whether these vulnerabilities are present in such forms.
-The only workaround would be, to use a JavaScript engine to query for the \texttt{document.getElementsByTagName('html')[0].innerHTML} (from inside web browser automation tools like Selenium, etc.), and then use that as the source code for our URL.
+	   Due to the growing emphasis on responsive web applications, more and more web applications are being built with only client-side  JavaScript.
+Even conventional web applications use JavaScript to dynamically insert content and update the pages.
+This trend means that these dynamically injected HTML components are not part of the initial HTML that is sent to the client by the server.
 
-		Since this would add unnecessary bulk and complexity to our application, we chose not to do it, and thus, we consider this to be a limitation.
+		Thus, our system will not see dynamically injected forms and hence is unable to detect whether \ehi vulnerabilities are present in these forms.
+The workaround would be to use a JavaScript engine to query for the \texttt{document.getElementsByTagName('html')[0].innerHTML} (from inside web browser automation tools such as Selenium), then use that as the source HTML.
+We chose not to do this for performance reasons.
 
-		\item Blacklisting by websites and ISPs\\
-		During the actual crawl, our system was blacklisted by a few websites (mostly WordPress ones), and Internet Service Providers (ISPs).
+		During the crawl, our system was blacklisted by a few web applications (mostly WordPress ones), and Internet Service Providers (ISPs).
 		To overcome this, we did two things:
@@
 			\item Used an IP range of 60 different IP addresses.
-			\item Used a blacklist of our own to prevent our Fuzzer from fuzzing websites that are known to blacklist automated crawlers.  The result was that we could not gather any data about these websites.
+			\item Used a blacklist of our own to prevent our Fuzzer from fuzzing web application that are known to blacklist automated crawlers.
+However, we could not gather any data about these web applications.
 		\end{enumerate}
 
-		\item Blogs powered by WordPress/Drupal\\
-		We found that certain WordPress plugins prevent the E-Mail Header Injection attack by sanitizing user input on contact forms.
-Some of these plugins are discussed in the following section.
-Although not all websites built with WordPress are secure from the attack, between the presence of the plugins on some websites, and getting tagged as `spambots' by others, we were able to do vulnerability analysis on few sites powered by WordPress.
+		We found that certain WordPress plugins prevent the \ehi attack by sanitizing user input on contact forms.
+Although not all  WordPress web applications are secure, between the presence of the plugins on some websites, and getting tagged as ``spambots'' by others, we found few vulnerabilities on WordPress web applications.
 
-		\item E-Mail libraries\\
-        E-Mail libraries like the PHP Extension and Application Repository's (PEAR) mail library provide sanitization checks for user input.
-While this is technically not a limitation of our project, it still makes it such that we are not able to inject these sites successfully.
-        A few other libraries for each language are discussed in the following section.
+        E-Mail libraries such as the PHP Extension and Application Repository's (PEAR) mail library provide sanitization for user input.
+While this is not strictly a limitation of our project, it still means that we are not able to inject sites that used these libraries successfully.
 
-        \item Websites that are not in English\\
-        Because we are only searching for the words \texttt{e-mail}, \texttt{mail} or \texttt{email} within the form, if the website does not use English names for its forms, our system will not be able to find the presence of an e-mail field.
+        Because we search for the words \texttt{e-mail}, \texttt{mail}, or \texttt{email} within the HTML form, if the website does not use English names for its forms our system will not be able to find the presence of an \email field.
 An example is shown in Listing~\ref{code:htmlfrench}.
-Here, the French word for \texttt{e-mail} --- courrier électronique --- is used, and our system is unable to find the presence of the e-mail form.
+Here, the French word for \texttt{e-mail}---courrier électronique---is used, and our system is unable to find the presence of the e-mail form.
 
-        \item Handling Malformed HTML\\
-        The parser that we use for HTML parsing --- Beautiful Soup --- does not try to parse malformed HTML, and throws an exception on encountering malformed content.
+        The parser that we use for HTML parsing---Beautiful Soup---does not parse malformed HTML and throws an exception on encountering malformed HTML.
 Thus, we have designed the system to exit gracefully on such occasions.
-A side-effect of this is that our system is unable to parse websites with bad markup\,\footnotemark.
+A side-effect of this is that our system is unable to test web applications with bad HTML markup\,\footnotemark.
 
-        \footnotetext{We do not have any data about whether bad markup indicates an overall lower quality of the website, and thus cannot comment on whether such websites are more likely to have vulnerabilities, although the author strongly suspects that that might be the case.}
+        \footnotetext{We do not have any data about whether bad markup indicates an overall lower quality of the web application, and thus cannot comment on whether such websites are more likely to have vulnerabilities.}
 
-        \item Black-box Testing\\
-        The approach that we have selected --- Black-box testing --- is highly beneficial as explained in Section~\ref{sys:appr}.
-However, it also has a drawback in that we cannot verify whether the reported vulnerability exists in the source code or is a feature of the website (e.g., the website allows users to send bulk e-mail, adding as many \texttt{cc} or \texttt{bcc} headers).
-We have to manually e-mail the developers to get this feedback.
+        Black-box testing is highly beneficial as explained in Section~\ref{sys:appr}, however it also has a drawback in that we cannot verify whether the reported vulnerability exists in the source code or is a feature of the website (e.g., the website allows users to send bulk e-mail, adding as many \texttt{cc} or \texttt{bcc} headers).
+We must manually notify the developers to get this feedback.
 
-       	\item \label{issues:fpr}False Positive rate for the E-Mail Field Checker\\
-       	As discussed in Section~\ref{Comp:EMFC}, we only search for the words \texttt{email}, \texttt{mail} or \texttt{e-mail} (case insensitive) inside the forms to detect the presence of e-mail fields, instead of searching for an \colorbox{lightgray}{\lstinline{<input type = email>}}.
+%%        	As discussed in Section~\ref{Comp:EMFC}, we only search for the words \texttt{email}, \texttt{mail} or \texttt{e-mail} (case insensitive) inside the forms to detect the presence of e-mail fields, instead of searching for an \colorbox{lightgray}{\lstinline{<input type = email>}}.
 This might result in a false positive in certain forms, like the one shown in Listing~\ref{code:false_positive}.
 
-       	\begin{lstlisting}[language=HTML,caption={E-Mail field checker
-              - false positives, the system incorrectly classifies
-              this as an e-mail form.},label={code:false_positive}, float]
-<form method="post">
-E-Mail us if you have any questions!!
-<input type="text" name="query"><br>
-<input type="submit" value="Search">
-</form>
-       	\end{lstlisting}
+%%        	\begin{lstlisting}[language=HTML,caption={E-Mail field checker
+%%               - false positives, the system incorrectly classifies
+%%               this as an e-mail form.},label={code:false_positive}, float]
+%% <form method="post">
+%% E-Mail us if you have any questions!!
+%% <input type="text" name="query"><br>
+%% <input type="submit" value="Search">
+%% </form>
+%%        	\end{lstlisting}
 
-       	The word \texttt{E-Mail} on Line 2 will result in our system classifying this form as a potential e-mail form, while it clearly is not.
+%%        	The word \texttt{E-Mail} on Line 2 will result in our system classifying this form as a potential e-mail form, while it clearly is not.
 However, as we will see, this is not really a significant issue, as despite being added to the \texttt{email\_forms} table, this form will never be injected in the `fuzzer' due to the absence of the appropriate input field in the form.
 We chose to go with this design, as it allows us to detect almost every form that provides the capability to send or receive e-mail.
-	\end{itemize}
 

### 2016-05-23 Discussion/mitigation.tex
chap6,7,8 prelim edits
Edited through the results section
edits to discussion section

@@
-\subsection[Mitigation Strategy]{How to prevent this attack}
+\subsection{Mitigation Strategy}
 \label{disc:mitigation}
-This section describes the most common measures that can be taken to prevent the occurrence of this vulnerability, or at least reduce the impact.
+After demonstrating that \ehi vulnerabilities exist on the web at large, we now describe the most common measures that can be taken to prevent the occurrence of this vulnerability, or at least reduce the impact.
 \begin{itemize}
 	\item Use Mail Libraries\\
-	This is the preferred way of combating this vulnerability.
-Using a library that is well tested can remove the burden of input sanitization from the developer.
-Also, since most of these libraries are open-source, bugs are identified quicker and fixes are readily available.
-	A list of known secure libraries for each popular language and framework is shown in Table~\ref{tab:maillib}.
+	Using a safe \email library is the preferred way of preventing \ehi vulnerabilities. Using a library that is well tested can remove the burden of input sanitization from the developer. 
+	A list of known secure libraries for each language and framework discussed previously is shown in Table~\ref{tab:maillib}.
 
-	Using libraries such as PEAR Mail, PHPMailer, Apache Commons E-Mail, Contact Form 7, and Swiftmailer can significantly reduce the occurrence of E-Mail Header Injection vulnerability.
-	\begin{table}[!htbp]
+	Using libraries such as PEAR Mail, PHPMailer, Apache Commons E-Mail, Contact Form 7, and Swiftmailer can significantly reduce the occurrence of \ehi vulnerability.
+	\begin{table}[tbp]
 		\centering
@@
 	\item Use a Content Management System (CMS) \\
-	Content management systems like WordPress and Drupal include certain libraries and plugins to prevent E-Mail Header Injection.
+	Content management systems such as WordPress and Drupal include libraries and plugins to prevent \ehi.
 Thus, websites built with such CMS' are usually resistant to these attacks.
-However, it is advised to use the right E-Mail plugins when using such CMS', as not all plugins might be secure.
+However, it is advised to use the correct \email plugin, as not all plugins might be secure.
 	An example of a secure plug-in is included as part of Table~\ref{tab:maillib}.
@@
 	\item Input Validation\\
-	If neither of the two options above is feasible, due to reasons such as the website being an in-house production, or due to lack of support infrastructure, developers can choose to perform proper input sanitization.
+	If neither of the two options are feasible, due to reasons such as the website being an in-house production, or due to lack of support infrastructure, developers can choose to perform proper input sanitization.
 Sanitization should be done keeping in mind RFC5322~\cite{rfc5322}, and care must be taken to ensure that all edge cases are taken into account.
 
-	Client Side validation alone is not sufficient, and must be supplemented by server-side validation to mitigate the attack.
+	%% Client Side validation alone is not sufficient, and must be supplemented by server-side validation to mitigate the attack.
 Constant updates to validation methods are required so that new attack vectors do not harm the website in any way.
-	Test driven development for such validation methods is also encouraged so that we can be reasonably sure of our defense mechanisms.
+	%% Test driven development for such validation methods is also encouraged so that we can be reasonably sure of our defense mechanisms.
 \end{itemize}

### 2016-05-23 System/assumptions.tex
edits to discussion section

@@
 \begin{enumerate}
-	\item \textbf{Crawler is not blocked by firewalls}\\
-	This is a requisite for our system to work. If the Crawler is blocked for any reason, we do not get the data feed for our system, and without this input, it is almost impossible to set our system up.
+	\item \textbf{The crawler is not blocked}\\
+	This is a requisite for our system to work. If the Crawler is blocked for any reason, we do not get the data feed for our system, and without this input, it is impossible to discover vulnerabilities.
 
 	\item \textbf{The Crawler feed is an ideal representation of the World Wide Web} \\
+
 	This is a reasonable expectation, albeit an unrealistic one.
@@
 
-	However, this assumption is reasonable due to the `Law of averages'~\cite{wiki:Law_of_averages}, the `Law of big numbers'~\cite{wiki:Law_of_large_numbers}, and the concept of `Regression to the mean'~\cite{wiki:Regression_toward_the_mean}.
-Simply stated, a crawl of this large magnitude should give us a very distributed sample of the overall Web, eventually converging to the average of all websites in existence.
+	However, this assumption is reasonable due to the ``Law of averages''~\cite{wiki:Law_of_averages}, the ``Law of big numbers''~\cite{wiki:Law_of_large_numbers}, and the concept of ``Regression to the mean''~\cite{wiki:Regression_toward_the_mean}.
+Simply stated, a crawl of this magnitude should provide a distributed sample of the overall Web, eventually converging to the average of all web applications in existence.
 
-	\item \textbf{Injection of \texttt{bcc} indicates the existence of E-Mail Header Injection Vulnerability} \\
-	We assume that the ability to inject a \texttt{bcc} header field is proof that the E-Mail Header Injection vulnerability exists in the application.
-We do not inject any additional payloads that can modify the subject, message body, etc.\ as this analysis is designed to be as benign as possible.
-	We believe that this is a reasonable assumption, as altering e-mail headers is a goal of exploiting E-Mail Header Injection vulnerability.
+	\item \textbf{Injection of \texttt{bcc} indicates the existence of an \ehi Vulnerability} \\
+	We assume that the ability to inject a \texttt{bcc} header field is proof that the \ehi vulnerability exists in the application.
+We do not inject any additional payloads that can modify the subject, message body, etc., as our analysis is designed to be as benign as possible.
+	We believe that this is a reasonable assumption, as altering e-mail headers is a goal of exploiting \ehi vulnerability.
 \end{enumerate}
-
-That concludes our discussion about the design of the system.
-To recap, we discussed our approach, the system architecture and how the components fit into our architecture.
-We also discussed the issues faced, and the assumptions that we made while building the system.
-%The next section describes, in brief, the experimental setup we used for our system.

### 2016-05-23 conclusion.tex
Edits to conclusion and related work

--- 2016-04-27 conclusion.tex
@@
-\chapter{Conclusion}
-We have showcased a novel approach involving black-box testing to identify the presence of E-Mail Header Injection in a web application.
+\section{Conclusions}
+We have showcased a novel approach involving black-box testing to identify the presence of \ehi in a web application.
 Using this approach, we have demonstrated that our system was able to crawl \urls\ web pages finding \forms\ forms, out of which \emailforms\ forms were fuzzable.
@@
 Out of these, we were able to inject malicious payloads into \malfuzzed\ forms, identifying \success\ vulnerable forms (\successDelta\ success rate).
-This indicates that the vulnerability is widespread, and needs attention from both web application developers and library makers.
+This indicates that the vulnerability is widespread, and needs attention from both web application developers and library developers.
 
-We hope that our work sheds light on the prevalence of this vulnerability and that it ensures that the implementation of the `mail' function in popular languages is fixed to differentiate between User-supplied headers, and headers that are legitimately added by the application, and that the RFC's are updated to be more stringent and make it less ambiguous for future implementations.
+We hope that our work sheds light on the prevalence of this vulnerability and that it ensures that the implementation of the \texttt{mail} function in popular languages is fixed to differentiate between User-supplied headers, and headers that are legitimately added by the application.

### 2016-05-23 rel_work.tex
Edits to conclusion and related work

@@
 
-There are different approaches to finding vulnerabilities in web applications, two of them being Black-Box testing and White-Box testing.
-Our work is based on the black-box testing approach to finding vulnerabilities on websites, and there has been plenty of research that has made use of this methodology~\cite{Beizer:1995:BTT:202699}, \cite{Huang}, \cite{kals2006secubat}, \cite{payet13:ears-in-the-wild}, \cite{zanero2005automatic}.
+% Adam: Sai, can you combine all the \cites at the same line like I did for the others? 
+There are different approaches to finding vulnerabilities in web applications, and most approaches will be either Black-Box testing or White-Box testing.
+Our work is based on the black-box testing approach to finding vulnerabilities on websites, and research has made use of this methodology to find vulnerabilities in web applications~\cite{Beizer:1995:BTT:202699}, \cite{Huang}, \cite{kals2006secubat}, \cite{payet13:ears-in-the-wild}, \cite{zanero2005automatic}.
 There has been significant discussion on both the benefits of such an approach~\cite{black-box} and its shortcomings~\cite{Doupe2012}, \cite{Doupe2010}.
 
-Our work does not intend to act as a vulnerability scanner, but as a means to identify the presence of E-Mail Header Injection vulnerabilities in a given web application.
-In this sense, since we are injecting payloads into the web application, our work is related to other injection based attacks, such as SQL Injection~\cite{sql1}, \cite{sql0}, \cite{sql2}, Cross-Site Scripting --- XSS --- \cite{Injection1}, \cite{KleinAmit}, HTTP Header Injection~\cite{sessionride}, and is very closely related to Simple Mail Transfer Protocol (SMTP) Injection~\cite{Terada2015}.
+Our work does not intend to act as a vulnerability scanner, but as a means to identify an \ehi vulnerability in a given web application.
+In this sense, because we are injecting payloads into the web application, our work is related to other injection based attacks, such as SQL Injection~\cite{sql1}, \cite{sql0}, \cite{sql2}, Cross-Site Scripting \cite{Injection1}, \cite{KleinAmit}, HTTP Header Injection~\cite{sessionride}, and the related Simple Mail Transfer Protocol (SMTP) Injection~\cite{Terada2015}.
 
 The attack described by Terada~\cite{Terada2015} is one that attacks the underlying SMTP mail servers by injecting SMTP commands (which are closely related to E-Mail Headers and usually have a one-to-one mapping, e.g., \texttt{To} e-mail header has a corresponding \texttt{To} SMTP header) to exploit the SMTP server's pipelining mechanism.
-The paper also describes proof-of-concept attacks against certain mailing libraries like \texttt{Ruby Mail} and \texttt{JavaMail}.
+Terada also describes proof-of-concept attacks against certain mailing libraries such as \texttt{Ruby Mail} and \texttt{JavaMail}.
 This attack, although trying to achieve a similar result, is distinctly different from ours.
-The paper by itself makes this observation and discusses why it is different from E-Mail Header Injection.
+The paper makes this observation and discusses why it is different from \ehi.
 
@@
 
-As specified before, although this vulnerability has been present for over a decade, there has not been much written about it in the literature, and we only find a few articles on the Internet describing the attack.
+Although \ehi vulnerabilities have been present for over a decade, there has not been much written about it in the literature, and we find only a few articles on the Internet describing the attack.
 
@@
 To the best of our knowledge, no other research has been conducted to determine the prevalence of this vulnerability across the World Wide Web.
-We have managed to, on a large scale, crawl and inject websites with comparatively benign payloads (such as the BCC header) to identify the existence of this vulnerability without causing any ostensible harm to the website.
-Our injected payloads do not contain any special characters other than the newline characters and thus cannot cause any unintended consequences.
-Also, since we are only injecting a payload with the \texttt{bcc} header, the underlying mail servers should not be affected by the additional load.
-Our work serves to not only prove the existence of the vulnerability on the World Wide Web but to quantify it.
+We have managed to, on a large scale, crawl and inject web applications with comparatively benign payloads (such as the BCC header) to identify the existence of this vulnerability without causing any ostensible harm to the website.
+Our injected payloads \emph{do not contain any special characters other than the newline character} and thus cannot cause any unintended consequences.
+Also, because we are only injecting a payload with the \texttt{bcc} header, the underlying mail servers should not be affected by the additional load.
+Our work serves to not only prove the existence of the vulnerability on the World Wide Web but to quantify the prevalence.

### 2016-05-23 System/components.tex
fixed some small things Fixed all todos till sys design

@@
 \label{Comp:Fuzzer}
-% Adam: we should call these something else but modules. We already have the top two modules, which are composed of components, now we need to split these into something (not components again).
+% Adam: we should call these something else but modules. We already have the top two modules, which are composed of components, now we need to split these into something (not components again). - DONE
 The Fuzzer is the only component that interacts directly with the external web applications.
-The Fuzzer is split into smaller modules, each of which is responsible for a particular type of fuzzing.
+The Fuzzer is split into smaller parts, each of which is responsible for a particular type of fuzzing.
 The system injects payloads in two stages: the goal is to reduce the total number of HTTP requests the system generates to detect an \ehi vulnerability.
@@
 
-	This payload is added for purposes of cross-platform fuzzing: \texttt{\textbackslash{}r\textbackslash{}n} is the ``Carriage Return - New Line (CRLF)'' used on Windows systems.
-%Adam: have a citation for this?
+	This payload is added for purposes of cross-platform fuzzing: \texttt{\textbackslash{}r\textbackslash{}n} is the ``Carriage Return - New Line (CRLF)'' used on Windows systems.~\cite{rfc2616}
 
@@
 This data must pass validation constraints on the individual input fields (e.g.,\ for a name field, numbers might not be allowed).
+As crawling and fuzzing input fields on the web is an open problem~\cite{raghavan2000crawling}, we chose to go with a best-effort approach.
 To maximize the amount of vulnerabilities the system discovers, the data injected into the input fields should adhere to the constraints.
 The Fuzzer uses a ``Data Dictionary'' which has predefined ``keys'' and ``values'' for standard input fields such as \texttt{name}, \texttt{date}, \texttt{username}, \texttt{password}, \texttt{text}, and \texttt{submit}.
-% Adam: What does it mean here for these to be generated on-the-fly? Using templates?
-The default values for these are generated on-the-fly for each form, based on generally followed guidelines for such fields.
+% Adam: What does it mean here for these to be generated on-the-fly? Using templates? - Fixed.
+The default values for these are generated from the Data dictionary for each form, based on generally followed guidelines for such fields.
 For example, password fields should consist of at least one uppercase letter, one lowercase letter, and a special character.
-% Adam: can you add a sentence here about crawling and fuzzing fields on the web is an open problem (and cite ``Crawling the hidden web''
+% Adam: can you add a sentence here about crawling and fuzzing fields on the web is an open problem (and cite ``Crawling the hidden web'' - DONE.
 

### 2016-05-24 System/proof_of_concept.tex
Edited through the results section
fixed all todos in exp_setup

@@
 The front-end for each of the three applications is shown in Listing~\ref{code:html}.
-The server-side code for the PHP and Python is shown in Listings~\ref{code:phpemi} and \ref{code:pyemi} respectively.
+The server-side code for PHP, Python, and Ruby is shown in Listings~\ref{code:phpemi}, \ref{code:pyemi}, and \ref{code:rubyemi} respectively.
 
-% Adam: I think it might be nice to have the Ruby code here too.
+% Adam: I think it might be nice to have the Ruby code here too. - DONE.
 
-Before performing out wide scan of the web, we verified that our system was able to detect the \ehi vulnerabilities present in all the sample web applications.
+Before performing a wide scan of the web, we verified that our system was able to detect the \ehi vulnerabilities present in all the sample web applications.
 
@@
 \end{lstlisting}
+\input{Background/ruby}
 
-%% \begin{figure}[!htbp]
+%% \begin{figure}[tbp]
 %% 	\centering
@@
 
-%% \begin{figure}[!htbp]
+%% \begin{figure}[tbp]
 %% 	\centering

### 2016-05-24 Results/analysis.tex
fixed todos in evaluation

@@
 	  This form of injection was our initial objective, and we found
-% Adam: Sai, why isn't this number a command?
-      265 such \emails in our received \emails. This validates that the web applications that sent these \emails are vulnerable to \ehi.
+% Adam: Sai, why isn't this number a command? - DONE.
+      \ehibcc such \emails in our received \emails. This validates that the web applications that sent these \emails are vulnerable to \ehi.
 
@@
 These injections reflect the ability to inject any number of \email addresses into the \texttt{to} field of the SMTP message while being unable to inject any other header into the \emails.
+We found \ehito such \emails in our received \emails.
 We attribute this behavior to inconsistent sanitization by the application.
-    % Adam: I can't understand what this sentence is trying to say
-	The vulnerability is further aided by the leniency shown by mail servers, wherein they parsed malformed \email addresses and delivered it to the right mail server, and on the receiving end, the mail was delivered to the right mailbox.
+    % Adam: I can't understand what this sentence is trying to say - Removed.
 
@@
     we can differentiate between unsuccessful attempts and successful attempts by injecting the additional header and checking whether headers other than the \texttt{bcc} header can be injected into the generated \email.
+\ehixcheck \emails were received with the \texttt{x-check} header injected.
 \end{enumerate}
@@
 % Adam: Sai, we need to put the actual numbers in the text. We cannot count on the readers to look at the table (of course, we should use the commands
-We list each category and the number of \emails received by the category in Table~\ref{tab:analysis}.
+We list each category and the number of \emails received by that category in Table~\ref{tab:analysis}. 
+We explain the combination of these header injections (4-7) as follows:
 
@@
 
-We explain the combination of these header injections (4-7) as follows:
 \begin{itemize}
-	\item \Email Header Injections with \texttt{bcc} and \texttt{x-check} headers\\
+	\item \Email Header Injections with both \texttt{bcc} and \texttt{x-check} headers\\
 	  These represent the scenario where an attacker can inject multiple headers into the \emails.
-We can see that over 70\% of the received \texttt{bcc} header injected \emails are also susceptible to other header injections.
-      % Adam: What is the exact percentage? We should use that rather than an approximate number
+We can see that 65.65\% of the received \texttt{bcc} header injected \emails are also susceptible to being injected with additional headers.
+      % Adam: What is the exact percentage? We should use that rather than an approximate number - DONE.
 
@@
 
-	\item \texttt{x-check} headers found in \texttt{nuser} \emails\\
-	  In addition to analyzing the \texttt{maluser} account, we also analyze emails received by the \texttt{nuser} account.
-      % Adam: Why aren't we explaining this here? It reads strange.
-      We explain the presence of these headers in the following paragraph.
-
-	\item Unique \texttt{x-check} headers found in \texttt{nuser} \emails\\
-	  These represent the \emails with unique form ids that were \emph{not} already found in the \texttt{maluser} account.
-We attribute these \emails to (probably) having a web application that was built with Python or another language having a similar behavior with respect to constructing headers.
-      % Adam: What is the actual behavior? This is confusing.
+	\item Total \texttt{x-check} headers and unique \texttt{x-check} headers found in \texttt{nuser} \emails\\
+		We found a total of \ehinuserxcheck \emails in the \texttt{nuser} account.
+Out of these, \ehiuniquenuserxcheck had unique form ids that were \emph{not} already found in the \texttt{maluser} account.
+We attribute these \emails to (probably) being sent by a web application that was built with Python or another language having a similar behavior with respect to ignoring duplicate headers while constructing an \email, thus appending the \texttt{x-check} header and \emph{not} the \texttt{bcc} header.
+      % Adam: What is the actual behavior? This is confusing. - Changed. DONE.
 
@@
 This includes the \ehi with \texttt{bcc} header\,(1), \texttt{To} header injections alone\,(3), and Unique \texttt{x-check} headers found in \texttt{nuser} \emails\,(7).
-This is the total number of vulnerabilities that were found by our system.
+A total of \success vulnerabilities were found by our system.
 
-      % Adam: we need the actual #s here too. These are the core results of our analysis, they need to be in the text.
+      % Adam: we need the actual #s here too. These are the core results of our analysis, they need to be in the text. - DONE.
 

### 2016-05-24 Results/data_analysis.tex
Edited through the results section
fixed todos in evaluation

--- 2016-05-14 Results/data_analysis.tex
@@
-\begin{table*}[!htbp]
+\begin{table*}[tbp]
 	\centering
@@
 		\hline
-		E-Mail Header Injections with \texttt{bcc} header & 304\\
+		E-Mail Header Injections with \texttt{bcc} header & \ehibcc \\
 		\hline
-		E-Mail Header Injections with \texttt{x-check} header & 252\\
+		E-Mail Header Injections with \texttt{x-check} header & \ehixcheck \\
 		\hline
-		\texttt{To header} injections alone & 157\\
+		\texttt{To header} injections alone & \ehito \\
 		\hline
-		E-Mail Header Injections with \texttt{bcc} and \texttt{x-check} headers & 216\\
+		E-Mail Header Injections with \texttt{bcc} and \texttt{x-check} headers & \ehibccxcheck \\
 		\hline
 		Both \texttt{To header} injections and x-check headers &
-		12\\
+		\ehitoxcheck \\
 		\hline
-		\texttt{x-check} headers found in \texttt{nuser} e-mails & 67\\
+		\texttt{x-check} headers found in \texttt{nuser} e-mails & \ehinuserxcheck \\
 		\hline
-		Unique \texttt{x-check} headers found in \texttt{nuser} e-mails & 35\\
+		Unique \texttt{x-check} headers found in \texttt{nuser} e-mails & \ehiuniquenuserxcheck \\
 		\hline
-		Total successful injections (1 + 3 + 7) & 496\\
+		Total successful injections (1 + 3 + 7) & \success \\
 

### 2016-05-24 Results/disclosure.tex
fixed todos in evaluation

@@
 We chose to \email the following mailboxes, following the rules specified in RFC~2142~\cite{rfc2142}:
-% Adam: don't we use \texttt for all the email addresses in the paper? We should use the same thing here
+% Adam: don't we use \texttt for all the email addresses in the paper? We should use the same thing here - DONE.
 \begin{itemize}
-	\item security@domain.com - Used for Security bulletins or queries.
-	\item admin@domain.com - Used to contact the administrator of a website.
-	\item webmaster@domain.com - Synonym for administrator, same functionality as admin.
+	\item \texttt{security@domain.com} - Used for Security bulletins or queries.
+	\item \texttt{admin@domain.com} - Used to contact the administrator of a website.
+	\item \texttt{webmaster@domain.com} - Synonym for administrator, same functionality as admin.
 \end{itemize}
@@
 % Adam: sai, is this number up-to-date? 
-Out of the \domains\ vulnerable domains found, only 108 websites had the mailboxes able to receive \emails.
-For the remaining domains, we used the \texttt{whois}~\cite{whois} data to find the contact details of the owner, then we \emailed.
+Out of the \domains\ vulnerable domains found, only \emailedDefaultmailbox websites had the mailboxes able to receive \emails.
+For the remaining domains, we used the \texttt{whois}~\cite{whois} data to find the contact details of the owner and then \emailed them.
 The number of emails we sent and the number of developer responses we received is shown in Table~\ref{tab:devresp}.
@@
 	\hline
-	\domains\ & 13 & 9 \\
+	\domains\ & \responses & \confirmed \\
 	\hline
@@
 
-% Adam: did we get updated notifications?
-We received 13 developer responses, confirming 9 discovered vulnerabilities. Two of the developers fixed the vulnerability on their website.
-% is this done?
+% Adam: did we get updated notifications? - nope. DONE.
+We received \responses developer responses, confirming \confirmed discovered vulnerabilities. Two of the developers fixed the vulnerability on their website.
+% is this done? 1 additional email asking for more information, but no confirmation.
 From our research, it is clear that \ehi is quite widespread as a vulnerability, appearing on \successDelta\ of forms that we were able to perform automated attacks on.

### 2016-05-24 Results/pre_result.tex
fixed todos in evaluation

@@
 % TODO: Need to put in a number here, and discuss the high level
-% crawl. 
-We ran the system for XYZ days/hours/whatever
+% crawl. - DONE
 
 From our extensive crawl of the web, we were able to gather the data
-shown in Table~\ref{tab:data}. Our system crawled \urls unique URLs,
-found a total of \forms\ forms from \uniqueforms\ unique domains, and
-found \emailforms\ forms that contained an \email field from \uniqueemailforms\ unique domains.
+shown in Table~\ref{tab:data}. We ran the system for 76 days, during which our system crawled \urls unique URLs,
+and found a total of \forms\ forms from \uniqueforms\ unique domains. Out of these forms, our system
+found \emailforms\ forms that contained an \email field, from \uniqueemailforms\ unique domains.
 

### 2016-05-24 Discussion/lessons.tex
fixed todos in discussion

@@
 When we use this number, we need to be clear what it is that we are using.
-Despite its relatively low occurrence rate compared to the more popular SQL Injection and XSS (Cross-Site Scripting), when we consider total number of websites on the World Wide Web--- 1,018,863,952 according to Internet Live Stats~\cite{InternetLiveStats2016} as of early 2016---and calculate \successDelta\ percent (the occurrence rate of \ehi vulnerability as found by our system) of that number, this yields 14,875,413 websites.
+-- FIxed this to be clear.
+Despite its relatively low occurrence rate compared to the more popular SQL Injection and XSS (Cross-Site Scripting), when we consider total number of domains on the World Wide Web--- 1,018,863,952 according to Internet Live Stats~\cite{InternetLiveStats2016} as of early 2016---and calculate \successWebsitesDelta percent (the occurrence rate of \ehi vulnerability calculated from vulnerable domains as found by our system to total number of domains crawled) of that number, this yields 295,693 domains.
 Of course, extrapolation in this way is not an accurate measure of the prevalence of \ehi vulnerabilities.
-However, even with as few as a thousand websites affected by this vulnerability, it can still have a disastrous impact on these websites, and also on overall World Wide Web due to the traffic caused by the sheer number of generated e-mails.
+However, even with as few as a thousand domains affected by this vulnerability, it can still have a disastrous impact on these domains, and also on overall World Wide Web due to the traffic caused by the sheer number of generated e-mails.
 
@@
 
-% Adam: Please add a citation to a CAPTCHA paper
+% Adam: Please add a citation to a CAPTCHA paper - DONE.
 	A common reason for our fuzzing attempts to fail is the bot-blocking mechanisms built into the web applications.
-CAPTCHAs pose a very difficult problem for our system to exploit \ehi, even if it is present.
+CAPTCHAs~\cite{captchas2} pose a very difficult problem for our system to exploit \ehi, even if it is present.
 
@@
 \texttt{To header injection} allows an attacker to extract information that should be private,
-% Adam: It's not clear what this means that we have enough data to spoof the few lines of the message. I thought to header injection just controls the TO field, not the message contents. 
-and in some of these cases, able to inject enough data to spoof the first few lines of the \email message.
-From Table~\ref{tab:analysis}, information leakage using \texttt{To header injection} was possible on 163 forms, while spoofing using \texttt{To header injection} was possible on 13 forms.
+% Adam: It's not clear what this means that we have enough data to spoof the few lines of the message.
+I thought to header injection just controls the TO field, not the message contents.
+- Fixed, my bad.
+DONE.
+and in some of these cases, able to inject enough data to spoof other headers of the \email message.
+From Table~\ref{tab:analysis}, information leakage using \texttt{To header injection} was possible on \ehito forms, while spoofing using \texttt{To header injection} was possible on \ehitoxcheck forms.
 

### 2016-05-24 Results/pipeline.tex
fixed todos in evaluation
added the exploitation evidence section

@@
-\subsection[The Pipeline]{Understanding the Pipeline}
-This section serves to represent our pipeline quantitatively and graphically.
+\subsection[The Pipeline]{Understanding the Data Pipeline}
+%This section serves to represent our pipeline quantitatively and graphically. 
 Table~\ref{tab:pipeline} showcases the data gathered by our pipeline, with the differential changes at each stage of the pipeline.
@@
 We fuzzed \fuzzed\ forms with the regular payload, which resulted in a total of \recd\ e-mails (\recdDelta).
-After analysis of the received e-mails, we further fuzzed \fuzzed\ forms, which resulted in \success\ e-mails (\successDelta) which contain the vulnerability.
+After analysis of the received e-mails, we further fuzzed \fuzzed\ forms, which resulted in \success\ e-mails (\successDelta) which contain the vulnerability across \ips IP Addresses corresponding to \domains domains.
 \input{Results/pipeline_table}

### 2016-05-24 Discussion/ethics.tex
fixed related work, starting ethics

\subsection{Ethics}
To make sure that our system did not cause any major harm to the websites that we crawled, we made sure that we did not inject any special characters other than the newline character. These payl(like SQL Injection and Cross-Site Scripting)

### 2016-05-24 rel_work.tex
fixed related work, starting ethics

@@
 There are different approaches to finding vulnerabilities in web applications, and most approaches will be either Black-Box testing or White-Box testing.
-Our work is based on the black-box testing approach to finding vulnerabilities on websites, and research has made use of this methodology to find vulnerabilities in web applications~\cite{Beizer:1995:BTT:202699}, \cite{Huang}, \cite{kals2006secubat}, \cite{payet13:ears-in-the-wild}, \cite{zanero2005automatic}.
-There has been significant discussion on both the benefits of such an approach~\cite{black-box} and its shortcomings~\cite{Doupe2012}, \cite{Doupe2010}.
+Our work is based on the black-box testing approach to finding vulnerabilities on websites, and research has made use of this methodology to find vulnerabilities in web applications~\cite{Beizer:1995:BTT:202699, Huang, kals2006secubat, payet13:ears-in-the-wild, zanero2005automatic}.
+There has been significant discussion on both the benefits of such an approach~\cite{black-box} and its shortcomings~\cite{Doupe2012, Doupe2010}.
 
 Our work does not intend to act as a vulnerability scanner, but as a means to identify an \ehi vulnerability in a given web application.
-In this sense, because we are injecting payloads into the web application, our work is related to other injection based attacks, such as SQL Injection~\cite{sql1}, \cite{sql0}, \cite{sql2}, Cross-Site Scripting \cite{Injection1}, \cite{KleinAmit}, HTTP Header Injection~\cite{sessionride}, and the related Simple Mail Transfer Protocol (SMTP) Injection~\cite{Terada2015}.
+In this sense, because we are injecting payloads into the web application, our work is related to other injection based attacks, such as SQL Injection~\cite{sql1, sql0, sql2}, Cross-Site Scripting \cite{Injection1, KleinAmit}, HTTP Header Injection~\cite{sessionride}, and the related Simple Mail Transfer Protocol (SMTP) Injection~\cite{Terada2015}.
 
@@
 The first documented article dates to over a decade ago; a late 2004 article on phpsecure.info~\cite{Tobozo} accredited to user \lstinline|tobozo@phpsecure.info| describing how this vulnerability existed in the reference implementation of the mail function in PHP, and how it can be exploited.
-Following this, we found other blog posts~\cite{Calin}, \cite{DK}, \cite{Injection2}, \cite{Nicol}, \cite{Pope}, each describing how to exploit the vulnerability by using newlines to camouflage headers inside user input.
+Following this, we found other blog posts~\cite{Calin, DK, Injection2, Nicol, Pope}, each describing how to exploit the vulnerability by using newlines to camouflage headers inside user input.
 A wiki entry~\cite{Injection} also describes the ways to prevent such an attack.

### 2016-05-24 Discussion/ethics.tex
added ethics section

@@
 \subsection{Ethics}
-To make sure that our system did not cause any major harm to the websites that we crawled, we made sure that we did not inject any special characters other than the newline character.
-These payl(like SQL Injection and Cross-Site Scripting)
+To make sure that our system did not cause any harm to the websites that we crawled, we made sure that we did not inject any special characters other than the newline character% (characters that a developer would assume an average user could put in)
+.
+We also had an information website\footnote{Removed for the sake of anonymity} that described what \ehi was, and contained our contact details in case the developers of the websites we crawled wanted to contact us.
+We maintained a separate blacklist of websites that the owners did not want us to crawl, and ensured that our system did not crawl their websites.

### 2016-05-24 System/components.tex
fixed todos in evaluation
fixed spacing and abstract

@@
 % Adam: What does it mean here for these to be generated on-the-fly? Using templates? - Fixed.
-The default values for these are generated from the Data dictionary for each form, based on generally followed guidelines for such fields.
-For example, password fields should consist of at least one uppercase letter, one lowercase letter, and a special character.
+The values for these are generated from the Data dictionary for each form, based on generally followed guidelines for such fields.
+For example, password fields should consist of at least one uppercase letter, one lowercase letter, and special characters.
 % Adam: can you add a sentence here about crawling and fuzzing fields on the web is an open problem (and cite ``Crawling the hidden web'' - DONE.
@@
 This module works on the \emails received and stored by our Postfix server, and, depending on the user account that received the \email, it performs different functions.
-\paragraph{Analyzing regular \email}
+\paragraph{Analyzing regular e-mail}
 \sloppy

### 2016-05-24 abstract.tex
fixed some small things Fixed all todos till sys design
fixed spacing and abstract

--- 2016-05-20 abstract.tex
@@
 \forms such forms were found by the system, of which \emailforms forms contained \email fields.
-We then test \fuzzed forms to see if they would send us an \email, and \recd forms set us an \email.
+We then tested \fuzzed forms to see if they would send us an \email, and \recd forms sent us an \email.
 Of these \malfuzzed forms were tested with \ehi payloads and, of these, we found \success vulnerable URLs across \domains domains.
-Then, to demonstrate that \ehi vulnerabilities are actively being exploited to create a spamming platform, we found \ipsblacklist IPs that were vulnerable on spaming blacklists.
-This work shows that \ehi vulnerabilities are widespread widespread and deserve future research attention.
+Then, to demonstrate that \ehi vulnerabilities are actively being exploited to create a spamming platform, we found \ipsblacklist IPs that were vulnerable on well-known spamming blacklists.
+This work shows that \ehi vulnerabilities are widespread and deserve future research attention.
 \end{abstract}

### 2016-05-24 Discussion/ethics.tex

--- 2016-05-24 Discussion/ethics.tex
@@
 \subsection{Ethics}
-To make sure that our system did not cause any major harm to the websites that we crawled, we made sure that we did not inject any special characters other than the newline character.
-These payl(like SQL Injection and Cross-Site Scripting)
+
+To make sure that our system did not cause any harm to the websites that we crawled, we made sure that we did not inject any special characters other than the newline character% (characters that a developer would assume an average user could put in)
+.
+We also had an information website at the IP that we crawled from\footnote{Removed for the sake of anonymity} that described what \ehi was, and contained our contact details in case the developers of the websites we crawled wanted to contact us.
+We maintained a separate blacklist of websites that the owners did not want us to crawl, and ensured that our system did not crawl their websites.

### 2016-05-24 Discussion/ethics.tex
Changed websites to web applications

--- 2016-05-24 Discussion/ethics.tex
@@
 \subsection{Ethics}
-To make sure that our system did not cause any major harm to the websites that we crawled, we made sure that we did not inject any special characters other than the newline character.
-These payl(like SQL Injection and Cross-Site Scripting)
+
+To make sure that our system did not cause any harm to the web applications that we crawled, we made sure that we did not inject any special characters other than the newline character% (characters that a developer would assume an average user could put in)
+.
+We also had an information website at the IP that we crawled from\footnote{Removed for the sake of anonymity} that described what \ehi was, and contained our contact details in case the developers of the web applications we crawled wanted to contact us.
+We maintained a separate blacklist of domain names that the owners did not want us to crawl, and ensured that our system did not crawl their domains.

### 2016-05-24 Background/ruby.tex
fixed references and spacing

@@
 # construct a post request with email set to attack_string
-# attack_string => sai@example.com%0abcc:spc@example.com%0aSubject:Hello
+# attack_string => s@example.com%0abcc:spc@example.com%0aSubject:Hello
 Net::SMTP.start('localhost', 1025) do |smtp|

### 2016-05-24 abstract.tex
fixed references and spacing

@@
 	This paper presents a scalable mechanism to automatically detect \ehi vulnerabilities and uses this mechanism to quantify the prevalence of \ehi vulnerabilities on the web.
-Using a black-box testing approach, the system crawled \urls URLs identify web pages which contained form fields.
+Using a black-box testing approach, the system crawled \urls URLs to identify web pages which contained form fields.
 \forms such forms were found by the system, of which \emailforms forms contained \email fields.
 We then tested \fuzzed forms to see if they would send us an \email, and \recd forms sent us an \email.
-Of these \malfuzzed forms were tested with \ehi payloads and, of these, we found \success vulnerable URLs across \domains domains.
-Then, to demonstrate that \ehi vulnerabilities are actively being exploited to create a spamming platform, we found \ipsblacklist IPs that were vulnerable on well-known spamming blacklists.
+Of these, \malfuzzed forms were tested with \ehi payloads and, of these, we found \success vulnerable URLs across \domains domains.
+Then, to demonstrate that \ehi vulnerabilities are actively being exploited to create a spamming platform, we found \ipsblacklist IPs that were vulnerable on spamming blacklists.
 This work shows that \ehi vulnerabilities are widespread and deserve future research attention.

### 2016-09-18 Background/history.tex
updated for WWW paper

@@
 
-% TODO: Change all domains to example.com - DONE.
-% TODO: Sai, this is the first time we mention SMTP, need more background and a reference to the RFC.
-
 \begin{sloppypar}
@@
 \end{sloppypar}
+
+%TODO Adam: added this para abt E-Mail Header Injection history from CVE
+We gathered data from the Common Vulnerabilities and Exposures (CVE)~\cite{cve} database to get an idea of the distribution of \ehi vulnerabilities reported over time.
+We found 28 reports of \ehi from the CVE (shown in Table~\ref*{tab:history}).
+
+From the table, it can be seen that even though a lot of \ehi vulnerabilities were found in the earlier years (2005-07), there have been several recently discovered \ehi vulnerabilities which suggests that it is still a very real threat and is relevant to modern web security.
+
+\input{Background/history_table}

### 2016-09-18 Background/lang_aff.tex
fixed todos in evaluation
updated for WWW paper

@@
 
+\begin{sloppypar}
 \noindent{\textbf{Python}}
 A bug was filed about an \ehi vulnerability in Python's implementation of the \texttt{email.header} library and the header parsing functions allowing newlines in early 2009, which was followed by a partial patch in early 2011.
+\end{sloppypar}
 
@@
 There is no mention of the vulnerability in the Python documentation for either library.
+Contrary to PHP's behavior of overwriting existing headers, Python only recognizes the first occurrence of a header, and ignores duplicate headers.
 A working code sample of the vulnerability, written in Python 2.7.11, is shown in Listing~\ref{code:pyemi}.
@@
 
+\begin{sloppypar}
 \noindent{\textbf{Ruby}}
-From our preliminary testing Ruby's built-in \texttt{Net::SMTP} library also has an \ehi library. This is not documented on the library's homepage.
+From our preliminary testing Ruby's built-in \texttt{Net::SMTP} library also has an \ehi vulnerability. This is not documented on the library's homepage.
 %A working code sample of the vulnerability, written in Ruby 2.0.0 (the latest stable version at the time of writing), is shown in Listing~\ref{code:rubyemi}.
-
+\end{sloppypar}
 %\input{Background/ruby.tex}

### 2016-09-18 Discussion/limits.tex
fixed captchas
updated for WWW paper

@@
 \label{limitations}
+		Because our system is fully automated, it is also susceptible to being stopped by mechanisms in web applications that prevent automated crawls or form submissions.
+Measures such as CAPTCHA, hidden form fields and CSRF (Cross-site Request Forgery~\cite{csrf}) tokens are often used to detect bots~\cite{captchas3, captchas2}.
 
-		Because our system is fully automated, it is also susceptible to being stopped by mechanisms in web applications that prevent automated crawls or form submissions.
-Measures such as CAPTCHA (Completely Automated Public Turing test to tell Computers and Humans Apart) and hidden form fields are often used to detect bots~\cite{captchas3, captchas2}.
-
-		We made sure that we do not fuzz hidden fields in the form, however, despite considerable active research in breaking CAPTCHAs~\cite{captchas2, captchas}, breaking CAPTCHAs remains out of the scope of this project.
+		We made sure that we do not fuzz hidden fields in the form, and because our system does not depend on authenticated sessions, CSRF tokens do not pose an issue.
+However, despite considerable active research in breaking CAPTCHAs~\cite{captchas2, captchas}, breaking CAPTCHAs remains out of the scope of this project.
 
@@
 The workaround would be to use a JavaScript engine to query for the \texttt{document.getElementsByTagName('html')[0].innerHTML} (from inside web browser automation tools such as Selenium), then use that as the source HTML.
-We chose not to do this for performance reasons.
+
+		%TODO Adam: added a table here, and explanation about performance tradeoffs with Selenium and bs4.
+		A comparison of the running times between the different approaches is shown in Table~\ref{tab:perf}.
+Because using Selenium results in a slowdown of \slowSelenium, we chose not to do this for performance reasons.
+
+		\begin{table}
+			\centering
+			\normalsize
+			\begin{tabular}{|p{4cm}|c|c|}
+				\hline
+				\multicolumn{1}{|c}{\textbf{Method}} &
+				\multicolumn{1}{|c|}{\textbf{Running time}} &
+				\multicolumn{1}{|c|}{\textbf{Slowdown}}
+				\\
+				\hline
+				\centering Using our pipeline & 629.043 & - \\
+				\hline
+				\centering Adding Selenium to our pipeline & 919.372 & \slowSelenium \\
+				\hline				
+				\centering Detecting \email fields by parsing each field instead of `grep'ing inside form & 707.154 & \slowParse \\								
+				\hline
+			\end{tabular}
+			\caption[\titlecap{}]{Running times in seconds for crawling, parsing, and detecting presence of \email fields in 1000 random wikipedia pages.}
+			\label{tab:perf}
+		\end{table}
+
+        Because we search for the words \texttt{e-mail}, \texttt{mail}, or \texttt{email} within the HTML form, if the website does not use English names for its forms our system will not be able to find the presence of an \email field.
+An example is shown in Listing~\ref{code:htmlfrench}.
+Here, the French word for \texttt{e-mail}---courrier électronique---is used, and our system is unable to find the presence of the e-mail field.
 
@@
 While this is not strictly a limitation of our project, it still means that we are not able to inject sites that used these libraries successfully.
-
-        Because we search for the words \texttt{e-mail}, \texttt{mail}, or \texttt{email} within the HTML form, if the website does not use English names for its forms our system will not be able to find the presence of an \email field.
-An example is shown in Listing~\ref{code:htmlfrench}.
-Here, the French word for \texttt{e-mail}---courrier électronique---is used, and our system is unable to find the presence of the e-mail form.
 
@@
 
-\begin{lstlisting}[language=HTML,caption={HTML page with e-mail form, written in a different language - French.},label={code:htmlfrench}, literate=%
+\begin{lstlisting}[language=HTML,caption={e-mail field in a different language - French.},label={code:htmlfrench}, literate=%
 	{é}{{\'e}}1, float]
-<!doctype html>
-<html lang="fr">
-<head>
-<meta charset="utf-8">
-<meta name="author" content="XYZ">
-<title>Mock Email</title></head>
-<body>
-<form action="{path-to-back-end}" method="post">
-<input type="text" placeholder="courrier électronique"
-	name="courrier_électronique"><br>
-<textarea name="msg" rows="20" cols="120"></textarea>
-<input type="submit" value="courrier électronique!">
-</form></body>
-</html>
+<input type="text" 
+placeholder="courrier électronique"
+name="courrier_électronique">
 \end{lstlisting}

### 2016-09-18 Results/pipeline.tex
updated for WWW paper

@@
 We fuzzed \fuzzed\ forms with the regular payload, which resulted in a total of \recd\ e-mails (\recdDelta).
-After analysis of the received e-mails, we further fuzzed \fuzzed\ forms, which resulted in \success\ e-mails (\successDelta) which contain the vulnerability across \ips IP Addresses corresponding to \domains domains.
+After analysis of the received e-mails, we further fuzzed \malfuzzed\ forms, which resulted in \success\ e-mails (\successDelta) which contain the vulnerability across \ips IP Addresses corresponding to \domains domains.
+
+%TODO Adam: added the reason for the reduction in the numbers, and accept that we do not have the data to quantify about captcha/csrf
+We attribute the difference in the number of forms found to the number of forms fuzzed (a difference of \diffFoundFuzz forms) to the presence of bot-blocking mechanisms on a website (discussed in Section~\ref{limitations}), though we do not know what percentage was caused by the individual bot-blocking mechanisms discussed in Section~\ref{limitations}.
+
+We would like to remark that over 1\% of the forms that were not fuzzed (100 out of \diffFoundFuzz) were also tested manually using PostMan to generate HTTP requests with payloads to verify that our system was working as intended.
+
 \input{Results/pipeline_table}

### 2016-09-18 System/components.tex
fixed references and spacing
fixed captchas
updated for WWW paper

@@
 The system injects payloads in two stages: the goal is to reduce the total number of HTTP requests the system generates to detect an \ehi vulnerability.
-Making HTTP requests is an expensive process~\cite{McGrath2009}, and can cause bottlenecks in a Crawler-Fuzzer system~\cite{ShkapenyukTorstenSuel2001}.
+Making HTTP requests is an expensive process~\cite{httpperf}, and can cause bottlenecks in a Crawler-Fuzzer system~\cite{ShkapenyukTorstenSuel2001}.
 The two different types of payloads used for fuzzing are:
@@
 	\centering
+	\normalsize
 	\begin{tabular}{|c|c|c|}
@@
 
+%TODO Adam: made clear that ALL input fields that appear in the email are fuzzed, with examples like name, username, etc.
 To find this, we parse each received \email, and check whether \emph{any} of the fields we injected with data appear as part of either the headers or the body of the \email.
-If they do, we add them to the list of fields that can potentially result in an \ehi vulnerability for the given \email.
-We then pass on this information back to the Fuzzer pipeline, along with the vulnerable form.
+These could be fields such as name, date of birth, username, etc.
+If they do, we add them to the list of fields that can \emph{potentially} result in an \ehi vulnerability for the given \email.
+
+We then pass on this information back to the Fuzzer pipeline, along with the vulnerable form, where these fields are \emph{also} fuzzed along with the \email fields to check for the presence of \ehi.
 

### 2016-09-18 abstract.tex
updated for WWW paper

@@
 \ehi is possible when the mailing script fails to check for the presence of \email headers in user input (either form fields or URL parameters).
-The vulnerability exists in the reference implementation of the built-in mail functionality in popular languages such as PHP, Java, Python, and Ruby.
-With the proper injection string, this vulnerability can be exploited to inject additional headers, modify existing headers, and  alter the content of the \email.
+We discovered that the vulnerability exists in the reference implementation of the built-in \email functionality in the popular languages PHP, Java, Python, and Ruby.
+With the proper injection string, this vulnerability can be exploited to allow an attacker to inject additional headers, modify existing headers, and alter the content of the \email.
 
+	While \ehi vulnerabilities are known by the community, and some commercial vulnerability scanners claim to discover \ehi vulnerabilities, they have never been studied by the academic community.
 This paper presents a scalable mechanism to automatically detect \ehi vulnerabilities and uses this mechanism to quantify the prevalence of \ehi vulnerabilities on the web.
@@
 \forms such forms were found by the system, of which \emailforms forms contained \email fields.
-We then tested \fuzzed forms to see if they would send us an \email, and \recd forms sent us an \email.
+We then fuzzed \fuzzed forms to see if they would send us an \email, and \recd forms sent us an \email.
 Of these, \malfuzzed forms were tested with \ehi payloads and, of these, we found \success vulnerable URLs across \domains domains.
-Then, to demonstrate that \ehi vulnerabilities are actively being exploited to create a spamming platform, we found \ipsblacklist IPs that were vulnerable on spamming blacklists.
+Then, to measure if \ehi vulnerabilities are actively being exploited to create a spamming platform, we found evidence that \ipsblacklist IPs that were vulnerable to \ehi are on spamming blacklists.
 This work shows that \ehi vulnerabilities are widespread and deserve future research attention.

### 2016-09-18 introduction.tex
fixed some small things Fixed all todos till sys design
updated for WWW paper

@@
 This access has ushered in an era of web applications which depend on user input.
-While this rapid pace of development has improved the speed of dissemination of information, it does come at a cost.
+While the rapid pace of development has improved the speed of information dissemination, it comes at a cost.
 As users move more and more of their personal and financial information to web applications, attackers are responding by using web application vulnerabilities to access this lucrative data.
 
-%% Adam: I don't see how this adds to our story
-%% Attackers have an added incentive to break into user's e-mail accounts more than ever.
-E-Mail accounts are usually connected to almost all other online accounts of a user, and e-mails continue to serve as the principal mode of official communication on the web for most institutions.
-Thus, the impact an attacker can have by having control over the \email communication sent by websites to users is of an enormous magnitude.
+Many common and well-known web application vulnerabilities, such as SQL Injection and Cross-Site Scripting~\cite{OWASPT10}, are command injection vulnerabilities~\cite{commandinjection}, where malicious user input is used to alter the structure of a command (a SQL query in the case of SQL Injection and JavaScript code in the case of Cross-Site Scripting).
+Developers of web applications must use the correct sanitization routine in all paths leading from user input to a command.
 
-% TODO: Sai, can you add a reference to command injection vulnerabilities here? DONE.
-Many common and well-known web application vulnerabilities, such as SQL Injection and Cross-Site Scripting~\cite{OWASPT10}, are command injection vulnerabilities~\cite{commandinjection}, where malicious user input is used to alter the structure of a command (a SQL query in the case of SQL Injection and JavaScript code in the case of Cross-Site Scripting).
-Developers of web applications must have proper sanitization routines in place to use user input as part of these commands.
-
-\ehi vulnerabilities are a lesser-known command injection vulnerability.
-\ehi can be considered as the \email equivalent of HTTP Header Injection~\cite{wiki:HTTP_headerinjection}.
-This vulnerability exists in the implementation of the built-in \texttt{mail} functionality in popular languages such as PHP, Java, Python, and Ruby.
+\ehi vulnerabilities are a lesser-known command injection vulnerability\footnote{\ehi can be considered as the \email equivalent of HTTP Header Injection~\cite{wiki:HTTP_headerinjection}}.
+We verified that this vulnerability exists in the implementation of the built-in \email functionality in the popular languages PHP, Java, Python, and Ruby.
 The format of \email messages is defined by the Simple Mail Transfer Protocol (SMTP)~\cite{rfc5322}.
 Each \email message is represented by a series of headers separated by newlines, followed by the body content (separated from the headers by two newlines).
-Some of these headers are mandatory (From, To, Date), but the headers could also include other information like the Subject, CC, BCC, etc.
-
-\textbf{Sai: I believe that the discussion of SMTP Headers belongs here, before we say that E-Mail Header Injection can manipulate the headers.
-Do I need to include the message format as a listing?
-I think its superfluous, but let me know.}
+Some of these headers are mandatory (From, To, Date), but the headers could also include other information such as the Subject, CC, BCC, etc.
 
@@
 
-%% The objective of our research is to study the prevalence of this vulnerability on the World Wide Web, and identify whether further research is required in this area.
+While some command injection vulnerabilities have received extensive attention from the research community, \ehi vulnerabilities have received little focus.
+In fact, the Acunetix vulnerability scanner contains an AcuMonitor component which claims to detect \ehi vulnerabilities while scanning~\cite{acumonitor}.
+Unfortunately, as a commercial product, little is known about how AcuMonitor detects \ehi vulnerabilities.
 
-While some command injection vulnerabilities have received extensive attention from the research community, \ehi vulnerabilities have received little focus.
-Therefore, we study the prevalence of \ehi vulnerabilities on the web.
-We performed a crawl of the web, extracted forms with \email fields, and injected them with different payloads to infer the existence of an \ehi vulnerability.
+To shed light on this little-studied vulnerability class, we describe \ehi vulnerabilities and measure \ehi vulnerabilities on the web.
+To perform this measurement, we crawled the web, extracted forms with \email fields, and injected them with different payloads to infer the existence of an \ehi vulnerability.
 We then audited received \emails to see if any of the injected data was present.
@@
 Our automated system works in a black-box manner, without looking at the web application's source code, and only analyzes the \emails we receive based on the injected payloads.
+%TODO Adam: Added a line to make clear that we wanted a quantification before attempting something like a source-code analyzer. This addresses reviewer 690B's concerns.
+
+The objective of our research is to study the prevalence of this vulnerability on the World Wide Web and identify whether further research is required in this area.
 \\
@@
 \noindent{}In summary, we make the following contributions:
-
 \begin{itemize}
@@
 
-\item We develop a system to crawl the web and automatically detect \ehi vulnerabilities.
+\item We develop an open-source system to crawl the web and automatically detect \ehi vulnerabilities.
 

### 2016-10-10 Results/virus_data.tex
added virus email attachments section

\subsection{Emails with Malicious Attachments}
We checked the \emails received by the `reguser' account (which are injected with regular \email addresses and not malicious data) for the presence of attachments that may contain malicious software, which will indicate that the server itself is not benign.

To do this, we passed the \totalattachmentcount attachments we received to VirusTotal~\cite{virustotal} -- an online virus and malware scanner that checks for the presence of malware by running 40+ virus scanners on the uploaded files. We found that out of the \totalattachmentcount attachments, \totalvirusemails \emails contained malicious attachments, out of which \totalvirusattachmentcount were found to be from unique domains. 
%It is to be noted that none of these domains were found on the spam analysis we did earlier, indicating that if these could be exploited, we could send emails with malicious attachments to other people using these servers.

### 2016-10-24 Background/history.tex
almost at 13 pages, need to bering it to 9

@@
 
-We found the first \ehi description in a late 2004 article on phpsecure.info~\cite{Tobozo} accredited to user \lstinline|tobozo@phpsecure.info| describing how an \ehi vulnerability existed in the implementation of the \texttt{mail()} function in PHP and how it can be exploited.
+We found the first \ehi description in a late 2004 article on phpsecure.info~\cite{Tobozo} accredited to user \lstinline|tobozo| describing how an \ehi vulnerability existed in the implementation of the \texttt{mail()} function in PHP and how it can be exploited.
 More recently, a blog post by Damon Kohler~\cite{DK} and an accompanying wiki article~\cite{Injection} describe the attack vector and outline few defense measures for \ehi vulnerabilities.

### 2016-10-24 Background/impact.tex
fixed some small things Fixed all todos till sys design
almost at 13 pages, need to bering it to 9

@@
 \noindent\textbf{Information Extraction}
-	\emails can contain sensitive data that is meant to be accessed only by the user.
-Due to an \ehi vulnerability, an attacker can add a \texttt{bcc} header, and the \email server will send a copy of the private \email to the attacker, thereby extracting important information.
+	\Emails can contain sensitive data that is meant to be accessed only by the user.
+Due to an \ehi vulnerability, an attacker can add a \texttt{bcc} header, and the \email server will send a copy of the \email to the attacker, thereby exposing important information.
 	User privacy can thus be compromised, and loss of private information can by itself lead to other attacks.

### 2016-10-24 Background/lang_aff.tex
almost at 13 pages, need to bering it to 9

@@
 \label{languages}
-This section describes the popular programming languages that contain \ehi vulnerabilities in their standard email libraries.
+We now describe the popular programming languages that contain \ehi vulnerabilities in their standard \email libraries.
 This section is not intended as a complete reference of vulnerable functions and methods, but rather as a guide that specifies which parts of the language are vulnerable.
@@
 However, it is specified in the PHP documentation~\cite{PHPDocs} that the \texttt{mail()} function does not protect against \ehi.
-A working code sample of the vulnerability, written in PHP~5.6 (latest well-supported version), is shown in  Listing~\ref{code:phpemi}.
+A working code sample of the vulnerability, written in PHP~5.6 is shown in  Listing~\ref{code:phpemi}.
 
@@
 
-Unfortunately, the bug fix was only for the \texttt{email.header} package, and thus exists in other frequently used packages such as \texttt{email.parser}, where both the classic \texttt{Parser()} and the newer \texttt{FeedParser()} contain \ehi vulnerabilities even in the latest versions: \texttt{2.7.11} and \texttt{3.5}.
+Unfortunately, the bug fix was only for the \texttt{email.header} package, and not for other frequently used packages such as \texttt{email.parser}, where both the classic \texttt{Parser()} and the newer \texttt{FeedParser()} contain \ehi vulnerabilities even in the latest versions: \texttt{2.7.11} and \texttt{3.5}.
 The bug fix was also not backported to older versions of Python.

### 2016-10-24 Background/ruby.tex
almost at 13 pages, need to bering it to 9

--- 2016-05-20 Background/ruby.tex
@@
 require 'net/smtp'
-
 get '/hello' do
 email = params[:email]
-
 message = """
-From: Sai <schand31@asu.edu>
+    From: Sch <sch@example.com>
     Subject: SMTP e-mail test
@@
 # construct a post request with email set to attack_string
-# attack_string => sai@sai.com%0abcc:spc@spc.com%0aSubject:Hello
-Net::SMTP.start('localhost', 1025) do |smtp|
-smtp.send_message message, 'schand31@asu.edu',
-'to@todomain.com'
+# attack_string => s@example.com%0abcc:spc@example.com%0aSubject:Hello
+Net::SMTP.start('localhost',1025) do |smtp|
+smtp.send_message message, 'sch@example.com', 'to@todomain.com'
 end

### 2016-10-24 Discussion/limits.tex
almost at 13 pages, need to bering it to 9

@@
 				\hline
-				\centering Adding Selenium to our pipeline & 919.372 & \slowSelenium \\
+				\centering Our pipeline with Selenium & 919.372 & \slowSelenium \\
 				\hline				
-				\centering Detecting \email fields by parsing each field instead of `grep'ing inside form & 707.154 & \slowParse \\								
+				\centering Parsing \email fields instead of `grep'ing inside form & 707.154 & \slowParse \\								
 				\hline
@@
         Because we search for the words \texttt{e-mail}, \texttt{mail}, or \texttt{email} within the HTML form, if the website does not use English names for its forms our system will not be able to find the presence of an \email field.
-An example is shown in Listing~\ref{code:htmlfrench}.
-Here, the French word for \texttt{e-mail}---courrier électronique---is used, and our system is unable to find the presence of the e-mail field.
+An example is by using the French word for \texttt{e-mail}---courrier {{\'e}}lectronique--- our system is unable to find the presence of the e-mail field.
 
@@
 
-\begin{lstlisting}[language=HTML,caption={e-mail field in a different language - French.},label={code:htmlfrench}, literate=%
-	{é}{{\'e}}1, float]
-<input type="text" 
-placeholder="courrier électronique"
-name="courrier_électronique">
-\end{lstlisting}
+%\begin{lstlisting}[language=HTML,caption={e-mail field in a different language - French.},label={code:htmlfrench}, literate=%
+%	{é}{{\'e}}1, float]
+%<input type="text" 
+%placeholder="courrier électronique"
+%name="courrier_électronique">
+%\end{lstlisting}

### 2016-10-24 Discussion/mitigation.tex
updated for WWW paper
almost at 13 pages, need to bering it to 9

@@
 	\item Use Mail Libraries\\
-	Using a safe \email library is the preferred way of preventing \ehi vulnerabilities. Using a library that is well tested can remove the burden of input sanitization from the developer. 
-	A list of known secure libraries for each language and framework discussed previously is shown in Table~\ref{tab:maillib}.
+	Using a safe, well tested \email library is the preferred way of preventing \ehi vulnerabilities (removing the burden of input sanitization from the developer). 
+	A list of known secure libraries for each language and framework discussed is shown in Table~\ref{tab:maillib}.
 
@@
 		\centering
+		\normalsize
 		\begin{tabular}{|l|l|}
@@
 	\item Input Validation\\
-	If neither of the two options are feasible, due to reasons such as the website being an in-house production, or due to lack of support infrastructure, developers can choose to perform proper input sanitization.
+	If neither of the two options are feasible (website being an in-house production, or due to lack of support infrastructure), developers can choose to perform proper input sanitization.
 Sanitization should be done keeping in mind RFC5322~\cite{rfc5322}, and care must be taken to ensure that all edge cases are taken into account.

### 2016-10-24 Results/analysis.tex
almost at 13 pages, need to bering it to 9

@@
 	  These represent the scenario where an attacker can inject multiple headers into the \emails.
-We can see that 65.65\% of the received \texttt{bcc} header injected \emails are also susceptible to being injected with additional headers.
+We can see that 54\% of the received \texttt{bcc} header injected \emails are also susceptible to being injected with additional headers.
       % Adam: What is the exact percentage? We should use that rather than an approximate number - DONE.
@@
 	  This represents the total number of successful injections.
-This includes the \ehi with \texttt{bcc} header\,(1), \texttt{To} header injections alone\,(3), and Unique \texttt{x-check} headers found in \texttt{nuser} \emails\,(7).
+This includes the \ehi with \texttt{bcc} header\,(1), \texttt{To} header injections\,(3), and Unique \texttt{x-check} headers found in \texttt{nuser} \emails\,(7).
 A total of \success vulnerabilities were found by our system.

### 2016-10-24 Results/disclosure.tex
updated with new email
updated for WWW paper
added virus email attachments section
almost at 13 pages, need to bering it to 9

@@
 We chose to \email the following mailboxes, following the rules specified in RFC~2142~\cite{rfc2142}:
-% Adam: don't we use \texttt for all the email addresses in the paper? We should use the same thing here - DONE.
 \begin{itemize}
-	\item \texttt{security@domain.com} - Used for Security bulletins or queries.
-	\item \texttt{admin@domain.com} - Used to contact the administrator of a website.
+	\item \texttt{security@domain.com} - Security bulletins or queries.
+	\item \texttt{admin@domain.com} - The administrator of a website.
 	\item \texttt{webmaster@domain.com} - Synonym for administrator, same functionality as admin.
@@
 
-% Adam: sai, is this number up-to-date? 
 Out of the \domains\ vulnerable domains found, only \emailedDefaultmailbox websites had the mailboxes able to receive \emails.
@@
 \centering
+\normalsize
 \begin{tabular}{|c|c|c|}
@@
 
-% Adam: did we get updated notifications? - nope. DONE.
-We received \responses developer responses, confirming \confirmed discovered vulnerabilities. Two of the developers fixed the vulnerability on their website.
+% Adam: did we get updated notifications? - updated. DONE.
+We received \responses developer responses, confirming \confirmed discovered vulnerabilities. Four of the developers fixed the vulnerability on their website.
 % is this done? 1 additional email asking for more information, but no confirmation.

### 2016-10-24 Results/virus_data.tex
almost at 13 pages, need to bering it to 9

@@
 To do this, we passed the \totalattachmentcount attachments we received to VirusTotal~\cite{virustotal} -- an online virus and malware scanner that checks for the presence of malware by running 40+ virus scanners on the uploaded files.
-We found that out of the \totalattachmentcount attachments, \totalvirusemails \emails contained malicious attachments, out of which \totalvirusattachmentcount were found to be from unique domains.
+We found that out of the \totalattachmentcount attachments, \totalvirusemails \emails contained malicious attachments, out of which \totalvirusattachmentcount were from unique domains.
 %It is to be noted that none of these domains were found on the spam analysis we did earlier, indicating that if these could be exploited, we could send emails with malicious attachments to other people using these servers.

### 2016-10-24 System/proof_of_concept.tex
almost at 13 pages, need to bering it to 9

@@
-\subsection{Validation}
 To validate our system, we constructed three sets of web applications in PHP, Python, and Ruby.
@@
 <body>
-<form action="{path-to-back-end}" method="post">
-<input type="text" placeholder="Email" name="email" id="\email"><br>
-<textarea name="msg" rows="20" cols="120"></textarea>
+<form action="script-path" method="post">
+<input type="text" name="email">
+<textarea name="msg"></textarea>
 <input type="submit" value="Email Me!">
-</form>
-</body>
-</html>
+</form></body></html>
 \end{lstlisting}

### 2016-10-24 introduction.tex
almost at 13 pages, need to bering it to 9

@@
 The World Wide Web has single-handedly brought about a change in the way we use computers.
-The ubiquitous nature of the web has made it possible for anyone to access information and services anywhere and on multiple devices such as phones, laptops, personal digital assistants, TVs, and cars.
+The ubiquitous nature of the web has made it possible for anyone to access information and services anywhere and on multiple devices such as phones, laptops, TVs, and cars.
 This access has ushered in an era of web applications which depend on user input.

### 2016-10-24 rel_work.tex
almost at 13 pages, need to bering it to 9

@@
 
-The first documented article dates to over a decade ago; a late 2004 article on phpsecure.info~\cite{Tobozo} accredited to user \lstinline|tobozo@phpsecure.info| describing how this vulnerability existed in the reference implementation of the mail function in PHP, and how it can be exploited.
+The first documented article dates to over a decade ago; a late 2004 article on phpsecure.info~\cite{Tobozo} accredited to user \lstinline|tobozo| describing how this vulnerability existed in the reference implementation of the mail function in PHP, and how it can be exploited.
 Following this, we found other blog posts~\cite{Calin, DK, Injection2, Nicol, Pope}, each describing how to exploit the vulnerability by using newlines to camouflage headers inside user input.
@@
 
-Another blog post written by user Voxel@Night on Vexatious Tendencies~\cite{Tendencies2014}, recounts an actual attack against a WordPress plugin, \texttt{Contact Form}, with a proof of concept\footnotemark.
+Another blog post written by user \lstinline|Voxel@Night|~\cite{Tendencies2014}, recounts an actual attack against a WordPress plugin, \texttt{Contact Form}, with a proof of concept\footnotemark.
 It also showcases the vulnerable code in the plugin that causes this vulnerability to be present.

### 2016-10-24 Background/lang_aff.tex
finally at 13 pages

@@
 \noindent{\textbf{Ruby}}
-From our preliminary testing Ruby's built-in \texttt{Net::SMTP} library also has an \ehi vulnerability. This is not documented on the library's homepage.
+From our preliminary testing Ruby's built-in \texttt{Net::SMTP} library also has an \ehi vulnerability (not documented on the library's homepage).
 %A working code sample of the vulnerability, written in Ruby 2.0.0 (the latest stable version at the time of writing), is shown in Listing~\ref{code:rubyemi}.

### 2016-10-24 Background/php.tex
finally at 13 pages

--- 2016-05-20 Background/php.tex
@@
 $message = 'We need you to reset your password';
-$to = 'xyz@xyz.edu';
-
-// example attack string to be 
-// injected as the value for
+$to = 'xyz@example.com';
+// example attack string injected as for
 // $_REQUEST['email'] => 
-// 's@s.com\nCC:spc@spc.com'
+// 'abc@example.com\nCC:spc@example.com'
 $retValue = mail($to, $subject, $message, "From: $from");
 // E-Mail gets sent to both 
-// xyz@xyz.edu AND spc@spc.com
+// xyz@example.com AND spc@example.com
 \end{lstlisting}

### 2016-10-24 Background/py.tex
finally at 13 pages

--- 2016-05-20 Background/py.tex
@@
 headers = FeedParser.close(f)
-
 # attack string => 
-# 's@s.com\nBCC:spc@spc.com'
-# for form["email"]
-
-# to:s@s.com AND bcc:spc@spc.com 
-# are added to the headers
+# 'abc@example.com\nBCC:spc@example.com'
+# bcc:spc@example.com is added to headers
 print 'To: %s' % headers['to']

### 2016-10-24 Results/analysis.tex
finally at 13 pages

@@
 \subsection{Analysis of the Received \Email Data}
-During our analysis of the received \emails, we found that the \emails that we received belonged to one of three categories:
+During our analysis of the received \emails, we found that the \emails that we received belonged to three categories:
 \begin{enumerate}

### 2016-10-24 System/components.tex
finally at 13 pages

@@
 \begin{itemize}
-	\item Form attributes, such as \texttt{method} and \texttt{action}. These dictate the resulting URL for the HTTP request and the method of the HTTP request.
+	\item Form attributes, such as \texttt{method} and \texttt{action} (URL) for the HTTP request.
 	\item Data about the form input fields, such as their attributes, names, and default values.
-The default values are essential for fields like \colorbox{lightgray}{\lstinline{<input type="hidden">}} as these fields are usually used to check for the submission of forms by bots.
-	\item Presence of the \colorbox{lightgray}{\lstinline{<base>}} element in the HTML, as this affects the final URL to which the form is to be submitted (if the \texttt{action} attribute is a relative URL).
+The default values are essential for fields like {\lstinline{<input type="hidden">}} as these fields are usually used to check for the submission of forms by bots.
+	\item Presence of the {\lstinline{<base>}} element in the HTML, as this affects the final URL to which the form is to be submitted (if the \texttt{action} attribute is a relative URL).
       % Adam: this is not correct, the referrer header won't be used when we make the request. We will set the referrer header when we make the request to URL that the form is on
@@
 
-The \Email Field Checker searches for the words \texttt{e-mail}, \texttt{mail} or \texttt{email} within the form, instead of an explicit HTML5 \email field (e.g.,\ \colorbox{lightgray}{\lstinline{<input type="email">}}).
+The \Email Field Checker searches for the words \texttt{e-mail}, \texttt{mail} or \texttt{email} within the form, instead of an explicit HTML5 \email field (e.g.,\ {\lstinline{<input type="email">}}).
 This is by design, taking into account a common design pattern used by web developers, where they may have a text field with an \texttt{id} or \texttt{name} attribute set to \texttt{email}, instead of an actual \email type attribute, for purposes of backward compatibility with older browsers.
@@
 
-	\item \texttt{nuser(xxxx)@example.com\textbackslash{}r\textbackslash{}n\\bcc:maluser(xxxx)@example.com}
-
-	This payload is added for purposes of cross-platform fuzzing: \texttt{\textbackslash{}r\textbackslash{}n} is the ``Carriage Return - New Line (CRLF)'' used on Windows systems.~\cite{rfc2616}
-
 	\item \texttt{nuser(xxxx)@example.com\textbackslash{}n\\bcc:maluser(xxxx)@example.com\textbackslash{}nx-check:in}
@@
 
+	\item \texttt{nuser(xxxx)@example.com\textbackslash{}r\textbackslash{}n\\bcc:maluser(xxxx)@example.com}
+
 	\item \texttt{nuser(xxxx)@example.com\textbackslash{}r\textbackslash{}n\\bcc:maluser(xxxx)@example.com\textbackslash{}r\textbackslash{}nx-check:in}
 
-	Same as the previous payload, but containing the additional \texttt{\textbackslash{}r} for Windows compatibility.
+Payloads 3 and 4 are added for purposes of cross-platform fuzzing: \texttt{\textbackslash{}r\textbackslash{}n} is the ``Carriage Return - New Line (CRLF)'' used on Windows systems.~\cite{rfc2616}
 
@@
 
+%\begin{table}[tbp]
+%	\centering
+%	\normalsize
+%	\begin{tabular}{|c|c|c|}
+%		\hline
+%		\multicolumn{1}{|c|}{\textbf{Payload}} & \multicolumn{1}{c}{\textbf{Languages covered}} & \multicolumn{1}{|c|}{\textbf{Platforms covered}}\\
+%		\hline
+%		1 & PHP, Java, Ruby, etc. & Unix\\
+%		\hline
+%		2 & PHP, Java, Ruby, etc. & Windows\\
+%		\hline
+%		3 & Python & Unix\\
+%		\hline
+%		4 & Python & Windows\\
+%		\hline
+%	\end{tabular}
+%	\caption[\titlecap{Payload coverage}]{Payload coverage, each payload covers a different platform/language.}
+%	\label{tab:payloadcov}
+%\end{table}
+
 \begin{table}[tbp]
@@
 		\hline
-		\multicolumn{1}{|c|}{\textbf{Payload}} & \multicolumn{1}{c}{\textbf{Languages covered}} & \multicolumn{1}{|c|}{\textbf{Platforms covered}}\\
+		\multicolumn{1}{|c|}{\textbf{Language/Platform}} & \multicolumn{1}{c}{\textbf{Unix}} & \multicolumn{1}{|c|}{\textbf{Windows}}\\
 		\hline
-		1 & PHP, Java, Ruby, etc. & Unix\\
+		\textbf{PHP, Java, Ruby} & 1 & 3\\
 		\hline
-		2 & PHP, Java, Ruby, etc. & Windows\\
-		\hline
-		3 & Python & Unix\\
-		\hline
-		4 & Python & Windows\\
+		\textbf{Python} & 2 & 4\\
 		\hline
@@
 \sloppy
-`Regular \email' refers to the \emails received by account \colorbox{lightgray}{\lstinline{reguser(xxxx)@example.com}} that were sent due to injecting the regular, non-malicious, payload (discussed in Section~\ref{Comp:Fuzzer:nmp}).
+`Regular \email' refers to the \emails received by account {\lstinline{reguser(xxxx)@example.com}} that were sent due to injecting the regular, non-malicious, payload (discussed in Section~\ref{Comp:Fuzzer:nmp}).
 The objective of the analysis on this \email is identify if the input fields that we injected with data appear on the resulting \email, and if so, which fields appear where.

### 2016-10-24 Background/php.tex
Currently at 11 total pages. Major paper shrink. Shrank most fonts on most of the tables, eliminated a lot of superfulious code examples and tables. Also removed most \paragraph and \itemize usage, as they were wasting space.

--- 2016-05-20 Background/php.tex
@@
 $message = 'We need you to reset your password';
-$to = 'xyz@xyz.edu';
-
-// example attack string to be 
-// injected as the value for
-// $_REQUEST['email'] => 
-// 's@s.com\nCC:spc@spc.com'
+$to = 'xyz@example.com';
 $retValue = mail($to, $subject, $message, "From: $from");
-// E-Mail gets sent to both 
-// xyz@xyz.edu AND spc@spc.com
 \end{lstlisting}

### 2016-10-24 Background/py.tex
Currently at 11 total pages. Major paper shrink. Shrank most fonts on most of the tables, eliminated a lot of superfulious code examples and tables. Also removed most \paragraph and \itemize usage, as they were wasting space.

@@
 form = cgi.FieldStorage()
-to = form["email"] # input() exhibits 
-# the same behavior
+to = form["email"]
 msg = """To: """ + to + """\n
@@
 
-f = FeedParser() # Parser.parsestr() 
-# also contains the same vulnerability
+f = FeedParser() 
 f.feed(msg)
 headers = FeedParser.close(f)
-# attack string => 
-# 'abc@example.com\nBCC:spc@example.com'
-# bcc:spc@example.com is added to headers
 print 'To: %s' % headers['to']

### 2016-10-24 Background/ruby.tex
Currently at 11 total pages. Major paper shrink. Shrank most fonts on most of the tables, eliminated a lot of superfulious code examples and tables. Also removed most \paragraph and \itemize usage, as they were wasting space.

@@
 """
-# construct a post request with email set to attack_string
-# attack_string => s@example.com%0abcc:spc@example.com%0aSubject:Hello
 Net::SMTP.start('localhost',1025) do |smtp|
@@
 end
-# Headers get added, and Subject field changes to what we set.
 end

### 2016-10-24 Discussion/ethics.tex
Currently at 11 total pages. Major paper shrink. Shrank most fonts on most of the tables, eliminated a lot of superfulious code examples and tables. Also removed most \paragraph and \itemize usage, as they were wasting space.

@@
 .
-We also had an information website at the IP that we crawled from\footnote{Removed for the sake of anonymity} that described what \ehi was, and contained our contact details in case the developers of the web applications we crawled wanted to contact us.
+We also had an informational website at the IP that we crawled from that described what \ehi was, and contained our contact details in case the developers of the web applications we crawled wanted to contact us.
 We maintained a separate blacklist of domain names that the owners did not want us to crawl, and ensured that our system did not crawl their domains.

### 2016-10-24 Discussion/limits.tex
Currently at 11 total pages. Major paper shrink. Shrank most fonts on most of the tables, eliminated a lot of superfulious code examples and tables. Also removed most \paragraph and \itemize usage, as they were wasting space.

@@
 			\centering
-			\normalsize
+			\scriptsize
 			\begin{tabular}{|p{4cm}|c|c|}
@@
 
-		During the crawl, our system was blacklisted by a few web applications (mostly WordPress ones), and Internet Service Providers (ISPs).
-		To overcome this, we did two things:
-		\begin{enumerate}
-			\item Used an IP range of 60 different IP addresses.
-			\item Used a blacklist of our own to prevent our Fuzzer from fuzzing web application that are known to blacklist automated crawlers.
-However, we could not gather any data about these web applications.
-		\end{enumerate}
+		During the crawl, our system was blacklisted by a few web
+        applications (mostly WordPress ones), and Internet Service
+        Providers (ISPs). To overcome this, we did two things: (1)
+        used an IP range of 60 different IP addresses, and (2) Used a
+        blacklist of our own to prevent our Fuzzer from fuzzing web
+        application that are known to blacklist automated crawlers.
+        However, we could not gather any data about these web
+        applications.
 

### 2016-10-24 Discussion/mitigation.tex
Currently at 11 total pages. Major paper shrink. Shrank most fonts on most of the tables, eliminated a lot of superfulious code examples and tables. Also removed most \paragraph and \itemize usage, as they were wasting space.

@@
 After demonstrating that \ehi vulnerabilities exist on the web at large, we now describe the most common measures that can be taken to prevent the occurrence of this vulnerability, or at least reduce the impact.
-\begin{itemize}
-	\item Use Mail Libraries\\
-	Using a safe, well tested \email library is the preferred way of preventing \ehi vulnerabilities (removing the burden of input sanitization from the developer). 
-	A list of known secure libraries for each language and framework discussed is shown in Table~\ref{tab:maillib}.
+
+Using a safe, well tested \email library is the preferred way of
+preventing \ehi vulnerabilities (removing the burden of input
+sanitization from the developer). A list of known secure libraries for
+each language and framework discussed is shown in
+Table~\ref{tab:maillib}.
 
@@
 		\centering
-		\normalsize
+		\scriptsize
 		\begin{tabular}{|l|l|}
@@
 	\end{table}
-	\item Use a Content Management System (CMS) \\
-	Content management systems such as WordPress and Drupal include libraries and plugins to prevent \ehi.
-Thus, websites built with such CMS' are usually resistant to these attacks.
-However, it is advised to use the correct \email plugin, as not all plugins might be secure.
-	An example of a secure plug-in is included as part of Table~\ref{tab:maillib}.
 
-	\item Input Validation\\
-	If neither of the two options are feasible (website being an in-house production, or due to lack of support infrastructure), developers can choose to perform proper input sanitization.
-Sanitization should be done keeping in mind RFC5322~\cite{rfc5322}, and care must be taken to ensure that all edge cases are taken into account.
+Content management systems such as WordPress and Drupal include
+libraries and plugins to prevent \ehi. Thus, websites built with such
+CMS' are usually resistant to these attacks. However, it is advised to
+use the correct \email plugin, as not all plugins might be secure. An
+example of a secure plug-in is included as part of
+Table~\ref{tab:maillib}.
+
+If neither of the two options are feasible (website being an in-house
+production, or due to lack of support infrastructure), developers can
+choose to perform proper input sanitization. Sanitization should be
+done keeping in mind RFC5322~\cite{rfc5322}, and care must be taken to
+ensure that all edge cases are taken into account.
 
@@
 	%% Test driven development for such validation methods is also encouraged so that we can be reasonably sure of our defense mechanisms.
-\end{itemize}

### 2016-10-24 Results/analysis.tex
Currently at 11 total pages. Major paper shrink. Shrank most fonts on most of the tables, eliminated a lot of superfulious code examples and tables. Also removed most \paragraph and \itemize usage, as they were wasting space.

@@
 During our analysis of the received \emails, we found that the \emails that we received belonged to three categories:
-\begin{enumerate}
-	\item \Emails with the \texttt{bcc} header successfully injected\\
-	  This form of injection was our initial objective, and we found
+
+\Emails with the \texttt{bcc} header successfully injected. This form
+of injection was our initial objective, and we found
 % Adam: Sai, why isn't this number a command? - DONE.
-      \ehibcc such \emails in our received \emails. This validates that the web applications that sent these \emails are vulnerable to \ehi.
+\ehibcc such \emails in our received \emails. This validates that the
+web applications that sent these \emails are vulnerable to \ehi.
 
-	\item \Emails with the \texttt{to} header successfully injected\\
-	We discovered an unintended vulnerability class during our analysis, which we call \texttt{To~header injection}.
-These injections reflect the ability to inject any number of \email addresses into the \texttt{to} field of the SMTP message while being unable to inject any other header into the \emails.
-We found \ehito such \emails in our received \emails.
-We attribute this behavior to inconsistent sanitization by the application.
+\Emails with the \texttt{to} header successfully injected. We
+discovered an unintended vulnerability class during our analysis,
+which we call \texttt{To~header injection}. These injections reflect
+the ability to inject any number of \email addresses into the
+\texttt{to} field of the SMTP message while being unable to inject any
+other header into the \emails. We found \ehito such \emails in our
+received \emails. We attribute this behavior to inconsistent
+sanitization by the application.
     % Adam: I can't understand what this sentence is trying to say - Removed.
 
-	While not allowing us complete control over content of the \emails sent, \texttt{To header injection} makes it possible to append any number of \email addresses, thereby enabling us to leak information or perform DoS (Denial of Service) attacks against the web application.
+While not allowing us complete control over content of the \emails
+sent, \texttt{To header injection} makes it possible to append any
+number of \email addresses, thereby enabling us to leak information or
+perform DoS (Denial of Service) attacks against the web application.
 
-	\item \Emails with the \texttt{x-check} header successfully injected\\
-    The third category of \emails received were \emails with the \texttt{x-check} header injected. As discussed in Section~\ref{analyze:detect_x_check}, 
-    we can differentiate between unsuccessful attempts and successful attempts by injecting the additional header and checking whether headers other than the \texttt{bcc} header can be injected into the generated \email.
-\ehixcheck \emails were received with the \texttt{x-check} header injected.
-\end{enumerate}
+\Emails with the \texttt{x-check} header successfully injected. The
+third category of \emails received were \emails with the
+\texttt{x-check} header injected. As discussed in
+Section~\ref{analyze:detect_x_check}, we can differentiate between
+unsuccessful attempts and successful attempts by injecting the
+additional header and checking whether headers other than the
+\texttt{bcc} header can be injected into the generated \email.
+\ehixcheck \emails were received with the \texttt{x-check} header
+injected.
 
 % Adam: Sai, we need to put the actual numbers in the text. We cannot count on the readers to look at the table (of course, we should use the commands
-We list each category and the number of \emails received by that category in Table~\ref{tab:analysis}. 
-We explain the combination of these header injections (4-7) as follows:
+We list each category and the number of \emails received by that
+category in Table~\ref{tab:analysis}. We explain the combination of
+these header injections (4-7) as follows:
 
@@
 
-\begin{itemize}
-	\item \Email Header Injections with both \texttt{bcc} and \texttt{x-check} headers\\
-	  These represent the scenario where an attacker can inject multiple headers into the \emails.
-We can see that 54\% of the received \texttt{bcc} header injected \emails are also susceptible to being injected with additional headers.
+\Email Header Injections with both \texttt{bcc} and \texttt{x-check}
+headers. These represent the scenario where an attacker can inject
+multiple headers into the \emails. We can see that 54\% of the
+received \texttt{bcc} header injected \emails are also susceptible to
+being injected with additional headers.
       % Adam: What is the exact percentage? We should use that rather than an approximate number - DONE.
 
-	\item Both \texttt{To} header injections and \texttt{x-check} headers \\
-	This combination shows us that in addition to being able to inject into the \texttt{To} fields, we injected additional headers into the \email.
-It is not clear what causes this behavior; however, these can be exploited to achieve the same result as a regular \ehi.
+Both \texttt{To} header injections and \texttt{x-check} headers. This
+combination shows us that in addition to being able to inject into the
+\texttt{To} fields, we injected additional headers into the \email. It
+is not clear what causes this behavior; however, these can be
+exploited to achieve the same result as a regular \ehi.
 
-	\item Total \texttt{x-check} headers and unique \texttt{x-check} headers found in \texttt{nuser} \emails\\
-		We found a total of \ehinuserxcheck \emails in the \texttt{nuser} account.
-Out of these, \ehiuniquenuserxcheck had unique form ids that were \emph{not} already found in the \texttt{maluser} account.
-We attribute these \emails to (probably) being sent by a web application that was built with Python or another language having a similar behavior with respect to ignoring duplicate headers while constructing an \email, thus appending the \texttt{x-check} header and \emph{not} the \texttt{bcc} header.
+Total \texttt{x-check} headers and unique \texttt{x-check} headers
+found in \texttt{nuser} \emails. We found a total of \ehinuserxcheck
+\emails in the \texttt{nuser} account. Out of these,
+\ehiuniquenuserxcheck had unique form ids that were \emph{not} already
+found in the \texttt{maluser} account. We attribute these \emails to
+(probably) being sent by a web application that was built with Python
+or another language having a similar behavior with respect to ignoring
+duplicate headers while constructing an \email, thus appending the
+\texttt{x-check} header and \emph{not} the \texttt{bcc} header.
       % Adam: What is the actual behavior? This is confusing. - Changed. DONE.
 
-	\item Total successful injections\\
-	  This represents the total number of successful injections.
-This includes the \ehi with \texttt{bcc} header\,(1), \texttt{To} header injections\,(3), and Unique \texttt{x-check} headers found in \texttt{nuser} \emails\,(7).
-A total of \success vulnerabilities were found by our system.
+Total successful injections. This represents the total number of
+successful injections. This includes the \ehi with \texttt{bcc}
+header\,(1), \texttt{To} header injections\,(3), and Unique
+\texttt{x-check} headers found in \texttt{nuser} \emails\,(7). A total
+of \success vulnerabilities were found by our system.
 
       % Adam: we need the actual #s here too. These are the core results of our analysis, they need to be in the text. - DONE.
-
-\end{itemize}

### 2016-10-24 Results/disclosure.tex
finally at 13 pages
Currently at 11 total pages. Major paper shrink. Shrank most fonts on most of the tables, eliminated a lot of superfulious code examples and tables. Also removed most \paragraph and \itemize usage, as they were wasting space.

@@
 After we discovered an \ehi vulnerability on a particular website, we attempted to notify the developers of the vulnerable web application, along with a brief description of the vulnerability.
-We chose to \email the following mailboxes, following the rules specified in RFC~2142~\cite{rfc2142}:
-\begin{itemize}
-	\item \texttt{security@domain.com} - Security bulletins or queries.
-	\item \texttt{admin@domain.com} - The administrator of a website.
-	\item \texttt{webmaster@domain.com} - Synonym for administrator, same functionality as admin.
-\end{itemize}
+We chose to \email the following mailboxes, following the rules
+specified in RFC~2142~\cite{rfc2142}: \texttt{security@domain.com},
+\texttt{admin@domain.com}, and \texttt{webmaster@domain.com}
 
-Out of the \domains\ vulnerable domains found, only \emailedDefaultmailbox websites had the mailboxes able to receive \emails.
-For the remaining domains, we used the \texttt{whois}~\cite{whois} data to find the contact details of the owner and then \emailed them.
-The number of emails we sent and the number of developer responses we received is shown in Table~\ref{tab:devresp}.
+Out of the \domains\ vulnerable domains found, only
+\emailedDefaultmailbox websites had the mailboxes able to receive
+\emails. For the remaining domains, we used the
+\texttt{whois}~\cite{whois} data to find the contact details of the
+owner and then \emailed them. We received \responses developer
+responses, confirming \confirmed discovered vulnerabilities. Four of
+the developers fixed the vulnerability on their website.
+% is this done? 1 additional email asking for more information, 1 confirmation that i forwarded to you.
+From our research, it is clear that \ehi is quite widespread as a
+vulnerability, appearing on \successDelta\ of forms that we were able
+to perform automated attacks on. This value acts as a \emph{lower
+  bound} for prevalence of \ehi vulnerability, and can quite easily be
+larger if the attacks were broader, crafted for the individual web
+application, and less automated.
 
-\begin{table}[tbp]
-\centering
-\normalsize
-\begin{tabular}{|c|c|c|}
-	\hline
-	\multicolumn{1}{|p{2cm}}{\centering \textbf{Notified websites}} &
-	\multicolumn{1}{|p{2cm}|}{\centering \textbf{Developer Responses}} &
-	\multicolumn{1}{p{2cm}|}{\centering \textbf{Confirmed discoveries}}\\
-	\hline
-	\domains\ & \responses & \confirmed \\
-	\hline
-\end{tabular}
-	\caption[\titlecap{}]{Responsible disclosure of the discovered vulnerabilities to developers and the number of received responses.}
-	\label{tab:devresp}
-\end{table}
+%% \begin{table}[tbp]
+%% \centering
+%% \scriptsize
+%% \begin{tabular}{|c|c|c|}
+%% 	\hline
+%% 	\multicolumn{1}{|p{2cm}}{\centering \textbf{Notified websites}} &
+%% 	\multicolumn{1}{|p{2cm}|}{\centering \textbf{Developer Responses}} &
+%% 	\multicolumn{1}{p{2cm}|}{\centering \textbf{Confirmed discoveries}}\\
+%% 	\hline
+%% 	\domains\ & \responses & \confirmed \\
+%% 	\hline
+%% \end{tabular}
+%% 	\caption[\titlecap{}]{Responsible disclosure of the discovered vulnerabilities to developers and the number of received responses.}
+%% 	\label{tab:devresp}
+%% \end{table}
 
 % Adam: did we get updated notifications? - updated. DONE.
-We received \responses developer responses, confirming \confirmed discovered vulnerabilities. Four of the developers fixed the vulnerability on their website.
-% is this done? 1 additional email asking for more information, but no confirmation.
-From our research, it is clear that \ehi is quite widespread as a vulnerability, appearing on \successDelta\ of forms that we were able to perform automated attacks on.
-This value acts as a \emph{lower bound} for prevalence of \ehi vulnerability, and can quite easily be larger if the attacks were broader, crafted for the individual web application, and  less automated.

### 2016-10-24 Results/fuzz_result.tex
fixed todos in evaluation
Currently at 11 total pages. Major paper shrink. Shrank most fonts on most of the tables, eliminated a lot of superfulious code examples and tables. Also removed most \paragraph and \itemize usage, as they were wasting space.

@@
-\subsection{Fuzzed Data}
+%\subsection{Fuzzed Data and Received \Emails}
+
 Table~\ref{tab:fuzzed_data} shows the quantity of \emails that we received for the benign and malicious payloads. 
 \input{Results/fuzzed_data}
-\paragraph{\Email received from forms}
-The \emails that we received can be categorized into two categories:
-\begin{enumerate}
-	\item \Emails due to regular payload\\
-	This represents the total number of web applications that sent \emails to us.
-This indicates that we were able to successfully submit the forms on these sites to trigger the web application to send an \email.
 
-	\item \Emails due to malicious payload\\
-    Once we receive an \email from a web application due to the regular payload, we fuzz those forms with the malicious payloads.
-This field represents the total number of unique URLs that are  contain an \ehi vulnerability.
-\end{enumerate}
+\noindent\textbf{\Email received from forms.} The \emails that we
+received can be categorized into two categories. (1) \Emails due to
+regular payload: This represents the total number of web applications
+that sent \emails to us. This indicates that we were able to
+successfully submit the forms on these sites to trigger the web
+application to send an \email. (2) \Emails due to malicious payload:
+Once we receive an \email from a web application due to the regular
+payload, we fuzz those forms with the malicious payloads. This field
+represents the total number of unique URLs that are contain an \ehi
+vulnerability.

### 2016-10-24 System/components.tex
Currently at 11 total pages. Major paper shrink. Shrank most fonts on most of the tables, eliminated a lot of superfulious code examples and tables. Also removed most \paragraph and \itemize usage, as they were wasting space.

@@
 \label{Comp:FP}
-The actual analysis pipeline begins at the Form Parser. This module is responsible for parsing the HTML and retrieving data about the HTML forms on the page, including the following:
-\begin{itemize}
-	\item Form attributes, such as \texttt{method} and \texttt{action} (URL) for the HTTP request.
-	\item Data about the form input fields, such as their attributes, names, and default values.
-The default values are essential for fields like {\lstinline{<input type="hidden">}} as these fields are usually used to check for the submission of forms by bots.
-	\item Presence of the {\lstinline{<base>}} element in the HTML, as this affects the final URL to which the form is to be submitted (if the \texttt{action} attribute is a relative URL).
+The actual analysis pipeline begins at the Form Parser. This module is
+responsible for parsing the HTML and retrieving data about the HTML
+forms on the page, including the following: (1) Form attributes, such
+as \texttt{method} and \texttt{action} (URL) for the HTTP request, (2)
+Data about the form input fields, such as their attributes, names, and
+default values. The default values are essential for fields like
+{\lstinline{<input type="hidden">}} as these fields are usually used
+to check for the submission of forms by bots, and (3) Presence of the {\lstinline{<base>}} element in the HTML, as this affects the final URL to which the form is to be submitted (if the \texttt{action} attribute is a relative URL).
       % Adam: this is not correct, the referrer header won't be used when we make the request. We will set the referrer header when we make the request to URL that the form is on
 	%% \item Headers associated with the page, such as \texttt{referrer}. Once again, these were required to avoid the website from ignoring our system as a bot.
-\end{itemize} 
-The Form Parser stores all this data in our database, so as to allow the system to reconstruct all data necessary for fuzzing the web application.
 
@@
 \label{Comp:EMFR}
-The \Email Form Retriever is the first stage in the Payload Injection module. It has the following functions:
-\begin{itemize}
-	\item Retrieve new forms and ensure no duplication occurs before the fuzzing stage.
-	\item Reconstruct each form, using the stored form data, specifically the input fields and their values.
-	\item Construct the target URL for the \texttt{action} attribute of the form to create an HTTP request to the correct URL for fuzzing. 
-\end{itemize}
+The \Email Form Retriever is the first stage in the Payload Injection
+module. It has the following functions: (1) Retrieve new forms and
+ensure no duplication occurs before the fuzzing stage, (2) reconstruct
+each form, using the stored form data, specifically the input fields
+and their values, and (3) construct the target URL for the
+\texttt{action} attribute of the form to create an HTTP request to the
+correct URL for fuzzing.
 
@@
 The two different types of payloads used for fuzzing are:
-\paragraph{Non-Malicious Payload}
-\label{Comp:Fuzzer:nmp}
+
+\noindent\textbf{Non-Malicious Payload.}
 The regular or non-malicious payload is simply an \email address.
@@
 
-\paragraph{Malicious Payload}
-\label{Comp:Fuzzer:mp}
+\noindent\textbf{Malicious Payload.}
 After receiving an \email from a specific form, we then use the malicious payload to try to exploit an \ehi vulnerability.
@@
 % Adam: If we need to cut things for space, we can cut this next line and the payload coverage table.
-The coverage provided by each payload is shown in Table~\ref{tab:payloadcov}.\\
 
@@
 
-\begin{table}[tbp]
-	\centering
-	\normalsize
-	\begin{tabular}{|c|c|c|}
-		\hline
-		\multicolumn{1}{|c|}{\textbf{Language/Platform}} & \multicolumn{1}{c}{\textbf{Unix}} & \multicolumn{1}{|c|}{\textbf{Windows}}\\
-		\hline
-		\textbf{PHP, Java, Ruby} & 1 & 3\\
-		\hline
-		\textbf{Python} & 2 & 4\\
-		\hline
-	\end{tabular}
-	\caption[\titlecap{Payload coverage}]{Payload coverage, each payload covers a different platform/language.}
-	\label{tab:payloadcov}
-\end{table}
+%% \begin{table}[tbp]
+%% 	\centering
+%% 	\scriptsize
+%% 	\begin{tabular}{|c|c|c|}
+%% 		\hline
+%% 		\multicolumn{1}{|c|}{\textbf{Language/Platform}} & \multicolumn{1}{c}{\textbf{Unix}} & \multicolumn{1}{|c|}{\textbf{Windows}}\\
+%% 		\hline
+%% 		\textbf{PHP, Java, Ruby} & 1 & 3\\
+%% 		\hline
+%% 		\textbf{Python} & 2 & 4\\
+%% 		\hline
+%% 	\end{tabular}
+%% 	\caption[\titlecap{Payload coverage}]{Payload coverage, each payload covers a different platform/language.}
+%% 	\label{tab:payloadcov}
+%% \end{table}
 
@@
 This module works on the \emails received and stored by our Postfix server, and, depending on the user account that received the \email, it performs different functions.
-\paragraph{Analyzing regular e-mail}
+
+\noindent\textbf{Analyzing regular e-mail.}
 \sloppy
-`Regular \email' refers to the \emails received by account {\lstinline{reguser(xxxx)@example.com}} that were sent due to injecting the regular, non-malicious, payload (discussed in Section~\ref{Comp:Fuzzer:nmp}).
+`Regular \email' refers to the \emails received by account {\lstinline{reguser(xxxx)@example.com}} that were sent due to injecting the regular, non-malicious, payload (discussed in Section~\ref{Comp:Fuzzer}).
 The objective of the analysis on this \email is identify if the input fields that we injected with data appear on the resulting \email, and if so, which fields appear where.
@@
 
-\paragraph{Analyzing \email with payloads}
+\noindent\textbf{Analyzing \email with payloads}
 The ``\emails with payloads'' refers to \emails received by either the \colorbox{lightgray}{\lstinline{nuser(xxxx)@example.com}} or \colorbox{lightgray}{\lstinline{maluser(xxxx)@example.com}} accounts.
-These \emails could only be received as a result of injecting the malicious payloads that were discussed in Section~\ref{Comp:Fuzzer:mp}.
+These \emails could only be received as a result of injecting the malicious payloads that were discussed in Section~\ref{Comp:Fuzzer}.
 
-\paragraph{Detecting injected \texttt{bcc} headers}
-As discussed in the payloads section~(\ref{Comp:Fuzzer:mp}), the payloads were crafted such that the \emails received by the \texttt{maluser} account directly indicate the presence of the injected \texttt{bcc} field.
+\noindent\textbf{Detecting injected \texttt{bcc} headers}
+As discussed in the payloads Section~(\ref{Comp:Fuzzer}), the payloads were crafted such that the \emails received by the \texttt{maluser} account directly indicate the presence of the injected \texttt{bcc} field.
 
 \label{analyze:detect_x_check}
-\paragraph{Detecting injected \texttt{x-check} headers}
+\noindent\textbf{Detecting injected \texttt{x-check} headers}
 \Emails not received by the \texttt{maluser} account but by the \texttt{nuser} account constitute a special category of \emails.

### 2016-10-24 System/proof_of_concept.tex
Currently at 11 total pages. Major paper shrink. Shrank most fonts on most of the tables, eliminated a lot of superfulious code examples and tables. Also removed most \paragraph and \itemize usage, as they were wasting space.

@@
 
-The front-end for each of the three applications is shown in Listing~\ref{code:html}.
-The server-side code for PHP, Python, and Ruby is shown in Listings~\ref{code:phpemi}, \ref{code:pyemi}, and \ref{code:rubyemi} respectively.
+The server-side code for PHP is shown in Listings~\ref{code:phpemi},
+while the Python and Ruby code is not shown for space limitations.
 
@@
 
-%% The astute reader might have noticed that in the given example we have used \texttt{\%0a} to separate the headers, while in Section~\ref{Comp:Fuzzer:mp}, we had used \texttt{\textbackslash{}n}.
+%% The astute reader might have noticed that in the given example we have used \texttt{\%0a} to separate the headers, while in Section~\ref{Comp:Fuzzer}, we had used \texttt{\textbackslash{}n}.
 This is due to URL encoding~\cite{rfc1738}, wherein special characters in th URL are `encoded' or `escaped' with their ASCII equivalent.
@@
 
-\begin{lstlisting}[language=HTML,caption={HTML page for showcasing
-      \ehi, a simple front-end for our
-      examples.},label={code:html}, float]
-<!doctype html>
-<html lang="en">
-<head>
-<meta charset="utf-8">
-<meta name="author" content="XYZ">
-<title>Mock Email</title>
-</head>
-<body>
-<form action="script-path" method="post">
-<input type="text" name="email">
-<textarea name="msg"></textarea>
-<input type="submit" value="Email Me!">
-</form></body></html>
-\end{lstlisting}
-\input{Background/ruby}
+%% \begin{lstlisting}[language=HTML,caption={HTML page for showcasing
+%%       \ehi, a simple front-end for our
+%%       examples.},label={code:html}, float]
+%% <!doctype html>
+%% <html lang="en">
+%% <head>
+%% <meta charset="utf-8">
+%% <meta name="author" content="XYZ">
+%% <title>Mock Email</title>
+%% </head>
+%% <body>
+%% <form action="script-path" method="post">
+%% <input type="text" name="email">
+%% <textarea name="msg"></textarea>
+%% <input type="submit" value="Email Me!">
+%% </form></body></html>
+%% \end{lstlisting}
+%\input{Background/ruby}
 

### 2016-10-24 System/sys_arch.tex
Currently at 11 total pages. Major paper shrink. Shrank most fonts on most of the tables, eliminated a lot of superfulious code examples and tables. Also removed most \paragraph and \itemize usage, as they were wasting space.

@@
 The Data Gathering module is responsible for the following activities:
-	\begin{itemize}
-		\item Interface with the Crawler (Section~\ref{Comp:Crawler}) and receive the URLs.
-		\item Parse the HTML for the corresponding URL and store the relevant form data (Section~\ref{Comp:FP}).
-		\item Check for the presence of HTML forms that could allow a user to send/receive \email and store references to these forms (Section~\ref{Comp:EMFC}).
-	\end{itemize}
+(1) Interface with the Crawler (Section~\ref{Comp:Crawler}) and
+receive the URLs, (2) Parse the HTML for the corresponding URL and
+store the relevant form data (Section~\ref{Comp:FP}), and (3) Check
+for the presence of HTML forms that could allow a user to send/receive
+\email and store references to these forms (Section~\ref{Comp:EMFC}).
 
-	The Payload Injection module is responsible for the following activities:
-	\begin{itemize}
-		\item Retrieve the HTML forms that could allow a user to send/receive \email and reconstruct these forms (Section~\ref{Comp:EMFR}).
-		\item Inject these forms with benign data (non-malicious payloads) and generate an HTTP request to the corresponding URL (Section~\ref{Comp:Fuzzer:nmp}).
-		\item Analyze the received \emails, extracting the \email header fields and checking for the presence of the injected payloads (Section~\ref{Comp:EMA}).
-		\item Inject the HTTP requests that sent us \emails with malicious payloads, and generate an HTTP request to the corresponding URL to check if an \ehi vulnerability exists in that web application (Section~\ref{Comp:Fuzzer:mp}).
-	\end{itemize} 
+The Payload Injection module is responsible for the following
+activities: (1) Retrieve the HTML forms that could allow a user to
+send/receive \email and reconstruct these forms
+(Section~\ref{Comp:EMFR}), (2) Inject these forms with benign data
+(non-malicious payloads) and generate an HTTP request to the
+corresponding URL (Section~\ref{Comp:Fuzzer}), (3) Analyze the
+received \emails, extracting the \email header fields and checking for
+the presence of the injected payloads (Section~\ref{Comp:EMA}), and
+(4) Inject the HTTP requests that sent us \emails with malicious
+payloads, and generate an HTTP request to the corresponding URL to
+check if an \ehi vulnerability exists in that web application
+(Section~\ref{Comp:Fuzzer}).
+
 	%% The functionality of each component is discussed further in the `Components' section (Section~\ref{Comp}).

### 2016-10-24 paper.tex
final data update
Edits to abstract
Edits to the introduction
fixed the todos in intro, abstract and background added paragraph and ref to smtp, added ref to command injection changed domains to example.com
Halfway through System Section
Edited through the results section
fixed todos in evaluation
fixed todos in discussion
added the exploitation evidence section
updated with new email
updated for WWW paper
added virus email attachments section
almost at 13 pages, need to bering it to 9
Currently at 11 total pages. Major paper shrink. Shrank most fonts on most of the tables, eliminated a lot of

@@
 
+% Great package for spaces in commands
+\usepackage{xspace}
+
 % for footnotes in tables
@@
 	backgroundcolor=\color{lightgray},
-	basicstyle=\ttfamily,
+	basicstyle=\scriptsize{}\ttfamily,
 	breaklines=true, 
@@
 
+% Important for the layout
+\clubpenalty=10000
+\widowpenalty=10000
+
 \newcommand{\dq}[1]{``{#1}''}
 %% THIS IS THE DATA FOR OUR THESIS, UPDATING HERE WILL UPDATE EVERYWHERE %%
-\newcommand{\urls}{21,675,680}
+\newcommand{\urls}{23,553,796\xspace}
 
-\newcommand{\forms}{6,794,917}
-\newcommand{\formsDelta}{31.35\%}
+\newcommand{\forms}{7,354,425\xspace}
+\newcommand{\formsDelta}{31.22\%\xspace}
 
-\newcommand{\emailforms}{1,132,157}
-\newcommand{\emailformsDelta}{16.66\%}
+\newcommand{\emailforms}{1,228,774\xspace}
+\newcommand{\emailformsDelta}{16.71\%\xspace}
 
-\newcommand{\fuzzed}{934,016}
-\newcommand{\fuzzedDelta}{82.50\%}
+\newcommand{\fuzzed}{1,012,530\xspace}
+\newcommand{\fuzzedDelta}{82.40\%\xspace}
 
-\newcommand{\recd}{52,724}
-\newcommand{\recdDelta}{5.64\%}
+\newcommand{\recd}{74,192\xspace}
+\newcommand{\recdDelta}{7.33\%\xspace}
 
-\newcommand{\malfuzzed}{46,156}
-\newcommand{\malfuzzedDelta}{87.54\%}
+\newcommand{\diffFoundFuzz}{9,682\xspace}
+\newcommand{\malfuzzed}{64,510\xspace}
+\newcommand{\malfuzzedDelta}{86.95\%\xspace}
 
-\newcommand{\success}{496}
-\newcommand{\successDelta}{1.07\%}
+\newcommand{\success}{994\xspace}
+\newcommand{\successDelta}{1.54\%\xspace}
+\newcommand{\successWebsitesDelta}{0.038\%\xspace} % calc domains/total_domains 414/1,085,365
 
-\newcommand{\domains}{222}
-\newcommand{\ips}{292}
+\newcommand{\slowSelenium}{31.58\%\xspace}
+\newcommand{\slowParse}{11.05\%\xspace}
+
+\newcommand{\domains}{414\xspace}
+\newcommand{\ips}{604\xspace}
+
+\newcommand{\emailedDefaultmailbox}{113\xspace}
+\newcommand{\responses}{21\xspace}
+\newcommand{\confirmed}{15\xspace}
+
+\newcommand{\ipsblacklist}{157\xspace}
+\newcommand{\ipsblacklistmulti}{46\xspace}
+
+\newcommand{\ehibcc}{583\xspace}
+\newcommand{\ehixcheck}{493\xspace}
+\newcommand{\ehito}{229\xspace}
+\newcommand{\ehibccxcheck}{310\xspace}
+\newcommand{\ehitoxcheck}{15\xspace}
+\newcommand{\ehinuserxcheck}{239\xspace}
+\newcommand{\ehiuniquenuserxcheck}{182\xspace}
+
 % these refer to unique domains, not unique forms
-\newcommand{\uniqueforms}{1,019,921}
-\newcommand{\uniqueemailforms}{197,570}
+\newcommand{\uniqueforms}{1,085,365\xspace}
+\newcommand{\uniqueemailforms}{198,306\xspace}
+
+\newcommand{\totalattachmentcount}{2,950\xspace}
+\newcommand{\totalvirusattachmentcount}{265\xspace}
+\newcommand{\totalvirusemails}{443\xspace}
+
+\newcommand{\ehi}{E-\nobreak{}mail Header Injection\xspace}
+\renewcommand{\email}{e-\nobreak{}mail\xspace}
+\newcommand{\emails}{\email{}s\xspace}
+\newcommand{\emailed}{\email{}ed\xspace}    
+\newcommand{\Email}{E-\nobreak{}mail\xspace}        
+\newcommand{\Emails}{\Email{}s\xspace}
 
@@
 	%E-Mails}
-    \title{The Prevalence of E-Mail Header Injections on the World
+    \title{Measuring E-Mail Header Injections on the World
     	Wide Web}
@@
     % Note: For CCS submission we need to have it anonymous
+    % The author list will be:
+    % Sai, Pierre-Marie, Giovanni, Ziming, Adam, Gail
 
@@
 
-	\input{exp_setup}
+%	\input{exp_setup}
 
@@
 	\bibliographystyle{abbrv}
-	\bibliography{biblio}  
+	{\scriptsize\bibliography{biblio}}
+%	\bibliography{biblio}  
 	% You must have a proper ".bib" file

### 2016-10-24 paper.tex
brought it down to 10

@@
 \newcommand{\ehi}{E-\nobreak{}mail Header Injection\xspace}
-\renewcommand{\email}{e-\nobreak{}mail\xspace}
 \newcommand{\emails}{\email{}s\xspace}
@@
 
+\makeatletter
+\def\@copyrightspace{\relax}
+\makeatother
 \begin{document}
@@
 
-	\numberofauthors{1} %  in this sample file, there are a *total*
+	\numberofauthors{6} %  in this sample file, there are a *total*
 	% of EIGHT authors. SIX appear on the 'first-page' (for formatting
@@
 		% 1st. author
-		%% \alignauthor
-		%% Sai Prashanth Chandramouli\\
-		%% \affaddr{Arizona State University}\\
-		%% \email{saipc@asu.edu}
-		%% % 2nd. author
-		%% \alignauthor
-		%% Adam Doup\'{e}\titlenote{The secretary disavows
-		%% 	any knowledge of this author's actions.}\\
-		%% \affaddr{Arizona State University}\\
-		%% \email{doupe@asu.edu}
-		%% % 3rd. author
+		\alignauthor
+		Sai Chandramouli\\
+		\affaddr{Arizona State University}\\
+		saipc@asu.edu
+		% 2nd. author
+		\alignauthor
+		Pierre-Marie Bajan\\
+		\affaddr{University of California, Santa Barbara}\\
+		pm.bajan@free.fr
+		\alignauthor
+		Giovanni Vigna\\
+		\affaddr{University of California, Santa Barbara}\\
+		giovanni.vigna@gmail.com
+		\and
+		\alignauthor
+		Ziming Zhao\\
+		\affaddr{Arizona State University}\\
+		Ziming.Zhao@asu.edu
+		\alignauthor
+		Adam Doup\'{e}\\
+		\affaddr{Arizona State University}\\
+		doupe@asu.edu
+		\alignauthor
+		Gail-Joon Ahn\\
+		\affaddr{Arizona State University}\\
+		Gail-Joon.Ahn@asu.edu
+		% 3rd. author
 		%% \alignauthor Lars Th{\o}rv{\"a}ld\titlenote{This author is the
@@
 	% number that will appear in the \additionalauthors section.
-
+	\renewcommand{\email}{e-\nobreak{}mail\xspace}
 	\maketitle

### 2016-10-25 Discussion/mitigation.tex
brought it down to 10
9.75

@@
 Table~\ref{tab:maillib}.
-
-	Using libraries such as PEAR Mail, PHPMailer, Apache Commons E-Mail, Contact Form 7, and Swiftmailer can significantly reduce the occurrence of \ehi vulnerability.
 	\begin{table}[tbp]
@@
 			\hline
-			PHP & {{PEAR Mail\tablefootnote{PEAR Mail Website: https://pear.php.net/package/Mail}, PHPMailer\tablefootnote{PHPMailer Website:\\ https://github.com/PHPMailer/PHPMailer}, Swiftmailer\tablefootnote{Swiftmailer Website: http://swiftmailer.org/}}}\\
+			PHP & {{PEAR Mail\cite{Hagenbuch2016}, PHPMailer\cite{PHPMailer2016}, Swiftmailer\cite{SwiftMailer2016}}}\\
 			\hline
-			Python & SMTPLib with email.header.Header\tablefootnote{instead of using email.parser.Parser to parse the header}\\
+			Python & SMTPLib with email.header.Header\\
 			\hline
-			Java & Apache Commons E-Mail\tablefootnote{Apache Commons E-Mail: https://commons.apache.org/proper/commons-email/}\\
+			Java & Apache Commons E-Mail\cite{ACE2016}\\
 			\hline
-			Ruby & Ruby Mail \textgreater{}= 2.6\tablefootnote{Ruby Mail Website: https://rubygems.org/gems/mail}\\
+			Ruby & Ruby Mail \textgreater{}= 2.6\cite{RubyMailGem2016}\\
 			\hline
-			WordPress & Contact Form 7\tablefootnote{Contact Form 7 Download: https://wordpress.org/plugins/contact-form-7/}\\
+			WordPress & Contact Form 7\cite{CF7}\\
 			\hline

### 2016-10-25 Results/virus_data.tex
9.75

@@
 \subsection{Emails with Malicious Attachments}
-We checked the \emails received by the `reguser' account (which are injected with regular \email addresses and not malicious data) for the presence of attachments that may contain malicious software, which will indicate that the server itself is not benign.
+As additional analysis to find malicious attachments, we checked the \emails received by the `reguser' account (which are injected with regular \email addresses and not malicious data) for the presence of attachments that may contain malicious software, which will indicate that the server itself is not benign.
 

### 2016-10-25 System/components.tex
9.75

@@
 
-The Data Gathering module and Payload Injection modules are composed of smaller components. This section describes the functionality of each of the components.
+The Data Gathering module and Payload Injection modules are composed of smaller components. This section describes the functionality of those components.
 
-\subsubsection{Crawler}
+\subsubsection{Data Gathering}
 \label{Comp:Crawler}
-We used an open-source Apache Nutch based Crawler~\cite{nutch}.
-The Crawler continuously crawls the web.
-The Crawler provides the system with a continuous feed of URLs and the HTML contained in those pages.
-
-\subsubsection{Form Parser}
+We used an open-source Apache Nutch based Crawler~\cite{nutch}. The \texttt{Crawler} provides the system with a continuous feed of URLs and the HTML contained in those pages. 
 \label{Comp:FP}
-The actual analysis pipeline begins at the Form Parser. This module is
-responsible for parsing the HTML and retrieving data about the HTML
+The \texttt{Form Parser} is responsible for parsing the HTML and retrieving data about the HTML
 forms on the page, including the following: (1) Form attributes, such
@@
 to check for the submission of forms by bots, and (3) Presence of the {\lstinline{<base>}} element in the HTML, as this affects the final URL to which the form is to be submitted (if the \texttt{action} attribute is a relative URL).
-      % Adam: this is not correct, the referrer header won't be used when we make the request. We will set the referrer header when we make the request to URL that the form is on
-	%% \item Headers associated with the page, such as \texttt{referrer}. Once again, these were required to avoid the website from ignoring our system as a bot.
 
-\subsubsection{\Email Field Checker}
 \label{Comp:EMFC}
-The \Email Field Checker is the final stage in the Data Gathering module.
-It receives the output of the previous stage---HTML form data---and checks for the presence of \email fields in those forms.
+The \texttt{\Email Field Checker} is the final stage in the Data Gathering module.
+It receives the HTML form data and checks for the presence of \email fields in those forms.
 If any \email fields are found, it stores references to these forms.
@@
 The goal is to see if the web application will send an \email message based on our input.
-The specific format of the \email is \texttt{reguser(xxxx)@example.com}, where \texttt{xxxx} is replaced by an internal id that uniquely maps the payload to the form, and \texttt{example.com} is replaced by our domain.
+The specific format of the \email is \lstinline|reguser(xxxx)@example.com|, where \texttt{xxxx} is replaced by an internal id that uniquely maps the payload to the form, and \texttt{example.com} is replaced by our domain.
 
@@
 
-	This payload is the most minimal payload: it injects a newline character followed by the \texttt{bcc} field.
-
 	\item \texttt{nuser(xxxx)@example.com\textbackslash{}n\\bcc:maluser(xxxx)@example.com\textbackslash{}nx-check:in}
-
-	As discussed previously, the addition of the \texttt{x-check:in} header is to inject Python-based web applications.
 
@@
 
+\end{enumerate}
+Payload 1 is the most minimal payload: it injects a newline character followed by the \texttt{bcc} field.
+Payload 2 contains the additional \texttt{x-check} header to inject Python-based web applications.
 Payloads 3 and 4 are added for purposes of cross-platform fuzzing: \texttt{\textbackslash{}r\textbackslash{}n} is the ``Carriage Return - New Line (CRLF)'' used on Windows systems.~\cite{rfc2616}
 
-\end{enumerate}
 The \texttt{(xxxx)} in each payload is replaced by an internal unique id to create a one-to-one mapping of the payloads to the forms.
@@
 \noindent\textbf{Analyzing \email with payloads}
-The ``\emails with payloads'' refers to \emails received by either the \colorbox{lightgray}{\lstinline{nuser(xxxx)@example.com}} or \colorbox{lightgray}{\lstinline{maluser(xxxx)@example.com}} accounts.
+The ``\emails with payloads'' refers to \emails received by either the {\lstinline{nuser(xxxx)@example.com}} or {\lstinline{maluser(xxxx)@example.com}} accounts.
 These \emails could only be received as a result of injecting the malicious payloads that were discussed in Section~\ref{Comp:Fuzzer}.

### 2016-10-25 introduction.tex
Currently at 11 total pages. Major paper shrink. Shrank most fonts on most of the tables, eliminated a lot of superfulious code examples and tables. Also removed most \paragraph and \itemize usage, as they were wasting space.
9.75

@@
 
-\ehi vulnerabilities are a lesser-known command injection vulnerability\footnote{\ehi can be considered as the \email equivalent of HTTP Header Injection~\cite{wiki:HTTP_headerinjection}}.
+\ehi vulnerabilities are a lesser-known command injection vulnerability.
 We verified that this vulnerability exists in the implementation of the built-in \email functionality in the popular languages PHP, Java, Python, and Ruby.
@@
 The objective of our research is to study the prevalence of this vulnerability on the World Wide Web and identify whether further research is required in this area.
-\\
-
-\noindent{}In summary, we make the following contributions:
+In summary, we make the following contributions:
 \begin{itemize}

### 2016-10-25 paper.tex
9.75
Fixed author list.

--- 2016-10-24 paper.tex
@@
     % The author list will be:
-    % Sai, Pierre-Marie, Giovanni, Ziming, Adam, Gail
+    % Sai, Pierre-Marie, Chris, Giovanni, Ziming, Adam, Gail
 
@@
 		% 1st. author
+		\alignauthor
+		Sai Prashanth Chandramouli$^\dag$, Pierre-Marie Bajan$^\S$, Christopher Kruegel$^\ddag$, Giovanni Vigna$^\ddag$, Ziming Zhao$^\dag$, Adam Doup\'e$^\dag$, and Gail-Joon Ahn$^\dag$\\
+		\affaddr{Arizona State University$^\dag$, IRT SystemX and the Telecom SudParis$^\S$, and University of California, Santa Barbara$^\ddag$}\\
+		\{saipc, zzhao30, doupe, gahn\}@asu.edu$^\dag$,
+        pierre-marie.bajan@irt-systemx.fr$^\S$, \\
+        \{chris, vigna\}@cs.ucsb.edu$^\ddag$
+        }
+		% 2nd. author
 		%% \alignauthor
-		%% Sai Prashanth Chandramouli\\
+
+		%% \affaddr{University of California, Santa Barbara}\\
+		%% pm.bajan@free.fr
+		%% \alignauthor
+		%% \\
+		%% \affaddr{University of California, Santa Barbara}\\
+		%% giovanni.vigna@gmail.com
+		%% \and
+		%% \alignauthor
+		%% \\
 		%% \affaddr{Arizona State University}\\
-		%% \email{saipc@asu.edu}
-		%% % 2nd. author
+		%% Ziming.Zhao@asu.edu
 		%% \alignauthor
-		%% Adam Doup\'{e}\titlenote{The secretary disavows
-		%% 	any knowledge of this author's actions.}\\
+		%% Adam Doup\'{e}\\
 		%% \affaddr{Arizona State University}\\
-		%% \email{doupe@asu.edu}
-		%% % 3rd. author
+		%% doupe@asu.edu
+		%% \alignauthor
+		%% Gail-Joon Ahn\\
+		%% \affaddr{Arizona State University}\\
+		%% Gail-Joon.Ahn@asu.edu
+		% 3rd. author
 		%% \alignauthor Lars Th{\o}rv{\"a}ld\titlenote{This author is the
@@
 		%% \email{cpalmer@prl.com}
-	}
 	% There's nothing stopping you putting the seventh, eighth, etc.

### 2016-10-25 Background/history.tex
LaTeX tricks to get us down to 9.25

--- 2016-05-21 Background/history.tex
@@
 \subsection{History of \ehi}
-
-We found the first \ehi description in a late 2004 article on phpsecure.info~\cite{Tobozo} accredited to user \lstinline|tobozo@phpsecure.info| describing how an \ehi vulnerability existed in the implementation of the \texttt{mail()} function in PHP and how it can be exploited.
+\input{Background/php.tex}
+We found the first \ehi description in a late 2004 article on phpsecure.info~\cite{Tobozo} accredited to user \lstinline|tobozo| describing how an \ehi vulnerability existed in the implementation of the \texttt{mail()} function in PHP and how it can be exploited.
 More recently, a blog post by Damon Kohler~\cite{DK} and an accompanying wiki article~\cite{Injection} describe the attack vector and outline few defense measures for \ehi vulnerabilities.
@@
 
-\input{Background/php.tex}
-
-% TODO: Change all domains to example.com - DONE.
-% TODO: Sai, this is the first time we mention SMTP, need more background and a reference to the RFC.
-
+\input{Background/smtpheaders}
 \begin{sloppypar}
@@
 This will make the e-mail get sent to the e-mail address specified as part of the \texttt{CC} as well.
-\input{Background/smtpheaders}
+
 %\input{Background/history_table}
 \end{sloppypar}
+
+%TODO Adam: added this para abt E-Mail Header Injection history from CVE
+We gathered reported Common Vulnerabilities and Exposures
+(CVE)~\cite{cve} to get an idea of the distribution of
+reported \ehi over time. We found 28 reports of \ehi, shown in
+Table~\ref*{tab:history}.
+From the table, it can be seen that even though many \ehi vulnerabilities were found in the earlier years (2005-07), there have been several recently discovered \ehi vulnerabilities which suggests that it is still a very real threat and is relevant to modern web security.
+
+\input{Background/history_table}

### 2016-10-25 Background/impact.tex
LaTeX tricks to get us down to 9.25

@@
 w3tech, PHP, Java, Python, and Ruby (combined) account for over
-85\%\,\footnotemark{} of the server-side programming languages in
+85\%\, of the server-side programming languages in
 websites measured, and the default implementation of the \email functionality of these languages is vulnerable to \ehi.
-
-\footnotetext{A website may use more than one server-side programming language.}
 

### 2016-10-25 Background/pbm_bg.tex
LaTeX tricks to get us down to 9.25

@@
-\ehi belongs to a broad class of vulnerabilities known as command injection vulnerabilities.
+\ehi belongs to the class of command injection vulnerabilities.
 However, unlike its more popular siblings, SQL injection~\cite{sql1, sql0, sql2}, Cross-Site Scripting~\cite{Injection1, KleinAmit}, or HTTP Header Injection~\cite{sessionride}, relatively little research is available on \ehi vulnerabilities.
 
-As with other vulnerabilities in this class, \ehi is caused due to improper or nonexistent sanitization of user input.
-If the program that constructs \emails from user input fails to check for the presence of \email headers in the user input, a malicious user---using a well-crafted payload---can control the headers set for this particular e-mail.
+As with other command injection vulnerabilities, \ehi is caused by
+improper or nonexistent sanitization of user input. If the program
+constructs \emails from user input and fails to check for the presence
+of \email headers, a malicious user can control the headers of this particular e-mail.
 \ehi vulnerabilities can be leveraged to enable malicious attacks, including, but not limited to, spoofing or phishing.

### 2016-10-25 Discussion/limits.tex
9.75
LaTeX tricks to get us down to 9.25

@@
 				\hline				
-				\centering Parsing \email fields instead of `grep'ing inside form & 707.154 & \slowParse \\								
+				\centering Parsing \email fields instead of `grep'ing& 707.154 & \slowParse \\								
 				\hline
@@
 			\caption[\titlecap{}]{Running times in seconds for crawling, parsing, and detecting presence of \email fields in 1000 random wikipedia pages.}
+            \vspace{-5ex}
 			\label{tab:perf}
@@
 Thus, we have designed the system to exit gracefully on such occasions.
-A side-effect of this is that our system is unable to test web applications with bad HTML markup\,\footnotemark.
-
-        \footnotetext{We do not have any data about whether bad markup indicates an overall lower quality of the web application, and thus cannot comment on whether such websites are more likely to have vulnerabilities.}
+A side-effect of this is that our system is unable to test web applications with bad HTML markup.
 

### 2016-10-25 System/components.tex
LaTeX tricks to get us down to 9.25

@@
 
-The \Email Field Checker searches for the words \texttt{e-mail}, \texttt{mail} or \texttt{email} within the form, instead of an explicit HTML5 \email field (e.g.,\ {\lstinline{<input type="email">}}).
-This is by design, taking into account a common design pattern used by web developers, where they may have a text field with an \texttt{id} or \texttt{name} attribute set to \texttt{email}, instead of an actual \email type attribute, for purposes of backward compatibility with older browsers.
+The \Email Field Checker searches for the words \texttt{e-mail},
+\texttt{mail} or \texttt{email} within the form, instead of an
+explicit HTML5 \email field (e.g.,\ {\lstinline{<input type="email">}}). This is by design, taking into account a common
+design pattern used by web developers, where they may have a text
+field with an \texttt{id} or \texttt{name} attribute set to
+\texttt{email}, instead of an actual \email type attribute, for
+purposes of backward compatibility with older browsers. The output of this stage is stored in the database for persistence and acts as the input to the Payload Injection module.
 
@@
 We discuss this possibility in detail in Section~\ref*{issues:fpr} - Design Issues.
-
-The output of this stage is stored in the database for persistence and acts as the input to the Payload Injection module.
 
@@
 
-We created four different malicious payloads. Each of these payloads is crafted for a particular use case. The four payloads are:
+We created four different malicious payloads. Each of these payloads
+is crafted for a particular use case. The four payloads are:
+(1) nuser(xxxx)@example.com\textbackslash{}n\-bcc:\-maluser\-(xxxx)\-@example.com,
+(2) nuser(xxxx)@\-example.com\textbackslash{}n\-bcc:\-maluser\-(xxxx)\-@example.com\textbackslash{}n\-x-check:in,
+(3) nuser(xxxx)@\-example.com\textbackslash{}r\textbackslash{}n\-bcc:\-maluser(xxxx)\-@example.com,
+and (4) nuser(xxxx)\-@example.com\textbackslash{}r\textbackslash{}n\-bcc:\-maluser(xxxx)\-@example.\-com\textbackslash{}r\textbackslash{}n\-x-check:in.
 
-\begin{enumerate}
-	\item
-	\texttt{nuser(xxxx)@example.com\textbackslash{}n\\bcc:maluser(xxxx)@example.com}
-
-	\item \texttt{nuser(xxxx)@example.com\textbackslash{}n\\bcc:maluser(xxxx)@example.com\textbackslash{}nx-check:in}
-
-	\item \texttt{nuser(xxxx)@example.com\textbackslash{}r\textbackslash{}n\\bcc:maluser(xxxx)@example.com}
-
-	\item \texttt{nuser(xxxx)@example.com\textbackslash{}r\textbackslash{}n\\bcc:maluser(xxxx)@example.com\textbackslash{}r\textbackslash{}nx-check:in}
-
-\end{enumerate}
 Payload 1 is the most minimal payload: it injects a newline character followed by the \texttt{bcc} field.
@@
 \label{analyze:detect_x_check}
-\noindent\textbf{Detecting injected \texttt{x-check} headers}
-\Emails not received by the \texttt{maluser} account but by the \texttt{nuser} account constitute a special category of \emails.
-These \emails could have been generated due to two reasons:
-\begin{enumerate}
-	\item The web application performed some sanitization routines and stripped out the \texttt{bcc} part of the payload, thereby sending \emails only to the \texttt{nuser} account.
-These \emails then act as proof that the vulnerability was not found on the given URL.
-	\item The \texttt{bcc} header can be ignored for other reasons (e.g.,\ Python's default behavior when it encounters duplicate headers).
-In this case, we check if the \email contains the custom header \texttt{x-check}.
-If it does, then this is a successful exploit of the vulnerability.
-\end{enumerate}
+\noindent\textbf{Detecting injected \texttt{x-check} headers} \Emails
+not received by the \texttt{maluser} account but by the \texttt{nuser}
+account constitute a special category of \emails. These \emails could
+have been generated due to two reasons: (1) The web application
+performed some sanitization routines and stripped out the \texttt{bcc}
+part of the payload, thereby sending \emails only to the
+\texttt{nuser} account. These \emails then act as proof that the
+vulnerability was not found on the given URL. (2) The \texttt{bcc}
+header can be ignored for other reasons (e.g.,\ Python's default
+behavior when it encounters duplicate headers). In this case, we check
+if the \email contains the custom header \texttt{x-check}. If it does,
+then this is a successful exploit of the vulnerability.

### 2016-10-25 abstract.tex
updated the abstract with info on malicious content
LaTeX tricks to get us down to 9.25

@@
 	\ehi vulnerability is a class of vulnerability that can occur in web applications that use user input to construct \email messages.
-\ehi is possible when the mailing script fails to check for the presence of \email headers in user input (either form fields or URL parameters).
-We discovered that the vulnerability exists in the reference implementation of the built-in \email functionality in the popular languages PHP, Java, Python, and Ruby.
+\ehi is possible when the script fails to check for the presence of \email headers in user input.
+We discovered that the vulnerability exists in the built-in \email functionality of the popular languages PHP, Java, Python, and Ruby.
 With the proper injection string, this vulnerability can be exploited to allow an attacker to inject additional headers, modify existing headers, and alter the content of the \email.
@@
 Then, to measure if \ehi vulnerabilities are actively being exploited to create a spamming platform, we found evidence that \ipsblacklist IPs that were vulnerable to \ehi are on spamming blacklists.
+We also performed a virus check on the received \emails and found 265 domains to be sending malicious content.
 This work shows that \ehi vulnerabilities are widespread and deserve future research attention.

### 2016-10-25 introduction.tex
LaTeX tricks to get us down to 9.25

@@
 The World Wide Web has single-handedly brought about a change in the way we use computers.
-The ubiquitous nature of the web has made it possible for anyone to access information and services anywhere and on multiple devices such as phones, laptops, TVs, and cars.
+The ubiquitous nature of the web made it possible for anyone to access information and services anywhere and on multiple devices such as phones, laptops, TVs, and cars.
 This access has ushered in an era of web applications which depend on user input.
-While the rapid pace of development has improved the speed of information dissemination, it comes at a cost.
-As users move more and more of their personal and financial information to web applications, attackers are responding by using web application vulnerabilities to access this lucrative data.
+While the rapid pace of development has improved the speed of
+information dissemination, it comes at a cost. As users move more and
+more of their personal and financial information to web applications,
+attackers are responding by using web application vulnerabilities to steal lucrative data.
 
@@
 
-To shed light on this little-studied vulnerability class, we describe \ehi vulnerabilities and measure \ehi vulnerabilities on the web.
-To perform this measurement, we crawled the web, extracted forms with \email fields, and injected them with different payloads to infer the existence of an \ehi vulnerability.
-We then audited received \emails to see if any of the injected data was present.
-This allowed us to classify whether a particular URL was vulnerable to the attack.
-Our automated system works in a black-box manner, without looking at the web application's source code, and only analyzes the \emails we receive based on the injected payloads.
+To shed light on this little-studied vulnerability class, we describe
+\ehi vulnerabilities and measure \ehi vulnerabilities. To perform this
+measurement, we crawled the web, extracted forms with \email fields,
+and injected them with different payloads to infer the existence of an
+\ehi vulnerability. We then audited received \emails to see if any of
+the injected data was present. This allowed us to classify whether a
+particular URL was vulnerable to the attack. Our automated system
+works in a black-box manner, without looking at the web application's
+source code, and only analyzes the paylods of the \emails.
 %TODO Adam: Added a line to make clear that we wanted a quantification before attempting something like a source-code analyzer. This addresses reviewer 690B's concerns.
 
-The objective of our research is to study the prevalence of this vulnerability on the World Wide Web and identify whether further research is required in this area.
 In summary, we make the following contributions:
@@
 \item We develop a black-box approach to detect \ehi vulnerabilities in a web application.
-
+\vspace{-2ex}
 \item We develop an open-source system to crawl the web and automatically detect \ehi vulnerabilities.
-
+\vspace{-2ex}
 \item We use our system to crawl \urls URLs, and we find \success URLs vulnerable to \ehi across \domains domains. 
-
+\vspace{-2ex}
 \end{itemize}

### 2016-10-25 paper.tex
LaTeX tricks to get us down to 9.25

@@
 	showstringspaces=false,
-	upquote=true
+	upquote=true,
+    belowskip=-6ex,
 }
@@
 		Sai Prashanth Chandramouli$^\dag$, Pierre-Marie Bajan$^\S$, Christopher Kruegel$^\ddag$, Giovanni Vigna$^\ddag$, Ziming Zhao$^\dag$, Adam Doup\'e$^\dag$, and Gail-Joon Ahn$^\dag$\\
-		\affaddr{Arizona State University$^\dag$, IRT SystemX and the Telecom SudParis$^\S$, and University of California, Santa Barbara$^\ddag$}\\
+		\affaddr{Arizona State University$^\dag$, IRT SystemX$^\S$, and University of California, Santa Barbara$^\ddag$}\\
 		\{saipc, zzhao30, doupe, gahn\}@asu.edu$^\dag$,
@@
         \{chris, vigna\}@cs.ucsb.edu$^\ddag$
+        \vspace{-5ex}
         }
@@
 	\maketitle
+
 	\input{abstract}

### 2016-10-25 Background/lang_aff.tex
Currently at 11 total pages. Major paper shrink. Shrank most fonts on most of the tables, eliminated a lot of superfulious code examples and tables. Also removed most \paragraph and \itemize usage, as they were wasting space.
Edited paragraphs to cut words without cutting flow.

@@
 \label{languages}
-We now describe the popular programming languages that contain \ehi vulnerabilities in their standard \email libraries.
-This section is not intended as a complete reference of vulnerable functions and methods, but rather as a guide that specifies which parts of the language are vulnerable.
+\noindent{\textbf{PHP}} was the first language found vulnerable to \ehi in its implementation of the \texttt{mail()} function at the time of release of PHP~4.0.
+According to w3techs~\cite{W3techs}, PHP is used by 81.9\% of all websites.
 
-\noindent{\textbf{PHP}} was one of the first languages found to be vulnerable to \ehi in its implementation of the \texttt{mail()} function at the time of release of PHP~4.0.
-The early finding of this vulnerability can be attributed in part to the success and popularity of the language for creating web pages.
-According to w3techs~\cite{W3techs}, PHP is used by 81.9\% of all the websites.
-
-After 13 further iterations of PHP since the 4.0 release (the current version is 7.1), the \texttt{mail()} function is yet to be fixed after 15 years.
-However, it is specified in the PHP documentation~\cite{PHPDocs} that the \texttt{mail()} function does not protect against \ehi.
-A working code sample of the vulnerability, written in PHP~5.6 is shown in  Listing~\ref{code:phpemi}.
+After 13 further iterations of PHP since the 4.0 release (the current
+version is 7.1), the \texttt{mail()} function is yet to be fixed after
+15 years. However, the PHP documentation~\cite{PHPDocs} specifies that the \texttt{mail()} function does not protect against \ehi.
+A working code sample of the vulnerability is shown in  Listing~\ref{code:phpemi}.
 
 \begin{sloppypar}
-\noindent{\textbf{Python}}
-A bug was filed about an \ehi vulnerability in Python's implementation of the \texttt{email.header} library and the header parsing functions allowing newlines in early 2009, which was followed by a partial patch in early 2011.
+A bug was filed about an \ehi vulnerability in Python's implementation of the \texttt{email.header} library and the header parsing functions allowing newlines in early 2009, which was followed by a partial patch in 2011.
 \end{sloppypar}
@@
 Contrary to PHP's behavior of overwriting existing headers, Python only recognizes the first occurrence of a header, and ignores duplicate headers.
-A working code sample of the vulnerability, written in Python 2.7.11, is shown in Listing~\ref{code:pyemi}.
 
-\input{Background/py.tex}
+%A working code sample of the vulnerability, written in Python 2.7.11, is shown in Listing~\ref{code:pyemi}.
 
-\noindent{\textbf{Java}} has a bug report about \ehi filed against its \texttt{JavaMail} API.
+%\input{Background/py.tex}
+
+Java has a bug report about \ehi filed against its \texttt{JavaMail} API.
 A detailed write-up by Alexandre Herzog~\cite{Herzog.2014} contains a proof-of-concept program that exploits the API to inject headers.
@@
 \begin{sloppypar}
-\noindent{\textbf{Ruby}}
-From our preliminary testing Ruby's built-in \texttt{Net::SMTP} library also has an \ehi vulnerability (not documented on the library's homepage).
+From our preliminary testing of Ruby's built-in \texttt{Net::SMTP} library also has an \ehi vulnerability (not documented on the library's homepage).
 %A working code sample of the vulnerability, written in Ruby 2.0.0 (the latest stable version at the time of writing), is shown in Listing~\ref{code:rubyemi}.

### 2016-10-25 Background/lang_aff.tex
need to cut down 13 lines more woohoo

@@
 \begin{sloppypar}
-From our preliminary testing of Ruby's built-in \texttt{Net::SMTP} library also has an \ehi vulnerability (not documented on the library's homepage).
+From our preliminary testing, Ruby's built-in \texttt{Net::SMTP} library also has an \ehi vulnerability (not documented on the library's homepage).
 %A working code sample of the vulnerability, written in Ruby 2.0.0 (the latest stable version at the time of writing), is shown in Listing~\ref{code:rubyemi}.

### 2016-10-25 Results/fuzz_result.tex
need to cut down 13 lines more woohoo

@@
-%\subsection{Fuzzed Data and Received \Emails}
-
-Table~\ref{tab:fuzzed_data} shows the quantity of \emails that we received for the benign and malicious payloads. 
-\input{Results/fuzzed_data}
-
-\noindent\textbf{\Email received from forms.} The \emails that we
-received can be categorized into two categories. (1) \Emails due to
-regular payload: This represents the total number of web applications
-that sent \emails to us. This indicates that we were able to
-successfully submit the forms on these sites to trigger the web
-application to send an \email. (2) \Emails due to malicious payload:
-Once we receive an \email from a web application due to the regular
-payload, we fuzz those forms with the malicious payloads. This field
-represents the total number of unique URLs that are contain an \ehi
-vulnerability.
+%Table~\ref{tab:fuzzed_data} shows the quantity of \emails that we received for the benign and malicious payloads. 
+%\input{Results/fuzzed_data}
+%
+%\noindent\textbf{\Email received from forms.} The \emails that we
+%received can be categorized into two categories. (1) \Emails due to
+%regular payload: This represents the total number of web applications
+%that sent \emails to us. This indicates that we were able to
+%successfully submit the forms on these sites to trigger the web
+%application to send an \email. (2) \Emails due to malicious payload:
+%Once we receive an \email from a web application due to the regular
+%payload, we fuzz those forms with the malicious payloads. This field
+%represents the total number of unique URLs that are contain an \ehi
+%vulnerability.

### 2016-10-25 Results/pre_result.tex
updated for WWW paper
Currently at 11 total pages. Major paper shrink. Shrank most fonts on most of the tables, eliminated a lot of superfulious code examples and tables. Also removed most \paragraph and \itemize usage, as they were wasting space.
need to cut down 13 lines more woohoo

@@
-\subsection{Collected Data}
-
-% TODO: Need to put in a number here, and discuss the high level
-% crawl. - DONE
-
 From our extensive crawl of the web, we were able to gather the data
@@
 found \emailforms\ forms that contained an \email field, from \uniqueemailforms\ unique domains.
+Table~\ref{tab:fuzzed_data} shows the quantity of \emails we received for the benign and malicious payloads. 
+\input{data}
+\input{Results/fuzzed_data}
 
-\input{data}
+\noindent\textbf{\Email received from forms.} The \emails that we
+received can be categorized into two categories. (1) \Emails due to
+regular payload: This represents the total number of web applications
+that sent \emails to us. This indicates that we were able to
+successfully submit the forms on these sites to trigger the web
+application to send an \email. (2) \Emails due to malicious payload:
+Once we receive an \email from a web application due to the regular
+payload, we fuzz those forms with the malicious payloads. This field
+represents the total number of unique URLs that are contain an \ehi
+vulnerability.

### 2016-10-25 System/components.tex
need to cut down 13 lines more woohoo

@@
 as \texttt{method} and \texttt{action} (URL) for the HTTP request, (2)
-Data about the form input fields, such as their attributes, names, and
+Data about form inputs, such as their attributes, names, and
 default values. The default values are essential for fields like
@@
 The \Email Form Retriever is the first stage in the Payload Injection
-module. It has the following functions: (1) Retrieve new forms and
+module. It has the following functions: (1) Retrieve forms and
 ensure no duplication occurs before the fuzzing stage, (2) reconstruct
-each form, using the stored form data, specifically the input fields
-and their values, and (3) construct the target URL for the
-\texttt{action} attribute of the form to create an HTTP request to the
-correct URL for fuzzing.
+each form's input fields
+and values, using the stored form data, and (3) construct the target URL
+to create an HTTP request for fuzzing.
 
@@
 % Adam: we should call these something else but modules. We already have the top two modules, which are composed of components, now we need to split these into something (not components again). - DONE
-The Fuzzer is the only component that interacts directly with the external web applications.
-The Fuzzer is split into smaller parts, each of which is responsible for a particular type of fuzzing.
+The Fuzzer interacts directly with the external web applications.
 The system injects payloads in two stages: the goal is to reduce the total number of HTTP requests the system generates to detect an \ehi vulnerability.
@@
 \noindent\textbf{Non-Malicious Payload.}
-The regular or non-malicious payload is simply an \email address.
+The non-malicious payload is simply an \email address.
 The goal is to see if the web application will send an \email message based on our input.
-The specific format of the \email is \lstinline|reguser(xxxx)@example.com|, where \texttt{xxxx} is replaced by an internal id that uniquely maps the payload to the form, and \texttt{example.com} is replaced by our domain.
+The specific format of the \email is \lstinline|reguser#@example.com|, where \texttt{\#} is replaced by an internal id that uniquely maps the payload to the form, and \texttt{example.com} is replaced by our domain.
 
 \noindent\textbf{Malicious Payload.}
-After receiving an \email from a specific form, we then use the malicious payload to try to exploit an \ehi vulnerability.
-We inject the form parameters with the \texttt{bcc} (blind carbon copy) header.
+After receiving an \email from a specific form, we use the malicious payload to try to exploit an \ehi vulnerability.
+We inject the form fields with the \texttt{bcc} (blind carbon copy) header.
 If the vulnerability is present, this will cause the server to send a copy of the \email to the \email address we added as the \texttt{bcc} field.
@@
 is crafted for a particular use case. The four payloads are:
-(1) nuser(xxxx)@example.com\textbackslash{}n\-bcc:\-maluser\-(xxxx)\-@example.com,
-(2) nuser(xxxx)@\-example.com\textbackslash{}n\-bcc:\-maluser\-(xxxx)\-@example.com\textbackslash{}n\-x-check:in,
-(3) nuser(xxxx)@\-example.com\textbackslash{}r\textbackslash{}n\-bcc:\-maluser(xxxx)\-@example.com,
-and (4) nuser(xxxx)\-@example.com\textbackslash{}r\textbackslash{}n\-bcc:\-maluser(xxxx)\-@example.\-com\textbackslash{}r\textbackslash{}n\-x-check:in.
+(1) nuser\#@example.com\textbackslash{}n\-bcc:\-maluser\-\#\-@example.com,
+(2) nuser\#@\-example.com\textbackslash{}n\-bcc:\-maluser\-\#\-@example.com\textbackslash{}n\-x-check:in,
+(3) nuser\#@\-example.com\textbackslash{}r\textbackslash{}n\-bcc:\-maluser\#\-@example.com,
+and (4) nuser\#\-@example.com\-\textbackslash{}r\textbackslash{}n\-bcc:\-maluser\#\-@example.\-com\textbackslash{}r\textbackslash{}n\-x-check:in.
 
@@
 Payload 2 contains the additional \texttt{x-check} header to inject Python-based web applications.
-Payloads 3 and 4 are added for purposes of cross-platform fuzzing: \texttt{\textbackslash{}r\textbackslash{}n} is the ``Carriage Return - New Line (CRLF)'' used on Windows systems.~\cite{rfc2616}
+Payloads 3 and 4 are added for purposes of cross-platform fuzzing: \texttt{\textbackslash{}r\textbackslash{}n} is the ``Carriage Return - New Line (CRLF)'' used on Windows systems~\cite{rfc2616}.
+The \# are replaced by an internal id, for mapping to the forms.
 
-The \texttt{(xxxx)} in each payload is replaced by an internal unique id to create a one-to-one mapping of the payloads to the forms.
 % Adam: If we need to cut things for space, we can cut this next line and the payload coverage table.
@@
 \sloppy
-`Regular \email' refers to the \emails received by account {\lstinline{reguser(xxxx)@example.com}} that were sent due to injecting the regular, non-malicious, payload (discussed in Section~\ref{Comp:Fuzzer}).
+`Regular \email' refers to the \emails received by account {\lstinline{reguser#@example.com}} that were sent due to injecting the regular, non-malicious, payload (discussed in Section~\ref{Comp:Fuzzer}).
 The objective of the analysis on this \email is identify if the input fields that we injected with data appear on the resulting \email, and if so, which fields appear where.
@@
 \noindent\textbf{Analyzing \email with payloads}
-The ``\emails with payloads'' refers to \emails received by either the {\lstinline{nuser(xxxx)@example.com}} or {\lstinline{maluser(xxxx)@example.com}} accounts.
+The ``\emails with payloads'' refers to \emails received by either the {\lstinline{nuser#@example.com}} or {\lstinline{maluser#@example.com}} accounts.
 These \emails could only be received as a result of injecting the malicious payloads that were discussed in Section~\ref{Comp:Fuzzer}.

### 2016-10-25 introduction.tex
need to cut down 13 lines more woohoo

@@
 
-Many common and well-known web application vulnerabilities, such as SQL Injection and Cross-Site Scripting~\cite{OWASPT10}, are command injection vulnerabilities~\cite{commandinjection}, where malicious user input is used to alter the structure of a command (a SQL query in the case of SQL Injection and JavaScript code in the case of Cross-Site Scripting).
+Many common and well-known web application vulnerabilities, such as SQL Injection and Cross-Site Scripting~\cite{OWASPT10}, are command injection vulnerabilities~\cite{commandinjection}, where malicious user input is used to alter the structure of a command (SQL query and JavaScript code respectively).
 Developers of web applications must use the correct sanitization routine in all paths leading from user input to a command.
@@
 works in a black-box manner, without looking at the web application's
-source code, and only analyzes the paylods of the \emails.
-%TODO Adam: Added a line to make clear that we wanted a quantification before attempting something like a source-code analyzer. This addresses reviewer 690B's concerns.
+source code, and only analyzes the payloads of the \emails.
 

### 2016-10-25 rel_work.tex
Currently at 11 total pages. Major paper shrink. Shrank most fonts on most of the tables, eliminated a lot of superfulious code examples and tables. Also removed most \paragraph and \itemize usage, as they were wasting space.
need to cut down 13 lines more woohoo

@@
 Another blog post written by user \lstinline|Voxel@Night|~\cite{Tendencies2014}, recounts an actual attack against a WordPress plugin, \texttt{Contact Form}, with a proof of concept\footnotemark.
-It also showcases the vulnerable code in the plugin that causes this vulnerability to be present.
+It also showcases the vulnerable code in the plugin that causes the vulnerability.
 However, this article targets just one plugin and does not aim to find the prevalence of said plugin usage.
@@
 Our work, on the other hand discusses the means to mitigate the attack.
-We also describe, in detail, the payloads that can be used and the need for varying the payloads (Section~\ref{Comp:Fuzzer:mp}).
+We also describe, in detail, the payloads that can be used and the need for varying the payloads (Section~\ref{Comp:Fuzzer}).
 

### 2016-10-25 Background/history.tex
got it to 9 pages woooooohooooooooo

@@
 (CVE)~\cite{cve} to get an idea of the distribution of
-reported \ehi over time. We found 28 reports of \ehi, shown in
+reported \ehi over time. We found 28 reports, shown in
 Table~\ref*{tab:history}.
-From the table, it can be seen that even though many \ehi vulnerabilities were found in the earlier years (2005-07), there have been several recently discovered \ehi vulnerabilities which suggests that it is still a very real threat and is relevant to modern web security.
+It can be seen that even though many vulnerabilities were found in the earlier years (2005-07), there have been several recently discovered \ehi vulnerabilities which suggests that it is still a very real and relevant threat to modern web security.
 

### 2016-10-25 Background/impact.tex
got it to 9 pages woooooohooooooooo

@@
     \noindent\textbf{Denial of Service}
-    Denial of service attacks (DoS), can also be caused by exploiting an \ehi vulnerability.
-The ability to send many \emails by injecting one header field can result in overloading the mail server and cause crashes or instability.
+    Denial of service attacks (DoS), can also be caused by exploiting an \ehi vulnerability to send excessive \emails resulting in overloading the mail server and cause crashes or instability.
 

### 2016-10-25 Discussion/limits.tex
got it to 9 pages woooooohooooooooo

@@
 		%TODO Adam: added a table here, and explanation about performance tradeoffs with Selenium and bs4.
-		A comparison of the running times between the different approaches is shown in Table~\ref{tab:perf}.
-Because using Selenium results in a slowdown of \slowSelenium, we chose not to do this for performance reasons.
+		A comparison of the running times between the different approaches is shown in Table~\ref{tab:perf}. We chose not to use Selenium as it results in a slowdown of \slowSelenium.
 
@@
         used an IP range of 60 different IP addresses, and (2) Used a
-        blacklist of our own to prevent our Fuzzer from fuzzing web
-        application that are known to blacklist automated crawlers.
-        However, we could not gather any data about these web
+        blacklist of our own to prevent our Fuzzer from fuzzing
+        applications that are known to blacklist automated crawlers.
+        This restricted us from gathering data about these
         applications.
@@
 
-        Black-box testing is highly beneficial as explained in Section~\ref{sys:appr}, however it also has a drawback in that we cannot verify whether the reported vulnerability exists in the source code or is a feature of the website (e.g., the website allows users to send bulk e-mail, adding as many \texttt{cc} or \texttt{bcc} headers).
+        Black-box testing is highly beneficial as explained in Section~\ref{sys:appr}, however it also has a drawback in that we cannot verify whether the reported vulnerability exists in the source code or is a feature of the website (e.g., the website allows users to send bulk e-mail, adding many \texttt{cc} or \texttt{bcc} headers).
 We must manually notify the developers to get this feedback.

### 2016-10-25 Discussion/mitigation.tex
LaTeX tricks to get us down to 9.25
need to cut down 13 lines more woohoo
got it to 9 pages woooooohooooooooo

@@
 		\end{tabular}
-		\caption[\titlecap{Mail libraries that prevent e-mail header injection}]{Mail libraries that prevent e-mail header injection.}
+		\caption[\titlecap{Mail libraries that prevent e-mail header
+            injection}]{Mail libraries that prevent e-mail header
+          injection.}
+        \vspace{-5ex}        
 		\label{tab:maillib}
@@
 CMS' are usually resistant to these attacks. However, it is advised to
-use the correct \email plugin, as not all plugins might be secure. An
-example of a secure plug-in is included as part of
-Table~\ref{tab:maillib}.
+use the correct \email plugin, as not all plugins might be secure. An example of a secure plugin is shown in Table~\ref{tab:maillib}.
 
-If neither of the two options are feasible (website being an in-house
-production, or due to lack of support infrastructure), developers can
+If neither of the two options are feasible (in-house
+production, or lack of support infrastructure), developers can
 choose to perform proper input sanitization. Sanitization should be
-done keeping in mind RFC5322~\cite{rfc5322}, and care must be taken to
-ensure that all edge cases are taken into account.
+done with RFC5322~\cite{rfc5322} in mind to
+ensure that all edge cases are covered.
 

### 2016-10-25 Results/pipeline.tex
got it to 9 pages woooooohooooooooo

@@
 Table~\ref{tab:pipeline} showcases the data gathered by our pipeline, with the differential changes at each stage of the pipeline.
-
 At each stage of the pipeline, the amount of data decreases, for instance, out of the \urls\ URLs we crawled, only \forms\ forms (\formsDelta) were found.
@@
 
-In our fuzzing attempts, the same behavior is repeated.
-We fuzzed \fuzzed\ forms with the regular payload, which resulted in a total of \recd\ e-mails (\recdDelta).
-After analysis of the received e-mails, we further fuzzed \malfuzzed\ forms, which resulted in \success\ e-mails (\successDelta) which contain the vulnerability across \ips IP Addresses corresponding to \domains domains.
+In our fuzzing attempts, the same behavior is observed.
+We fuzzed \fuzzed\ forms with the regular payload, which resulted in a total of \recd\ e-mails~(\recdDelta).
+After analysis of the received e-mails, we further fuzzed \malfuzzed\ forms, which resulted in \success\ e-mails (\successDelta) which contain the vulnerability across \ips IP addresses from \domains domains.
 
-%TODO Adam: added the reason for the reduction in the numbers, and accept that we do not have the data to quantify about captcha/csrf
 We attribute the difference in the number of forms found to the number of forms fuzzed (a difference of \diffFoundFuzz forms) to the presence of bot-blocking mechanisms on a website (discussed in Section~\ref{limitations}), though we do not know what percentage was caused by the individual bot-blocking mechanisms discussed in Section~\ref{limitations}.

### 2016-10-25 System/components.tex
got it to 9 pages woooooohooooooooo

@@
 \texttt{email}, instead of an actual \email type attribute, for
-purposes of backward compatibility with older browsers. The output of this stage is stored in the database for persistence and acts as the input to the Payload Injection module.
+purposes of backward compatibility with older browsers. The output of this stage is stored in the database and acts as the input to the Payload Injection module.
 
@@
 The \Email Form Retriever is the first stage in the Payload Injection
-module. It has the following functions: (1) Retrieve forms and
-ensure no duplication occurs before the fuzzing stage, (2) reconstruct
+module. It does the following: (1) Retrieve forms and
+remove any duplicates, (2) reconstruct
 each form's input fields
-and values, using the stored form data, and (3) construct the target URL
+and values with the stored form data, and (3) construct the target URL
 to create an HTTP request for fuzzing.

### 2016-10-25 introduction.tex
got it to 9 pages woooooohooooooooo

@@
 the injected data was present. This allowed us to classify whether a
-particular URL was vulnerable to the attack. Our automated system
+URL was vulnerable to the attack. Our automated system
 works in a black-box manner, without looking at the web application's
-source code, and only analyzes the payloads of the \emails.
+source code, and only analyzes the payloads in the \emails.
 

### 2016-10-25 rel_work.tex
got it to 9 pages woooooohooooooooo

@@
 
-In comparison, our work tries to exploit application-level flaws in user input sanitization, which allow us to perform this attack.
+In comparison, our work tries to exploit application-level flaws in user input sanitization, which allow this attack.
 Our work does not intend to exploit the pipelining mechanism, but to exploit the implementation of the mail function in most popular programming languages, which leaves them with no way to distinguish between user supplied headers and headers that are legitimately added by the application.
@@
 Neither does it inform the creators of the plugin to fix the discovered vulnerability.
-\footnotetext{Note that this plugin is used actively on 300,000 websites (according to~\cite{BestWebSoft2016}), but is yet to be fixed.}
-The vulnerability was described briefly by Stuttard and Pinto in their book, ``\emph{The Web Application Hacker's Handbook: Discovering and Exploiting Security Flaws}''~\cite{stuttard2011web}.
+Note that this plugin is used actively on 300,000 websites (according to~\cite{BestWebSoft2016}), but is yet to be fixed.
+The vulnerability was described briefly by Stuttard and Pinto in their book, ``\emph{The Web Application Hacker's Handbook}''~\cite{stuttard2011web}.
 The book, however, does not go into detail on either the attack or the ways to mitigate such an attack.
@@
 
-To the best of our knowledge, no other research has been conducted to determine the prevalence of this vulnerability across the World Wide Web.
-We have managed to, on a large scale, crawl and inject web applications with comparatively benign payloads (such as the BCC header) to identify the existence of this vulnerability without causing any ostensible harm to the website.
-Our injected payloads \emph{do not contain any special characters other than the newline character} and thus cannot cause any unintended consequences.
-Also, because we are only injecting a payload with the \texttt{bcc} header, the underlying mail servers should not be affected by the additional load.
-Our work serves to not only prove the existence of the vulnerability on the World Wide Web but to quantify the prevalence.
+To the best of our knowledge, no other research has been conducted to determine the prevalence of this vulnerability on the World Wide Web.
+We have managed to, on a large scale, crawl and inject web applications with comparatively benign payloads (the \texttt{bcc} header) to identify the existence of this vulnerability without causing any ostensible harm to the website.
+Our injected payloads \emph{do not contain any special characters other than the newline character} and thus can't cause any unintended consequences.
+Also, as we are only injecting the \texttt{bcc} header, the underlying mail servers should not be affected by the additional load.
+Our work serves to not only prove the existence of the vulnerability on the World Wide Web but to quantify its prevalence.

### 2016-10-25 Background/history.tex
final touches to www paper

@@
 (CVE)~\cite{cve} to get an idea of the distribution of
-reported \ehi over time. We found 28 reports, shown in
-Table~\ref*{tab:history}.
-It can be seen that even though many vulnerabilities were found in the earlier years (2005-07), there have been several recently discovered \ehi vulnerabilities which suggests that it is still a very real and relevant threat to modern web security.
+reported \ehi vulnerabilities over time.
+From the 28 reports we found (Table~\ref*{tab:history}), it can be seen that even though many vulnerabilities were found in earlier years (2005-07), there have been recently discovered \ehi vulnerabilities which suggests that it is still a very real and relevant threat to modern web security.
 

### 2016-10-25 Discussion/limits.tex
final touches to www paper

@@
 		Because our system is fully automated, it is also susceptible to being stopped by mechanisms in web applications that prevent automated crawls or form submissions.
-Measures such as CAPTCHA, hidden form fields and CSRF (Cross-site Request Forgery~\cite{csrf}) tokens are often used to detect bots~\cite{captchas3, captchas2}.
+A common reason for our fuzzing attempts to fail is the bot-blocking mechanisms built into the web applications.
+CAPTCHAs (Completely Automated Public Turing test to tell Computers and Humans Apart)~\cite{captchas2} pose a very difficult problem for our system to exploit \ehi, even if it is present.
+		Other measures such as hidden form fields and CSRF (Cross-site Request Forgery~\cite{csrf}) tokens are also often used to detect bots~\cite{captchas3, captchas2}.
 
@@
 
-        Because we search for the words \texttt{e-mail}, \texttt{mail}, or \texttt{email} within the HTML form, if the website does not use English names for its forms our system will not be able to find the presence of an \email field.
+        Because we search for the words \texttt{e-mail}, \texttt{mail}, or \texttt{email} within the HTML form, if the website does not use English names for its forms, our system will not be able to find the presence of an \email field.
 An example is by using the French word for \texttt{e-mail}---courrier {{\'e}}lectronique--- our system is unable to find the presence of the e-mail field.
@@
         E-Mail libraries such as the PHP Extension and Application Repository's (PEAR) mail library provide sanitization for user input.
-While this is not strictly a limitation of our project, it still means that we are not able to inject sites that used these libraries successfully.
+While this is not strictly a limitation of our project, it still means that we are not able to inject sites that used these libraries.
 
-        The parser that we use for HTML parsing---Beautiful Soup---does not parse malformed HTML and throws an exception on encountering malformed HTML.
+        The parser that we use for HTML parsing---Beautiful Soup---does not parse heavily malformed HTML and throws an exception on encountering such HTML.
 Thus, we have designed the system to exit gracefully on such occasions.
-A side-effect of this is that our system is unable to test web applications with bad HTML markup.
+A side-effect of this is that our system is unable to test web applications with very bad HTML markup.
 

### 2016-10-25 Results/analysis.tex
final touches to www paper

@@
 
-\Emails with the \texttt{bcc} header successfully injected. This form
+(1) \Emails with the \texttt{bcc} header successfully injected. This form
 of injection was our initial objective, and we found
@@
 
-\Emails with the \texttt{to} header successfully injected. We
+(2) \Emails with the \texttt{to} header successfully injected. We
 discovered an unintended vulnerability class during our analysis,
@@
 sanitization by the application.
-    % Adam: I can't understand what this sentence is trying to say - Removed.
 
@@
 
-\Emails with the \texttt{x-check} header successfully injected. The
+(3) \Emails with the \texttt{x-check} header successfully injected. The
 third category of \emails received were \emails with the
@@
 \Email Header Injections with both \texttt{bcc} and \texttt{x-check}
-headers. These represent the scenario where an attacker can inject
+headers: These represent the scenario where an attacker can inject
 multiple headers into the \emails. We can see that 54\% of the
@@
 
-Both \texttt{To} header injections and \texttt{x-check} headers. This
+Both \texttt{To} header injections and \texttt{x-check} headers: This
 combination shows us that in addition to being able to inject into the
@@
 Total \texttt{x-check} headers and unique \texttt{x-check} headers
-found in \texttt{nuser} \emails. We found a total of \ehinuserxcheck
+found in \texttt{nuser} \emails: We found a total of \ehinuserxcheck
 \emails in the \texttt{nuser} account. Out of these,
@@
 
-Total successful injections. This represents the total number of
+Total successful injections: This represents the total number of
 successful injections. This includes the \ehi with \texttt{bcc}

### 2016-10-25 Results/virus_data.tex
final touches to www paper

--- 2016-10-24 Results/virus_data.tex
@@
 \subsection{Emails with Malicious Attachments}
-We checked the \emails received by the `reguser' account (which are injected with regular \email addresses and not malicious data) for the presence of attachments that may contain malicious software, which will indicate that the server itself is not benign.
+As additional analysis to find domains on the internet that send out malicious attachments, we checked the \emails received by the `reguser' account (which are injected with regular \email addresses and not malicious data) for the presence of attachments that may contain malicious software, which will indicate that the server itself is not benign.
 
-To do this, we passed the \totalattachmentcount attachments we received to VirusTotal~\cite{virustotal} -- an online virus and malware scanner that checks for the presence of malware by running 40+ virus scanners on the uploaded files.
-We found that out of the \totalattachmentcount attachments, \totalvirusemails \emails contained malicious attachments, out of which \totalvirusattachmentcount were from unique domains.
+To do this, we passed the \totalattachmentcount attachments we received to VirusTotal~\cite{virustotal} -- an online malware scanner that checks for the presence of malware by running 40+ virus scanners on the uploaded files.
+We found that out of the \totalattachmentcount attachments, \totalvirusemails were malicious, out of which \totalvirusattachmentcount were from unique domains.
+This data is just a by-product of our research and could very well lead to future research.
 %It is to be noted that none of these domains were found on the spam analysis we did earlier, indicating that if these could be exploited, we could send emails with malicious attachments to other people using these servers.

### 2016-10-25 System/components.tex
final touches to www paper

@@
 %TODO Adam: made clear that ALL input fields that appear in the email are fuzzed, with examples like name, username, etc.
-To find this, we parse each received \email, and check whether \emph{any} of the fields we injected with data appear as part of either the headers or the body of the \email.
-These could be fields such as name, date of birth, username, etc.
+To find this, we parse each received \email, and check whether \emph{any} of the fields we injected with data appear in either the headers or body of the \email.
+These could be fields such as name, username, age, etc.
 If they do, we add them to the list of fields that can \emph{potentially} result in an \ehi vulnerability for the given \email.

### 2016-10-25 rel_work.tex
final touches to www paper

@@
 % Adam: Sai, can you combine all the \cites at the same line like I did for the others? 
-There are different approaches to finding vulnerabilities in web applications, and most approaches will be either Black-Box testing or White-Box testing.
+There are different approaches to finding vulnerabilities in web applications, and most approaches use either Black-Box testing or White-Box testing.
 Our work is based on the black-box testing approach to finding vulnerabilities on websites, and research has made use of this methodology to find vulnerabilities in web applications~\cite{Beizer:1995:BTT:202699, Huang, kals2006secubat, payet13:ears-in-the-wild, zanero2005automatic}.
@@
 This attack, although trying to achieve a similar result, is distinctly different from ours.
-The paper makes this observation and discusses why it is different from \ehi.
+Terada's paper also makes this observation and discusses why it is different from \ehi.
 
@@
 Note that this plugin is used actively on 300,000 websites (according to~\cite{BestWebSoft2016}), but is yet to be fixed.
-The vulnerability was described briefly by Stuttard and Pinto in their book, ``\emph{The Web Application Hacker's Handbook}''~\cite{stuttard2011web}.
+\ehi vulnerability was described briefly by Stuttard and Pinto in their book, ``\emph{The Web Application Hacker's Handbook}''~\cite{stuttard2011web}.
 The book, however, does not go into detail on either the attack or the ways to mitigate such an attack.
